### 2014-09-23 paper/egpaper_for_review.tex
added paper files

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[square,sort,comma,numbers]{natbib}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------

\subsection{Related Work}

\subsubsection{Multicut}
   \begin{itemize}
   \item Andres \etal~\cite{andres_2011_iccv}
   \item Kappes \etal~\cite{kappes_2011_emmcvpr}
   \item Bagon and Galun~\cite{bagon_2011_arxiv}
   \item Yarkony \etal~\cite{yarkony_2012_eccv}
   \item Beier \etal~\cite{beier_2014_cvpr}
   \end{itemize}

\subsubsection{Fusion Moves}
Move making algorithms, in particular fusion moves, 
have become increasingly popular for energy minimization~\cite{???,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.

\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

By submitting a manuscript to CVPR, the authors guarantee that it has
not been previously published or accepted for publication in substantially
similar form in an archival peer-reviewed forum. Furthermore, no paper which
contains significant overlap with the contributions of this paper is neither
under review at the moment of submission nor will be submitted during the
CVPR 2014 review period to {\bf any of the following}: another conference,
a workshop, or a journal. The authors also attest that they did not submit
substantially similar submissions to CVPR 2014. {\bf Violation of any of
these conditions will lead to rejection.} If you are not sure about the
extent of overlap, you may upload a copy of the paper in question as
supplementary material. Note that a Technical Report (departmental,
arXiv.org, etc.) that is put up without any form of direct peer-review is
{\bf NOT} considered a publication. Likewise, mention of the work under
review in a presentation is {\bf NOT} considered a violation.

If there are papers that may appear to the reviewers
to violate this condition, then it is your responsibility to: (1)~cite
these papers (preserving anonymity as described in Section 1.6 below),
(2)~argue in the body of your paper why your CVPR paper is non-trivially
different from these concurrent submissions, and (3)~include anonymized
versions of those papers in the supplemental material.

\subsection{Paper length}
CVPR papers may be between 6 pages and 8 pages, with a \$100 per page added
fee.  Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.  If you submit 8 for review expect to pay the added page
charges for them.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith, it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Color is valuable, and will be visible to readers of the electronic copy.
However ensure that, when printed on a monochrome printer, no important
information is lost by the conversion to grayscale.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

Please direct any questions to the production editor in charge of these
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
Fax (714) 761-1784.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2014-09-23 paper/egpaper_for_review.tex
delted files
first version of explaining figure

@@
 
+\usepackage{eso-pic}
 \usepackage{cvpr}
@@
 \usepackage{amssymb}
-%\usepackage[square,sort,comma,numbers]{natbib}
+
 % Include other packages here, before hyperref.
+\usepackage{framed}
+\usepackage{caption}
+\usepackage{subcaption}
+%for tikz
+\usepackage{tikz}
+\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
+\usetikzlibrary{arrows,petri,topaths}
+\usepackage{tkz-berge}
+
+\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
 
@@
 \begin{document}
-
+%\GraphInit[vstyle=Normal] 
 %%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for CVPR Proceedings}
+\title{FancyMc Moves \\ Fusion Moves for Multicut Objectives}
 
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+   Multicuts rule.
 \end{abstract}
-
-%%%%%%%%% BODY TEXT
 \section{Introduction}
 
-Please follow the steps outlined below when submitting your manuscript to
-the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against the
-use of sticky tape to attach your artwork to the paper), so all authors
-should read this new version.
+The tale of the multicut
 
@@
 
-\subsection{Language}
-
-All manuscripts must be in English.
-
-\subsection{Dual submission}
-
-By submitting a manuscript to CVPR, the authors guarantee that it has
-not been previously published or accepted for publication in substantially
-similar form in an archival peer-reviewed forum. Furthermore, no paper which
-contains significant overlap with the contributions of this paper is neither
-under review at the moment of submission nor will be submitted during the
-CVPR 2014 review period to {\bf any of the following}: another conference,
-a workshop, or a journal. The authors also attest that they did not submit
-substantially similar submissions to CVPR 2014. {\bf Violation of any of
-these conditions will lead to rejection.} If you are not sure about the
-extent of overlap, you may upload a copy of the paper in question as
-supplementary material. Note that a Technical Report (departmental,
-arXiv.org, etc.) that is put up without any form of direct peer-review is
-{\bf NOT} considered a publication. Likewise, mention of the work under
-review in a presentation is {\bf NOT} considered a violation.
-
-If there are papers that may appear to the reviewers
-to violate this condition, then it is your responsibility to: (1)~cite
-these papers (preserving anonymity as described in Section 1.6 below),
-(2)~argue in the body of your paper why your CVPR paper is non-trivially
-different from these concurrent submissions, and (3)~include anonymized
-versions of those papers in the supplemental material.
-
-\subsection{Paper length}
-CVPR papers may be between 6 pages and 8 pages, with a \$100 per page added
-fee.  Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.  If you submit 8 for review expect to pay the added page
-charges for them.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document using a non-\LaTeX\
-document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
-note that the ruler measurements do not align well with lines in the paper
---- this turns out to be very difficult to do well when the paper contains
-many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
-expect that the approximate location will be adequate.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith, it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors14} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a techreport for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the CVPR70 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
-
-FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.
-
 \begin{figure}[t]
@@
 
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
-
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-\cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
+.
 
 %------------------------------------------------------------------------
-\section{Formatting your paper}
+\section{Name of My Method (Union Fusion Cut)}
 
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
+Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
+Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
+but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
+
+\input{move_graph.tex}
 
 %-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
+\subsection{Proposal Generators}
 
 %-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
+\subsection{Fusion Move Solver}
 
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
+\section{Experiments}
 
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Color is valuable, and will be visible to readers of the electronic copy.
-However ensure that, when printed on a monochrome printer, no important
-information is lost by the conversion to grayscale.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
-
-Please direct any questions to the production editor in charge of these
-proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
-Fax (714) 761-1784.
+\section{Conclusion}
 

### 2014-09-24 src/interfaces/python/examples/test_fancy_stuff.py
minor changes

@@ -10,9 +10,10 @@ numpy.random.seed(42)
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/291000.bmp.h5","gm")
 gm=opengm.loadGm("/home/tbeier/datasets/image-seg/148026.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_102.h5","gm")#(ROTTEN)
-gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-300/gm_knott_3d_078.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-300/gm_knott_3d_078.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-150/gm_knott_3d_038.h5","gm")
-
+gm=opengm.loadGm("/home/tbeier/datasets/modularity-clustering/polbooks.h5","gm")
 #---------------------------------------------------------------
 # Minimize
 #---------------------------------------------------------------
@@ -26,72 +27,147 @@ print gm
 
 
 
-
-
+verbose = True
+useQpbo = True
+useCgc = True
+useWs = True
 
 with opengm.Timer("with new method"):
 
-    infParam = opengm.InfParam(
-        numStopIt=0,
-        numIt=40,
-        generator='qpboBased'
-    )
-    inf=opengm.inference.IntersectionBased(gm, parameter=infParam)
-    # inf.setStartingPoint(arg)
-    # start inference (in this case verbose infernce)
-    visitor=inf.verboseVisitor(printNth=1,multiline=False)
-    inf.infer(visitor)
-    arg = inf.arg()
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False)
+
+    arg = None
+    if useQpbo:
+        infParam = opengm.InfParam(
+            numStopIt=0,
+            numIt=40,
+            generator='qpboBased',
+            fusionParam = fusionParam
+        )
+        inf=opengm.inference.IntersectionBased(gm, parameter=infParam)
+        # inf.setStartingPoint(arg)
+        # start inference (in this case verbose infernce)
+        visitor=inf.verboseVisitor(printNth=1,multiline=False)
+        if verbose:
+            inf.infer(visitor)
+        else:
[…]

### 2014-09-24 exp/patch_W.py
pixel wise mc!

@@ -1,0 +1,167 @@
+import vigra
+import opengm
+import numpy
+import matplotlib.pyplot as plt
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/118035.jpg')
+img = img[::1, ::1,:]
+grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(img), 1.5).squeeze()
+grad -= grad.min()
+grad /= grad.max()
+grad2 = grad.copy()
+grad2[numpy.where(grad2<0.3)] = 0
+
+grad2 = numpy.exp(1.5*grad2)-1.0
+show = True
+
+if show:
+    imgplot = plt.imshow(grad2.swapaxes(0,1))
+    plt.colorbar()
+    plt.show()
+
+expGrad = numpy.exp(-2.1*grad)
+w =  2*expGrad -1.0
+w-=w.min()
+
+if show:
+    imgplot = plt.imshow(w.swapaxes(0,1))
+    plt.colorbar()
+    plt.show()
+
+gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), 10.0*w.astype(numpy.float64), 20, 4,10, 0.01)
+print gm
+
+verbose = True
+useQpbo = False
+useCgc = False
+useWs = False
+
+with opengm.Timer("with new method"):
+
+    fusionParam = opengm.InfParam(fusionSolver = 'hc', planar=False)
+
+    arg = None
+    if useQpbo:
+        infParam = opengm.InfParam(
+            numStopIt=0,
+            numIt=200,
+            generator='qpboBased',
+            fusionParam = fusionParam
+        )
+        inf=opengm.inference.IntersectionBased(gm, parameter=infParam)
+        # inf.setStartingPoint(arg)
+        # start inference (in this case verbose infernce)
+        visitor=inf.verboseVisitor(printNth=1,multiline=False)
+        if verbose:
+            inf.infer(visitor)
+        else:
+            inf.infer()
+        inf.infer()
+        arg = inf.arg()
+
+
+    proposalParam = opengm.InfParam(
+        randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.700000001, ignoreSeed=False),
+        stopWeight=0.0,
+        reduction=0.999,
+        setCutToZero=False
+    )
[…]

### 2014-09-25 exp/non_local_edge_gm.py
nice exp

@@ -1,0 +1,79 @@
+import opengm
+import vigra
+
+
+
+
+class PixelMulticut(object):
+    def __init__(self, shape):
+        self.shape = shape
+
+
+    def addLocalWeights(self, cutCost, cutBenefit=None):
+        """
+            cutCost:
+                these cutCost should ONLY encourage merging.
+                The weight for NOT merging can be 0 if there is
+                *STRONG* indicator for boundary.
+                Therefore cutCost should be >=0.
+                (can be negative, but one should use cut Benefit
+                 for that)
+                In practice cutCost can be
+                a strict positive image as gaussianGradientMagnitude
+                filter applied to the image
+
+            cutBenefit:
+                a sparse image which is zero in every pixel
+                where we do not want a label transition.
+                if the pixel is negative, a label transition
+                will be encouraged.
+                Furthermore, if the pixel is negative, all
+                values of cutCost are overwritten.
+        """
+        pass
+
+    def addNonLocalCannotLinkConstraints(self, constraints):
+        """ add "hard" constraints 
+        (implemented as soft constraints with high energy)
+        to NOT link a pair of pixels.
+            constraints:
+                a |C| x 4 numpy array
+                xa1,ya1,xb1:yb1,
+                xa2,ya2,xb2:yb2
+                ...
+                xa|C|,ya|C|,xb|C|:yb|C|
+        """
+        pass
+
+    def addSlicLikeSeeds(self,seedDist):
+        pass
+
+    def selfAddMaxSizeWeights(self, size, weights):
+        pass
+
+
+    def addPatchWeights(self, image, edgeImage, maxRad=10, minRad=1, stepRad=2):
+        """ add semi local weights within a path which ONLY encourage label transitions
+            image :
+                RGB or feature image to compute "color" difference on
+            edgeImage :
+                image to compute max intervening edge weight on.
+                Via line or shortest path? Lets make a weighted combination
+
+            maxRad :
+                max radius 
+
+            minRad :
+                min radius
+
+            stepRad: 
+                radius increment (maybe non linear is better)
+
+        """
+        pass
+
+
+    def addGlobalWeights(self, image, edgeImage):
+        """ add sparse global edges which ONLY encourage label transitions
+        """
+        pass

### 2014-09-25 exp/patch_W_nice_res.py

@@ -3,15 +3,13 @@ import opengm
 import numpy
 import matplotlib.pyplot as plt
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
-img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/val/69020.jpg')
-img = img[::1, ::1,:]
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/118035.jpg')
+img = vigra.resize(img, (200, 100))
 grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(img), 1.5).squeeze()
 grad -= grad.min()
 grad /= grad.max()
 grad2 = grad.copy()
-t = 0.1
-grad2[numpy.where(grad2<t)] = 0
-grad2[numpy.where(grad2>=t)] = 1
+grad2[numpy.where(grad2<0.3)] = 0
 
 grad2 = numpy.exp(1.5*grad2)-1.0
 show = True
@@ -41,7 +39,6 @@ useWs = False
 with opengm.Timer("with new method"):
 
     fusionParam = opengm.InfParam(fusionSolver = 'cgc', planar=False)
-
     arg = None
     if useQpbo:
         infParam = opengm.InfParam(
@@ -73,7 +70,7 @@ with opengm.Timer("with new method"):
 
     infParam = opengm.InfParam(
         numStopIt=20,
-        numIt=50,
+        numIt=100,
         generator='randomizedHierarchicalClustering',
         proposalParam=proposalParam,
         fusionParam = fusionParam

### 2014-09-25 exp/patch_W_nice_res2.py

@@ -3,15 +3,13 @@ import opengm
 import numpy
 import matplotlib.pyplot as plt
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
-img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/val/69020.jpg')
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/118035.jpg')
 img = img[::1, ::1,:]
 grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(img), 1.5).squeeze()
 grad -= grad.min()
 grad /= grad.max()
 grad2 = grad.copy()
-t = 0.1
-grad2[numpy.where(grad2<t)] = 0
-grad2[numpy.where(grad2>=t)] = 1
+grad2[numpy.where(grad2<0.3)] = 0
 
 grad2 = numpy.exp(1.5*grad2)-1.0
 show = True
@@ -30,7 +28,7 @@ if show:
     plt.colorbar()
     plt.show()
 
-gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), 10.0*w.astype(numpy.float64), 20, 4,10, 0.01)
+gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), 10.0*w.astype(numpy.float64), 40, 5 ,20, 0.01)
 print gm
 
 verbose = True
@@ -41,7 +39,6 @@ useWs = False
 with opengm.Timer("with new method"):
 
     fusionParam = opengm.InfParam(fusionSolver = 'cgc', planar=False)
-
     arg = None
     if useQpbo:
         infParam = opengm.InfParam(
@@ -73,7 +70,7 @@ with opengm.Timer("with new method"):
 
     infParam = opengm.InfParam(
         numStopIt=20,
-        numIt=50,
+        numIt=100,
         generator='randomizedHierarchicalClustering',
         proposalParam=proposalParam,
         fusionParam = fusionParam

### 2014-09-25 exp/play.py

@@ -3,15 +3,13 @@ import opengm
 import numpy
 import matplotlib.pyplot as plt
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
-img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/val/69020.jpg')
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/118035.jpg')
 img = img[::1, ::1,:]
 grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(img), 1.5).squeeze()
 grad -= grad.min()
 grad /= grad.max()
 grad2 = grad.copy()
-t = 0.1
-grad2[numpy.where(grad2<t)] = 0
-grad2[numpy.where(grad2>=t)] = 1
+grad2[numpy.where(grad2<0.3)] = 0
 
 grad2 = numpy.exp(1.5*grad2)-1.0
 show = True
@@ -30,7 +28,7 @@ if show:
     plt.colorbar()
     plt.show()
 
-gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), 10.0*w.astype(numpy.float64), 20, 4,10, 0.01)
+gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), 10.0*w.astype(numpy.float64), 40, 3 ,20, 0.01)
 print gm
 
 verbose = True
@@ -41,7 +39,6 @@ useWs = False
 with opengm.Timer("with new method"):
 
     fusionParam = opengm.InfParam(fusionSolver = 'cgc', planar=False)
-
     arg = None
     if useQpbo:
         infParam = opengm.InfParam(
@@ -73,7 +70,7 @@ with opengm.Timer("with new method"):
 
     infParam = opengm.InfParam(
         numStopIt=20,
-        numIt=50,
+        numIt=100,
         generator='randomizedHierarchicalClustering',
         proposalParam=proposalParam,
         fusionParam = fusionParam

### 2014-09-25 exp/patch_W_nice_res.py
fobar

@@ -11,6 +11,7 @@ grad /= grad.max()
 grad2 = grad.copy()
 grad2[numpy.where(grad2<0.3)] = 0
 
+
 grad2 = numpy.exp(1.5*grad2)-1.0
 show = True
 

### 2014-09-25 exp/foo.py
minor changes

@@ -1,41 +1,58 @@
 import vigra
 import opengm
 import numpy
+import matplotlib
 import matplotlib.pyplot as plt
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/118035.jpg')
-img = img[::1, ::1,:]
+img = vigra.resize(img, (img.shape[0]/3, img.shape[1]/3))[::2,::2,:]
+
+
+
 grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(img), 1.5).squeeze()
-grad -= grad.min()
-grad /= grad.max()
-grad2 = grad.copy()
-grad2[numpy.where(grad2<0.3)] = 0
 
-grad2 = numpy.exp(1.5*grad2)-1.0
-show = True
 
-if show:
-    imgplot = plt.imshow(grad2.swapaxes(0,1))
-    plt.colorbar()
-    plt.show()
 
-expGrad = numpy.exp(-2.1*grad)
-w =  2*expGrad -1.0
-w-=w.min()
+attractive  = numpy.exp(-0.0005*grad)+0.5
+repulsive  = (1.0 - attractive)*10.0
 
-if show:
-    imgplot = plt.imshow(w.swapaxes(0,1))
-    plt.colorbar()
-    plt.show()
 
-gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), 10.0*w.astype(numpy.float64), 40, 3 ,20, 0.01)
+imgplot = plt.imshow(attractive.swapaxes(0,1))
+plt.colorbar()
+plt.show()
+
+imgplot = plt.imshow(1.0*repulsive.swapaxes(0,1))
+plt.colorbar()
+plt.show()
+
+
+
+
+
+gm = opengm.adder.gridPatchAffinityGm(
+    repulsive.astype(numpy.float64), 
+    attractive.astype(numpy.float64), 
+    12, 3 ,3, 0.0, 10000.40
+)
 print gm
 
 verbose = True
-useQpbo = False
+useQpbo = True
 useCgc = False
-useWs = False
+useWs = True
 
+#with opengm.Timer("with cgc"):
+#    infParam = opengm.InfParam(
+#        planar=False,
+#        startFromThreshold=False,
+#        doCutMove = True,
+#        doGlueCutMove = True,
[…]

### 2014-09-25 exp/play.py

@@ -9,7 +9,7 @@ grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(im
 grad -= grad.min()
 grad /= grad.max()
 grad2 = grad.copy()
-grad2[numpy.where(grad2<0.3)] = 0
+#grad2[numpy.where(grad2<0.3)] = 0
 
 grad2 = numpy.exp(1.5*grad2)-1.0
 show = True
@@ -21,14 +21,14 @@ if show:
 
 expGrad = numpy.exp(-2.1*grad)
 w =  2*expGrad -1.0
-w-=w.min()
+w-=w.min()*2.5
 
 if show:
     imgplot = plt.imshow(w.swapaxes(0,1))
     plt.colorbar()
     plt.show()
 
-gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), 10.0*w.astype(numpy.float64), 40, 3 ,20, 0.01)
+gm = opengm.adder.gridPatchAffinityGm(grad2.astype(numpy.float64), w.astype(numpy.float64), 40, 3 ,20, 0.01)
 print gm
 
 verbose = True
@@ -70,7 +70,7 @@ with opengm.Timer("with new method"):
 
     infParam = opengm.InfParam(
         numStopIt=20,
-        numIt=100,
+        numIt=200,
         generator='randomizedHierarchicalClustering',
         proposalParam=proposalParam,
         fusionParam = fusionParam

### 2014-09-26 exp/superpixel.py
foo

@@ -1,0 +1,225 @@
+import vigra
+import opengm
+import numpy
+import matplotlib.pyplot as plt
+#img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/val/145086.jpg')
+imgLab = vigra.colors.transform_RGB2Lab(img)
+
+
+show = 2
+
+# get overseg
+sp,nseg = vigra.analysis.slicSuperpixels(imgLab, 15.0, 20)
+sp = vigra.analysis.labelImage(sp)-1
+gridGraph = vigra.graphs.gridGraph(img.shape[0:2])
+rag = vigra.graphs.regionAdjacencyGraph(gridGraph, sp)
+
+print rag
+if show<=1:
+    rag.show(img)
+    vigra.show()
+
+
+# get edge indicator
+imgLabBig = vigra.resize(imgLab, [imgLab.shape[0]*2-1, imgLab.shape[1]*2-1])
+gradMag = vigra.filters.gaussianGradientMagnitude(imgLabBig,8.0).squeeze()
+
+
+expImg =numpy.exp(gradMag**(0.5))**2
+
+expImg2 =numpy.exp(-0.01*gradMag)
+
+
+wImg = expImg
+
+if show<=2:
+    vigra.imshow(wImg)
+    vigra.show()
+
+
+
+gridGraphEdgeIndicator = vigra.graphs.edgeFeaturesFromInterpolatedImage(gridGraph,
+                                                                  expImg)
+gridGraphEdgeIndicator2 = vigra.graphs.edgeFeaturesFromInterpolatedImage(gridGraph,
+                                                                  expImg2)
+
+
+# accumulate edge indicator
+weights = rag.accumulateEdgeFeatures(gridGraphEdgeIndicator)
+weights2 = rag.accumulateEdgeFeatures(gridGraphEdgeIndicator2)
+weights = weights
+pathFinder = vigra.graphs.ShortestPathPathDijkstra(rag)
+
+assert rag.nodeNum == rag.maxNodeId +1
+
+dists = numpy.zeros([rag.nodeNum,rag.nodeNum], dtype=numpy.float64)
+# run all pairs of shortest path
+for i in range(rag.maxNodeId):
+    #print i
+
+    pathFinder.run(weights,rag.nodeFromId(i))
+    distances = pathFinder.distances()
[…]

### 2014-09-26 src/interfaces/python/examples/test_fancy_stuff.py

@@ -178,8 +178,8 @@ with opengm.Timer("with multicut method"):
     inf=opengm.inference.Multicut(gm, parameter=infParam)
     # inf.setStartingPoint(arg)
     # start inference (in this case verbose infernce)
-    visitor=inf.verboseVisitor(printNth=10)
-    if verbose:
+visitor=inf.verboseVisitor(printNth=10)
+if verbose:
         inf.infer(visitor)
     else:
         inf.infer()

### 2014-09-26 paper/alg_graph.tex
added paper

%!TEX root = egpaper_for_review.tex
\begin{figure}[H]

\tikzfading[name=fade right0,left color=transparent!0, right color=transparent!70]
\tikzfading[name=fade right1,left color=transparent!70, right color=transparent!100]
\tikzstyle{gNode}=[fill=white,draw,solid,font=\sffamily\small]
\tikzstyle{cutNode}=[fill=white,draw,solid,font=\sffamily\small]
\tikzstyle{opBox}=[fill=black,text=white,draw,solid,font=\sffamily\tiny,align=center]
\tikzstyle{label}=[fill=black,text=white,draw,solid,font=\sffamily\tiny]
\tikzstyle{edgeLabelNode}=[ellipse,text=black,solid,font=\sffamily\tiny,align=left,minimum size=0.5cm]
\tikzstyle{aEdge}=[->,node distance=0.5cm]
\begin{tikzpicture}

    \draw node[opBox] (gen) {GENERATOR};
    \draw node[cutNode,right = 1cm of gen] (proposal_cut) {$\bar{P}$};
    \draw node[right of = proposal_cut](dummy){};
    \draw node[cutNode,right of = dummy] (best_cut) {$P$};
    \draw node[opBox,below of = dummy] (intersect) {INTERSECT\\UNCUT};
    \draw node[cutNode,below of = intersect] (int_cut){$\tilde{P}$};
    \draw node[opBox,below of = int_cut] (contract) {CONTRACT\\UNCUT\\EDGES};
    \draw node[gNode,right = 2cm of contract](cgraph)  {$( \tilde{\mathcal{G}}, \tilde{\mathcal{W}})$};
    \draw node[opBox, above of =  cgraph] (multicut) {MULTICUT};
    \draw node[cutNode,above of = multicut] (rcut) {$\bar{P}^{\tilde{\mathcal{G}}}$};
    \draw node[opBox, above of =  rcut] (pback) {PROJECT\\CUT\\BACK};

    \node[draw,dotted,fit=(proposal_cut) (cgraph),inner sep = 3mm,thick, draw=gray,opacity=0.5] {};

    \draw node[gNode,below = of gen](graph)  {$( \mathcal{G}, \mathcal{W})$};
    \path[]
    (gen) edge[aEdge]  node[]{} (proposal_cut)
    (graph) edge[aEdge] (gen)
    (proposal_cut)  edge[aEdge]   (intersect)
    (best_cut)      edge[aEdge]   (intersect)
    (intersect)     edge[aEdge]   (int_cut)
    (int_cut)       edge[aEdge]   (contract) 
    (contract)      edge[aEdge,above]   
        node[edgeLabelNode]{coarse graphs\\with fewer nodes}(cgraph)
    (cgraph)        edge[aEdge]   (multicut)
    (multicut)      edge[aEdge]   (rcut)
    (rcut)          edge[aEdge]   (pback)
    (pback)         edge[aEdge]   (best_cut)
    (graph)         edge[aEdge]   (contract.west)
    (best_cut)      edge[aEdge,dashed,bend angle=90,bend right,draw=gray!30]  
        node[edgeLabelNode]{current best solution\\can influence generator}  (gen)
    ;
\end{tikzpicture}
\caption{
    The proposed algorithm works in the following way:
    Given a graph $\mathcal{G}$, edge weights $\mathcal{W}$ and
    a proposal generator, the current best solution $P$ is iteratively improved.
    A proposal generator generates different versatile
    proposal partitions $\bar{P}$.
    The proposal  $\bar{P}$ is intersected with $P$ which results in
    $\tilde{P}$. Contracting each each which is not 
    cut in $\tilde{P}$ leads to a coarser graph  
    $\tilde{\mathcal{G}} = ( \tilde{\mathcal{V}}, \tilde{\mathcal{E}} )$ 
    with new edge weights $\tilde{\mathcal{W}}$.
    If  $\bar{P}$ and $P$ have a small fraction of cut edges, $\tilde{\mathcal{G}}$ will be small ( $|\tilde{\mathcal{V}}| << |\mathcal{V}|$
    and $|\tilde{\mathcal{E}}| << |\mathcal{E}|$).
    The multicut objective on the smaller graph $\tilde{\mathcal{G}}$ can be optimized magnitudes 
    faster than on $\tilde{\mathcal{G}}$.
    It is guaranteed that the optimal multicut partitioning $\bar{P}^{\tilde{\mathcal{G}}}$ on $\tilde{\mathcal{G}}$ projected 
    back to $\mathcal{G}$ as a lower or equal energy than any of the two input partitions $P$ and $\bar{P}$, 
    therefore we store the result of fusion as new best state $P$ and repeat the procedure.
}\label{fig:algo_graph}
\end{figure}

\begin{figure}[H]

\begin{tikzpicture}
    \tikzstyle{pixel}=[regular polygon,regular polygon sides=4,inner sep=0pt,draw,solid,font=\sffamily\small]

    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
        \draw[red,ultra thick,rounded corners] (0.62,0.65) rectangle (0.78,0.75);
        \draw node[pixel ](100.5,100.5) {BLAAA};
    \end{scope}
\end{tikzpicture}

\end{figure}

### 2014-09-26 exp/foo.py

@@ -3,9 +3,10 @@ import opengm
 import numpy
 import matplotlib
 import matplotlib.pyplot as plt
+
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/118035.jpg')
-img = vigra.resize(img, (img.shape[0]/3, img.shape[1]/3))[::2,::2,:]
+#img = vigra.resize(img, (img.shape[0]/1, img.shape[1]/1))#[::1,::1,:]
 
 
 
@@ -13,8 +14,8 @@ grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(im
 
 
 
-attractive  = numpy.exp(-0.0005*grad)+0.5
-repulsive  = (1.0 - attractive)*10.0
+attractive  = numpy.exp(-0.0005*grad)
+repulsive  = (1.0 - attractive)*5.0
 
 
 imgplot = plt.imshow(attractive.swapaxes(0,1))
@@ -32,13 +33,14 @@ plt.show()
 gm = opengm.adder.gridPatchAffinityGm(
     repulsive.astype(numpy.float64), 
     attractive.astype(numpy.float64), 
-    12, 3 ,3, 0.0, 10000.40
+    20, 5 ,5, 2.2, 2.2
 )
 print gm
 
 verbose = True
 useQpbo = True
-useCgc = False
+useRC = True
+useCgc = True
 useWs = True
 
 #with opengm.Timer("with cgc"):
@@ -55,65 +57,20 @@ useWs = True
 #
 with opengm.Timer("with new method"):
 
-    fusionParam = opengm.InfParam(fusionSolver = 'cgc', planar=False)
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False)
     arg = None
-    if useQpbo:
-        infParam = opengm.InfParam(
-            numStopIt=0,
-            numIt=200,
-            generator='qpboBased',
-            fusionParam = fusionParam
-        )
-        inf=opengm.inference.IntersectionBased(gm, parameter=infParam)
-        # inf.setStartingPoint(arg)
-        # start inference (in this case verbose infernce)
-        visitor=inf.verboseVisitor(printNth=1,multiline=False)
-        if verbose:
-            inf.infer(visitor)
-        else:
-            inf.infer()
-        inf.infer()
[…]

### 2014-09-26 exp/foo.py
minor changs

@@ -15,7 +15,7 @@ grad = vigra.filters.gaussianGradientMagnitude(vigra.colors.transform_Lab2RGB(im
 
 
 attractive  = numpy.exp(-0.0005*grad)
-repulsive  = (1.0 - attractive)*5.0
+repulsive  = (1.0 - attractive)*4.5
 
 
 imgplot = plt.imshow(attractive.swapaxes(0,1))
@@ -33,13 +33,13 @@ plt.show()
 gm = opengm.adder.gridPatchAffinityGm(
     repulsive.astype(numpy.float64), 
     attractive.astype(numpy.float64), 
-    20, 5 ,5, 2.2, 2.2
+    20, 5 ,5, 1.5, 2.2
 )
 print gm
 
 verbose = True
-useQpbo = True
-useRC = True
+useQpbo = False
+useRC = False
 useCgc = True
 useWs = True
 
@@ -64,13 +64,13 @@ with opengm.Timer("with new method"):
     if useWs:
         print "ws"
         proposalParam = opengm.InfParam(
-            randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.100000001,ignoreSeed=False),
+            randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=10.100000001,ignoreSeed=False),
             ignoreNegativeWeights = True,
             seedFraction = 100.0
         )
         infParam = opengm.InfParam(
-            numStopIt=200,
-            numIt=4000,
+            numStopIt=400,
+            numIt=2000,
             generator='randomizedWatershed',
             proposalParam=proposalParam,
             fusionParam = fusionParam
@@ -90,9 +90,10 @@ with opengm.Timer("with new method"):
 
     if useRC:
         proposalParam = opengm.InfParam(
-            randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=3.700000001, ignoreSeed=False),
+            randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.700000001, ignoreSeed=False),
             stopWeight=-100.0,
-            reduction=0.9999,
+            nodeStopNum=200,
+            ignoreNegativeWeights=True,
             setCutToZero=False
         )
         

### 2014-09-26 exp/superpixel.py

@@ -94,70 +94,27 @@ for vi0 in range(rag.maxNodeId):
 
 verbose = True
 useQpbo = False
+useRC = False
 useCgc = True
-useWs = False
+useWs = True
+
 
 with opengm.Timer("with new method"):
 
-    fusionParam = opengm.InfParam(fusionSolver = 'cgc', planar=False)
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False)
     arg = None
-    if useQpbo:
-        infParam = opengm.InfParam(
-            numStopIt=0,
-            numIt=200,
-            generator='qpboBased',
-            fusionParam = fusionParam
-        )
-        inf=opengm.inference.IntersectionBased(gm, parameter=infParam)
-        # inf.setStartingPoint(arg)
-        # start inference (in this case verbose infernce)
-        visitor=inf.verboseVisitor(printNth=1,multiline=False)
-        if verbose:
-            inf.infer(visitor)
-        else:
-            inf.infer()
-        inf.infer()
-        arg = inf.arg()
 
-
-    proposalParam = opengm.InfParam(
-        randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=50.700000001, ignoreSeed=False),
-        stopWeight=0.0,
-        reduction=0.95,
-        setCutToZero=False
-    )
-    
-
-
-    infParam = opengm.InfParam(
-        numStopIt=5,
-        numIt=200,
-        generator='randomizedHierarchicalClustering',
-        proposalParam=proposalParam,
-        fusionParam = fusionParam
-    )
-
-
-    inf=opengm.inference.IntersectionBased(gm, parameter=infParam)
-    if arg is not None:
-        inf.setStartingPoint(arg)
-    # start inference (in this case verbose infernce)
-    visitor=inf.verboseVisitor(printNth=1,multiline=False)
-    if verbose:
-        inf.infer(visitor)
-    else:
-        inf.infer()
-    arg = inf.arg()
 
     if useWs:
         print "ws"
         proposalParam = opengm.InfParam(
-            randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.100000001,ignoreSeed=False),
-            seedFraction = 0.005
+            randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=10.100000001,ignoreSeed=False),
+            ignoreNegativeWeights = True,
+            seedFraction = 5.0
         )
         infParam = opengm.InfParam(
-            numStopIt=20,
-            numIt=10,
[…]

### 2014-09-26 paper/alg_graph.tex
fixed figure

@@
 
-\begin{tikzpicture}
-    \tikzstyle{pixel}=[regular polygon,regular polygon sides=4,inner sep=0pt,draw,solid,font=\sffamily\small]
+%\begin{tikzpicture}
+%    \tikzstyle{pixel}=[regular polygon,regular polygon sides=4,inner sep=0pt,draw,solid,font=\sffamily\small]
+%
+%    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
+%    \begin{scope}[x={(image.south east)},y={(image.north west)}]
+%        \draw[red,ultra thick,rounded corners] (0.62,0.65) rectangle (0.78,0.75);
+%        \draw node[pixel ](100.5,100.5) {BLAAA};
+%    \end{scope}
+%\end{tikzpicture}
 
-    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
-    \begin{scope}[x={(image.south east)},y={(image.north west)}]
-        \draw[red,ultra thick,rounded corners] (0.62,0.65) rectangle (0.78,0.75);
-        \draw node[pixel ](100.5,100.5) {BLAAA};
+% 481 / 321
+\begin{tikzpicture}[scale=1.0]
+
+    \node[anchor=south west,inner sep=0] (image) at (0,0) 
+        {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
+    \begin{scope}[x={(image.south east)},y={(image.north west)},xscale=100/481,yscale=100/321]   
+        %   \draw (0,0) grid (481,321);
+        \draw[gray,xstep=3.21/15, ystep=3.21/15] (0,0) grid (4.81,3.21);
     \end{scope}
+
 \end{tikzpicture}

### 2014-09-26 exp/foo.py

@@ -40,7 +40,7 @@ print gm
 verbose = True
 useQpbo = False
 useRC = False
-useCgc = True
+useCgc = False
 useWs = True
 
 #with opengm.Timer("with cgc"):
@@ -57,7 +57,7 @@ useWs = True
 #
 with opengm.Timer("with new method"):
 
-    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False)
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False, nThreads=-1)
     arg = None
 
 
@@ -66,11 +66,13 @@ with opengm.Timer("with new method"):
         proposalParam = opengm.InfParam(
             randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=10.100000001,ignoreSeed=False),
             ignoreNegativeWeights = True,
-            seedFraction = 100.0
+            seedFromNegativeEdges = True,
+            seedFraction = 300.0
         )
         infParam = opengm.InfParam(
-            numStopIt=400,
-            numIt=2000,
+            numStopIt=100,
+            numIt=100,
+            parallelProposals=8,
             generator='randomizedWatershed',
             proposalParam=proposalParam,
             fusionParam = fusionParam

### 2014-09-26 paper/alg_graph.tex
new figure explaining pixel wise multicut graph

@@
 % 481 / 321
+
+\end{figure}
+
+\newcounter{cX}
+\newcounter{cY}
+
+\newcounter{NPY}
+\setcounter{NPY}{30}
+\tikzstyle{pixel}=[opacity=1.0,thick,draw opacity=1.0, draw=black]
+\tikzstyle{ln}=[opacity=0.6,fill=green,circle,draw, inner sep=0,font=\tiny,minimum size=0.15cm]
+\tikzstyle{gn}=[opacity=0.6,fill=red,circle,draw, inner sep=0,font=\tiny,minimum size=0.15cm]
+\tikzstyle{p}=[opacity=0.6,fill=white,circle,draw, inner sep=0,font=\tiny,minimum size=0.15cm]
+\begin{figure}
+\begin{center}
 \begin{tikzpicture}[scale=1.0]
+    \node[anchor=south west,inner sep=0] (image) at (0,0) 
+        {\includegraphics[width=0.5\textwidth]{images/120093.jpg}};
+    % shift scope to the image 
+    \begin{scope}[x={(image.south east)},y={(image.north west)},xscale=100/481,yscale=100/321]   
+        \draw[gray,xstep=3.21/\theNPY, ystep=3.21/\theNPY] (0,0) grid (4.81,3.21);
+        % scope of the grid
+        \begin{scope}[xscale=3.21/\theNPY,yscale=3.21/\theNPY]
 
-    \node[anchor=south west,inner sep=0] (image) at (0,0) 
-        {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
-    \begin{scope}[x={(image.south east)},y={(image.north west)},xscale=100/481,yscale=100/321]   
-        %   \draw (0,0) grid (481,321);
-        \draw[gray,xstep=3.21/15, ystep=3.21/15] (0,0) grid (4.81,3.21);
+        \foreach \x\y in {22/18, 10/8} { 
+        \setcounter{cX}{\x}
+        \setcounter{cY}{\y}
+        \draw (\thecX+0.5,\thecY+0.5) node[p]  (centerPixel){};
+        \foreach \xx in {-4,0,4} { 
+        \foreach \yy in {-4,0,4} { 
+            \ifthenelse{\NOT 0 = \xx \OR \NOT 0 = \yy}{
+                %\filldraw[green!40!white,pixel] 
+                %(\thecX+\xx,\thecY+\yy) rectangle (\thecX+1+\xx,\thecY+1+\yy);
+                \draw (\thecX+\xx+0.5,\thecY+\yy+0.5) node[gn](nonLocalPixel){};
+                \path[]
+                (centerPixel) edge[bend left=0*\xx*\yy ] (nonLocalPixel)
+                ;
+            }{
+            }
+        }
+        }
+        \foreach \xx/\yy/\pColor in {0/1/blue, 0/-1/blue, 1/0/blue, -1/0/blue} { 
+            \draw (\thecX+\xx+0.5,\thecY+\yy+0.5) node[ln](nonLocalPixel){};
+            (\thecX+\xx,\thecY+\yy) rectangle (\thecX+1+\xx,\thecY+1+\yy);
+        }
+        }
+        % \filldraw[gray,pixel] (\thecX,\thecY) rectangle (\thecX+1,\thecY+1);
+
+        \end{scope}
     \end{scope}
@@
 \end{tikzpicture}
-
+\end{center}
+\caption{
+    Pixel Level Multicut:
+    every pixel (white nodes) is connected
+    to its 4 \emph{local} neighbors (green nodes).
+    Furthermore each pixel is connected to some \emph{non-local} neighbors within a 
+    certain radius (red nodes).
+    The local neighbors are connected with a \emph{positive}
+    edge weight. If the edge indicator (as gradient magnitude)
+    is very high, the local edge weight should be close to zero.
+    The non-local edge weights are \emph{negative} to
+    encourage label transitions.
+    The weight of the non-local edge weights can
+    be the negative value of the maximum gradient magnitude
+    along a line between the red and white node.
+    If there is evidence for a cut between red and white, 
+    the weight should be strongly(?) negative.
+}
 \end{figure}

### 2014-09-29 src/interfaces/python/examples/test_fancy_stuff.py
bla

@@ -7,8 +7,8 @@ numpy.random.seed(42)
 
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/3096.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/175032.bmp.h5","gm")
-#gm=opengm.loadGm("/home/tbeier/datasets/image-seg/291000.bmp.h5","gm")
-gm=opengm.loadGm("/home/tbeier/datasets/image-seg/148026.bmp.h5","gm")
+gm=opengm.loadGm("/home/tbeier/datasets/image-seg/291000.bmp.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/image-seg/148026.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_102.h5","gm")#(ROTTEN)
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-300/gm_knott_3d_078.h5","gm")
@@ -27,76 +27,39 @@ print gm
 
 
 
+
+
 verbose = True
-useQpbo = False
-useCgc = True
+useQpbo = True
+useRC = False
+useCgc = False
 useWs = False
+
+
 
 with opengm.Timer("with new method"):
 
-    fusionParam = opengm.InfParam(fusionSolver = 'cgc', planar=True)
-
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False)
+    randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.500000001,ignoreSeed=False)
+    parallelProposals = 8
     arg = None
-    if useQpbo:
-        infParam = opengm.InfParam(
-            numStopIt=0,
-            numIt=40,
-            generator='qpboBased',
-            fusionParam = fusionParam
-        )
-        inf=opengm.inference.IntersectionBased(gm, parameter=infParam)
-        # inf.setStartingPoint(arg)
-        # start inference (in this case verbose infernce)
-        visitor=inf.verboseVisitor(printNth=1,multiline=False)
-        if verbose:
-            inf.infer(visitor)
-        else:
-            inf.infer()
-        inf.infer()
-        arg = inf.arg()
 
-
-    proposalParam = opengm.InfParam(
[…]

### 2014-09-29 paper/egpaper_for_review.tex
minor changes
fixed figure
cleanup

@@
 % Include other packages here, before hyperref.
-\usepackage{framed}
+\usepackage{my_macros}
+\usepackage{paralist}
+%\usepackage{framed}
 \usepackage{caption}
@@
 %for tikz
-\usepackage{tikz}
+\usepackage{tikz,pgfplots}
 \usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
 \usetikzlibrary{arrows,petri,topaths}
+\usetikzlibrary{positioning,fit,calc}
+\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
 \usepackage{tkz-berge}
-
+\DeclareMathOperator*{\argmin}{arg\,min}
 \definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
@@
 \begin{document}
-%\GraphInit[vstyle=Normal] 
 %%%%%%%%% TITLE
+\include{my_macros.tex}
 \title{FancyMc Moves \\ Fusion Moves for Multicut Objectives}
@@
 
-\subsubsection{Multicut}
+\subsubsection{Multicut Objective}
+
+The multicut / correlation clustering objective 
+can be formulated in different ways.
+
+\paragraph{Edge Indicator Variables:}
+\begin{center}
+    \begin{eqnarray}
+        y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
+        s.t.:& & y \in \textit{Multicut Polytope} \nonumber
+    \end{eqnarray}
+\end{center}
+
+\paragraph{Fully Connected Graph:}
+\begin{center}
+    \begin{eqnarray}
+        y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
+        s.t.: &  & x_{ij} + x_{jk} < x_{i,k} \quad \forall i, j, k   \nonumber
+    \end{eqnarray}
+\end{center}
+
+\paragraph{Node Coloring:}
+\begin{center}
+    \begin{eqnarray}
+        l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
+        y_{ij}^* &=& [l_{u} \neq l_{v}]  
+    \end{eqnarray}
+\end{center}
+
+The multicut objective has been used for
+\begin{inparaenum}[(i)]
+    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
+    \item with optional long range repulsive edges~\cite{yarknoy???}.
+    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
+    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv}
+    \item and to cluster fully connected graphs~\cite{???}.
+\end{inparaenum}
+
+\subsubsection{Solver for the Multicut Objective}
    \begin{itemize}
-   \item Andres \etal~\cite{andres_2011_iccv}
-   \item Kappes \etal~\cite{kappes_2011_emmcvpr}
-   \item Bagon and Galun~\cite{bagon_2011_arxiv}
-   \item Yarkony \etal~\cite{yarkony_2012_eccv}
-   \item Beier \etal~\cite{beier_2014_cvpr}
+   \item Multicut~\cite{kappes_2011_emmcvpr}
+   \item Expand and Explorer~\cite{bagon_2011_arxiv}
+   \item Fast Planar CC~\cite{yarkony_2012_eccv}
+   \item Break and Conquer \cite{alush_2013_simbad}.
+   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
    \end{itemize}
@@
 
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-.
-
 %------------------------------------------------------------------------
@@
 Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
-Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
+Good approximate solvers for planar graphs exist \cite{beifiger_2014_cvpr,yarkony_2012_eccv} 
 but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
 
-\input{move_graph.tex}
+\input{inputs/fig_alg_graph.tex}
+
+\input{inputs/fig_move_graph.tex}
 
@@
 \subsection{Proposal Generators}
+
+\input{inputs/fig_hc.tex}
 
@@
 \section{Experiments}
+\subsection{Benchmark Models}
+\subsection{Pixel-wise Multicuts}
+\input{inputs/fig_pixel_mc.tex}
 

### 2014-09-29 paper/inputs/fig_alg_graph.tex
cleanup

--- 2014-09-26 paper/alg_graph.tex
@@
-%!TEX root = egpaper_for_review.tex
+%!TEX root = ../egpaper_for_review.tex
 \begin{figure}[H]
@@
 \end{figure}
-
-\begin{figure}[H]
-
-\begin{tikzpicture}
-    \tikzstyle{pixel}=[regular polygon,regular polygon sides=4,inner sep=0pt,draw,solid,font=\sffamily\small]
-
-    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
-    \begin{scope}[x={(image.south east)},y={(image.north west)}]
-        \draw[red,ultra thick,rounded corners] (0.62,0.65) rectangle (0.78,0.75);
-        \draw node[pixel ](100.5,100.5) {BLAAA};
-    \end{scope}
-\end{tikzpicture}
-
-\end{figure}

### 2014-09-29 paper/inputs/fig_hc.tex
cleanup

%!TEX root = ../egpaper_for_review.tex

\tikzstyle{nS}=[circle,minimum size = 0.3cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=red, font=\small,align=left]
\tikzstyle{eNC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green, font=\small,align=left]
\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]

\begin{center}
\begin{figure}
\resizebox{!}{0.30\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,2) node[nS] (n0) {$0$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (2,0) node[nS] (n3) {$3$}; 
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

    \path
        (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}$} (n2) 
        (n3) edge[eS] node[eNS]{$w_{34}$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}$} (n5)
        (n0) edge[eC] node[eNS]{$w_{03}$} (n3)
        (n1) edge[eS] node[eNS]{$w_{14}$} (n4)
        (n2) edge[eS] node[eNS]{$w_{25}$} (n5)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

    \path
        (n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}$} (n2) 
        (n03) edge[eS] node[eNS]{$w_{34}$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}$} (n5)
        (n1) edge[eS] node[eNS]{$w_{14}$} (n4)
        (n2) edge[eC] node[eNS]{$w_{25}$} (n5)
    ;
    \end{tikzpicture}
}

\resizebox{!}{0.30\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \draw (4,0) node[nS] (n4) {$4$};
    \path
        (n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
        (n1) edge[eS] node[eNS]{$w_{12}$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{34}$} (n4) 
        (n4) edge[eS] node[eNS]{$w_{45}$} (n25)
        (n1) edge[eC] node[eNS]{$w_{14}$} (n4)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,1) node[nS] (n14) {$\{1,4\}$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \path
        %(n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
        (n14) edge[eNC] node[eNS]{$w_{12}+$\\$w_{45}$} (n25) 
        (n03) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}$} (n14) 
    ;
    \end{tikzpicture}
}
\caption{
    To use hierarchical clustering as an approximator for
    the multicut objective we contract the edge with the highest weight
    in each step (to be contracted edge is shown in red). 
    Whenever multiple edges are merged into a single edge,
    we use the sum of the weight as a new weight, since
    we have to pay for all edges which are cut in the uncontracted 
    graph.
    We stop when the highest edge weight is smaller
    or equal to zero (edge shown in green).
    Doing so, hierarchical clustering can be
    interpreted as an greedy approximator for
    the multicut objective.
}\label{fig:hc_proposal}
\end{figure}
\end{center}

### 2014-09-29 paper/inputs/fig_pixel_mc.tex
cleanup

--- 2014-09-26 paper/alg_graph.tex
@@
-%!TEX root = egpaper_for_review.tex
-\begin{figure}[H]
-
-\tikzfading[name=fade right0,left color=transparent!0, right color=transparent!70]
-\tikzfading[name=fade right1,left color=transparent!70, right color=transparent!100]
-\tikzstyle{gNode}=[fill=white,draw,solid,font=\sffamily\small]
-\tikzstyle{cutNode}=[fill=white,draw,solid,font=\sffamily\small]
-\tikzstyle{opBox}=[fill=black,text=white,draw,solid,font=\sffamily\tiny,align=center]
-\tikzstyle{label}=[fill=black,text=white,draw,solid,font=\sffamily\tiny]
-\tikzstyle{edgeLabelNode}=[ellipse,text=black,solid,font=\sffamily\tiny,align=left,minimum size=0.5cm]
-\tikzstyle{aEdge}=[->,node distance=0.5cm]
-\begin{tikzpicture}
-
-    \draw node[opBox] (gen) {GENERATOR};
-    \draw node[cutNode,right = 1cm of gen] (proposal_cut) {$\bar{P}$};
-    \draw node[right of = proposal_cut](dummy){};
-    \draw node[cutNode,right of = dummy] (best_cut) {$P$};
-    \draw node[opBox,below of = dummy] (intersect) {INTERSECT\\UNCUT};
-    \draw node[cutNode,below of = intersect] (int_cut){$\tilde{P}$};
-    \draw node[opBox,below of = int_cut] (contract) {CONTRACT\\UNCUT\\EDGES};
-    \draw node[gNode,right = 2cm of contract](cgraph)  {$( \tilde{\mathcal{G}}, \tilde{\mathcal{W}})$};
-    \draw node[opBox, above of =  cgraph] (multicut) {MULTICUT};
-    \draw node[cutNode,above of = multicut] (rcut) {$\bar{P}^{\tilde{\mathcal{G}}}$};
-    \draw node[opBox, above of =  rcut] (pback) {PROJECT\\CUT\\BACK};
-
-    \node[draw,dotted,fit=(proposal_cut) (cgraph),inner sep = 3mm,thick, draw=gray,opacity=0.5] {};
-
-    \draw node[gNode,below = of gen](graph)  {$( \mathcal{G}, \mathcal{W})$};
-    \path[]
-    (gen) edge[aEdge]  node[]{} (proposal_cut)
-    (graph) edge[aEdge] (gen)
-    (proposal_cut)  edge[aEdge]   (intersect)
-    (best_cut)      edge[aEdge]   (intersect)
-    (intersect)     edge[aEdge]   (int_cut)
-    (int_cut)       edge[aEdge]   (contract) 
-    (contract)      edge[aEdge,above]   
-        node[edgeLabelNode]{coarse graphs\\with fewer nodes}(cgraph)
-    (cgraph)        edge[aEdge]   (multicut)
-    (multicut)      edge[aEdge]   (rcut)
-    (rcut)          edge[aEdge]   (pback)
-    (pback)         edge[aEdge]   (best_cut)
-    (graph)         edge[aEdge]   (contract.west)
-    (best_cut)      edge[aEdge,dashed,bend angle=90,bend right,draw=gray!30]  
-        node[edgeLabelNode]{current best solution\\can influence generator}  (gen)
-    ;
-\end{tikzpicture}
-\caption{
-    The proposed algorithm works in the following way:
-    Given a graph $\mathcal{G}$, edge weights $\mathcal{W}$ and
-    a proposal generator, the current best solution $P$ is iteratively improved.
-    A proposal generator generates different versatile
-    proposal partitions $\bar{P}$.
-    The proposal  $\bar{P}$ is intersected with $P$ which results in
-    $\tilde{P}$. Contracting each each which is not 
-    cut in $\tilde{P}$ leads to a coarser graph  
-    $\tilde{\mathcal{G}} = ( \tilde{\mathcal{V}}, \tilde{\mathcal{E}} )$ 
-    with new edge weights $\tilde{\mathcal{W}}$.
-    If  $\bar{P}$ and $P$ have a small fraction of cut edges, $\tilde{\mathcal{G}}$ will be small ( $|\tilde{\mathcal{V}}| << |\mathcal{V}|$
-    and $|\tilde{\mathcal{E}}| << |\mathcal{E}|$).
-    The multicut objective on the smaller graph $\tilde{\mathcal{G}}$ can be optimized magnitudes 
-    faster than on $\tilde{\mathcal{G}}$.
-    It is guaranteed that the optimal multicut partitioning $\bar{P}^{\tilde{\mathcal{G}}}$ on $\tilde{\mathcal{G}}$ projected 
-    back to $\mathcal{G}$ as a lower or equal energy than any of the two input partitions $P$ and $\bar{P}$, 
-    therefore we store the result of fusion as new best state $P$ and repeat the procedure.
-}\label{fig:algo_graph}
-\end{figure}
-
-\begin{figure}[H]
-
-%\begin{tikzpicture}
-%    \tikzstyle{pixel}=[regular polygon,regular polygon sides=4,inner sep=0pt,draw,solid,font=\sffamily\small]
-%
-%    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
-%    \begin{scope}[x={(image.south east)},y={(image.north west)}]
-%        \draw[red,ultra thick,rounded corners] (0.62,0.65) rectangle (0.78,0.75);
-%        \draw node[pixel ](100.5,100.5) {BLAAA};
-%    \end{scope}
-%\end{tikzpicture}
-
-% 481 / 321
-
-\end{figure}
+%!TEX root = ../egpaper_for_review.tex
 
@@
 \tikzstyle{p}=[opacity=0.6,fill=white,circle,draw, inner sep=0,font=\tiny,minimum size=0.15cm]
-\begin{figure}
+\begin{figure}[H]
 \begin{center}
@@
     \node[anchor=south west,inner sep=0] (image) at (0,0) 
-        {\includegraphics[width=0.5\textwidth]{images/120093.jpg}};
+        {\includegraphics[width=0.4\textwidth]{images/120093.jpg}};
     % shift scope to the image 
@@
     every pixel (white nodes) is connected
-    to its 4 \emph{local} neighbors (green nodes).
+    to its 4 \emph{local} neighbors (edges between white and green nodes).
     Furthermore each pixel is connected to some \emph{non-local} neighbors within a 
-    certain radius (red nodes).
+    certain radius  (edges between white and green nodes).
     The local neighbors are connected with a \emph{positive}
@@
     is very high, the local edge weight should be close to zero.
-    The non-local edge weights are \emph{negative} to
+    If there is no evidence for a cut (low gradient magnitude for example)
+    the local edge weight should be high.
+    The \emph{non-local edge weights} are \emph{negative} to
     encourage label transitions.

### 2014-09-29 paper/egpaper_for_review.tex
improved paper

@@
 \usepackage{paralist}
+\usepackage{amsthm}
 %\usepackage{framed}
@@
 \usepackage{subcaption}
+\usepackage{algorithm}
+%\usepackage{algorithmic}
+\usepackage{algpseudocode}
+\usepackage{setspace}
 %for tikz
@@
 \DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
 \definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
+
+\newtheorem{theorem}{Theorem}
 
@@
 \subsubsection{Solver for the Multicut Objective}
+
+    \input{inputs/tab_mc_overview.tex}
+
    \begin{itemize}
@@
 
+\begin{theorem}[NameMe]
+Solving ??? on the contracted graph is 
+equivalent to solving ??? on the 
+original graph with additional 
+must link constraints
+\end{theorem}
+
+\begin{proof}[Proof of theorem ]
+todo
+\end{proof}
+
+\begin{theorem}[NameMe]
+Solving ??? and ??? will never increase the best energy...
+\end{theorem}
+
+\begin{proof}[Proof of theorem ]
+todo
+\end{proof}
+
+\begin{theorem}[NameMe]
+If the all cut edges of the global optimal
+solution are included in the union of
+the cut edges of two proposals, solving
+??? will find the global optimal solution
+\end{theorem}
+
+\begin{proof}[Proof of of theorem]
+todo
+\end{proof}
+
 \input{inputs/fig_alg_graph.tex}
@@
 \subsection{Proposal Generators}
+
+\begin{algorithm}
+\begin{scriptsize}
+\caption{Fusion Based Algorithms}\label{alg:fusion}
+\begin{algorithmic}[1]
+\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
+\State $x^0 \gets \textrm{initial state form } X$
+\State $n \gets 0 $                                 \Comment{Number of moves}
+\State $m \gets 0 $                                 \Comment{Number of moves without progress}
+\While{$m < m_{\max}$ and $n < n_{\max}$ }
+\State $n \gets n+1$ 
+ \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
+ \If{$J(x^{n-1}) \leq J(x')$}                       
+   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
+ \Else
+   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
+ \EndIf
+ \If{$J(x^{n}) \leq J(x^{n-1})$}
+   \State $m \gets 0$                                 \Comment{Reset counter}
+ \Else
+   \State $m \gets m+1$                               \Comment{Increment counter}
+ \EndIf
+\EndWhile
+\State \textbf{return} $x^n$
+\EndProcedure
+\end{algorithmic}
+\end{scriptsize}
+\end{algorithm}
+
+\begin{algorithm}
+\begin{scriptsize}
+\caption{Fusion Moves}\label{alg:fusion_moves}
+\scriptsize
+\begin{algorithmic}[1]
+\Require $J(x) \leq J(x')$
+\Ensure $J(\hat{x}) \leq J(x)$
+\vspace{0.2cm}
+\Procedure{Fuse}{$x,x',J$}
+\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
+    \Comment{
+        \begin{minipage}{0.4\linewidth} 
+            \begin{tiny}
+            \begin{singlespace}
+                intersect
+                uncut edges in $x$ and $x'$,
+                return  
+                connected component labeling
+            \end{singlespace}
+            \end{tiny}
+        \end{minipage}
+    }
+\vspace{0.1cm}
+\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
+    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
+    \Comment{ 
+        \begin{minipage}{0.2\linewidth} 
+            \begin{tiny}
+            \begin{singlespace}
+                Contract all edges 
+                which are uncut in $\bar{x}$ 
+            \end{singlespace}
+            \end{tiny}
+        \end{minipage}
+    }
+\vspace{0.1cm}
+\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
+    \Comment{ 
+        \begin{minipage}{0.3\linewidth} 
+            \begin{tiny}
+            \begin{singlespace}
+                Solve the multicut objective
+                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
+            \end{singlespace}
+            \end{tiny}
+        \end{minipage}
+    }
+
+\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
+    \Comment{ 
+        \begin{minipage}[\textheight]{0.4\linewidth} 
+            \begin{tiny}
+            \begin{singlespace}
+                Translate the connected component
+                labeling $\tilde{x}^*$ of $\tilde{G}$ 
+                to a connected component labeling of $G$
+            \end{singlespace}
+            \end{tiny}
+        \end{minipage}
+    }
+\State \textbf{return} $\hat{x}$
+\EndProcedure
+\vspace{0.3cm}
+\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
+\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
+\EndProcedure
+\end{algorithmic}
+\end{scriptsize}
+\end{algorithm}
+
+\begin{algorithm}
+    \begin{scriptsize}
+        \caption{Proposal Generators}\label{alg:proposal_gen}   
+        \begin{algorithmic}[1]
+            %\Require $J(x) \leq J(x')$
+            %\Ensure $J(\hat{x}) \leq J(x)$
+            %\vspace{0.3cm}
+            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
+            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
+            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
+
+            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
+            \State \textbf{return} $x'$
+            \EndProcedure
+            %
+            %
+            \vspace{0.3cm}
+            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
+            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
+            \State $ getRandomSeeds$
+            \State $ runEdgeWeightedWs$
+            \EndProcedure   
+            %
+            %
+            \vspace{0.3cm}
+            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
+            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
+            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
+            \State $\hat{W} \gets W$
+            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
+                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
+                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
+            \EndWhile
+            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
+            \EndProcedure
+        \end{algorithmic}
+    \end{scriptsize}
+\end{algorithm}
 

### 2014-09-30 paper/inputs/tab_mc_overview.tex
add missing file

%!TEX root = ../egpaper_for_review.tex
\begin{table}
\begin{center}
    \begin{tiny}
    \begin{tabular}{ p{1cm} p{1cm} p{1.5cm} p{2.5cm} }
    \hline
    \hline
    Method &    & Limitations &   \\ \hline
    Multicut \cite{andres_2011_iccv,kappes_2011_emmcvpr} & 
        (I)LP & 
        not scalable, slow &
        Cutting plane method.
        Global optimal but slow for huge problems. 
        However, applicable for medium size superpixel RAG. 
        \\ \hline
    Expand And Explorer \cite{bagon_2011_arxiv} & 
        movemaker & 
        gets stuck early &
        $\alpha$-Expansion modification. Applicable to
        large scale problems but gets stuck in local minima(???).
        \\ \hline
    Fast Planar CC \cite{yarkony_2012_eccv} & 
        dual-decompositon & 
        planar graphs only, 
        duality/integrality gab &
        Dual decompositon in planar subgraphs??
        Works on planar graphs only. Fast (is there a word for fast to medium fast) for
        small to medium size graphs.
        \\ \hline
    Cut Glue and Cut \cite{beier_2014_cvpr} & 
        move-making & 
        gets stuck in poor minima for non planar graphs &
        Greedy solver based on a series of 2 colorings.
        State of the art any time performance. Very
        fast for planar graphs. Gets stuck in local minima
        for non planar graphs.
        \\ \hline
    THIS WORK & 
        fusion move-making & 
        no natural stopping condition &
        Fusion of a proposal segmentation with
        the current best segmentation.
        State of the art any time performance for (???)
        \\ \hline
        \hline
    \end{tabular}
    \end{tiny}
\end{center}
\caption{
    Overview of correlation clustering / multicut solvers
}
\end{table}

### 2014-09-30 paper/egpaper_for_review.tex
minor improvements

@@
     \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
-    \item with optional long range repulsive edges~\cite{yarknoy???}.
+    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
     \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
-    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv}
+    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
+    \item for co-segmentation~\cite{glassner_2011_cvpr}
     \item and to cluster fully connected graphs~\cite{???}.

### 2014-09-30 src/interfaces/python/opengm/opengmcore/__init__.py

@@ -202,6 +202,16 @@ def modelViewFunction(factor):
       return self.factor[labeling]
   return PythonFunction( _ModelViewFunction(factor) ,factor.shape.__tuple__())
 
+
+
+def gridVisNh4(shape, numpyOrder=True):
+    hFactors=(shape[0]-1)*shape[1];
+    vFactors=(shape[1]-1)*shape[0];
+    nFac =  hFactors+vFactors;
+    vis = numpy.zeros(shape=[nFac,2],dtype=index_type)
+    secondOrderGridVisNew(shape[0], shape[1], numpyOrder, vis)
+    return vis
+
 #Model generators
 def grid2d2Order(unaries,regularizer,order='numpy',operator='adder'):
    """ 

### 2014-10-01 exp/better_model.py
better model

@@ -1,0 +1,87 @@
+import vigra
+import opengm
+import numpy
+import matplotlib
+import matplotlib.pyplot as plt
+
+
+import numpy as np
+import pylab
+import matplotlib.cm as cm
+import Image
+from matplotlib.colors import LinearSegmentedColormap
+
+
+
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')
+#img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/118035.jpg')
+img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/val/21077.jpg')
+#img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/val/101087.jpg')
+#img = vigra.resize(img, (img.shape[0]/1, img.shape[1]/1))#[::1,::1,:]
+imgLab = vigra.colors.transform_RGB2Lab(img)
+
+
+scalesForStrength = (0.4, 0.8)
+scalesForOrientation = (0.1, 0.1)
+gamma = 0.002
+offset = -0.5
+
+structTensorForStrength = vigra.filters.structureTensor(imgLab,*scalesForStrength)
+structTensorOrientation = vigra.filters.structureTensor(imgLab,*scalesForOrientation)
+eigenReprForStrength  = vigra.filters.tensorEigenRepresentation2D(structTensorForStrength)
+eigenReprForOrientation  = vigra.filters.tensorEigenRepresentation2D(structTensorOrientation)
+
+
+edgeIndicator = eigenReprForStrength[:, :, 0]
+orientation = eigenReprForOrientation[:, :, 2]
+edgeWeight = numpy.exp(-1.0*gamma*edgeIndicator) + offset
+#edgeWeight[0,0] = -1.0
+#edgeWeight[0,1] = 1.0
+
+
+
+
+
+
+
+matplotlib.cm.ScalarMappable()
+
+cdict = {'red':   [(0.0,  1.0, 1.0),
+                   (0.33, 0.0, 0.0),
+                   (0.66, 0.0, 0.0),
+                   (1.0,  1.0, 1.0)],
+
+         'green': [(0.0,  0.0, 0.0),
+                   (0.33, 1.0, 1.0),
+                   (0.66, 0.0, 0.0),
+                   (1.0,  0.0, 0.0)],
+
+         'blue':  [(0.0,  0.0, 0.0),
[…]

### 2014-10-02 exp/better_model.py
caller first version

@@ -4,13 +4,11 @@ import numpy
 import matplotlib
 import matplotlib.pyplot as plt
 
-
 import numpy as np
 import pylab
 import matplotlib.cm as cm
 import Image
 from matplotlib.colors import LinearSegmentedColormap
-
 
 
 img = vigra.readImage('/home/tbeier/datasets/BSR/BSDS500/data/images/train/56028.jpg')

### 2014-10-08 paper/egpaper_for_review.tex
improvment

@@
 \usepackage{amsthm}
+\usepackage{dirtytalk}
 %\usepackage{framed}
@@
 \include{my_macros.tex}
-\title{FancyMc Moves \\ Fusion Moves for Multicut Objectives}
+\title{Intersection Fusion Moves \\ Fusion Moves for Multicut Objectives}
 
@@
 
-The tale of the multicut
+  Nunez-Iglesias \etal describe the multicut as
+  \say{one-shot agglomeration of supervoxels} whose 
+  main drawback is the scalability \cite{nunez_iglesias_2013}.
+  Within this work we will overcome the scalability issues.
 
@@
 \begin{theorem}[NameMe]
-Solving ??? and ??? will never increase the best energy...
+Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{new}$ the solution of \ref{???}.
+$x_{new}$  will never decrease the energy:
+$x_{new} \cdot w \leq  \min( x_{a}\cdot w,  x_{b}\cdot w) $ 
 \end{theorem}
@@
 \begin{theorem}[NameMe]
-If the all cut edges of the global optimal
-solution are included in the union of
-the cut edges of two proposals, solving
-??? will find the global optimal solution
+
+Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{opt}$ the global solution,
+$X_{a}^c, X_{b}^c$ and $ X_{opt}^c$ the set of cut edges in  $x_{a}, x_{b}$  and $ x_{opt}$
+optimal solution.
+Iff  $ X_{opt}^c \subseteq  (X_{a}^c \cup X_{b}^c)$,  the solution of \ref{???} will be $x_{opt}$.
 \end{theorem}

### 2014-10-09 paper/egpaper_for_review.tex
improved paper, and new autoScale option
permutation as option

@@
 \include{my_macros.tex}
-\title{Intersection Fusion Moves \\ Fusion Moves for Multicut Objectives}
+\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
 
@@
 
+\subsection{Karger-Stein Algorithms}
+Use randomized procedure to reduce the number of nodes / edges to a reasonable 
+number.
+On the smaller graph, more expensive solvers are used.
+
 %------------------------------------------------------------------------
-\section{Name of My Method (Union Fusion Cut)}
+\section{Intersection Fusion Cut}
 
 Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
-Good approximate solvers for planar graphs exist \cite{beifiger_2014_cvpr,yarkony_2012_eccv} 
+Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
 but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
+%
+To make multicuts scalable, it is desirable to replace the graph $G$
+with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
+If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.
+%
+A trivial way to reduce the size of the graph  is edge contraction.
+Until a desirable size is reached, one might contract the edge with
+the highest weight. A cut on the contracted graph  $\hat{G}$ is always
+a valid cut on $\hat{G}$.
+%
+On the other hand, if an edge $e$ is contracted, it will never be cut.
+If $e$ is part of the cut in a global optimal solution, we cannot find
+this cut.
+%
+To overcome this problem  we can randomize the edge contraction,
+and repeat this multiple times and remember the best solution.
+%
+But this would throw away all the ``not the best'' solutions (rewrite me).
+Within this work we propose the following nifty trick.
+Instead of throwing away solutions, we intersect them with the 
+best solution, and solve the multicut on the resulting
+graph.
+Therefore we fuse multiple solutions,
 

### 2014-10-09 paper/egpaper_for_review.tex
improved paper

@@
 
+\subsubsection{Randomized HierarchicalClustering (RHC)}
+
+To generate proposals cut we can use bottom up hierarchical clustering.
+In each step we contract the edge with the highest weight.
+Parallel edges are merged into single edges by summing their weights.
+We stop when a certain number of nodes is reached, or the
+largest edge weight is smaller then a certain threshold.
+To get versatile proposals we either add noise 
+to the edge weighs or permute a certain number of weights.
+
+\subsubsection{Randomized MaxCut  (RMC)}
+
+To get energy aware proposals we can use max cuts.
+The max cut objective is the same as
+the multicut objective, but only two 
+node colors are allowed.
+Therefore solutions of the max cut objective
+might be useful proposals.
+To create different proposals we set 
+the weight of edges which are cut 
+in the best solution to zero.
+In this way we favor solutions 
+different form the current best. 
+In addition we either add noise permute a certain number of weights.
+
+\subsubsection{Randomized Watersheds (RWS)}
+
+The edge weighted watershed algorithm
+with random seeds can be used to get 
+cheap proposals.
+
 \input{inputs/fig_hc.tex}

### 2014-10-09 paper/egpaper_for_review.tex
paper

@@
 \definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
-
+\usepackage{xargs} 
 \newtheorem{theorem}{Theorem}
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
+\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
+\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
+\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
 
@@
 
+\listoftodos[Notes]
 %%%%%%%%% ABSTRACT
 \begin{abstract}
-   Multicuts rule.
+   We address the problem of partitioning a  graph
+   into a previously unknown number of clusters.
+   Among all partitions, the one with the minimal 
+   sum of of cut edge weights is chosen. 
+   This problem is known as correlation clustering 
+   or multicut.
+   We propose a general framework to find
+   high quality approximate solutions for 
+   this NP-hard problem based on a move making algorithm:
+   We use candidate solutions from a proposal generator
+   to iteratively improve the best observed solution similar
+   to fusion moves.
+   The proposed solver outperforms any other solver
+   w.r.t. to any time performance.
+   The solutions found by this solver are close
+   to global optimal solutions w.r.t. energy
+   and problem specific measurements as VI for
+   image segmentation problems.
+
 \end{abstract}
 \section{Introduction}
+
+\todo[inline]{should there be a general introduction to multicuts?}
 
@@
 main drawback is the scalability \cite{nunez_iglesias_2013}.
-  Within this work we will overcome the scalability issues.
+To address scalability, supernodes can be useful.
+To create supernodes, some edges will be contracted
+and their nodes are merged into super-nodes.
+Doing so, we can reduce  the graph 
+to a reasonable size, such that we can find
+global optimal multicut solutions within reasonable time.
+%
+Any edge which is contracted is lost.
+If such an edge is cut in the global optimal solution, we cannot 
+find this global optimal solutions.
+Therefore we avoid fixed decisions and use a
+dynamic energy aware contraction scheme.
+%
+Different edge contractions lead to different super-node graphs.
+A trivial approach is the following.
+Create different super-node graphs, optimize them with multicuts,
+and take the result which leads to the lowest energy
+on the unmodified initial graph.
+% 
+Doing so, we throw away all results which do not have the lowest energy.
+Within this work we propose a framework which 
+combine multiple \emph{proposal} super-node graphs
+without any premature irreversible decisions.
+Furthermore, multiple super-node graphs are combined such
+that the information form all of them is used.
+\todo[inline]{\emph{proposal} super-node graphs sounds shitty}
 
@@
 Therefore we fuse multiple solutions,
-
-\begin{theorem}[NameMe]
-Solving ??? on the contracted graph is 
-equivalent to solving ??? on the 
-original graph with additional 
-must link constraints
-\end{theorem}
-
-\begin{proof}[Proof of theorem ]
-todo
-\end{proof}
-
-\begin{theorem}[NameMe]
-Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{new}$ the solution of \ref{???}.
-$x_{new}$  will never decrease the energy:
-$x_{new} \cdot w \leq  \min( x_{a}\cdot w,  x_{b}\cdot w) $ 
-\end{theorem}
-
-\begin{proof}[Proof of theorem ]
-todo
-\end{proof}
-
-\begin{theorem}[NameMe]
-
-Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{opt}$ the global solution,
-$X_{a}^c, X_{b}^c$ and $ X_{opt}^c$ the set of cut edges in  $x_{a}, x_{b}$  and $ x_{opt}$
-optimal solution.
-Iff  $ X_{opt}^c \subseteq  (X_{a}^c \cup X_{b}^c)$,  the solution of \ref{???} will be $x_{opt}$.
-\end{theorem}
-
-\begin{proof}[Proof of of theorem]
-todo
-\end{proof}
-
-\input{inputs/fig_alg_graph.tex}
-
-\input{inputs/fig_move_graph.tex}
-
-%-------------------------------------------------------------------------
-\subsection{Proposal Generators}
 
@@
 
+\begin{theorem}[NameMe]
+Solving ??? on the contracted graph is 
+equivalent to solving ??? on the 
+original graph with additional 
+must link constraints
+\end{theorem}
+
+\begin{proof}[Proof of theorem ]
+todo
+\end{proof}
+
+\begin{theorem}[NameMe]
+Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{new}$ the solution of \ref{???}.
+$x_{new}$  will never decrease the energy:
+$x_{new} \cdot w \leq  \min( x_{a}\cdot w,  x_{b}\cdot w) $ 
+\end{theorem}
+
+\begin{proof}[Proof of theorem ]
+todo
+\end{proof}
+
+\begin{theorem}[NameMe]
+
+Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{opt}$ the global solution,
+$X_{a}^c, X_{b}^c$ and $ X_{opt}^c$ the set of cut edges in  $x_{a}, x_{b}$  and $ x_{opt}$
+optimal solution.
+Iff  $ X_{opt}^c \subseteq  (X_{a}^c \cup X_{b}^c)$,  the solution of \ref{???} will be $x_{opt}$.
+\end{theorem}
+
+\begin{proof}[Proof of of theorem]
+todo
+\end{proof}
+
+\input{inputs/fig_alg_graph.tex}
+
+\input{inputs/fig_move_graph.tex}
+
+%-------------------------------------------------------------------------
+\subsection{Proposal Generators}
+
 \begin{algorithm}

### 2014-10-10 paper/egpaper_for_review.tex
minor changes

@@
 
+Given an edge weighted graph, positive weights (\emph{attractive})
+encourage the adjacent nodes to be in the same 
+connected component, while negative weights (\emph{repulsive}) encourage
+the nodes to stay in different connect components.
+Therefore the sign of the weights encodes if two
+nodes should be merged or not and the magnitude of the weights encodes
+the certainty of this desire.
+The objective of correlation clustering / multicuts
+is finding the cut with a minimal sum of cut edge weights.
+The number of connected components / clusters is discovered
+from the weights ( rewrite?!?).
+Correlation clustering / the multicut is NP-hard \cite{???}.
+%
+Despite the NP-hardness, correlation clustering has been 
+successfully used for
+\begin{inparaenum}[(i)]
+    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
+    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
+    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
+    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
+    \item for co-segmentation~\cite{glassner_2011_cvpr}
+    \item and to cluster fully connected graphs~\cite{???}.
+\end{inparaenum}
+
+\todo[inline]{WHY WE NEED THIS NEW SOLVER?}
+
 Nunez-Iglesias \etal describe the multicut as
@@
 main drawback is the scalability \cite{nunez_iglesias_2013}.
+
+\todo[inline]{BETTER MOTIVATE SUPERNODES}
+
 To address scalability, supernodes can be useful.
@@
 \todo[inline]{\emph{proposal} super-node graphs sounds shitty}
+%
+The proposed algorithm can be interpreted as a fusion moves
+algorithm for correlation clustering / multicut objective.
+We generate cheap and versatile proposals
+and \emph{fuse} them with the current best solution with the
+guarantee that this cannot increase the energy.
 
@@
         y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
-        s.t.: &  & x_{ij} + x_{jk} < x_{i,k} \quad \forall i, j, k   \nonumber
+        s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
     \end{eqnarray}
@@
 \end{center}
-
-The multicut objective has been used for
-\begin{inparaenum}[(i)]
-    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
-    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
-    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
-    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
-    \item for co-segmentation~\cite{glassner_2011_cvpr}
-    \item and to cluster fully connected graphs~\cite{???}.
-\end{inparaenum}
 

### 2014-10-13 paper/tables/knott-3d-300.tex
add tables

\begin{table}[H]
\scriptsize
\centering
\caption{knott-3d-300 (8 instances)}
\label{tab:smalltable-knott-3d-300}
\begin{tabular}{lrrrrrr}
\toprule
           algorithm &       runtime     &         value &         bound &           mem &     best &      opt   \\ \midrule 
             ogm-ICM & $        84.37$ sec & $    -25196.51$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
              ogm-KL & $        13.16$ sec & $    -25556.93$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
            ogm-LF-1 & $        29.08$ sec & $    -25243.76$ & $-\infty$ & $         0.02$ GB & $       0$ & $       0$ \\ 
\cmidrule{1-1} 
              MCR-CC & $      3423.65$ sec & $    -26161.81$ & $    -27434.30$ & $         0.57$ GB & $       1$ & $       1$ \\ 
           MCR-CCFDB & $      1338.99$ sec & $    -27276.12$ & $    -27307.22$ & $         0.15$ GB & $       1$ & $       1$ \\ 
       MCR-CCFDB-OWC & $      1367.03$ sec & $    -27287.23$ & $    -27309.62$ & $         0.15$ GB & $       6$ & $       6$ \\ 
\cmidrule{1-1} 
     MCI-CCFDB-CCIFD & $      1261.99$ sec & $    -26826.57$ & $    -27308.19$ & $         0.37$ GB & $       6$ & $       6$ \\ 
             MCI-CCI & $       220.30$ sec & $    -27302.78$ & $    -27305.02$ & $         0.28$ GB & $       8$ & $       7$ \\ 
           MCI-CCIFD & $       104.55$ sec & $    -27302.78$ & $    -27302.78$ & $         0.16$ GB & $       8$ & $       8$ \\ 
\cmidrule{1-1} 
            ogm-CGC* & $         4.53$ sec & $    -27251.42$ & $    -28901.58$ & $         0.02$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE* & $         1.19$ sec & $         0.00$ & $-\infty$ & $         0.02$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE-CGCF* & $         2.38$ sec & $    -24707.81$ & $-\infty$ & $         0.04$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC* & $         5.60$ sec & $    -27282.58$ & $-\infty$ & $         0.03$ GB & $       2$ & $       0$ \\ 
ogm-mcfusion-HC-CGC-CGCF* & $         5.61$ sec & $    -27283.82$ & $-\infty$ & $         0.04$ GB & $       3$ & $       0$ \\ 
 ogm-mcfusion-HC-MC* & $         8.87$ sec & $    -27283.36$ & $-\infty$ & $         0.05$ GB & $       3$ & $       0$ \\ 
ogm-mcfusion-HC-MC-CGCF* & $         8.92$ sec & $    -27284.60$ & $-\infty$ & $         0.06$ GB & $       4$ & $       0$ \\ 
ogm-mcfusion-WS-BASE* & $         0.24$ sec & $         0.00$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-BASE-CGCF* & $         4.91$ sec & $    -27253.30$ & $-\infty$ & $         0.03$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-CGC* & $        22.99$ sec & $    -27273.39$ & $-\infty$ & $         0.01$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-WS-CGC-CGCF* & $        23.91$ sec & $    -27286.88$ & $-\infty$ & $         0.03$ GB & $       4$ & $       0$ \\ 
 ogm-mcfusion-WS-MC* & $        36.85$ sec & $    -27280.59$ & $-\infty$ & $         0.05$ GB & $       2$ & $       0$ \\ 
ogm-mcfusion-WS-MC-CGCF* & $        37.77$ sec & $    -27293.33$ & $-\infty$ & $         0.06$ GB & $       6$ & $       0$ \\ 
\bottomrule
\end{tabular}
\end{table}

### 2014-10-13 paper/tables/seg-3d.tex
add tables

\begin{table}[H]
\scriptsize
\centering
\caption{seg-3d (2 instances)}
\label{tab:smalltable-seg-3d}
\begin{tabular}{lrrrrrr}
\toprule
           algorithm &       runtime     &         value &         bound &           mem &     best &      opt   \\ \midrule 
             ogm-ICM & $      1959.44$ sec & $    618075.17$ & $-\infty$ & $         0.22$ GB & $       0$ & $       0$ \\ 
              ogm-KL & $      2290.46$ sec & $    441695.84$ & $-\infty$ & $         0.20$ GB & $       0$ & $       0$ \\ 
            ogm-LF-1 & $      1857.93$ sec & $    552690.10$ & $-\infty$ & $         0.27$ GB & $       0$ & $       0$ \\ 
\cmidrule{1-1} 
              MCR-CC & $          NaN$ sec & $          NaN$ & $          NaN$ & $         0.11$ GB & $       1$ & $       1$ \\ 
           MCR-CCFDB & $          NaN$ sec & $          NaN$ & $          NaN$ & $         0.05$ GB & $       1$ & $       1$ \\ 
       MCR-CCFDB-OWC & $          NaN$ sec & $          NaN$ & $          NaN$ & $         0.05$ GB & $       1$ & $       1$ \\ 
\cmidrule{1-1} 
     MCI-CCFDB-CCIFD & $          NaN$ sec & $          NaN$ & $          NaN$ & $         0.05$ GB & $       1$ & $       1$ \\ 
             MCI-CCI & $      1806.76$ sec & $    414124.76$ & $    413523.92$ & $         4.43$ GB & $       1$ & $       1$ \\ 
           MCI-CCIFD & $      4201.35$ sec & $    650888.58$ & $    401952.16$ & $         1.01$ GB & $       1$ & $       1$ \\ 
\cmidrule{1-1} 
            ogm-CGC* & $          NaN$ sec & $          NaN$ & $          NaN$ & $         0.03$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE* & $        27.97$ sec & $    501728.60$ & $-\infty$ & $         0.38$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE-CGCF* & $        40.77$ sec & $    471105.16$ & $-\infty$ & $         0.55$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC* & $      1293.80$ sec & $    413546.15$ & $-\infty$ & $         0.72$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-HC-CGC-CGCF* & $      1291.94$ sec & $    413545.50$ & $-\infty$ & $         0.88$ GB & $       2$ & $       0$ \\ 
 ogm-mcfusion-HC-MC* & $      1171.51$ sec & $    413552.74$ & $-\infty$ & $         0.68$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-HC-MC-CGCF* & $      1172.41$ sec & $    413546.96$ & $-\infty$ & $         0.85$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-WS-BASE* & $         7.56$ sec & $    748369.02$ & $-\infty$ & $         0.19$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-BASE-CGCF* & $      6088.09$ sec & $    413807.74$ & $-\infty$ & $         0.40$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-CGC* & $      1838.10$ sec & $    413760.67$ & $-\infty$ & $         0.28$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-CGC-CGCF* & $      2484.01$ sec & $    413573.58$ & $-\infty$ & $         0.44$ GB & $       0$ & $       0$ \\ 
 ogm-mcfusion-WS-MC* & $     32840.49$ sec & $    427635.00$ & $-\infty$ & $        10.53$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-MC-CGCF* & $     34279.76$ sec & $    413814.27$ & $-\infty$ & $        10.69$ GB & $       1$ & $       0$ \\ 
\bottomrule
\end{tabular}
\end{table}

### 2014-10-13 paper/egpaper_for_review.tex
add tables
paper mine

@@
 
-The edge weighted watershed algorithm
+The edge weighted watershed algorithm \cite{meyer_2013}
 with random seeds can be used to get 
-cheap proposals.
+cheap proposals. Instead of $n$ seeds distributed uniformly
+over all nodes we use the following.
+Draw $n/k$ random edges only the negative edges, 
+and give the two nodes of each random edge different seeds.
+Doing so, a random subset of negative edges is forced
+to be cut within each proposal.
+For additional randomness, noise can be added to
+the edge weighs.
 

### 2014-10-13 paper/tables/image-seg.tex

\begin{table}[H]
\scriptsize
\centering
\caption{image-seg (100 instances)}
\label{tab:smalltable-image-seg}
\begin{tabular}{lrrrrrr}
\toprule
           algorithm &       runtime     &         value &         bound &           mem &     best &      opt   \\ \midrule 
     ogm-CGC-planar* & $         0.28$ sec & $      4445.22$ & $      4136.83$ & $         0.02$ GB & $      28$ & $       0$ \\ 
ogm-mcfusion-HC-BASE* & $         0.12$ sec & $      5462.60$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE-CGCF* & $         0.12$ sec & $      5085.80$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC* & $         1.23$ sec & $      4444.56$ & $-\infty$ & $         0.01$ GB & $      40$ & $       0$ \\ 
ogm-mcfusion-HC-CGC-CGCF* & $         1.22$ sec & $      4444.75$ & $-\infty$ & $         0.02$ GB & $      40$ & $       0$ \\ 
 ogm-mcfusion-HC-MC* & $         5.12$ sec & $      4443.61$ & $-\infty$ & $         0.04$ GB & $      73$ & $       0$ \\ 
ogm-mcfusion-HC-MC-CGCF* & $         5.14$ sec & $      4443.61$ & $-\infty$ & $         0.05$ GB & $      73$ & $       0$ \\ 
ogm-mcfusion-WS-BASE* & $         0.05$ sec & $      6622.98$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-BASE-CGCF* & $         1.77$ sec & $      4460.12$ & $-\infty$ & $         0.01$ GB & $       3$ & $       0$ \\ 
ogm-mcfusion-WS-CGC* & $         1.44$ sec & $      4445.57$ & $-\infty$ & $         0.01$ GB & $      16$ & $       0$ \\ 
ogm-mcfusion-WS-CGC-CGCF* & $         1.75$ sec & $      4444.59$ & $-\infty$ & $         0.01$ GB & $      27$ & $       0$ \\ 
 ogm-mcfusion-WS-MC* & $         6.00$ sec & $      4444.58$ & $-\infty$ & $         0.03$ GB & $      22$ & $       0$ \\ 
ogm-mcfusion-WS-MC-CGCF* & $         6.31$ sec & $      4443.79$ & $-\infty$ & $         0.03$ GB & $      46$ & $       0$ \\ 
\bottomrule
\end{tabular}
\end{table}

### 2014-10-13 paper/tables/knott-3d-150.tex

\begin{table}[H]
\scriptsize
\centering
\caption{knott-3d-150 (8 instances)}
\label{tab:smalltable-knott-3d-150}
\begin{tabular}{lrrrrrr}
\toprule
           algorithm &       runtime     &         value &         bound &           mem &     best &      opt   \\ \midrule 
            ogm-CGC* & $         0.08$ sec & $     -4566.41$ & $     -4855.18$ & $         0.01$ GB & $       5$ & $       0$ \\ 
ogm-mcfusion-HC-BASE* & $         0.12$ sec & $         0.00$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE-CGCF* & $         0.16$ sec & $     -4160.88$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC* & $         0.36$ sec & $     -4559.96$ & $-\infty$ & $         0.01$ GB & $       6$ & $       0$ \\ 
ogm-mcfusion-HC-CGC-CGCF* & $         0.36$ sec & $     -4565.61$ & $-\infty$ & $         0.01$ GB & $       6$ & $       0$ \\ 
 ogm-mcfusion-HC-MC* & $         0.88$ sec & $     -4559.96$ & $-\infty$ & $         0.03$ GB & $       6$ & $       0$ \\ 
ogm-mcfusion-HC-MC-CGCF* & $         0.88$ sec & $     -4565.61$ & $-\infty$ & $         0.03$ GB & $       6$ & $       0$ \\ 
ogm-mcfusion-WS-BASE* & $         0.03$ sec & $         0.00$ & $-\infty$ & $         0.01$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-BASE-CGCF* & $         0.12$ sec & $     -4565.95$ & $-\infty$ & $         0.01$ GB & $       5$ & $       0$ \\ 
ogm-mcfusion-WS-CGC* & $          NaN$ sec & $          NaN$ & $          NaN$ & $         0.01$ GB & $       4$ & $       0$ \\ 
ogm-mcfusion-WS-CGC-CGCF* & $         0.37$ sec & $     -4571.22$ & $-\infty$ & $         0.01$ GB & $       7$ & $       0$ \\ 
 ogm-mcfusion-WS-MC* & $         1.28$ sec & $     -4570.83$ & $-\infty$ & $         0.03$ GB & $       5$ & $       0$ \\ 
ogm-mcfusion-WS-MC-CGCF* & $         1.31$ sec & $     -4571.22$ & $-\infty$ & $         0.03$ GB & $       7$ & $       0$ \\ 
\bottomrule
\end{tabular}
\end{table}

### 2014-10-13 paper/tables/knott-3d-450.tex

\begin{table}[H]
\scriptsize
\centering
\caption{knott-3d-450 (8 instances)}
\label{tab:smalltable-knott-3d-450}
\begin{tabular}{lrrrrrr}
\toprule
           algorithm &       runtime     &         value &         bound &           mem &     best &      opt   \\ \midrule 
             ogm-ICM & $       883.63$ sec & $    -72464.54$ & $-\infty$ & $         0.03$ GB & $       0$ & $       0$ \\ 
              ogm-KL & $       186.89$ sec & $    -73188.82$ & $-\infty$ & $         0.03$ GB & $       0$ & $       0$ \\ 
            ogm-LF-1 & $       298.07$ sec & $    -72479.60$ & $-\infty$ & $         0.04$ GB & $       0$ & $       0$ \\ 
\cmidrule{1-1} 
              MCR-CC & $      9814.45$ sec & $     -4892.36$ & $    -83272.85$ & $         0.39$ GB & $       0$ & $       0$ \\ 
           MCR-CCFDB & $      6404.34$ sec & $     -4892.36$ & $    -83272.85$ & $         0.20$ GB & $       0$ & $       0$ \\ 
       MCR-CCFDB-OWC & $      6455.21$ sec & $     -4892.36$ & $    -83272.85$ & $         0.19$ GB & $       0$ & $       0$ \\ 
\cmidrule{1-1} 
     MCI-CCFDB-CCIFD & $      6404.14$ sec & $     -4892.36$ & $    -83272.85$ & $         0.19$ GB & $       0$ & $       0$ \\ 
             MCI-CCI & $      1196.62$ sec & $    -78135.34$ & $    -78518.55$ & $         0.83$ GB & $       6$ & $       6$ \\ 
           MCI-CCIFD & $      1379.90$ sec & $    -78180.20$ & $    -78507.25$ & $         0.54$ GB & $       6$ & $       6$ \\ 
\cmidrule{1-1} 
            ogm-CGC* & $        93.59$ sec & $    -78234.10$ & $    -83272.85$ & $         0.06$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE* & $         7.74$ sec & $         0.00$ & $-\infty$ & $         0.06$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE-CGCF* & $        34.02$ sec & $    -70750.35$ & $-\infty$ & $         0.10$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC* & $        68.29$ sec & $    -78422.82$ & $-\infty$ & $         0.10$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC-CGCF* & $        67.88$ sec & $    -78425.09$ & $-\infty$ & $         0.13$ GB & $       0$ & $       0$ \\ 
 ogm-mcfusion-HC-MC* & $       102.12$ sec & $    -78414.40$ & $-\infty$ & $         0.12$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-HC-MC-CGCF* & $        99.16$ sec & $    -78418.71$ & $-\infty$ & $         0.14$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-WS-BASE* & $         1.20$ sec & $         0.00$ & $-\infty$ & $         0.03$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-BASE-CGCF* & $        99.82$ sec & $    -78252.24$ & $-\infty$ & $         0.07$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-CGC* & $       420.51$ sec & $    -78434.90$ & $-\infty$ & $         0.04$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-CGC-CGCF* & $       442.00$ sec & $    -78455.68$ & $-\infty$ & $         0.08$ GB & $       0$ & $       0$ \\ 
 ogm-mcfusion-WS-MC* & $      1456.53$ sec & $    -78438.50$ & $-\infty$ & $         0.12$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-WS-MC-CGCF* & $      1492.79$ sec & $    -78452.38$ & $-\infty$ & $         0.14$ GB & $       4$ & $       0$ \\ 
\bottomrule
\end{tabular}
\end{table}

### 2014-10-13 paper/tables/knott-3d-550.tex

\begin{table}[H]
\scriptsize
\centering
\caption{knott-3d-550 (8 instances)}
\label{tab:smalltable-knott-3d-550}
\begin{tabular}{lrrrrrr}
\toprule
           algorithm &       runtime     &         value &         bound &           mem &     best &      opt   \\ \midrule 
             ogm-ICM & $      2787.19$ sec & $   -126335.53$ & $-\infty$ & $         0.06$ GB & $       0$ & $       0$ \\ 
              ogm-KL & $       604.50$ sec & $   -127032.70$ & $-\infty$ & $         0.06$ GB & $       0$ & $       0$ \\ 
            ogm-LF-1 & $       987.28$ sec & $   -126356.35$ & $-\infty$ & $         0.07$ GB & $       0$ & $       0$ \\ 
\cmidrule{1-1} 
              MCR-CC & $     68016.21$ sec & $     -8187.14$ & $   -144703.64$ & $         1.20$ GB & $       0$ & $       0$ \\ 
           MCR-CCFDB & $     53527.56$ sec & $     -8187.14$ & $   -144703.64$ & $         0.47$ GB & $       0$ & $       0$ \\ 
       MCR-CCFDB-OWC & $     53386.77$ sec & $     -8187.14$ & $   -144703.64$ & $         0.47$ GB & $       0$ & $       0$ \\ 
\cmidrule{1-1} 
     MCI-CCFDB-CCIFD & $     53404.59$ sec & $     -8187.14$ & $   -144703.64$ & $         0.47$ GB & $       0$ & $       0$ \\ 
             MCI-CCI & $      3436.37$ sec & $   -101592.17$ & $   -136714.73$ & $         1.53$ GB & $       2$ & $       2$ \\ 
           MCI-CCIFD & $      3299.31$ sec & $   -120874.65$ & $   -136699.49$ & $         0.86$ GB & $       2$ & $       2$ \\ 
\cmidrule{1-1} 
            ogm-CGC* & $       595.15$ sec & $   -136188.55$ & $   -144703.64$ & $         0.11$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE* & $        17.17$ sec & $         0.00$ & $-\infty$ & $         0.11$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-BASE-CGCF* & $       118.24$ sec & $   -123617.74$ & $-\infty$ & $         0.19$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC* & $       208.48$ sec & $   -136454.21$ & $-\infty$ & $         0.21$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-CGC-CGCF* & $       205.22$ sec & $   -136472.89$ & $-\infty$ & $         0.27$ GB & $       0$ & $       0$ \\ 
 ogm-mcfusion-HC-MC* & $       300.08$ sec & $   -136449.81$ & $-\infty$ & $         0.22$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-HC-MC-CGCF* & $       291.88$ sec & $   -136468.45$ & $-\infty$ & $         0.27$ GB & $       1$ & $       0$ \\ 
ogm-mcfusion-WS-BASE* & $         2.32$ sec & $         0.00$ & $-\infty$ & $         0.05$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-BASE-CGCF* & $       568.33$ sec & $   -136191.25$ & $-\infty$ & $         0.14$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-CGC* & $      1694.84$ sec & $   -136441.96$ & $-\infty$ & $         0.07$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-CGC-CGCF* & $      1900.61$ sec & $   -136491.63$ & $-\infty$ & $         0.15$ GB & $       0$ & $       0$ \\ 
 ogm-mcfusion-WS-MC* & $      3617.78$ sec & $   -136435.37$ & $-\infty$ & $         0.23$ GB & $       0$ & $       0$ \\ 
ogm-mcfusion-WS-MC-CGCF* & $      3773.77$ sec & $   -136494.37$ & $-\infty$ & $         0.28$ GB & $       4$ & $       0$ \\ 
\bottomrule
\end{tabular}
\end{table}

### 2014-10-23 paper/scatterplots/image-seg.tex
tables and plots

\begin{tikzpicture}
  \begin{loglogaxis}[
    xlabel = {runtime},
    ylabel = {distance to optimum/best},
    xlabel style={name=xlabel},
    mark size=1pt,
    every axis/.append style={font=\tiny}, 
    width = 0.95\textwidth, 
    height= 0.95\textwidth, 
    legend style = { at={(xlabel.south)}, yshift=-1ex, anchor=north,legend cell align=left, font=\tiny},  
    legend columns = 4 
   ]
  \addplot[only marks, mark=*,red, line width=\thickline,opacity=0.8] table[x=Togm_CGC_planar, y=Vogm_CGC_planar]{\scatterplotpath image-seg.data}; 
  \addlegendentry{CGC-planar};   
  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath image-seg.data}; 
  \addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath image-seg.data}; 
  \addlegendentry{ogm-KL};   
  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath image-seg.data}; 
  \addlegendentry{ogm-LF-1};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-HC-B};   
  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-HC-B-CGC};   
  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-HC-CGC-CGC};   
  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-HC-MC-CGC};   
  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-WS-B};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-WS-B-CGC};   
  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-WS-CGC};   
  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-WS-CGC-CGC};   
  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-WS-MC};   
  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath image-seg.data}; 
  \addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath image-seg.data}; 
  \addlegendentry{MCR-CC};   
  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath image-seg.data}; 
  \addlegendentry{MCR-CCFDB};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath image-seg.data}; 
  \addlegendentry{MCR-CCFDB-OWC};   
  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath image-seg.data}; 
  \addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath image-seg.data}; 
  \addlegendentry{MCI-CCI};   
  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath image-seg.data}; 
  \addlegendentry{MCI-CCIFD};   
  \end{loglogaxis} 
\end{tikzpicture}

### 2014-10-23 paper/scatterplots/knott-3d-300.tex
tables and plots

\begin{tikzpicture}
  \begin{loglogaxis}[
    xlabel = {runtime},
    ylabel = {distance to optimum/best},
    xlabel style={name=xlabel},
    mark size=1pt,
    every axis/.append style={font=\tiny}, 
    width = 0.95\textwidth, 
    height= 0.95\textwidth, 
    legend style = { at={(xlabel.south)}, yshift=-1ex, anchor=north,legend cell align=left, font=\tiny},  
    legend columns = 4 
   ]
  \addplot[only marks, mark=*,red, line width=\thickline,opacity=0.8] table[x=Togm_CGC, y=Vogm_CGC]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{CGC};   
  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{ogm-KL};   
  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{ogm-LF-1};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-HC-B};   
  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-HC-B-CGC};   
  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-HC-CGC-CGC};   
  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-HC-MC-CGC};   
  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-WS-B};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-WS-B-CGC};   
  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-WS-CGC};   
  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-WS-CGC-CGC};   
  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-WS-MC};   
  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{MCR-CC};   
  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{MCR-CCFDB};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{MCR-CCFDB-OWC};   
  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{MCI-CCI};   
  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath knott-3d-300.data}; 
  \addlegendentry{MCI-CCIFD};   
  \end{loglogaxis} 
\end{tikzpicture}

### 2014-10-23 paper/scatterplots/modularity-clustering.tex
tables and plots

\begin{tikzpicture}
  \begin{loglogaxis}[
    xlabel = {runtime},
    ylabel = {distance to optimum/best},
    xlabel style={name=xlabel},
    mark size=1pt,
    every axis/.append style={font=\tiny}, 
    width = 0.95\textwidth, 
    height= 0.95\textwidth, 
    legend style = { at={(xlabel.south)}, yshift=-1ex, anchor=north,legend cell align=left, font=\tiny},  
    legend columns = 4 
   ]
  \addplot[only marks, mark=*,red, line width=\thickline,opacity=0.8] table[x=Togm_CGC, y=Vogm_CGC]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{CGC};   
  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{ogm-KL};   
  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{ogm-LF-1};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-HC-B};   
  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-HC-B-CGC};   
  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-HC-CGC-CGC};   
  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-HC-MC-CGC};   
  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-WS-B};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-WS-B-CGC};   
  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-WS-CGC};   
  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-WS-CGC-CGC};   
  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-WS-MC};   
  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{MCR-CC};   
  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{MCR-CCFDB};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{MCR-CCFDB-OWC};   
  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{MCI-CCI};   
  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath modularity-clustering.data}; 
  \addlegendentry{MCI-CCIFD};   
  \end{loglogaxis} 
\end{tikzpicture}

### 2014-10-23 paper/scatterplots/seg-3d.tex
tables and plots

\begin{tikzpicture}
  \begin{loglogaxis}[
    xlabel = {runtime},
    ylabel = {distance to optimum/best},
    xlabel style={name=xlabel},
    mark size=1pt,
    every axis/.append style={font=\tiny}, 
    width = 0.95\textwidth, 
    height= 0.95\textwidth, 
    legend style = { at={(xlabel.south)}, yshift=-1ex, anchor=north,legend cell align=left, font=\tiny},  
    legend columns = 4 
   ]
  \addplot[only marks, mark=*,red, line width=\thickline,opacity=0.8] table[x=Togm_CGC, y=Vogm_CGC]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{CGC};   
  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{ogm-KL};   
  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{ogm-LF-1};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-HC-B};   
  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-HC-B-CGC};   
  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-HC-CGC-CGC};   
  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-HC-MC-CGC};   
  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-WS-B};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-WS-B-CGC};   
  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-WS-CGC};   
  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-WS-CGC-CGC};   
  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-WS-MC};   
  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{MCR-CC};   
  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{MCR-CCFDB};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{MCR-CCFDB-OWC};   
  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{MCI-CCI};   
  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath seg-3d.data}; 
  \addlegendentry{MCI-CCIFD};   
  \end{loglogaxis} 
\end{tikzpicture}

### 2014-10-23 paper/scatterplots/knott-3d-150.tex

\begin{tikzpicture}
  \begin{loglogaxis}[
    xlabel = {runtime},
    ylabel = {distance to optimum/best},
    xlabel style={name=xlabel},
    mark size=1pt,
    every axis/.append style={font=\tiny}, 
    width = 0.95\textwidth, 
    height= 0.95\textwidth, 
    legend style = { at={(xlabel.south)}, yshift=-1ex, anchor=north,legend cell align=left, font=\tiny},  
    legend columns = 4 
   ]
  \addplot[only marks, mark=*,red, line width=\thickline,opacity=0.8] table[x=Togm_CGC, y=Vogm_CGC]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{CGC};   
  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{ogm-KL};   
  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{ogm-LF-1};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-HC-B};   
  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-HC-B-CGC};   
  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-HC-CGC-CGC};   
  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-HC-MC-CGC};   
  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-WS-B};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-WS-B-CGC};   
  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-WS-CGC};   
  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-WS-CGC-CGC};   
  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-WS-MC};   
  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{MCR-CC};   
  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{MCR-CCFDB};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{MCR-CCFDB-OWC};   
  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{MCI-CCI};   
  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath knott-3d-150.data}; 
  \addlegendentry{MCI-CCIFD};   
  \end{loglogaxis} 
\end{tikzpicture}

### 2014-10-23 paper/scatterplots/knott-3d-450.tex

\begin{tikzpicture}
  \begin{axis}[
    xlabel = {runtime},
    ylabel = {distance to optimum/best},
    xlabel style={name=xlabel},
    mark size=1pt,
  %  xmax = 400,
  %  ymax = 1000,
    every axis/.append style={font=\tiny}, 
    width = 0.95\textwidth, 
    height= 0.95\textwidth, 
    legend style = { at={(xlabel.south)}, yshift=-1ex, anchor=north,legend cell align=left, font=\tiny},  
    legend columns = 4 
   ]
  \addplot[only marks, mark=*,red, line width=\thickline,opacity=0.8] table[x=Togm_CGC, y=Vogm_CGC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{CGC};   
  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{ogm-ICM};   
  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{ogm-KL};   
  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{ogm-LF-1};   
  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-B};   
  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-B-CGC};   
  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-CGC};   
  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-CGC-CGC};   
  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-MC};   
  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-HC-MC-CGC};   
  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-B};   
  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-B-CGC};   
  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-CGC};   
  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-CGC-CGC};   
  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-MC};   
  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{DYNCC-WS-MC-CGC};   
  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCR-CC};   
  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCR-CCFDB};   
  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCR-CCFDB-OWC};   
  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCI-CCFDB-CCIFD};   
  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCI-CCI};   
  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath knott-3d-450.data}; 
  \addlegendentry{MCI-CCIFD};   
  \end{axis} 
\end{tikzpicture}

### 2014-10-23 src/interfaces/python/examples/mmcw.py
fuba wuhuwuwu

@@ -1,0 +1,85 @@
+import opengm
+import numpy
+#---------------------------------------------------------------
+# MinSum  with SelfFusion
+#---------------------------------------------------------------
+numpy.random.seed(42)
+
+#gm=opengm.loadGm("/home/tbeier/datasets/image-seg/3096.bmp.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/image-seg/175032.bmp.h5","gm")
+gm=opengm.loadGm("/media/tbeier/TOSHIBA EXT/small_mmwc_gm","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/image-seg/148026.bmp.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_102.h5","gm")#(ROTTEN)
+#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-300/gm_knott_3d_078.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-150/gm_knott_3d_038.h5","gm")
+
+#---------------------------------------------------------------
+# Minimize
+#---------------------------------------------------------------
+#get an instance of the optimizer / inference-algorithm
+
+
+
+print gm
+
+
+
+
+verbose = True
+useRC = True
+
+
+with opengm.Timer("with new method"):
+
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False)
+    randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.500000001,ignoreSeed=False)
+    parallelProposals = 1
+    arg = None
+
+
+
+
+    if useRC:
+        proposalParam = opengm.InfParam(
+            randomizer = randomizer,
+            stopWeight=-0.0,
+            nodeStopNum=0.1,
+            ignoreNegativeWeights=False,
+            setCutToZero=False
+        )
+        
+        bv =  opengm.BoolVector()
+        bv.append(True)
+        bv.append(True)
+
+        infParam = opengm.InfParam(
+            numStopIt=50,
+            numIt=50,
+            generator='randomizedHierarchicalClustering',
+            proposalParam=proposalParam,
+            fusionParam = fusionParam,
+            parallelProposals=parallelProposals,
[…]

### 2014-10-23 src/interfaces/python/examples/mmcw.py
cout for niko

@@ -7,7 +7,7 @@ numpy.random.seed(42)
 
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/3096.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/175032.bmp.h5","gm")
-gm=opengm.loadGm("/media/tbeier/TOSHIBA EXT/small_mmwc_gm","gm")
+gm=opengm.loadGm("/media/tbeier/TOSHIBA EXT/bigger_mmwc_gm","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/148026.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_102.h5","gm")#(ROTTEN)
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
@@ -43,8 +43,8 @@ with opengm.Timer("with new method"):
     if useRC:
         proposalParam = opengm.InfParam(
             randomizer = randomizer,
-            stopWeight=-0.0,
-            nodeStopNum=0.1,
+            stopWeight=-1000000.0,
+            nodeStopNum=0.01,
             ignoreNegativeWeights=False,
             setCutToZero=False
         )
@@ -52,7 +52,7 @@ with opengm.Timer("with new method"):
         bv =  opengm.BoolVector()
         bv.append(True)
         bv.append(True)
-
+        bv.append(False)
         infParam = opengm.InfParam(
             numStopIt=50,
             numIt=50,

### 2014-10-23 paper/egpaper_for_review.tex
nativ multicuts without a gm
fixed nasty bug
up paper
tables and plots
add anytime plots

@@
 \usepackage{amssymb}
+\usepackage{xspace}
+\usepackage{booktabs}
 
@@
 \usepackage{tikz,pgfplots}
+\usepackage{pgfplotstable}
+\usepackage{filecontents}
 \usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
@@
 \usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
+\usetikzlibrary{calc, matrix, backgrounds}
+
+\pgfplotsset{every axis/.append style={
+  every axis y label/.style = {at={(ticklabel cs:0.5)}, rotate=90, anchor=south},
+  axis x line = {bottom},
+  axis y line = {left},
+  tick align = outside,
+  ymajorgrids = true,
+%  legend style = {draw=none, at={(1.05, 0.5)}, anchor=west, font=\small},
+  legend style = {font=\tiny},
+  legend columns = 1,
+  every axis plot/.append style = {line width=1pt},
+  label style = {font=\small},
+  tick label style={font=\small},
+  scaled ticks = false,
+}}
+
 \usepackage{tkz-berge}
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+\def\arraystretch{0.8}
+\renewcommand{\tabcolsep}{2pt}
+\newcommand{\thickline}{2pt}
+\newcommand{\scatterplotpath}{./scatterplots/}
 
@@
 We stop when a certain number of nodes is reached, or the
-largest edge weight is smaller then a certain threshold.
+largest edge weight among the not yet contracted edges is smaller then a certain threshold.
 To get versatile proposals we either add noise 
@@
 \subsection{Benchmark Models}
+
+\input{tables/anytime/image-seg.tex}
+
+\input{tables/anytime/knott-3d-150.tex}
+
+\input{tables/knott-3d-300.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}
+\begin{semilogxaxis}[
+restrict y to domain=-6000:-4500,
+xlabel = {runtime},
+xmin = 0,
+xmax = 4100,
+%ymin =  75282844.25,
+%ymax =  81774642.015,
+%xtick       = { 1 , 60 , 3600 },
+%xticklabels = { 1 sec. , 1 min.  , 1 hour },
+%ytick       = {75661636, 78718140, 81774643 },
+%yticklabels = {$75661636$, $78718140$, $81774643$ },
+width = 0.9\columnwidth,
+scaled ticks = false
+]
+%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
+%\addlegendentry{HC-CGC}
+
+\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-150.data};
+\addlegendentry{CGC}
+
+\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-150.data};
+\addlegendentry{MCI-CCIFD}
+
+\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-150.data};
+\addlegendentry{MC-Fusion (HC-MC-CGC)}
+
+\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-150.data};
+\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+
+\end{semilogxaxis}
+\end{tikzpicture}
+\caption{knott-3d-150}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}
+\begin{semilogxaxis}[
+restrict y to domain=-40000:-24000,
+xlabel = {runtime},
+xmin = 0,
+xmax = 4100,
+%ymin =  75282844.25,
+%ymax =  81774642.015,
+%xtick       = { 1 , 60 , 3600 },
+%xticklabels = { 1 sec. , 1 min.  , 1 hour },
+%ytick       = {75661636, 78718140, 81774643 },
+%yticklabels = {$75661636$, $78718140$, $81774643$ },
+width = 0.9\columnwidth,
+scaled ticks = false
+]
+\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
+\addlegendentry{HC-CGC}
+
+\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-300.data};
+\addlegendentry{CGC}
+
+\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-300.data};
+\addlegendentry{MCI-CCIFD}
+
+\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-300.data};
+\addlegendentry{MC-Fusion (HC-MC-CGC)}
+
+\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-300.data};
+\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+
+\end{semilogxaxis}
+\end{tikzpicture}
+\caption{knott-3d-300}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}
+\begin{semilogxaxis}[
+restrict y to domain=-80000:-60000,
+xlabel = {runtime},
+xmin = 0,
+xmax = 4100,
+%ymin =  75282844.25,
+%ymax =  81774642.015,
+%xtick       = { 1 , 60 , 3600 },
+%xticklabels = { 1 sec. , 1 min.  , 1 hour },
+%ytick       = {75661636, 78718140, 81774643 },
+%yticklabels = {$75661636$, $78718140$, $81774643$ },
+width = 0.9\columnwidth,
+scaled ticks = false
+]
+\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
+\addlegendentry{HC-CGC}
+
+\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-450.data};
+\addlegendentry{CGC}
+
+\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-450.data};
+\addlegendentry{MCI-CCIFD}
+
+\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-450.data};
+\addlegendentry{MC-Fusion (HC-MC-CGC)}
+
+\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-450.data};
+\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+
+\end{semilogxaxis}
+\end{tikzpicture}
+\caption{knott-3d-450}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}
+\begin{semilogxaxis}[
+restrict y to domain=-10000000:-100000,
+xlabel = {runtime},
+xmin = 0,
+xmax = 4100,
+%ymin =  75282844.25,
+%ymax =  81774642.015,
+%xtick       = { 1 , 60 , 3600 },
+%xticklabels = { 1 sec. , 1 min.  , 1 hour },
+%ytick       = {75661636, 78718140, 81774643 },
+%yticklabels = {$75661636$, $78718140$, $81774643$ },
+width = 0.9\columnwidth,
+scaled ticks = false
+]
+\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
+\addlegendentry{HC-CGC}
+
+\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-550.data};
+\addlegendentry{CGC}
+
+\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-550.data};
+\addlegendentry{MCI-CCIFD}
+
+\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-550.data};
+\addlegendentry{MC-Fusion (HC-MC-CGC)}
+
+\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-550.data};
+\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+
+\end{semilogxaxis}
+\end{tikzpicture}
+\caption{knott-3d-550}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{figure}[H]
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}
+\begin{semilogxaxis}[
+%restrict y to domain=-10000000:-100000,
+xlabel = {runtime},
+xmin = 0,
+xmax = 4100,
+%ymin =  75282844.25,
+%ymax =  81774642.015,
+%xtick       = { 1 , 60 , 3600 },
+%xticklabels = { 1 sec. , 1 min.  , 1 hour },
+%ytick       = {75661636, 78718140, 81774643 },
+%yticklabels = {$75661636$, $78718140$, $81774643$ },
+width = 0.9\columnwidth,
+scaled ticks = false
+]
+\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
+\addlegendentry{HC-CGC}
+
+\addplot[color=red,mark=x] table[x=time,y=CGC]{data/seg-3d.data};
+\addlegendentry{CGC}
+
+\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/seg-3d.data};
+\addlegendentry{MCI-CCIFD}
+
+\addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
+\addlegendentry{MC-Fusion (HC-MC-CGC)}
+
+\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/seg-3d.data};
+\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+
+\end{semilogxaxis}
+\end{tikzpicture}
+\caption{seg-3d}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{tables/anytime/knott-3d-450.tex}
+\begin{figure*}
+\input{scatterplots/knott-3d-450.tex}
+\end{figure*}
+
+\input{tables/knott-3d-550.tex}
+
+\input{tables/anytime/seg-3d.tex}
+
+\input{tables/modularity-clustering.tex}
+
 \subsection{Pixel-wise Multicuts}

### 2014-10-23 paper/egpaper_for_review.tex
add grid parameter search plots

@@
 \section{Experiments}
+
+\subsection{Parameter Choice}
+\begin{figure}
+\centering
+\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time.pdf}}
+\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value.pdf}}
+\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
+  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
+}
+\end{figure}
+
 \subsection{Benchmark Models}

### 2014-10-23 paper/egpaper_for_review.tex
update scatterplot

@@
 \input{tables/anytime/knott-3d-450.tex}
-\begin{figure*}
+\begin{figure}
 \input{scatterplots/knott-3d-450.tex}
-\end{figure*}
+\caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
+A more aggressive one would lead to much faster runtime with only a bit worse values.
+DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
+}
+\end{figure}
 

### 2014-10-23 paper/scatterplots/knott-3d-450.tex
update scatterplot

@@
 \begin{tikzpicture}
-  \begin{axis}[
+  \begin{loglogaxis}[
     xlabel = {runtime},
@@
     mark size=1pt,
-  %  xmax = 400,
-  %  ymax = 1000,
     every axis/.append style={font=\tiny}, 
-    width = 0.95\textwidth, 
-    height= 0.95\textwidth, 
+    width = 0.95\columnwidth, 
+    height= 0.95\columnwidth, 
     legend style = { at={(xlabel.south)}, yshift=-1ex, anchor=north,legend cell align=left, font=\tiny},  
@@
   \addlegendentry{CGC};   
-  \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{ogm-ICM};   
-  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath knott-3d-450.data}; 
+ % \addplot[only marks, mark=*,green, line width=\thickline,opacity=0.8] table[x=Togm_HC, y=Vogm_HC]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{HC};   
+  \addplot[only marks, mark=*,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_HC_CGC, y=Vogm_HC_CGC]{\scatterplotpath knott-3d-450.data}; 
+  \addlegendentry{HC-CGC};   
+  %\addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_icm, y=Vogm_icm]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{ogm-ICM};   
+  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_kl, y=Vogm_kl]{\scatterplotpath knott-3d-450.data}; 
   \addlegendentry{ogm-KL};   
-  \addplot[only marks, mark=*,cyan, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{ogm-LF-1};   
-  \addplot[only marks, mark=*,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-HC-B};   
-  \addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-HC-B-CGC};   
-  \addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-HC-CGC};   
-  \addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
+  %\addplot[only marks, mark=*,black, line width=\thickline,opacity=0.8] table[x=Togm_lf1, y=Vogm_lf1]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{ogm-LF-1};   
+  %\addplot[only marks, mark=*,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE, y=Vogm_mcfusion_HC_BASE]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-HC-B};   
+  %\addplot[only marks, mark=*,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_BASE_CGCF, y=Vogm_mcfusion_HC_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-HC-B-CGC};   
+  %\addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC, y=Vogm_mcfusion_HC_CGC]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-HC-CGC};   
+  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_CGC_CGCF, y=Vogm_mcfusion_HC_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
   \addlegendentry{DYNCC-HC-CGC-CGC};   
-  \addplot[only marks, mark=*,blue!40, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-HC-MC};   
-  \addplot[only marks, mark=*,blue, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
+  %\addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC, y=Vogm_mcfusion_HC_MC]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-HC-MC};   
+  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_HC_MC_CGCF, y=Vogm_mcfusion_HC_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
   \addlegendentry{DYNCC-HC-MC-CGC};   
-  \addplot[only marks, mark=x,red, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-WS-B};   
-  \addplot[only marks, mark=x,green, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-WS-B-CGC};   
-  \addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-WS-CGC};   
-  \addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-WS-CGC-CGC};   
-  \addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-WS-MC};   
-  \addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{DYNCC-WS-MC-CGC};   
-  \addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath knott-3d-450.data}; 
+  %\addplot[only marks, mark=x,orange!50, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE, y=Vogm_mcfusion_WS_BASE]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-WS-B};   
+  %\addplot[only marks, mark=x,cyan, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_BASE_CGCF, y=Vogm_mcfusion_WS_BASE_CGCF]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-WS-B-CGC};   
+  %\addplot[only marks, mark=x,magenta, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC, y=Vogm_mcfusion_WS_CGC]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-WS-CGC};   
+  %\addplot[only marks, mark=x,black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_CGC_CGCF, y=Vogm_mcfusion_WS_CGC_CGCF]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-WS-CGC-CGC};   
+  %\addplot[only marks, mark=x,brown, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC, y=Vogm_mcfusion_WS_MC]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-WS-MC};   
+  %\addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=Togm_mcfusion_WS_MC_CGCF, y=Vogm_mcfusion_WS_MC_CGCF]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{DYNCC-WS-MC-CGC};   
+  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CC, y=VMC_CC]{\scatterplotpath knott-3d-450.data}; 
   \addlegendentry{MCR-CC};   
-  \addplot[only marks, mark=x,yellow!70!black, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{MCR-CCFDB};   
-  \addplot[only marks, mark=x,blue!40, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{MCR-CCFDB-OWC};   
-  \addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath knott-3d-450.data}; 
-  \addlegendentry{MCI-CCFDB-CCIFD};   
-  \addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath knott-3d-450.data}; 
+  %\addplot[only marks, mark=x,blue, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB, y=VMC_CCFDB]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{MCR-CCFDB};   
+  %\addplot[only marks, mark=square*,red, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_OWC, y=VMC_CCFDB_OWC]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{MCR-CCFDB-OWC};   
+  %\addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCFDB_CCIFD, y=VMC_CCFDB_CCIFD]{\scatterplotpath knott-3d-450.data}; 
+  %\addlegendentry{MCI-CCFDB-CCIFD};   
+  \addplot[only marks, mark=square*,orange!50, line width=\thickline,opacity=0.8] table[x=TMC_CCI, y=VMC_CCI]{\scatterplotpath knott-3d-450.data}; 
   \addlegendentry{MCI-CCI};   
-  \addplot[only marks, mark=square*,green, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath knott-3d-450.data}; 
+  \addplot[only marks, mark=square*,cyan, line width=\thickline,opacity=0.8] table[x=TMC_CCIFD, y=VMC_CCIFD]{\scatterplotpath knott-3d-450.data}; 
   \addlegendentry{MCI-CCIFD};   
-  \end{axis} 
+  \end{loglogaxis} 
 \end{tikzpicture}

### 2014-10-24 paper/egpaper_for_review.tex
comments and data

@@
 \include{my_macros.tex}
-\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
+%\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
+\title{Fusion Moves for Correlation Clustering}
 
@@
 \section{Introduction}
+
+\begin{itemize}
+  \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
+  \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
+  \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
+\end{itemize}
 
@@
 
+\textbf{Contribution:}
+
+\textbf{Outline:}
+
 %-------------------------------------------------------------------------
 
-\subsection{Related Work}
-
-\subsubsection{Multicut Objective}
-
-The multicut / correlation clustering objective 
-can be formulated in different ways.
-
-\paragraph{Edge Indicator Variables:}
-\begin{center}
-    \begin{eqnarray}
-        y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
-        s.t.:& & y \in \textit{Multicut Polytope} \nonumber
-    \end{eqnarray}
-\end{center}
-
-\paragraph{Fully Connected Graph:}
-\begin{center}
-    \begin{eqnarray}
-        y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
-        s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
-    \end{eqnarray}
-\end{center}
-
-\paragraph{Node Coloring:}
+\subsection{Problem Formulation}
 \begin{center}
@@
 
-\subsubsection{Solver for the Multicut Objective}
+Problem-> Ambiguity
+
+% \subsubsection{Multicut Objective}
+
+% The multicut / correlation clustering objective 
+% can be formulated in different ways.
+
+% \paragraph{Edge Indicator Variables:}
+% \begin{center}
+%     \begin{eqnarray}
+%         y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
+%         s.t.:& & y \in \textit{Multicut Polytope} \nonumber
+%     \end{eqnarray}
+% \end{center}
+
+% \paragraph{Fully Connected Graph:}
+% \begin{center}
+%     \begin{eqnarray}
+%         y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
+%         s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
+%     \end{eqnarray}
+% \end{center}
+
+% \paragraph{Node Coloring:}
+% \begin{center}
+%     \begin{eqnarray}
+%         l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
+%         y_{ij}^* &=& [l_{u} \neq l_{v}]  
+%     \end{eqnarray}
+% \end{center}
+
+\subsection{Related Work}
+
+% \subsubsection{Solver for the Multicut Objective}
 
@@
 
+\subsubsection{Correlation Clustering}
    \begin{itemize}
@@
 
-\subsection{Karger-Stein Algorithms}
-Use randomized procedure to reduce the number of nodes / edges to a reasonable 
-number.
-On the smaller graph, more expensive solvers are used.
+% \subsection{Karger-Stein Algorithms}
+% Use randomized procedure to reduce the number of nodes / edges to a reasonable 
+% number.
+% On the smaller graph, more expensive solvers are used.
 
 %------------------------------------------------------------------------
-\section{Intersection Fusion Cut}
+\section{Correlation-Clustering-Fusion (CCF) Moves}
+Motivation Using Fusion moves -> problem ambiguity
+
+\input{inputs/fig_alg_graph.tex}
+
+\subsection{Define Fusion on Segmentations}
+\input{inputs/fig_move_graph.tex}
 
@@
 
-\input{inputs/fig_alg_graph.tex}
-
-\input{inputs/fig_move_graph.tex}
-
 %-------------------------------------------------------------------------
 \subsection{Proposal Generators}
+
+\textbf{Desired Properties}
 
@@
 
+\subsection{Polyhedral Interpretation}
+
 %-------------------------------------------------------------------------
@@
 
-\input{tables/anytime/image-seg.tex}
+\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[p]
+\centering
+\begin{tikzpicture}
+\begin{semilogxaxis}[
+restrict y to domain=0:4600,
+xlabel = {runtime},
+xmin = 0,
+xmax = 4100,
+%ymin =  75282844.25,
+%ymax =  81774642.015,
+%xtick       = { 1 , 60 , 3600 },
+%xticklabels = { 1 sec. , 1 min.  , 1 hour },
+%ytick       = {75661636, 78718140, 81774643 },
+%yticklabels = {$75661636$, $78718140$, $81774643$ },
+width = 0.9\columnwidth,
+scaled ticks = false
+]
+%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
+%\addlegendentry{HC-CGC}
 
-\input{tables/anytime/knott-3d-150.tex}
+\addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data/image-seg.data};
+\addlegendentry{CGC-planar}
 
-\input{tables/knott-3d-300.tex}
+\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/image-seg.data};
+\addlegendentry{MCI-CCIFD}
 
+\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/image-seg.data};
+\addlegendentry{MC-Fusion (HC-MC-CGC)}
+
+\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/image-seg.data};
+\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+
+\end{semilogxaxis}
+\end{tikzpicture}
+\caption{image-seg}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[H]
+\begin{figure}[p]
 \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[H]
+\begin{figure}[p]
 \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{figure}[H]
-\begin{figure}[H]
+\begin{figure}[p]
 \centering
@@
 %restrict y to domain=-10000000:-100000,
+restrict y to domain=-10000000:700000,
 xlabel = {runtime},
@@
 
+%\addplot[color=yellow,mark=o] table[x=time, y=DYNCC-HC-MC]{data/seg-3d.data};
+%\addlegendentry{MC-Fusion (HC-MC)}
+
 \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
@@
 
-\input{tables/anytime/knott-3d-450.tex}
 \begin{figure}
@@
 \end{figure}
-
-\input{tables/knott-3d-550.tex}
-
-\input{tables/anytime/seg-3d.tex}
-
-\input{tables/modularity-clustering.tex}
 
@@
 
+\newpage
+\onecolumn
+\section{Appendix}
+
+\input{tables/anytime/image-seg.tex}
+\input{tables/anytime/knott-3d-150.tex}
+\input{tables/knott-3d-300.tex}
+\input{tables/anytime/knott-3d-450.tex}
+\input{tables/knott-3d-550.tex}
+\input{tables/anytime/seg-3d.tex}
+\input{tables/modularity-clustering.tex}
+
 \end{document}

### 2014-10-24 paper/alg_graph.tex
minor changes

@@
     \draw node[opBox] (gen) {GENERATOR};
-    \draw node[cutNode,right = 1cm of gen] (proposal_cut) {$\bar{P}$};
+    \draw node[cutNode,right = 1cm of gen] (proposal_cut) {$\bar{y}$};
     \draw node[right of = proposal_cut](dummy){};
-    \draw node[cutNode,right of = dummy] (best_cut) {$P$};
+    \draw node[cutNode,right of = dummy] (best_cut) {$y$};
     \draw node[opBox,below of = dummy] (intersect) {INTERSECT\\UNCUT};
-    \draw node[cutNode,below of = intersect] (int_cut){$\tilde{P}$};
+    \draw node[cutNode,below of = intersect] (int_cut){$\tilde{y}$};
     \draw node[opBox,below of = int_cut] (contract) {CONTRACT\\UNCUT\\EDGES};
-    \draw node[gNode,right = 2cm of contract](cgraph)  {$( \tilde{\mathcal{G}}, \tilde{\mathcal{W}})$};
+    \draw node[gNode,right = 2cm of contract](cgraph)  {$( \tilde{\mathcal{G}}, \tilde{\mathcal{w}})$};
     \draw node[opBox, above of =  cgraph] (multicut) {MULTICUT};
-    \draw node[cutNode,above of = multicut] (rcut) {$\bar{P}^{\tilde{\mathcal{G}}}$};
+    \draw node[cutNode,above of = multicut] (rcut) {$\bar{w}^{\tilde{\mathcal{G}}}$};
     \draw node[opBox, above of =  rcut] (pback) {PROJECT\\CUT\\BACK};
@@
 
-    \draw node[gNode,below = of gen](graph)  {$( \mathcal{G}, \mathcal{W})$};
+    \draw node[gNode,below = of gen](graph)  {$( \mathcal{G}, \mathcal{w})$};
     \path[]
@@
     The proposed algorithm works in the following way:
-    Given a graph $\mathcal{G}$, edge weights $\mathcal{W}$ and
-    a proposal generator, the current best solution $P$ is iteratively improved.
+    Given a graph $\mathcal{G}$, edge weights $\mathcal{w}$ and
+    a proposal generator, the current best solution $y$ is iteratively improved.
     A proposal generator generates different versatile
-    proposal partitions $\bar{P}$.
-    The proposal  $\bar{P}$ is intersected with $P$ which results in
-    $\tilde{P}$. Contracting each each which is not 
-    cut in $\tilde{P}$ leads to a coarser graph  
+    proposal partitions $\bar{y}$.
+    The proposal  $\bar{y}$ is intersected with $y$ which results in
+    $\tilde{y}$. Contracting each each which is not 
+    cut in $\tilde{y}$ leads to a coarser graph  
     $\tilde{\mathcal{G}} = ( \tilde{\mathcal{V}}, \tilde{\mathcal{E}} )$ 
-    with new edge weights $\tilde{\mathcal{W}}$.
-    If  $\bar{P}$ and $P$ have a small fraction of cut edges, $\tilde{\mathcal{G}}$ will be small ( $|\tilde{\mathcal{V}}| << |\mathcal{V}|$
+    with new edge weights $\tilde{\mathcal{w}}$.
+    If  $\bar{y}$ and $y$ have a small fraction of cut edges, $\tilde{\mathcal{G}}$ will be small ( $|\tilde{\mathcal{V}}| << |\mathcal{V}|$
     and $|\tilde{\mathcal{E}}| << |\mathcal{E}|$).
@@
     faster than on $\tilde{\mathcal{G}}$.
-    It is guaranteed that the optimal multicut partitioning $\bar{P}^{\tilde{\mathcal{G}}}$ on $\tilde{\mathcal{G}}$ projected 
-    back to $\mathcal{G}$ as a lower or equal energy than any of the two input partitions $P$ and $\bar{P}$, 
-    therefore we store the result of fusion as new best state $P$ and repeat the procedure.
+    It is guaranteed that the optimal multicut partitioning $\bar{y}^{\tilde{\mathcal{G}}}$ on $\tilde{\mathcal{G}}$ projected 
+    back to $\mathcal{G}$ as a lower or equal energy than any of the two input partitions $y$ and $\bar{y}$, 
+    therefore we store the result of fusion as new best state $y$ and repeat the procedure.
 }\label{fig:algo_graph}

### 2014-10-24 paper/egpaper_for_review.tex
minor changes

@@
 
-\subsection{Problem Formulation}
+\section{Problem Formulation}
+Def: Graph, weighted graph, cut, multicut
+
 \begin{center}
     \begin{eqnarray}
-        l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
-        y_{ij}^* &=& [l_{u} \neq l_{v}]  
+        l^* &=& \argmin_{L \in \{1,\ldots,|V|\}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \label{eq:nodeproblem}\\
+   %     y_{ij}^* &=& [l_{u} \neq l_{v}] 
+        y^* &=& \argmin_{y \in MC(G)\cap \{0,1\}^{|E|}} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}%\\ 
     \end{eqnarray}
@@
 
-Problem-> Ambiguity
+The exist an surjective mapping from a node-label $l$ to edge-labeling $y$ and
+a bijective mapping from a partitioning of $V$ to vertices of the multicut polytope $MC$.
+Consequently, 
+(i) problems \ref{eq:nodeproblem} and \ref{eq:edgeproblem} are equivalent
+and (ii) the node-labeling is not unique for a given partitioning and introduce some
+ambiguities.
 
@@
 
-\subsection{Related Work}
+\section{Related Work}
 
@@
 
-\subsubsection{Correlation Clustering}
+\subsection{Correlation Clustering}
    \begin{itemize}
@@
 
-\subsubsection{Fusion Moves}
+\subsection{Fusion Moves}
 Move making algorithms, in particular fusion moves, 

### 2014-10-27 paper/egpaper_for_review.tex
update
polytope pic
polyhedral intepreation

@@
 
-\usepackage{tkz-berge}
+%\usepackage{tkz-berge}
 \DeclareMathOperator*{\argmin}{arg\,min}
@@
 %-------------------------------------------------------------------------
+\subsection{Fusion Move Solver}
+
+%-------------------------------------------------------------------------
 \subsection{Proposal Generators}
@@
 \subsection{Polyhedral Interpretation}
-
-%-------------------------------------------------------------------------
-\subsection{Fusion Move Solver}
+\begin{figure}
+\centering
+\input{polytope-tikz.tex}
+\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
+Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
+and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
+When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
+}
+\end{figure}
 
@@
 
-\subsection{Benchmark Models}
+\subsection{Synthetic Models}
+
+\subsection{Real World Models}
 
@@
 
-\subsection{Pixel-wise Multicuts}
-\input{inputs/fig_pixel_mc.tex}
+%\subsection{Pixel-wise Multicuts}
+%\input{inputs/fig_pixel_mc.tex}
 
@@
 
+\newpage
 {\small

### 2014-10-27 paper/egpaper_for_review.tex
added notation
shift theorems
contradict graph
polyherdal section

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{remark}{Remark}
 
@@
 \newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
+\newcommand{\OR}{\textrm{ or }}
 
@@
 \section{Introduction}
+
+\paragraph{Our Notation}
+$G$ Graph.
+$V$ Set of Nodes.
+$E$ Set of Edges.
+$l$ node label.
+$y$ edge label.
+$w$ edge weight
+$MC(G)$ multicut polytope
+$P(G)$ the set of valid edge labeling (MC(G) is convex hull of P(G))
+$y^*$ for opt. labeling
+$G_y=(V_y,E_y)$ contradiction of graph $G$ with respect to $y$
 
@@
 
-\begin{theorem}[NameMe]
-Solving ??? on the contracted graph is 
-equivalent to solving ??? on the 
-original graph with additional 
-must link constraints
-\end{theorem}
-
-\begin{proof}[Proof of theorem ]
-todo
-\end{proof}
-
-\begin{theorem}[NameMe]
-Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{new}$ the solution of \ref{???}.
-$x_{new}$  will never decrease the energy:
-$x_{new} \cdot w \leq  \min( x_{a}\cdot w,  x_{b}\cdot w) $ 
-\end{theorem}
-
-\begin{proof}[Proof of theorem ]
-todo
-\end{proof}
-
-\begin{theorem}[NameMe]
-
-Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{opt}$ the global solution,
-$X_{a}^c, X_{b}^c$ and $ X_{opt}^c$ the set of cut edges in  $x_{a}, x_{b}$  and $ x_{opt}$
-optimal solution.
-Iff  $ X_{opt}^c \subseteq  (X_{a}^c \cup X_{b}^c)$,  the solution of \ref{???} will be $x_{opt}$.
-\end{theorem}
-
-\begin{proof}[Proof of of theorem]
-todo
-\end{proof}
-
 %-------------------------------------------------------------------------
@@
 
-\subsection{Polyhedral Interpretation}
+\subsection{Properties and Polyhedral Interpretation}
+An alternative interpretation of our method is shown in Fig.~\ref{fig:polyheadral}.
+In each iteration the current and proposed segmentation define an inner polyheadral 
+approximation of the original multicut polytope. 
+Optimizing over this polytope is the same problem as the original one, but much smaller.
+Furthermore, the costs does not change and and improvement in the smaller polytope will 
+be the same in the original graph.
+The choice of the proposal defines the shape of the auxiliary polytope. 
+In the given toy example, the first (red) polytope give a huge improvement, the second proposal
+defines the blue polytope which does not lead to an improvement. 
+The third proposal generates the green polytope that includes the global optimal solution.
+
+This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
+which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
+
 \begin{figure}
@@
 }
+\label{fig:polyheadral}
 \end{figure}
+
+\begin{theorem}[Equivalence]
+The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
+is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
+with additional must link constraints ($y^* \leq y$).
+%
+\begin{proof}
+Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
+Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
+\end{proof}
+%
+\end{theorem}
+
+\begin{theorem}[Monotone]
+Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
+Than $y^*$  will never decrease the energy:
+$y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
+%
+\begin{proof}
+The feasible set of the fusion move includes per definition  $y'$ and $y''$.
+If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
+and that why not the propose segmentation of a fusion.
+\end{proof}
+%
+\end{theorem}
+
+\begin{remark}[Fix-point]
+Let $Y$ be the set of possible proposals, than
+$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
+\end{remark}
+
+\begin{remark}[Optimality]
+Let $y'$ be the current and $y''$ the proposed segmentation.
+If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
+\end{remark}
 

### 2014-10-27 paper/egpaper_for_review.tex
future work

@@
 
+%$\rho_y : E \to E_y$
+%$\rho_y^{-1} : E_y \to E$
+
+$\rho_y : P(G) \to P(G_y)$
+
+$\rho_y^{-1} : P(G_y) \to P(G)$
 \begin{itemize}
@@
 
+\section{Further Work}
+So far we have generated the proposals randomly and do not take the current segmentation into account.
+
+So far we only enforce must link constraints to obtain smaller problems.
+One can also enforce must-not link constraints to the problem. 
+If those are closed, they automatically lead to a decomposition of the problem, which is a interesting property for very huge data.
+
 \section{Conclusion}

### 2014-10-28 src/interfaces/python/examples/test_fancy_stuff.py
dmc is working for mc

@@ -7,10 +7,10 @@ numpy.random.seed(42)
 
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/3096.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/175032.bmp.h5","gm")
-gm=opengm.loadGm("/home/tbeier/datasets/image-seg/291000.bmp.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/image-seg/291000.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/148026.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_102.h5","gm")#(ROTTEN)
-#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
+gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-300/gm_knott_3d_078.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-150/gm_knott_3d_038.h5","gm")
 
@@ -23,174 +23,49 @@ gm=opengm.loadGm("/home/tbeier/datasets/image-seg/291000.bmp.h5","gm")
 
 print gm
 
-
-
-
-
-
-
 verbose = True
-useQpbo = True
-useRC = False
-useCgc = False
-useWs = False
-
-
 
 with opengm.Timer("with new method"):
 
-    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False)
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False, decompose=True)
     randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.500000001,ignoreSeed=False)
     parallelProposals = 8
     arg = None
 
 
-    if useWs:
-        print "ws"
-        proposalParam = opengm.InfParam(
-            randomizer = randomizer,
-            ignoreNegativeWeights = False,
-            seedFromNegativeEdges=True,
-            seedFraction = 100.0
-        )
-        infParam = opengm.InfParam(
-            numStopIt=100,
-            numIt=100,
-            generator='randomizedWatershed',
-            proposalParam=proposalParam,
[…]

### 2014-10-28 src/interfaces/python/examples/test_fancy_stuff.py
dmc is working for mc

@@ -10,8 +10,8 @@ numpy.random.seed(42)
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/291000.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/image-seg/148026.bmp.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_102.h5","gm")#(ROTTEN)
-gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
-#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-300/gm_knott_3d_078.h5","gm")
+#gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-450/gm_knott_3d_096.h5","gm")
+gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-300/gm_knott_3d_078.h5","gm")
 #gm=opengm.loadGm("/home/tbeier/datasets/knott-3d-150/gm_knott_3d_038.h5","gm")
 
 #---------------------------------------------------------------
@@ -27,7 +27,7 @@ verbose = True
 
 with opengm.Timer("with new method"):
 
-    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False, decompose=True)
+    fusionParam = opengm.InfParam(fusionSolver = 'multicut', planar=False, decompose=False)
     randomizer = opengm.weightRandomizer(noiseType='normalAdd',noiseParam=1.500000001,ignoreSeed=False)
     parallelProposals = 8
     arg = None
@@ -38,7 +38,7 @@ with opengm.Timer("with new method"):
     proposalParam = opengm.InfParam(
     randomizer = randomizer,
     stopWeight=-0.0,
-    nodeStopNum=0.01,
+    nodeStopNum=0.1,
     ignoreNegativeWeights=False,
     setCutToZero=False
     )
@@ -46,8 +46,8 @@ with opengm.Timer("with new method"):
 
 
     infParam = opengm.InfParam(
-    numStopIt=10,
-    numIt=10,
+    numStopIt=20,
+    numIt=20,
     generator='randomizedHierarchicalClustering',
     proposalParam=proposalParam,
     fusionParam = fusionParam,

### 2014-10-29 paper/egpaper_for_review.tex
worked on text

@@
 
-\todo[inline]{should there be a general introduction to multicuts?}
-
 Given an edge weighted graph, positive weights (\emph{attractive})
@@
     \item for co-segmentation~\cite{glassner_2011_cvpr}
-    \item and to cluster fully connected graphs~\cite{???}.
+    \item and to cluster sparse and graphs~\cite{???}.
 \end{inparaenum}
 
-\todo[inline]{WHY WE NEED THIS NEW SOLVER?}
-
-Nunez-Iglesias \etal describe the multicut as
-\say{one-shot agglomeration of supervoxels} whose 
-main drawback is the scalability \cite{nunez_iglesias_2013}.
-
-\todo[inline]{BETTER MOTIVATE SUPERNODES}
-
-To address scalability, supernodes can be useful.
-To create supernodes, some edges will be contracted
-and their nodes are merged into super-nodes.
-Doing so, we can reduce  the graph 
-to a reasonable size, such that we can find
-global optimal multicut solutions within reasonable time.
-%
-Any edge which is contracted is lost.
-If such an edge is cut in the global optimal solution, we cannot 
-find this global optimal solutions.
-Therefore we avoid fixed decisions and use a
-dynamic energy aware contraction scheme.
-%
-Different edge contractions lead to different super-node graphs.
-A trivial approach is the following.
-Create different super-node graphs, optimize them with multicuts,
-and take the result which leads to the lowest energy
-on the unmodified initial graph.
-% 
-Doing so, we throw away all results which do not have the lowest energy.
-Within this work we propose a framework which 
-combine multiple \emph{proposal} super-node graphs
-without any premature irreversible decisions.
-Furthermore, multiple super-node graphs are combined such
-that the information form all of them is used.
-\todo[inline]{\emph{proposal} super-node graphs sounds shitty}
-%
-The proposed algorithm can be interpreted as a fusion moves
-algorithm for correlation clustering / multicut objective.
-We generate cheap and versatile proposals
-and \emph{fuse} them with the current best solution with the
-guarantee that this cannot increase the energy.
+Despite the nice properties of correlation clustering
+to perform a \say{one-shot agglomeration of supervoxels} ~\cite{nunez_iglesias_2013},
+the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}.
+Existing solvers for correlation clustering do not scale for non planar graphs.
+Even state of the art approximate move making algorithm fail 
+to give good approximations non planar graphs.
+When increasing the problem sizes, either the runtime explodes or the 
+approximations are far away from being useful.
 
 \textbf{Contribution:}
+\begin{inparaenum}[(i)]
+\item Within this work we propose a fast and scalable move making algorithm for correlation clustering,
+\item which generalized  fusion moves \cite{???} to correlation clustering problems.
+\item We reduce the inference to a series of moves where
+each moves optimizes over a subspace spanned by the current best solution
+and a proposal solution.
+\item We propose two versatile proposal generators,
+\item and show how to optimize these moves.
+\item We give a polyhedral interpretation of this algorithm,
+\item and evaluate the proposed method 
+on existing benchmark problems.
+\item We show state of the art any time performance on those instances.
+\end{inparaenum}[(i)]
 
 \textbf{Outline:}
-
+In sec.~\ref{sec:problem_formulation} we will give a 
+detailed problem definition where we introduce 
+the correlation clustering objective.
+In sec.~\ref{sec:related_work} we will 
+discuss existing methods for correlation 
+clustering and briefly explain the concept of fusion moves.
+In sec: ~\ref{sec:cc_fm} we describe our proposed
+method and show the properties of the algorithm.
+In sec.~\ref{sec:exp} we show an evaluation
+of the method on existing parameter  and discuss the effects of parameters.
+Future work will be discussed in sec. \ref{sec:future} and
+we will conclude in ~\ref{sec:conclusion}.
 %-------------------------------------------------------------------------
 
-\section{Problem Formulation}
+\section{Problem Formulation}\label{sec:problem_formulation}
 Def: Graph, weighted graph, cut, multicut
@@
 
-\section{Related Work}
+\section{Related Work}\label{sec:related_work}
 
-% \subsubsection{Solver for the Multicut Objective}
+\subsection{Correlation Clustering}\label{sec:cc}
+A major branch of research has focused on solving 
+relaxations of eq.~\ref{eq:edgeproblem} by linear programming
+or solving  eq.~\ref{eq:edgeproblem} directly to global optimality
+by using integer linear programming in a cutting plane fashion  \cite{kappes_2011_emmcvpr,andres_2011_iccv}.
 
-    \input{inputs/tab_mc_overview.tex}
+Yarkony et al ~\cite{yarkony_2012_eccv} uses 
+a dual decomposition based approach for planar graphs
+where the subproblems are planar max cut instances.
 
-\subsection{Correlation Clustering}
-   \begin{itemize}
-   \item Multicut~\cite{kappes_2011_emmcvpr}
-   \item Expand and Explorer~\cite{bagon_2011_arxiv}
-   \item Fast Planar CC~\cite{yarkony_2012_eccv}
-   \item Break and Conquer \cite{alush_2013_simbad}.
-   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
-   \end{itemize}
+An other branch of research uses move making algorithm 
+to optimize correlation clustering.
+Bansal and Bagon use a modified $\alpha-$expansion \cite{bansal_2004_ml} 
+algorithm suitable for correlation clustering,
+while the state of the art method from  Beier \etal~\cite{beier_2014_cvpr} iteratively re-optimizes the cuts
+between adjacent connected components.
 
-\subsection{Fusion Moves}
+   % \begin{itemize}
+   % \item Multicut~\cite{kappes_2011_emmcvpr}
+   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
+   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
+   % \item Break and Conquer \cite{alush_2013_simbad}.
+   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
+   % \end{itemize}
+
+\subsection{Fusion Moves}\label{sec:fm}
 Move making algorithms, in particular fusion moves, 
@@
 with state of the art any time performance~\cite{kappes_2014_ws}.
+The fusion move algorithm works as follows:
+A current best solution is maintained and proposal solutions 
+are generated.
+Within each move, the variables can choose the label from the current best or from the 
+proposed solution. This problem can be formulated as an 
+optimization problem with a binary label space.
+Any optimal solution of this auxiliary problem is guaranteed
+to not worsen the current best solution.
 
@@
 %------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion (CCF) Moves}
+\section{Correlation-Clustering-Fusion (CCF) Moves}\label{sec:cc_fm}
 Motivation Using Fusion moves -> problem ambiguity
@@
 
-\section{Experiments}
+\section{Experiments}\label{sec:exp}
 
@@
 
-\section{Further Work}
+\section{Further Work}\label{sec:future}
 So far we have generated the proposals randomly and do not take the current segmentation into account.
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusion}
 

### 2014-10-30 paper/egpaper_for_review.tex
w.i.p.

@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
+\usepackage{bm}% ändert \boldsymbol
 \def\arraystretch{0.8}
@@
     \begin{eqnarray}
-        l^* &=& \argmin_{L \in \{1,\ldots,|V|\}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \label{eq:nodeproblem}\\
+        l^* &=& \argmin_{L \in \{1,\ldots,|V|\}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}] \label{eq:nodeproblem}\\
    %     y_{ij}^* &=& [l_{u} \neq l_{v}] 
@@
 
-\input{inputs/fig_alg_graph.tex}
+%\input{inputs/fig_alg_graph.tex}
 
 \subsection{Define Fusion on Segmentations}
+
+Given two proposal solutions $y'$ and $y''$
+the fusion move between those solutions is defined
+as follows:
+
+Let the $\bar{y}$ be the edge wise or of  $y'$ and $y''$.
+\begin{equation}
+\breve{y} =  y' \cup y''.
+\end{equation}
+Contraction of all edges in $G$ where $\bar{y}=0$ defines
+a smaller graph $G_{\bar{y}}$ and the corresponding
+edge weights $W_{\hat{y}}$.
+Any cut $\bar{y}$ on $G_{\hat{y}}$ induces a cut $y$ on $G$.
+The function 
+$\rho_y^{-1}$ maps a cut from $G_{\hat{y}}$  to $G$
+
+\begin{equation}
+   \rho_y^{-1} : P(G_y) \to P(G)
+\end{equation}
+
+Therefore solving eq. \ref{eq:edgeproblem} 
+on $G_{\hat{y}}$
+leads to a cut on $G$ which is guaranteed to 
+to have a better or equal energy
+then any of the two proposal solutions.
+
 \input{inputs/fig_move_graph.tex}
 
-Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
-Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
-but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
-%
-To make multicuts scalable, it is desirable to replace the graph $G$
-with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
-If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.
-%
-A trivial way to reduce the size of the graph  is edge contraction.
-Until a desirable size is reached, one might contract the edge with
-the highest weight. A cut on the contracted graph  $\hat{G}$ is always
-a valid cut on $\hat{G}$.
-%
-On the other hand, if an edge $e$ is contracted, it will never be cut.
-If $e$ is part of the cut in a global optimal solution, we cannot find
-this cut.
-%
-To overcome this problem  we can randomize the edge contraction,
-and repeat this multiple times and remember the best solution.
-%
-But this would throw away all the ``not the best'' solutions (rewrite me).
-Within this work we propose the following nifty trick.
-Instead of throwing away solutions, we intersect them with the 
-best solution, and solve the multicut on the resulting
-graph.
-Therefore we fuse multiple solutions,
+% Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
+% Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
+% but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
+
+% To make multicuts scalable, it is desirable to replace the graph $G$
+% with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
+% If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.
+
+% A trivial way to reduce the size of the graph  is edge contraction.
+% Until a desirable size is reached, one might contract the edge with
+% the highest weight. A cut on the contracted graph  $\hat{G}$ is always
+% a valid cut on $\hat{G}$.
+
+% On the other hand, if an edge $e$ is contracted, it will never be cut.
+% If $e$ is part of the cut in a global optimal solution, we cannot find
+% this cut.
+
+% To overcome this problem  we can randomize the edge contraction,
+% and repeat this multiple times and remember the best solution.
+
+% But this would throw away all the ``not the best'' solutions (rewrite me).
+% Within this work we propose the following nifty trick.
+% Instead of throwing away solutions, we intersect them with the 
+% best solution, and solve the multicut on the resulting
+% graph.
+% Therefore we fuse multiple solutions,
 
@@
 \caption{Fusion Based Algorithms}\label{alg:fusion}
+
 \begin{algorithmic}[1]
@@
 \subsection{Fusion Move Solver}
+
+\begin{center}
+    \begin{eqnarray}
+        y 
+        &=& 
+        \rho_{\hat{y}}^{-1}(
+        \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
+        \sum_{ (i,j) \in E_{\hat{y}} } 
+        w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
+    \end{eqnarray}
+\end{center}
+
+\begin{center}
+    \begin{eqnarray}
+      y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
+    \end{eqnarray}
+\end{center}
 
@@
 
-\begin{remark}[Fix-point]
+\begin{remark}[Fix-point (pointless to me)]
 Let $Y$ be the set of possible proposals, than

### 2014-10-31 paper/egpaper_for_review.tex
text social networks

@@
 
+\subsection{Social Networks}
+A application for large scale correlation clustering are social networks.
+We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{http://snap.stanford.edu/data/index.html}.
+Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
+%
+The first network is called \emph{Epinions}. 
+This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
+Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ is the edge-weight is positive or negative, respectively.
+The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
+%
+The first network is called \emph{Slashdot}. 
+Slashdot is a technology-related news website know for its specific user community. 
+In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
+The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.
+
+We consider the problem to cluster this graphs such that positively weighted edges link inside and negatively weighted between clusters.
+In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
+% 
+To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
+\begin{align}
+  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
+\end{align}
+We define the following energy function
+\begin{align}
+ J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
+      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
+\end{align}
+which is zero if the given partitioning does not violated any relation and larger otherwise.
+
 \subsection{Real World Models}

### 2014-11-02 paper/egpaper_for_review.tex
inital version of descripton of 3d models

@@
 \subsection{Real World Models}
+An example for large scale correlation clustering is 
+segmentation of region adjacency graphs (RAG) for
+3D closed surface segmentation of neural tissue data 
+\cite{kroeger_2012_eccv}.
+The energy is based on a likelihood of merging adjacent super-voxels.
+Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
+or to merge them ($p(y_{ij} = 0)$).
+The energy function is defined as following.
+\begin{align}
+ J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
+\end{align}
+Where $\beta$ is used as a prior.
+Models of different size are included in the graphical model
+benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr} (???).
+We use models with the cube sizes $300^3$, $450^3$, $550^3$ and $900^3$.
+The number of variables varies from ??? to ???, and the number
+of edges from ??? to ???.
+
+\begin{center}
+    \begin{figure}
+        \begin{center}
+            \begin{subfigure}[b]{0.45\linewidth}
+                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
+            \end{subfigure}
+            \quad
+            \begin{subfigure}[b]{0.45\linewidth}
+                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
+            \end{subfigure}
+        \end{center}
+    \caption{
+        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv}
+    }
+    \end{figure}
+\end{center}
 

### 2014-11-05 paper/egpaper_for_review.tex
wip

@@
 
+\newcommand{\realplot}[1]{
+\begin{tikzpicture}
+    \begin{axis}
+        \addlegendimage{empty legend}\addlegendentry{Matrix #1}
+        \addplot {0};
+        \addplot {1};
+        \addplot {2};
+        \addplot {3};
+    \end{axis}
+\end{tikzpicture}}
+
 % Pages are numbered in submission mode, and unnumbered in camera-ready
@@
 
-\begin{algorithm}
-\begin{scriptsize}
-\caption{Fusion Based Algorithms}\label{alg:fusion}
-
-\begin{algorithmic}[1]
-\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
-\State $x^0 \gets \textrm{initial state form } X$
-\State $n \gets 0 $                                 \Comment{Number of moves}
-\State $m \gets 0 $                                 \Comment{Number of moves without progress}
-\While{$m < m_{\max}$ and $n < n_{\max}$ }
-\State $n \gets n+1$ 
- \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
- \If{$J(x^{n-1}) \leq J(x')$}                       
-   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
- \Else
-   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
- \EndIf
- \If{$J(x^{n}) \leq J(x^{n-1})$}
-   \State $m \gets 0$                                 \Comment{Reset counter}
- \Else
-   \State $m \gets m+1$                               \Comment{Increment counter}
- \EndIf
-\EndWhile
-\State \textbf{return} $x^n$
-\EndProcedure
-\end{algorithmic}
-\end{scriptsize}
-\end{algorithm}
-
-\begin{algorithm}
-\begin{scriptsize}
-\caption{Fusion Moves}\label{alg:fusion_moves}
-\scriptsize
-\begin{algorithmic}[1]
-\Require $J(x) \leq J(x')$
-\Ensure $J(\hat{x}) \leq J(x)$
-\vspace{0.2cm}
-\Procedure{Fuse}{$x,x',J$}
-\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
-    \Comment{
-        \begin{minipage}{0.4\linewidth} 
-            \begin{tiny}
-            \begin{singlespace}
-                intersect
-                uncut edges in $x$ and $x'$,
-                return  
-                connected component labeling
-            \end{singlespace}
-            \end{tiny}
-        \end{minipage}
-    }
-\vspace{0.1cm}
-\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
-    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
-    \Comment{ 
-        \begin{minipage}{0.2\linewidth} 
-            \begin{tiny}
-            \begin{singlespace}
-                Contract all edges 
-                which are uncut in $\bar{x}$ 
-            \end{singlespace}
-            \end{tiny}
-        \end{minipage}
-    }
-\vspace{0.1cm}
-\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
-    \Comment{ 
-        \begin{minipage}{0.3\linewidth} 
-            \begin{tiny}
-            \begin{singlespace}
-                Solve the multicut objective
-                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
-            \end{singlespace}
-            \end{tiny}
-        \end{minipage}
-    }
-
-\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
-    \Comment{ 
-        \begin{minipage}[\textheight]{0.4\linewidth} 
-            \begin{tiny}
-            \begin{singlespace}
-                Translate the connected component
-                labeling $\tilde{x}^*$ of $\tilde{G}$ 
-                to a connected component labeling of $G$
-            \end{singlespace}
-            \end{tiny}
-        \end{minipage}
-    }
-\State \textbf{return} $\hat{x}$
-\EndProcedure
-\vspace{0.3cm}
-\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
-\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
-\EndProcedure
-\end{algorithmic}
-\end{scriptsize}
-\end{algorithm}
+%\begin{algorithm}
+%\begin{scriptsize}
+%\caption{Fusion Based Algorithms}\label{alg:fusion}
+%
+%
+%
+%
+%\begin{algorithmic}[1]
+%\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
+%\State $x^0 \gets \textrm{initial state form } X$
+%\State $n \gets 0 $                                 \Comment{Number of moves}
+%\State $m \gets 0 $                                 \Comment{Number of moves without progress}
+%\While{$m < m_{\max}$ and $n < n_{\max}$ }
+%\State $n \gets n+1$ 
+% \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
+% \If{$J(x^{n-1}) \leq J(x')$}                       
+%   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
+% \Else
+%   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
+% \EndIf
+% \If{$J(x^{n}) \leq J(x^{n-1})$}
+%   \State $m \gets 0$                                 \Comment{Reset counter}
+% \Else
+%   \State $m \gets m+1$                               \Comment{Increment counter}
+% \EndIf
+%\EndWhile
+%\State \textbf{return} $x^n$
+%\EndProcedure
+%\end{algorithmic}
+%\end{scriptsize}
+%\end{algorithm}
+
+%\begin{algorithm}
+%\begin{scriptsize}
+%\caption{Fusion Moves}\label{alg:fusion_moves}
+%\scriptsize
+%\begin{algorithmic}[1]
+%\Require $J(x) \leq J(x')$
+%\Ensure $J(\hat{x}) \leq J(x)$
+%\vspace{0.2cm}
+%\Procedure{Fuse}{$x,x',J$}
+%\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
+%    \Comment{
+%        \begin{minipage}{0.4\linewidth} 
+%            \begin{tiny}
+%            \begin{singlespace}
+%                intersect
+%                uncut edges in $x$ and $x'$,
+%                return  
+%                connected component labeling
+%            \end{singlespace}
+%            \end{tiny}
+%        \end{minipage}
+%    }
+%\vspace{0.1cm}
+%\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
+%    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
+%    \Comment{ 
+%        \begin{minipage}{0.2\linewidth} 
+%            \begin{tiny}
+%            \begin{singlespace}
+%                Contract all edges 
+%                which are uncut in $\bar{x}$ 
+%            \end{singlespace}
+%            \end{tiny}
+%        \end{minipage}
+%    }
+%\vspace{0.1cm}
+%\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
+%    \Comment{ 
+%        \begin{minipage}{0.3\linewidth} 
+%            \begin{tiny}
+%            \begin{singlespace}
+%                Solve the multicut objective
+%                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
+%            \end{singlespace}
+%            \end{tiny}
+%        \end{minipage}
+%    }
+%
+%\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
+%    \Comment{ 
+%        \begin{minipage}[\textheight]{0.4\linewidth} 
+%            \begin{tiny}
+%            \begin{singlespace}
+%                Translate the connected component
+%                labeling $\tilde{x}^*$ of $\tilde{G}$ 
+%                to a connected component labeling of $G$
+%            \end{singlespace}
+%            \end{tiny}
+%        \end{minipage}
+%    }
+%\State \textbf{return} $\hat{x}$
+%\EndProcedure
+%\vspace{0.3cm}
+%\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
+%\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
+%\EndProcedure
+%\end{algorithmic}
+%\end{scriptsize}
+%\end{algorithm}
 
@@
 
-\begin{algorithm}
-    \begin{scriptsize}
-        \caption{Proposal Generators}\label{alg:proposal_gen}   
-        \begin{algorithmic}[1]
-            %\Require $J(x) \leq J(x')$
-            %\Ensure $J(\hat{x}) \leq J(x)$
-            %\vspace{0.3cm}
-            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
-            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
-
-            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
-            \State \textbf{return} $x'$
-            \EndProcedure
-            %
-            %
-            \vspace{0.3cm}
-            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
-            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-            \State $ getRandomSeeds$
-            \State $ runEdgeWeightedWs$
-            \EndProcedure   
-            %
-            %
-            \vspace{0.3cm}
-            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
-            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
-            \State $\hat{W} \gets W$
-            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
-                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
-                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
-            \EndWhile
-            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
-            \EndProcedure
-        \end{algorithmic}
-    \end{scriptsize}
-\end{algorithm}
+%\begin{algorithm}
+%    \begin{scriptsize}
+%        \caption{Proposal Generators}\label{alg:proposal_gen}   
+%        \begin{algorithmic}[1]
+%            %\Require $J(x) \leq J(x')$
+%            %\Ensure $J(\hat{x}) \leq J(x)$
+%            %\vspace{0.3cm}
+%            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
+%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
+%            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
+%
+%            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
+%            \State \textbf{return} $x'$
+%            \EndProcedure
+%            %
+%            %
+%            \vspace{0.3cm}
+%            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
+%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
+%            \State $ getRandomSeeds$
+%            \State $ runEdgeWeightedWs$
+%            \EndProcedure   
+%            %
+%            %
+%            \vspace{0.3cm}
+%            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
+%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
+%            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
+%            \State $\hat{W} \gets W$
+%            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
+%                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
+%                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
+%            \EndWhile
+%            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
+%            \EndProcedure
+%        \end{algorithmic}
+%    \end{scriptsize}
+%\end{algorithm}
 
@@
 \newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[p]
+\pgfplotsset{every axis legend/.append style={
+at={(1.0,1.2)},
+anchor=north east}} 
+\begin{figure*}
+  \begin{subfigure}[b]{0.33\textwidth}
   \centering
@@
   %yticklabels = {$75661636$, $78718140$, $81774643$ },
-width = 0.9\columnwidth,
-scaled ticks = false
+  width = 1.0\columnwidth,
+  scaled ticks = false,
   ]
@@
   \addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data/image-seg.data};
-\addlegendentry{CGC-planar}
+  %\addlegendentry{CGC-planar}
 
   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/image-seg.data};
-\addlegendentry{MCI-CCIFD}
+  %\addlegendentry{MCI-CCIFD}
 
   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/image-seg.data};
-\addlegendentry{MC-Fusion (HC-MC-CGC)}
+  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
 
   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/image-seg.data};
-\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
 
@@
   \caption{image-seg}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[p]
+  \end{subfigure}
+  \begin{subfigure}[b]{0.33\textwidth}
     \centering
@@
     %yticklabels = {$75661636$, $78718140$, $81774643$ },
-width = 0.9\columnwidth,
+    width = 1.0\columnwidth,
     scaled ticks = false
@@
     %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
-%\addlegendentry{HC-CGC}
-
+    %%\addlegendentry{HC-CGC}
+    %
     \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-150.data};
-\addlegendentry{CGC}
-
+    %\addlegendentry{CGC} 
+    %
     \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-150.data};
-\addlegendentry{MCI-CCIFD}
-
+    %\addlegendentry{MCI-CCIFD} 
+    %
     \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-150.data};
-\addlegendentry{MC-Fusion (HC-MC-CGC)}
-
+    %\addlegendentry{MC-Fusion (HC-MC-CGC)}
+    %
     \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-150.data};
-\addlegendentry{MC-Fusion (HC-CGC-CGC)}
-
+    %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+    %
     \end{semilogxaxis}
@@
     \caption{knott-3d-150}
-\end{figure}
+  \end{subfigure}
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[p]
+  \begin{subfigure}[b]{0.33\textwidth}
   \centering
@@
   %yticklabels = {$75661636$, $78718140$, $81774643$ },
-width = 0.9\columnwidth,
-scaled ticks = false
+  width = 1.0\columnwidth,
+  scaled ticks = false,
+  legend to name = named,
+  legend columns=5
   ]
@@
   \caption{knott-3d-300}
-\end{figure}
+  \end{subfigure}
+  \newline
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[p]
+  \begin{subfigure}[b]{0.33\textwidth}
   \centering
@@
   %yticklabels = {$75661636$, $78718140$, $81774643$ },
-width = 0.9\columnwidth,
+  width = 1.0\columnwidth,
   scaled ticks = false
@@
   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
-\addlegendentry{HC-CGC}
+  %\addlegendentry{HC-CGC}
 
   \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-450.data};
-\addlegendentry{CGC}
+  %\addlegendentry{CGC}
 
   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-450.data};
-\addlegendentry{MCI-CCIFD}
+  %\addlegendentry{MCI-CCIFD}
 
   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-450.data};
-\addlegendentry{MC-Fusion (HC-MC-CGC)}
+  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
 
   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-450.data};
-\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
 
@@
   \caption{knott-3d-450}
-\end{figure}
+  \end{subfigure}
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[p]
+  \begin{subfigure}[b]{0.33\textwidth}
   \centering
@@
   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
-\addlegendentry{HC-CGC}
+  %\addlegendentry{HC-CGC}
 
   \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-550.data};
-\addlegendentry{CGC}
+  %\addlegendentry{CGC}
 
   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-550.data};
-\addlegendentry{MCI-CCIFD}
+  %\addlegendentry{MCI-CCIFD}
 
   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-550.data};
-\addlegendentry{MC-Fusion (HC-MC-CGC)}
+  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
 
   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-550.data};
-\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
 
@@
   \caption{knott-3d-550}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{figure}[H]
-\begin{figure}[p]
+  \end{subfigure}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{subfigure}[H]
+  \begin{subfigure}[b]{0.33\textwidth}
   \centering
@@
   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
-\addlegendentry{HC-CGC}
+  %\addlegendentry{HC-CGC}
 
   \addplot[color=red,mark=x] table[x=time,y=CGC]{data/seg-3d.data};
-\addlegendentry{CGC}
+  %\addlegendentry{CGC}
 
   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/seg-3d.data};
-\addlegendentry{MCI-CCIFD}
+  %\addlegendentry{MCI-CCIFD}
 
   %\addplot[color=yellow,mark=o] table[x=time, y=DYNCC-HC-MC]{data/seg-3d.data};
-%\addlegendentry{MC-Fusion (HC-MC)}
+  %%\addlegendentry{MC-Fusion (HC-MC)}
 
   \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
-\addlegendentry{MC-Fusion (HC-MC-CGC)}
-
+  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/seg-3d.data};
-\addlegendentry{MC-Fusion (HC-CGC-CGC)}
+  %DYNCC-HC-CGC-CGC
+  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
 
@@
   \caption{seg-3d}
-\end{figure}
+  \end{subfigure}
+  \begin{center}
+  \hypersetup{linkcolor = black}
+  \ref{named}
+  \hypersetup{linkcolor = red}
+  \end{center}
+  \caption{
+    Among all tested solvers, the proposed method is the only
+    one scaling to large 3D data.
+    Except for the small 3D block, CC-Fusion finds very low
+    energies one to three magnitudes faster 
+    than any other method.
+    With increasing block size, is outperformed even more.
+    For the 2D datasets CGC is very fast, but our proposed
+    solver finds lower energies while still being faster
+    than the global optimal multicut solver.
+  }
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-05 paper/egpaper_for_review.tex
fubar

@@
 \subsection{Real World Models}
-An example for large scale correlation clustering is 
-segmentation of region adjacency graphs (RAG) for
-3D closed surface segmentation of neural tissue data 
-\cite{kroeger_2012_eccv}.
+To segment images or volumes into a previously
+unknown number of clusters, correlation clustering
+can be used.
+Starting from a super-pixel / super-voxel segmentation
+which defines a region adjacency graphs (RAG),
+correlation clustering finds the cut with the lowest energy.
 The energy is based on a likelihood of merging adjacent super-voxels.
@@
 or to merge them ($p(y_{ij} = 0)$).
-The energy function is defined as following.
+The energy function is defined as following:
 \begin{align}
@@
 Where $\beta$ is used as a prior.
-Models of different size are included in the graphical model
-benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr} (???).
-We use models with the cube sizes $300^3$, $450^3$, $550^3$ and $900^3$.
-The number of variables varies from ??? to ???, and the number
-of edges from ??? to ???.
-
-\begin{center}
-    \begin{figure}
-        \begin{center}
-            \begin{subfigure}[b]{0.45\linewidth}
-                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
-            \end{subfigure}
-            \quad
-            \begin{subfigure}[b]{0.45\linewidth}
-                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
-            \end{subfigure}
-        \end{center}
-    \caption{
-        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv}
-    }
-    \end{figure}
-\end{center}
-
-\newpage
+
+For 2D images, we took the models from \cite{andres_2011_iccv}
+which are defined on the images of the Berkeley Segmentation
+Database \cite{martin_2001}.
+For 3D volume segmentation we took the models from
+Andres \etal \cite{kroeger_2012_eccv}.
+We use models with the cube sizes $150^3$, $300^3$, $450^3$, $550^3$ and $900^3$.
+Both, the 2D and 3D models are available in a recent graphical model
+benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr}.
+We use the same names for the datasets as in the benchmark,
+\emph{image-seg} for the models from  \cite{andres_2011_iccv} and \emph{knott-150 - knott-550} and \emph{3d-seg}
+for the models from \cite{kroeger_2012_eccv}.
+The size of instances is given in tab. ~\ref{tab:instance_sizes}.
+
+\begin{table}[H]
+   \tiny
+   \centering
+   \caption{Datasets used for evaluation}
+   \label{tab:instance_sizes}
+   \begin{tabular}{llllc}
+      \toprule
+         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
+      \midrule 
+         image-seg        &     156-3764        & ???        & 100          & $\bullet$    \\ 
+         knott-150        &     572-972         & ???        & 2            & $\times$ \\
+         knott-300        &     3846 - 5896     & ???        & 2            & $\times$ \\
+         knott-450        &     15150-17070     & ???        & 2            & $\times$ \\
+         knott-550        &     27286 - 31249   & ???        & 2            & $\times$ \\
+         3d-seg           &     7958 - 101220   & ???        & 2            & $\times$ \\
+         slashdot         &     ???             & ???        & ???          & $\times$ \\     
+      \bottomrule
+   \end{tabular}
+\end{table}
+
+%\begin{center}
+%    \begin{figure}
+%        \begin{center}
+%            \begin{subfigure}[b]{0.45\linewidth}
+%                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
+%            \end{subfigure}
+%            \quad
+%            \begin{subfigure}[b]{0.45\linewidth}
+%                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
+%            \end{subfigure}
+%        \end{center}
+%    \caption{
+%        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv%}
+%    }
+%    \end{figure}
+%\end{center}
+%
+%\newpage
 
@@
 
+We have presented a fast and scalable 
+approximate solver for correlation 
+clustering, named Fusion Moves for correlation clustering (FM-CC).
+The best solution is iteratively improved 
+by a fusion with proposal solutions.
+The itself is formulated as correlation
+clustering on a smaller graph fewer edges and nodes
+and can therefore be solved very fast.
+Our evaluation shows that CC-FF
+significantly outperforms 
+other solvers w.r.t. any time performance 
+with increasing problem size.
+
 \newpage
+
 {\small
@@
 \newpage
+
 \onecolumn

### 2014-11-05 paper/egpaper_for_review.tex
work on introduction

--- 2014-11-05 paper/egpaper_for_review.tex
@@
 
-\listoftodos[Notes]
 %%%%%%%%% ABSTRACT
@@
 
-\paragraph{Our Notation}
-$G$ Graph.
-$V$ Set of Nodes.
-$E$ Set of Edges.
-$l$ node label.
-$y$ edge label.
-$w$ edge weight
-$MC(G)$ multicut polytope
-$P(G)$ the set of valid edge labeling (MC(G) is convex hull of P(G))
-$y^*$ for opt. labeling
-$G_y=(V_y,E_y)$ contradiction of graph $G$ with respect to $y$
-
-%$\rho_y : E \to E_y$
-%$\rho_y^{-1} : E_y \to E$
-
-$\rho_y : P(G) \to P(G_y)$
-
-$\rho_y^{-1} : P(G_y) \to P(G)$
-\begin{itemize}
-  \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
-  \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
-  \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
-\end{itemize}
-
-Given an edge weighted graph, positive weights (\emph{attractive})
-encourage the adjacent nodes to be in the same 
-connected component, while negative weights (\emph{repulsive}) encourage
-the nodes to stay in different connect components.
-Therefore the sign of the weights encodes if two
-nodes should be merged or not and the magnitude of the weights encodes
-the certainty of this desire.
-The objective of correlation clustering / multicuts
-is finding the cut with a minimal sum of cut edge weights.
-The number of connected components / clusters is discovered
-from the weights ( rewrite?!?).
-Correlation clustering / the multicut is NP-hard \cite{???}.
-%
-Despite the NP-hardness, correlation clustering has been 
-successfully used for
-\begin{inparaenum}[(i)]
-    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
-    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
-    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
-    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
-    \item for co-segmentation~\cite{glassner_2011_cvpr}
-    \item and to cluster sparse and graphs~\cite{???}.
-\end{inparaenum}
-
-Despite the nice properties of correlation clustering
-to perform a \say{one-shot agglomeration of supervoxels} ~\cite{nunez_iglesias_2013},
-the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}.
-Existing solvers for correlation clustering do not scale for non planar graphs.
-Even state of the art approximate move making algorithm fail 
-to give good approximations non planar graphs.
-When increasing the problem sizes, either the runtime explodes or the 
+Segmentation is an important problem in computer vision and data mining as a first step
+towards understanding an image or data in general. 
+Many algorithms start with an over-segmentation
+into superpixels (superregions), which are then clustered into ``perceptually meaningful''
+regions.
+Usually, the number of these regions is \emph{not} known beforehand.
+
+Recently, the multicut formulation~\cite{chopra_1993_mp, Kappes-2013-multicut}
+(sometimes called \emph{correlation clustering}, \cite{bansal_2004_ml})
+has become increasingly popular for unsupervised image segmentation.
+%
+Given an edge-weighted region adjacency graph,
+the problem is to find the segmentation which
+minimizes the cost of the cut edges.
+Such an approach has been shown to yield
+state-of-the-art results on the Berkeley Segmentation Database
+\cite{andres_2011_iccv,yarkony_2012_eccv,alush_2013_simbad}.
+
+Despite the clear mathematical formulation and nice properties of correlation clustering
+to perform a one-shot agglomeration of supervoxels,
+the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}
+which arise from the NP-hardness of the problem.
+
+Recently, Beier~\etal~\cite{Beier-2014} presented a promising 
+approximative method called Cut, Clue \& Cut.
+While this scales well for planar graphs, it does not for non planar graphs and has a bad any-time performance.
+A further inherent drawback of this method is that the subproblems are not limited in their size.
+%
+Consequently, partition problems on large scale data, \eg
+huge volume images in computational neuroscience~\cite{kroeger_2012_eccv}
+or social networks~\cite{Leskovec-2010}, 
+are not tractable, because the runtime explodes or the 
 approximations are far away from being useful.
+
+In the present work we present a novel approach that uses the concept of fusion for correlation clustering.
+Starting with an initial segmentation we fuse the current segmentations with a proposed one.
+Due to the ambiguity of node-labeling for unsupervised segmentations~\cite{} 
+original fusion moves~\cite{Lempinski-2010} are improper, see Sec.~\ref{sec:fusion} for discussion.
+To overcome this problem we suggest to use fusion moves on the edge-variables that indicates a cut and form a
+bijective representation of segmentations.
+The subproblem of fusing of segmentations reduce to a much smaller multicut problem which can be solved extremely efficiently.
 
@@
 \begin{inparaenum}[(i)]
-\item Within this work we propose a fast and scalable move making algorithm for correlation clustering,
-\item which generalized  fusion moves \cite{???} to correlation clustering problems.
-\item We reduce the inference to a series of moves where
-each moves optimizes over a subspace spanned by the current best solution
-and a proposal solution.
+\item We propose a fast and scalable move making algorithm for correlation clustering,
+\item and give a polyhedral interpretation of this algorithm.
 \item We propose two versatile proposal generators, 
-\item and show how to optimize these moves.
-\item We give a polyhedral interpretation of this algorithm,
-\item and evaluate the proposed method 
-on existing benchmark problems.
-\item We show state of the art any time performance on those instances.
-\end{inparaenum}[(i)]
+\item and evaluate the proposed method on existing and new benchmark problems.
+\end{inparaenum}
+
+% Given an edge weighted graph, positive weights (\emph{attractive})
+% encourage the adjacent nodes to be in the same 
+% connected component, while negative weights (\emph{repulsive}) encourage
+% the nodes to stay in different connect components.
+% Therefore the sign of the weights encodes if two
+% nodes should be merged or not and the magnitude of the weights encodes
+% the certainty of this desire.
+% The objective of correlation clustering / multicuts
+% is finding the cut with a minimal sum of cut edge weights.
+% The number of connected components / clusters is discovered
+% from the weights ( rewrite?!?).
+% Correlation clustering / the multicut is NP-hard \cite{???}.
+% %
+% Despite the NP-hardness, correlation clustering has been 
+% successfully used for
+% \begin{inparaenum}[(i)]
+%     \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
+%     \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
+%     \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
+%     \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
+%     \item for co-segmentation~\cite{glassner_2011_cvpr}
+%     \item and to cluster sparse and graphs~\cite{???}.
+% \end{inparaenum}
+
+% Despite the nice properties of correlation clustering
+% to perform a \say{one-shot agglomeration of supervoxels} ~\cite{nunez_iglesias_2013},
+% the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}.
+% Existing solvers for correlation clustering do not scale for non planar graphs.
+% Even state of the art approximate move making algorithm fail 
+% to give good approximations non planar graphs.
+% When increasing the problem sizes, either the runtime explodes or the 
+% approximations are far away from being useful.
+
+% \textbf{Contribution:}
+% \begin{inparaenum}[(i)]
+% \item Within this work we propose a fast and scalable move making algorithm for correlation clustering,
+% \item which generalized  fusion moves \cite{???} to correlation clustering problems.
+% \item We reduce the inference to a series of moves where
+% each moves optimizes over a subspace spanned by the current best solution
+% and a proposal solution.
+% \item We propose two versatile proposal generators,
+% \item and show how to optimize these moves.
+% \item We give a polyhedral interpretation of this algorithm,
+% \item and evaluate the proposed method 
+% on existing benchmark problems.
+% \item We show state of the art any time performance on those instances.
+% \end{inparaenum}[(i)]
 
@@
 
-\section{Problem Formulation}\label{sec:problem_formulation}
-Def: Graph, weighted graph, cut, multicut
-
-\begin{center}
+\section{Notation and Problem Formulation}\label{sec:problem_formulation}
+Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
+%
+The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
+A positive weight expresses the desire that two adjacent nodes should
+be merged, whereas a negative weight indicates
+that these nodes should be separated into two different regions.
+%
+A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
+of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
+%
+A segmentation of the graph $G$ can by either given by an 
+node labeling $l \in \mathbb{N}^{|V|}$
+or an edge labeling $y \in\{0,1\}^{|E|}$.  
+An edge labeling is only consistent if it contains no dangling edges~\cite{Kappes-2013-multicut}.
+We denote the set of all consistent edge labelings by $P(G)$.
+The convex hull of this set is known as the \emph{multicut polytope} $MC(G)$.
+
+A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
+in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the node $v\in V$.
+
+We define the contradiction of graph $G_y=(V_y,E_y)$
+with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
+
+%$\rho_y : P(G) \to P(G_y)$
+%$\rho_y^{-1} : P(G_y) \to P(G)$
+
+% \begin{itemize}
+%   \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
+%   \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
+%   \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
+% \end{itemize}
+
+% Def: Graph, weighted graph, cut, multicut
+
+Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
+of the edges between distinct segments is minimized. This can be formulated in the node~\ref{eq:nodeproblem} 
+or edge domain~\ref{eq:edgeproblem}
+
 \begin{eqnarray}
-        l^* &=& \argmin_{L \in \{1,\ldots,|V|\}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}] \label{eq:nodeproblem}\\
+  l^* &=& \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}] \label{eq:nodeproblem}\\
   % y_{ij}^* &=& [l_{u} \neq l_{v}] 
-        y^* &=& \argmin_{y \in MC(G)\cap \{0,1\}^{|E|}} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}%\\ 
+  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}%\\ 
 \end{eqnarray}
-\end{center}
-
-The exist an surjective mapping from a node-label $l$ to edge-labeling $y$ and
-a bijective mapping from a partitioning of $V$ to vertices of the multicut polytope $MC$.
-Consequently, 
-(i) problems \ref{eq:nodeproblem} and \ref{eq:edgeproblem} are equivalent
-and (ii) the node-labeling is not unique for a given partitioning and introduce some
-ambiguities.
+
+% The exist an surjective mapping from a node-label $l$ to edge-labeling $y$ and
+% a bijective mapping from a partitioning of $V$ to vertices of the multicut polytope $MC$.
+% Consequently, 
+% (i) problems \ref{eq:nodeproblem} and \ref{eq:edgeproblem} are equivalent
+% and (ii) the node-labeling is not unique for a given partitioning and introduce some
+% ambiguities.
 

### 2014-11-05 paper/anytimefigure.tex
update experimental evaluation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  ]
  %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
  %\addlegendentry{HC-CGC}

  \addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data2/image-seg.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/image-seg.data};
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/image-seg.data};
 % \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/image-seg.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data2/image-seg.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/image-seg.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[
    restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    %ymin =  75282844.25,
    %ymax =  81774642.015,
    %xtick       = { 1 , 60 , 3600 },
    %xticklabels = { 1 sec. , 1 min.  , 1 hour },
    %ytick       = {75661636, 78718140, 81774643 },
    %yticklabels = {$75661636$, $78718140$, $81774643$ },
    width = 1.0\columnwidth,
    scaled ticks = false
    ]
    %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-150.data};
    %%\addlegendentry{HC-CGC}
    %
    \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-150.data};            
    \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-150.data};
    \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-150.data};  
    \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-150.data}; 
    \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-150.data};
    \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-150.data};

    \end{semilogxaxis}
    \end{tikzpicture}
    \caption{knott-3d-150}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-40000:-24000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false,
  legend to name = named,
  legend columns=5
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-300.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-300.data};               \addlegendentry{CGC}
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-300.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-300.data};          \addlegendentry{KL}

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-300}
  \end{subfigure}
  \newline
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-80000:-60000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-450.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-450.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-450.data};
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-450.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-450.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-450.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-450.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-450}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  restrict y to domain=-10000000:-100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-550.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-550.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-550.data};
  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-550.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-550.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-550.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-550.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{knott-3d-550}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{subfigure}[H]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:1200000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/seg-3d.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/seg-3d.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/seg-3d.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/seg-3d.data}; 
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/seg-3d.data}; 
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/seg-3d.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/seg-3d.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{seg-3d}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/socialnets.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/socialnets.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/socialnets.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/socialnets.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/socialnets.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/socialnets.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{social nets}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/normalizedsocialnets.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/normalizedsocialnets.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/normalizedsocialnets.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/normalizedsocialnets.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/normalizedsocialnets.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/normalizedsocialnets.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{social nets}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[
  %restrict y to domain=-10000000:-100000,
  %restrict y to domain=-10000000:100000,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  %ymin =  75282844.25,
  %ymax =  81774642.015,
  %xtick       = { 1 , 60 , 3600 },
  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
  %ytick       = {75661636, 78718140, 81774643 },
  %yticklabels = {$75661636$, $78718140$, $81774643$ },
  width = 1.0\columnwidth,
  scaled ticks = false
  ]
  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/modularity-clustering.data};
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/modularity-clustering.data};
  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/modularity-clustering.data};
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/modularity-clustering.data};
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/modularity-clustering.data};
  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/modularity-clustering.data};
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/modularity-clustering.data};

  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{modularity clustering}
  \end{subfigure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{named}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    Among all tested solvers, the proposed method is the only
    one scaling to large 3D data.
    Except for the small 3D block, CC-Fusion finds very low
    energies one to three magnitudes faster 
    than any other method.
    With increasing block size, is outperformed even more.
    For the 2D datasets CGC is very fast, but our proposed
    solver finds lower energies while still being faster
    than the global optimal multicut solver.
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-05 paper/egpaper_for_review.tex
mychanges
update experimental evaluation

@@
 \centering
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time.pdf}}
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value.pdf}}
+\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
+\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
 \caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
@@
 
+\input{anytimefigure.tex}
+
 \begin{figure}

### 2014-11-06 paper/egpaper_for_review.tex
energy based hc section

@@
 % On the smaller graph, more expensive solvers are used.
+
+\section{Energy Based Hierarchical Clustering (EBHC)}
+
+Hierarchical clustering can be used to find approximate
+solutions for correlation clustering.
+In each step, the edge with the highest weight $w$ is
+contracted (red edges in fig. ~\ref{fig:hc_alg}).
+Doing so, parallel edges edges can occur.
+Whenever there are multiple edges between 
+a pair of nodes, these edges are merged into a single edge
+by summing up their weights.
+The algorithm stops if the highest edge weight is
+smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
+contraction leads to worse energies.
+
+Given the intrinsic greediness of hierarchical clustering, 
+we do not expect very good solutions, but still a good starting 
+point for move making algorithm as CGC \cite{beier_2014_cvpr}.
+Therefore we propose to initialize  CGC with EBHC
+and hope speedup of CGC.
+
+Furthermore, we propose a algorithm to combine / fuse together
+multiple EBHC results from perpetuated energies.
+This algorithm, namely
+
+\input{inputs/fig_hc_alg.tex} Correlation-Clustering-Fusion (CCF) Moves 
+will be discussed in the following section.
 
@@
 So far we only enforce must link constraints to obtain smaller problems.
-One can also enforce must-not link constraints to the problem. 
-If those are closed, they automatically lead to a decomposition of the problem, which is a interesting property for very huge data.
+One can also enforce cannot link constraints to the problem. 
+If those are closed, they automatically lead to a decomposition of the problem, 
+which is a interesting property for very huge data.
 

### 2014-11-06 paper/egpaper_for_review.tex
energy based hc section
wip

@@
 
-Hierarchical clustering can be used to find approximate
+Agglomerative hierarchical clustering (HC) is widely used
+in graph / energy segmentation
+\cite{arbelaez_2006}.
+Hierarchical clustering is fast, and 
+due to the agglomeration of edge weights, 
+hierarchical clustering is robust against noise.
+
+HC can be used to find approximate
 solutions for correlation clustering.
@@
 Therefore we propose to initialize  CGC with EBHC
-and hope speedup of CGC.
+and hope to speedup of CGC with this starting point.
 

### 2014-11-06 paper/egpaper_for_review.tex
relatex work in progress

--- 2014-11-06 paper/egpaper_for_review.tex
@@
 
-In the present work we present a novel approach that uses the concept of fusion for correlation clustering.
-Starting with an initial segmentation we fuse the current segmentations with a proposed one.
-Due to the ambiguity of node-labeling for unsupervised segmentations~\cite{} 
-original fusion moves~\cite{Lempinski-2010} are improper, see Sec.~\ref{sec:fusion} for discussion.
-To overcome this problem we suggest to use fusion moves on the edge-variables that indicates a cut and form a
-bijective representation of segmentations.
-The subproblem of fusing of segmentations reduce to a much smaller multicut problem which can be solved extremely efficiently.
-
 \textbf{Contribution:}
-\begin{inparaenum}[(i)]
-\item We propose a fast and scalable move making algorithm for correlation clustering,
-\item and give a polyhedral interpretation of this algorithm.
-\item We propose two versatile proposal generators, 
-\item and evaluate the proposed method on existing and new benchmark problems.
-\end{inparaenum}
+In the present work we present some novel approaches that are designed for large scale correlation clustering problems.
+First, we define a novel energy based agglomerative clustering algorithm that monotonically increase the energy.
+With this at hand we show how to improve the anytime performance of Cut, Clue \& Cut.
+Second, we introduce cluster-fusion moves, which extend the original fusion moves~\cite{Lempinski-2010} 
+used in supervised segmentation to the unsupervised case and give a polyhedral interpretation of this algorithm.
+We propose two versatile proposal generators, and evaluate the proposed methods on existing and new benchmark problems.
+That experiments show that we can improve the computation time by one to two magnitudes without worsening the segmentation 
+quality significantly.
 
@@
 An edge labeling is only consistent if it contains no dangling edges~\cite{Kappes-2013-multicut}.
-We denote the set of all consistent edge labelings by $P(G)$.
-The convex hull of this set is known as the \emph{multicut polytope} $MC(G)$.
-
-A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
-in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the node $v\in V$.
-
-We define the contradiction of graph $G_y=(V_y,E_y)$
-with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
+We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
+The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.
 
@@
 Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
-of the edges between distinct segments is minimized. This can be formulated in the node~\ref{eq:nodeproblem} 
-or edge domain~\ref{eq:edgeproblem}
-
-\begin{eqnarray}
-  l^* &=& \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}] \label{eq:nodeproblem}\\
-  % y_{ij}^* &=& [l_{u} \neq l_{v}] 
-  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}%\\ 
-\end{eqnarray}
+of the edges between distinct segments is minimized. This can be formulated in the node domain
+by assigning each node $v$ a label $l_v \in \mathbb{N}$
+\begin{align}
+  l^* &= \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
+\end{align}  % y_{ij}^* &=& [l_{u} \neq l_{v}] 
+or in the edge domain, by label each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
+\begin{align}
+  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}.%\\ 
+\end{align}
+As shown in~\cite{Kappes-2013-multicut} both problems are equivalent, but formulation \ref{eq:nodeproblem}
+suffers from ambiguities in the formulation~\cite{Kappes-2011}.
 
@@
 
-\section{Related Work}\label{sec:related_work}
-
-\subsection{Correlation Clustering}\label{sec:cc}
-A major branch of research has focused on solving 
-relaxations of eq.~\ref{eq:edgeproblem} by linear programming
-or solving  eq.~\ref{eq:edgeproblem} directly to global optimality
-by using integer linear programming in a cutting plane fashion  \cite{kappes_2011_emmcvpr,andres_2011_iccv}.
-
-Yarkony et al ~\cite{yarkony_2012_eccv} uses 
-a dual decomposition based approach for planar graphs
-where the subproblems are planar max cut instances.
+\section{Related Work}\label{sec:related_work}%
+%
+Due to the ambiguity of formulation~\ref{eq:nodeproblem},
+a major branch of research has focused on solving 
+relaxations of eq.~\ref{eq:edgeproblem}.
+To keep the objective and system of inequalities small, they 
+work on sparse graphs and
+use cutting plane methods
+in combination with (integer) linear programming and efficient 
+separation procedures~\cite{kappes_2011_emmcvpr,andres_2011_iccv,kappes_2013_arxiv}.
+
+With no time restrictions and integer constraints these methods can solve the problem to global optimality.
+For huge problems both, separation and solving the ILP in each round, becomes very time consuming.
+
+For planar problems, Yarkony \etal~\cite{yarkony_2012_eccv} 
+suggested a column generating strategy for the LP-relaxation
+that includes all cycle-inequalities of problem \ref{eq:edgeproblem}.
+The column generation base on solving planar max cut instances.
+While this method is fast, 
+it only solve a relaxation of the problem and so requires additional rounding strategies,
+lacks of a practical stopping condition for the column generation,
+and most important  is restricted to planar problems.
 
@@
 
-\subsection{Fusion Moves}\label{sec:fm}
+%\subsection{Fusion Moves}\label{sec:fm}
 Move making algorithms, in particular fusion moves, 
@@
 Motivation Using Fusion moves -> problem ambiguity
+
+A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
+in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the node $v\in V$.
+
+We define the contradiction of graph $G_y=(V_y,E_y)$
+with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
 
@@
 
+Improving proposals.
+
 \section{Conclusion}\label{sec:conclusion}

### 2014-11-07 paper/egpaper_for_review.tex
mychanges

@@
 
-\section{Energy Based Hierarchical Clustering (EBHC)}
+\section{Energy Based Hierarchical Clustering (EHC)}
 
 Agglomerative hierarchical clustering (HC) is widely used
-in graph / energy segmentation
+in graph / image segmentation
 \cite{arbelaez_2006}.
@@
 hierarchical clustering is robust against noise.
-
-HC can be used to find approximate
+In agglomerative clustering, weights of
+parallel edges are merged into single edges.
+For image segmentation, the length
+weighted mean is used to do this update.
+
+We propose to use EHC find
 solutions for correlation clustering.
@@
 a pair of nodes, these edges are merged into a single edge
-by summing up their weights.
+by summing up their weights, since we 
+minimize the sum of the cut edges.
 The algorithm stops if the highest edge weight is

### 2014-11-07 paper/egpaper_for_review.tex
related work in progress

--- 2014-11-06 paper/egpaper_for_review.tex
@@
 For planar problems, Yarkony \etal~\cite{yarkony_2012_eccv} 
-suggested a column generating strategy for the LP-relaxation
+suggested a column generating strategy for the outer LP-relaxation
 that includes all cycle-inequalities of problem \ref{eq:edgeproblem}.
@@
 An other branch of research uses move making algorithm 
-to optimize correlation clustering.
-Bansal and Bagon use a modified $\alpha-$expansion \cite{bansal_2004_ml} 
-algorithm suitable for correlation clustering,
-while the state of the art method from  Beier \etal~\cite{beier_2014_cvpr} iteratively re-optimizes the cuts
-between adjacent connected components.
+to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kerninghan-1970}.
+Starting with an initial segmentation, auxiliary problems are solved that 
+strictly improve the segmentation.
+
+Bansal and Bagon propose a modified $\alpha-$expansion~\cite{bansal_2004_ml} 
+algorithm suitable for correlation clustering, that allows all variables to 
+change to cluster $\alpha$ in a single move. While the authors claim that this
+scales to large scale data, in~\cite{beier_2014_cvpr} it has been shown that 
+this is not the case in general. This is not surprising because the auxiliary 
+problems can have as many variables as the original problem.
+
+A more efficient move making method has been presented by Beier \etal~\cite{beier_2014_cvpr}.
+Their Cut, Glue and Cut method iteratively re-optimizes the cuts between adjacent clusters of the current solution.
+While this method scales better then  modified $\alpha-$expansion, it still faces three problems:
+Firstly, the subproblems can be as large as the original problem,
+secondly, the subproblems are max-cut problems on non-planar graphs that are NP-hard 
+and even the used approximation has high polynomial complexity.
+This limits the method, to be applicable to huge problems. The same holds for the 
+method of Kerninghan and Lin~\cite{Kerninghan-1970}.
 
@@
 
-%\subsection{Fusion Moves}\label{sec:fm}
-Move making algorithms, in particular fusion moves, 
-have become increasingly popular for energy minimization~\cite{???,kappes_2014_ws}.
+For energy minimization problems fusion moves have become increasingly popular~\cite{Lepinsky-2010,kappes_2014_ws}.
 For many large scale computer vision applications fusion moves lead to good approximations
 with state of the art any time performance~\cite{kappes_2014_ws}.
-The fusion move algorithm works as follows:
-A current best solution is maintained and proposal solutions 
-are generated.
-Within each move, the variables can choose the label from the current best or from the 
-proposed solution. This problem can be formulated as an 
-optimization problem with a binary label space.
-Any optimal solution of this auxiliary problem is guaranteed
-to not worsen the current best solution.
+
+The fusion move algorithm iteratively fuse the current best solution with a proposal solutions
+by optimizing over the subspace spanned by the two labeling. 
+Due to the ambiguity of a node-labeling, fusion moves can not be applied directly for correlation clustering.
+We will show how to overcome this point later.
+
+Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
+
+Greedy Algorithms
+Step 1: Permute the nodes according a random
+Step 2: Assign record to the cluster that minimize the costs. Start a new cluster if costs positive
+\begin{itemize}
+\item BEST: Cluster containing the most positive edge [Ng et al 2002 ACL]
+\item FIRST: Cluster contains the first positive edge [Soon et al 2001 CL]
+\item VOTE: Assign to cluster that minimizes objective function. [Elsner et al 08 ACL]
+\end{itemize}
+
+PIVOT Algorithm [Ailon et al 2008 JACM]: select pivot element and connect to all positiv neighbord nodes
+
+Run the algorithm for many random permutations , and pick the clustering with
+best objective value (better than average run)
+
+BOEM Algorithm [Gioniset al 2007 TKDD]
+\begin{itemize}
+\item Start with an initial clustering (e.g. output of greedy)
+\item Remove one random element from a cluster
+\item Make the Best One Element Move (BOEM)
+Move it to another cluster or Create a new cluster. 
+\end{itemize}
 
@@
 will be discussed in the following section.
+
+Common cluster distances
+\begin{itemize}
+\item Single-Link: Nearest Neighbor - their closest members.
+\item Complete-Link: Furthest Neighbor - their furthest members.
+\item Centroid: Distance between centroids
+\item Group Average: average of all cross-cluster pairs.
+\end{itemize}
 

### 2014-11-07 paper/egpaper_for_review.tex
my

--- 2014-11-07 paper/egpaper_for_review.tex
@@
 \cite{arbelaez_2006}.
+
+\input{inputs/fig_hc_alg.tex}
+
 Hierarchical clustering is fast, and 
@@
 
-We propose to use EHC find
+We propose to use Energy Based Hierarchical Clustering (EHC) to find
 solutions for correlation clustering.
@@
 Doing so, parallel edges edges can occur.
+To make EHC follow the energy, we propose 
+the following update rule:
 Whenever there are multiple edges between 
@@
 Given the intrinsic greediness of hierarchical clustering, 
-we do not expect very good solutions, but still a good starting 
-point for move making algorithm as CGC \cite{beier_2014_cvpr}.
+and the fact that EHC does only local decisions, it is 
+sensitive against salt and paper noise 
+and we do not expect very good solutions.
+
+But EHC is very fast, and can be used to initialize
+CGC \cite{beier_2014_cvpr}. Plenty of the time in CGC
+is spend in the \emph{cut phase} to solve the 
+first 2 coloring on the complete graph.
+
 Therefore we propose to initialize  CGC with EBHC
@@
 
-Furthermore, we propose a algorithm to combine / fuse together
-multiple EBHC results from perpetuated energies.
-This algorithm, namely
-
-\input{inputs/fig_hc_alg.tex} Correlation-Clustering-Fusion (CCF) Moves 
-will be discussed in the following section.
+%Furthermore, we propose a algorithm to combine / fuse together
+%multiple EBHC results from perpetuated energies.
+%This algorithm, namely 
+%Correlation-Clustering-Fusion (CCF) Moves 
+%will be discussed in the following section.
 

### 2014-11-07 paper/egpaper_for_review.tex
added real numbers to hc fig

@@
 
-\input{inputs/fig_hc_alg.tex}
-
 Hierarchical clustering is fast, and 
@@
 But EHC is very fast, and can be used to initialize
-CGC \cite{beier_2014_cvpr}. Plenty of the time in CGC
+CGC \cite{beier_2014_cvpr}. Excessive time in CGC
 is spend in the \emph{cut phase} to solve the 
 first 2 coloring on the complete graph.
-
-Therefore we propose to initialize  CGC with EBHC
-and hope to speedup of CGC with this starting point.
-
-%Furthermore, we propose a algorithm to combine / fuse together
-%multiple EBHC results from perpetuated energies.
-%This algorithm, namely 
-%Correlation-Clustering-Fusion (CCF) Moves 
-%will be discussed in the following section.
+As shown in ~\ref{sec:exp},
+allowing CGC to start from the EHC solution
+can improve performance drastically.
+
+\input{inputs/fig_hc_alg.tex}
 

### 2014-11-07 paper/egpaper_for_review.tex

--- 2014-11-07 paper/egpaper_for_review.tex
@@
 \cite{arbelaez_2006}.
+
 Hierarchical clustering is fast, and 
@@
 Given the intrinsic greediness of hierarchical clustering, 
-we do not expect very good solutions, but still a good starting 
-point for move making algorithm as CGC \cite{beier_2014_cvpr}.
-Therefore we propose to initialize  CGC with EBHC
-and hope to speedup of CGC with this starting point.
-
-Furthermore, we propose a algorithm to combine / fuse together
-multiple EBHC results from perpetuated energies.
-This algorithm, namely
-
-\input{inputs/fig_hc_alg.tex} Correlation-Clustering-Fusion (CCF) Moves 
-will be discussed in the following section.
+and the fact that EHC does only local decisions, it is 
+sensitive against salt and paper noise 
+and we do not expect very good solutions.
+
+But EHC is very fast, and can be used to initialize
+CGC \cite{beier_2014_cvpr}. Excessive time in CGC
+is spend in the \emph{cut phase} to solve the 
+first 2 coloring on the complete graph.
+As shown in ~\ref{sec:exp},
+allowing CGC to start from the EHC solution
+can improve performance drastically.
+
+\input{inputs/fig_hc_alg.tex}
 

### 2014-11-07 paper/egpaper_for_review.tex
related work

@@
 
-Segmentation is an important problem in computer vision and data mining as a first step
+Correlation clustering~\cite{Bansal-2004} also known as the multicut problem~\cite{chopra_1993_mp} 
+is a basic primitive in computer vision~\cite{andres_2011_iccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014} as a first step
 towards understanding an image or data in general. 
-Many algorithms start with an over-segmentation
+The correlation clustering problem is the following:
+Given an undirected edge weighted graph, 
+where positive weights (\emph{attractive}) encourage the adjacent nodes to be in the same cluster
+and negative weights (\emph{repulsive}) encourage the nodes to stay in different cluster, 
+find the clustering of nodes such that the sum over weights of edges between clusters is minimized.
+Note that this problem formulation does not included a predefined number of clusters.
+
+Despite the clear mathematical formulation and nice properties of correlation clustering
+to perform a one-shot agglomeration clustering,
+the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}
+which arise from the NP-hardness of the problem.
+
+For unsupervised image segmentation algorithms usually start with an over-segmentation
 into superpixels (superregions), which are then clustered into ``perceptually meaningful''
-regions.
-Usually, the number of these regions is \emph{not} known beforehand.
-
-Recently, the multicut formulation~\cite{chopra_1993_mp, Kappes-2013-multicut}
-(sometimes called \emph{correlation clustering}, \cite{bansal_2004_ml})
-has become increasingly popular for unsupervised image segmentation.
-%
-Given an edge-weighted region adjacency graph,
-the problem is to find the segmentation which
-minimizes the cost of the cut edges.
+regions by correlation clustering on sparse graphs.
 Such an approach has been shown to yield
@@
 \cite{andres_2011_iccv,yarkony_2012_eccv,alush_2013_simbad}.
-
-Despite the clear mathematical formulation and nice properties of correlation clustering
-to perform a one-shot agglomeration of supervoxels,
-the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}
-which arise from the NP-hardness of the problem.
 
@@
 Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
-
-Greedy Algorithms
-Step 1: Permute the nodes according a random
-Step 2: Assign record to the cluster that minimize the costs. Start a new cluster if costs positive
-\begin{itemize}
-\item BEST: Cluster containing the most positive edge [Ng et al 2002 ACL]
-\item FIRST: Cluster contains the first positive edge [Soon et al 2001 CL]
-\item VOTE: Assign to cluster that minimizes objective function. [Elsner et al 08 ACL]
-\end{itemize}
-
-PIVOT Algorithm [Ailon et al 2008 JACM]: select pivot element and connect to all positiv neighbord nodes
-
-Run the algorithm for many random permutations , and pick the clustering with
-best objective value (better than average run)
-
-BOEM Algorithm [Gioniset al 2007 TKDD]
-\begin{itemize}
-\item Start with an initial clustering (e.g. output of greedy)
-\item Remove one random element from a cluster
-\item Make the Best One Element Move (BOEM)
-Move it to another cluster or Create a new cluster. 
-\end{itemize}
+A common greedy approach is to randomly permute the nodes and than assign 
+iteratively each node to an existing cluster or create a new cluster if costs cannot be decreased by assigning to a cluster.
+Common assigning strategies are:
+\emph{BEST}; assign to cluster which is linked by the most positive edge [Ng et al 2002 ACL],
+\emph{FIRST}; Assign to the cluster which is first linked by a positive edge [Soon et al 2001 CL], and
+\emph{VOTE}; Assign to cluster that minimizes objective function. [Elsner et al 08 ACL].
+
+The PIVOT Algorithm [Ailon et al 2008 JACM] iterate over all nodes in random order.
+If the node is not assigned it construct a cluster containing the node and all its 
+unassigned positively linked neighbors.
+
+Typically these algorithms started for many random permutations, 
+and pick the clustering with best objective value.
+
+A widely use post-processing method is  Best One Element Move (BOEM) [Gioniset al 2007 TKDD].
+Start with an initial clustering one node is removed from a cluster and reassigned to an existing or new cluster such that the costs are minimized.
+BEOM stops if no move can decrease the costs.
 
@@
 \cite{arbelaez_2006}.
-
 Hierarchical clustering is fast, and 
@@
 
-We propose to use Energy Based Hierarchical Clustering (EHC) to find
+We propose to use EHC find
 solutions for correlation clustering.
@@
 Doing so, parallel edges edges can occur.
-To make EHC follow the energy, we propose 
-the following update rule:
 Whenever there are multiple edges between 
@@
 Given the intrinsic greediness of hierarchical clustering, 
-and the fact that EHC does only local decisions, it is 
-sensitive against salt and paper noise 
-and we do not expect very good solutions.
-
-But EHC is very fast, and can be used to initialize
-CGC \cite{beier_2014_cvpr}. Excessive time in CGC
-is spend in the \emph{cut phase} to solve the 
-first 2 coloring on the complete graph.
-As shown in ~\ref{sec:exp},
-allowing CGC to start from the EHC solution
-can improve performance drastically.
-
-\input{inputs/fig_hc_alg.tex}
+we do not expect very good solutions, but still a good starting 
+point for move making algorithm as CGC \cite{beier_2014_cvpr}.
+Therefore we propose to initialize  CGC with EBHC
+and hope to speedup of CGC with this starting point.
+
+Furthermore, we propose a algorithm to combine / fuse together
+multiple EBHC results from perpetuated energies.
+This algorithm, namely
+
+\input{inputs/fig_hc_alg.tex} Correlation-Clustering-Fusion (CCF) Moves 
+will be discussed in the following section.
 

### 2014-11-07 paper/inputs/fig_hc_alg.tex
missing file

--- 2014-09-29 paper/inputs/fig_hc.tex
@@
     \path
-        (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
-        (n1) edge[eS] node[eNS]{$w_{12}$} (n2) 
-        (n3) edge[eS] node[eNS]{$w_{34}$} (n4) 
-        (n4) edge[eS] node[eNS]{$w_{45}$} (n5)
-        (n0) edge[eC] node[eNS]{$w_{03}$} (n3)
-        (n1) edge[eS] node[eNS]{$w_{14}$} (n4)
-        (n2) edge[eS] node[eNS]{$w_{25}$} (n5)
+        (n0) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
+        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
+        (n3) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
+        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
+        (n0) edge[eC] node[eNS]{$w_{03}=4$} (n3)
+        (n1) edge[eS] node[eNS]{$w_{14}=2$} (n4)
+        (n2) edge[eS] node[eNS]{$w_{25}=3$} (n5)
     ;
@@
     \path
-        (n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
-        (n1) edge[eS] node[eNS]{$w_{12}$} (n2) 
-        (n03) edge[eS] node[eNS]{$w_{34}$} (n4) 
-        (n4) edge[eS] node[eNS]{$w_{45}$} (n5)
-        (n1) edge[eS] node[eNS]{$w_{14}$} (n4)
-        (n2) edge[eC] node[eNS]{$w_{25}$} (n5)
+        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
+        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
+        (n03) edge[eS] node[eNS]{$w_{34}-2$} (n4) 
+        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
+        (n1) edge[eS] node[eNS]{$w_{14}=1$} (n4)
+        (n2) edge[eC] node[eNS]{$w_{25}=3$} (n5)
     ;
@@
     \path
-        (n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
-        (n1) edge[eS] node[eNS]{$w_{12}$} (n25) 
-        (n03) edge[eS] node[eNS]{$w_{34}$} (n4) 
-        (n4) edge[eS] node[eNS]{$w_{45}$} (n25)
-        (n1) edge[eC] node[eNS]{$w_{14}$} (n4)
+        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
+        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n25) 
+        (n03) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
+        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n25)
+        (n1) edge[eC] node[eNS]{$w_{14}=2$} (n4)
     ;
@@
         %(n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
-        (n14) edge[eNC] node[eNS]{$w_{12}+$\\$w_{45}$} (n25) 
-        (n03) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}$} (n14) 
+        (n14) edge[eNC] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
+        (n03) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
     ;
@@
     or equal to zero (edge shown in green).
-    Doing so, hierarchical clustering can be
-    interpreted as an greedy approximator for
-    the multicut objective.
-}\label{fig:hc_proposal}
+}\label{fig:hc_alg}
 \end{figure}

### 2014-11-07 paper/egpaper_for_review.tex
update related work, relayout Figure EHC

@@
 \usepackage{booktabs}
+\usepackage{placeins}
 
@@
 \begin{abstract}
+  \color{red} \textbf{TODO:}
    We address the problem of partitioning a  graph
@@
 
-Correlation clustering~\cite{Bansal-2004} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014} as a first step
+Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
+is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010} as a first step
 towards understanding an image or data in general. 
@@
 the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}
-which arise from the NP-hardness of the problem.
-
-For unsupervised image segmentation algorithms usually start with an over-segmentation
+which arise from the NP-hardness of the problem~\cite{Bansal-2002}.
+
+In signed social networks, where positive and negative edges encodes friend and foe relationships, respectively,
+correlation clustering is a natural way to detect communities~\cite{Chierichetti-2014,Chen-2012}.
+Correlation clustering can also been used to cluster query refinements in web search~\cite{Sadikov-2010}.
+Because social and web-related networks are often very huge, heuristic methods, \eg the PIVOT-algorithm~\cite{Ailon-2008},
+are very popular~\cite{Chierichetti-2014}.
+
+In computer vision applications, unsupervised image segmentation algorithms usually start with an over-segmentation
 into superpixels (superregions), which are then clustered into ``perceptually meaningful''
@@
 
-Recently, Beier~\etal~\cite{Beier-2014} presented a promising 
+Recently, Beier~\etal~\cite{beier_2014_cvpr} presented a promising 
 approximative method called Cut, Clue \& Cut.
@@
 
+In the present work we will suggest some alternative approaches to deal with large scale correlation clustering problems.
+In the end we ill present a method that can be combined with any other correlation clustering method and 
+allows to reduce the overall problem to a sequence of correlation clustering problems which are by magnitudes smaller.
+
 \textbf{Contribution:}
@@
 With this at hand we show how to improve the anytime performance of Cut, Clue \& Cut.
-Second, we introduce cluster-fusion moves, which extend the original fusion moves~\cite{Lempinski-2010} 
+Second, we introduce cluster-fusion moves, which extend the original fusion moves~\cite{Lempitsky-2010} 
 used in supervised segmentation to the unsupervised case and give a polyhedral interpretation of this algorithm.
@@
 or an edge labeling $y \in\{0,1\}^{|E|}$.  
-An edge labeling is only consistent if it contains no dangling edges~\cite{Kappes-2013-multicut}.
+An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.
 We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
@@
 \end{align}
-As shown in~\cite{Kappes-2013-multicut} both problems are equivalent, but formulation \ref{eq:nodeproblem}
-suffers from ambiguities in the formulation~\cite{Kappes-2011}.
+As shown in~\cite{kappes_2013_arxiv} both problems are equivalent, but formulation \ref{eq:nodeproblem}
+suffers from ambiguities in the formulation~\cite{kappes_2011_emmcvpr}.
 
@@
 An other branch of research uses move making algorithm 
-to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kerninghan-1970}.
+to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
 Starting with an initial segmentation, auxiliary problems are solved that 
@@
 This limits the method, to be applicable to huge problems. The same holds for the 
-method of Kerninghan and Lin~\cite{Kerninghan-1970}.
+method of Kernighan and Lin~\cite{Kernighan-1970}.
 
@@
 
-For energy minimization problems fusion moves have become increasingly popular~\cite{Lepinsky-2010,kappes_2014_ws}.
+For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
 For many large scale computer vision applications fusion moves lead to good approximations
@@
 
+\input{inputs/fig_hc_alg.tex}
+
 Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
@@
 Common assigning strategies are:
-\emph{BEST}; assign to cluster which is linked by the most positive edge [Ng et al 2002 ACL],
-\emph{FIRST}; Assign to the cluster which is first linked by a positive edge [Soon et al 2001 CL], and
-\emph{VOTE}; Assign to cluster that minimizes objective function. [Elsner et al 08 ACL].
-
-The PIVOT Algorithm [Ailon et al 2008 JACM] iterate over all nodes in random order.
+\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
+\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
+\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
+%
+The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
 If the node is not assigned it construct a cluster containing the node and all its 
 unassigned positively linked neighbors.  
-
+%
 Typically these algorithms started for many random permutations, 
@@
 
-A widely use post-processing method is  Best One Element Move (BOEM) [Gioniset al 2007 TKDD].
+A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}.
 Start with an initial clustering one node is removed from a cluster and reassigned to an existing or new cluster such that the costs are minimized.
@@
 % On the smaller graph, more expensive solvers are used.
+
+%\input{inputs/fig_hc_alg.tex}
 
@@
 
-\input{inputs/fig_hc_alg.tex}
+%\input{inputs/fig_hc_alg.tex}
 
@@
 
+\FloatBarrier
 {\small

### 2014-11-07 paper/anytimefigure2.tex
new plots

--- 2014-11-05 paper/anytimefigure.tex
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
   scaled ticks = false,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ]  
-  %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
-  %\addlegendentry{HC-CGC}
-
-  \addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data2/image-seg.data};
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/image-seg.data};
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/image-seg.data};
- % \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/image-seg.data};
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data2/image-seg.data};
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/image-seg.data};
-
+  \anytimeplot{image-seg}
   \end{semilogxaxis}
@@
   \end{subfigure}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
   \begin{subfigure}[b]{0.33\textwidth}
@@
     xmax = 4100,
-    %ymin =  75282844.25,
-    %ymax =  81774642.015,
-    %xtick       = { 1 , 60 , 3600 },
-    %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-    %ytick       = {75661636, 78718140, 81774643 },
-    %yticklabels = {$75661636$, $78718140$, $81774643$ },
     width = 1.0\columnwidth,
-    scaled ticks = false
+    scaled ticks = false,
+    every axis legend/.code={\let\addlegendentry\relax} 
     ] 
-    %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-150.data};
-    %%\addlegendentry{HC-CGC}
-    %
-    \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-150.data};            
-    \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-150.data};
-    \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-150.data};  
-    \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-150.data}; 
-    \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-150.data};
-    \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-150.data};
+    \anytimeplot{knott-3d-150}
 
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
@@
   legend to name = named,
-  legend columns=5
+  legend columns=6
   ]  
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-300.data};          \addlegendentry{HC-CGC}
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-300.data};               \addlegendentry{CGC}
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-300.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-300.data};          \addlegendentry{KL}
-
+  \anytimeplot{knott-3d-300}
   \end{semilogxaxis}
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
-  scaled ticks = false
+  scaled ticks = false,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ] 
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-450.data};
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-450.data};
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-450.data};
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-450.data};
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-450.data};
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-450.data};
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-450.data};
-
+  \anytimeplot{knott-3d-450} 
   \end{semilogxaxis}
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
-  scaled ticks = false
+  scaled ticks = false,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ]
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/knott-3d-550.data};
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/knott-3d-550.data};
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/knott-3d-550.data};
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data2/knott-3d-550.data};
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/knott-3d-550.data};
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/knott-3d-550.data};
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/knott-3d-550.data};
-
+  \anytimeplot{knott-3d-550} 
   \end{semilogxaxis}
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
-  scaled ticks = false
+  scaled ticks = false,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ] 
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/seg-3d.data};
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/seg-3d.data};
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/seg-3d.data};
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/seg-3d.data}; 
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/seg-3d.data}; 
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/seg-3d.data};
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/seg-3d.data};
-
+  \anytimeplot{seg-3d} 
   \end{semilogxaxis}
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
-  scaled ticks = false
+  scaled ticks = false,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ] 
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/socialnets.data};
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/socialnets.data};
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/socialnets.data};
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/socialnets.data};
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/socialnets.data};
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/socialnets.data};
-
+  \anytimeplot{socialnets} 
   \end{semilogxaxis}
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
-  scaled ticks = false
+  scaled ticks = false,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ]
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/normalizedsocialnets.data};
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/normalizedsocialnets.data};
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/normalizedsocialnets.data};
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/normalizedsocialnets.data};
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/normalizedsocialnets.data};
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data2/normalizedsocialnets.data};
-
+  \anytimeplot{normalizedsocialnets}
   \end{semilogxaxis}
   \end{tikzpicture}
-  \caption{social nets}
+  \caption{normalized social nets}
   \end{subfigure}
@@
   xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
   width = 1.0\columnwidth,
-  scaled ticks = false
+  scaled ticks = false,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ] 
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data2/modularity-clustering.data};
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data2/modularity-clustering.data};
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data2/modularity-clustering.data};
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data2/modularity-clustering.data};
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/modularity-clustering.data};
-  \addplot[color=orange,mark=x] table[x=time, y=DYNCC-HC-CGC]{data2/modularity-clustering.data};
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data2/modularity-clustering.data};
-
+  \anytimeplot{modularity-clustering}
   \end{semilogxaxis}

### 2014-11-07 paper/egpaper_for_review.tex
new plots

@@
 \end{tikzpicture}}
+
+% \newcommand{\anytimeplot}[1]{
+%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
+%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
+%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
+%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
+%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
+%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
+%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
+%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
+%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
+%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
+% }
+\newcommand{\anytimeplot}[1]{
+  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
+  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
+  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
+  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL}
+  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
+  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
+  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{Fusion-HC-MC}
+  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{Fusion-HC-CGC}
+  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{Fusion-WS-MC}
+  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{Fusion-WS-CGC}
+}
 
@@
 
+\input{anytimefigure2.tex}
+
 \begin{figure}

### 2014-11-07 paper/anytimefigure2.tex
add PIVOT-BOEM

@@
     \begin{semilogxaxis}[
-    restrict y to domain=-6000:-4400,
+   % restrict y to domain=-6000:-4400,
     xlabel = {runtime},
@@
     \anytimeplot{knott-3d-150}
+    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/knott-3d-150.data};
 
@@
   \anytimeplot{modularity-clustering}
+    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/modularity-clustering.data};
   \end{semilogxaxis}

### 2014-11-07 paper/anytimefigure2.tex
fiure update

@@
   ]  
-  \anytimeplot{socialnets} 
+  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/socialnets.data};              \addlegendentry{HC}
+  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/socialnets.data};          \addlegendentry{HC-CGC}
+  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/socialnets.data};               \addlegendentry{CGC}
+  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
+  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/socialnets.data};     \addlegendentry{MC-R}
+  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/socialnets.data};       \addlegendentry{MC-I}
+  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-MC}
+  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-CGC}
+  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
+  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/socialnets.data};  \addlegendentry{Fusion-WS-CGC}
+  %\anytimeplot{socialnets} 
   \end{semilogxaxis}
@@
   ] 
-  \anytimeplot{normalizedsocialnets}
+  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/normalizedsocialnets.data};              \addlegendentry{HC}
+  %\addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/normalizedsocialnets.data};          \addlegendentry{HC-CGC}
+  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/normalizedsocialnets.data};               \addlegendentry{CGC}
+  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
+  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/normalizedsocialnets.data};     \addlegendentry{MC-R}
+  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/normalizedsocialnets.data};       \addlegendentry{MC-I}
+  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-MC}
+  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-CGC}
+  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
+  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-CGC}
+ % \anytimeplot{normalizedsocialnets}
   \end{semilogxaxis}

### 2014-11-09 paper/anytimefigure2.tex
new figures, new stuff

@@
+%!TEX root = egpaper_for_review.tex
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \begin{tikzpicture}
-  \begin{semilogxaxis}[
+  \begin{semilogxaxis}[  mark size=1pt,
   restrict y to domain=0:4620,
@@
     \begin{tikzpicture}
-    \begin{semilogxaxis}[
+    \begin{semilogxaxis}[  mark size=1pt,
    % restrict y to domain=-6000:-4400,
@@
   \begin{tikzpicture}
-  \begin{semilogxaxis}[
+  \begin{semilogxaxis}[  mark size=1pt,
   restrict y to domain=-40000:-24000,
@@
   scaled ticks = false,
-  legend to name = named,
+  legend to name = ledgendPosition,
   legend columns=6
@@
   \begin{tikzpicture}
-  \begin{semilogxaxis}[
+  \begin{semilogxaxis}[  mark size=1pt,
   restrict y to domain=-80000:-60000,
@@
   \begin{tikzpicture}
-  \begin{semilogxaxis}[
+  \begin{semilogxaxis}[  mark size=1pt,
   restrict y to domain=-10000000:-100000,
@@
   \begin{tikzpicture}
-  \begin{semilogxaxis}[
+  \begin{semilogxaxis}[  mark size=1pt,
   %restrict y to domain=-10000000:-100000,
@@
   \hypersetup{linkcolor = black}
-  \ref{named}
+  \ref{ledgendPosition}
   \hypersetup{linkcolor = red}
@@
   \caption{
+    FOO
     Among all tested solvers, the proposed method is the only

### 2014-11-09 paper/egpaper_for_review.tex
new figures, new stuff

@@
 
+\input{inputs/fig_notation.tex}
+
 \section{Related Work}\label{sec:related_work}%
@@
 %\input{inputs/fig_alg_graph.tex}
+
+\input{inputs/fig_contraction.tex}
 
@@
 
-\textbf{Desired Properties}
+\noindent \textbf{Desired Properties:}
+As discussed in \cite{Lempitsky-2010}, proposals
+should have two properties: \emph{quality} 
+and \emph{diversity}.
+The quality / energy of the individual proposals
+ensures low energy solutions since the
+result of the fusion cannot be higher then
+the energy of the current best solution.
+Diversity between the individual proposals
+reduces the chances to get stuck in local minima.
+For correlation clustering fusion we add a third
+property: \emph{size}.
+The size of the contraction graph directly
+depends on the number of connected components
+in the proposal solution and the current best solution.
+The extreme  case is a proposal where each 
+node is in a separate connnected component.
+Solving the fusion move with such a proposal
+is equivalent to solving the original problem.
+Solving the fusion move with a proposal with 
+a single connected component will result 
+in the current best solution.
+Therefore the size of the proposals
+should be small enough, such that solving
+eq.~\ref{eq:edgeproblem} can
+be done fast enough, but large enough to make
+meaningful moves (??? this last sentence needs to be rewritten).
 
@@
 
-\subsubsection{Randomized MaxCut  (RMC)}
-
-To get energy aware proposals we can use max cuts.
-The max cut objective is the same as
-the multicut objective, but only two 
-node colors are allowed.
-Therefore solutions of the max cut objective
-might be useful proposals.
-To create different proposals we set 
-the weight of edges which are cut 
-in the best solution to zero.
-In this way we favor solutions 
-different form the current best. 
-In addition we either add noise permute a certain number of weights.
+%\subsubsection{Randomized MaxCut  (RMC)}
+%
+%To get energy aware proposals we can use max cuts.
+%The max cut objective is the same as
+%the multicut objective, but only two 
+%node colors are allowed.
+%Therefore solutions of the max cut objective
+%might be useful proposals.
+%To create different proposals we set 
+%the weight of edges which are cut 
+%in the best solution to zero.
+%In this way we favor solutions 
+%different form the current best. 
+%In addition we either add noise permute a certain number of weights.
 
@@
 
-\input{inputs/fig_hc.tex}
+%\input{inputs/fig_hc.tex}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\pgfplotsset{every axis legend/.append style={
-at={(1.0,1.2)},
-anchor=north east}} 
-\begin{figure*}
-  \begin{subfigure}[b]{0.33\textwidth}
-  \centering
-  \begin{tikzpicture}
-  \begin{semilogxaxis}[
-  restrict y to domain=0:4600,
-  xlabel = {runtime},
-  xmin = 0,
-  xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
-  width = 1.0\columnwidth,
-  scaled ticks = false,
-  ]
-  %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
-  %\addlegendentry{HC-CGC}
-
-  \addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data/image-seg.data};
-  %\addlegendentry{CGC-planar}
-
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/image-seg.data};
-  %\addlegendentry{MCI-CCIFD}
-
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/image-seg.data};
-  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
-
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/image-seg.data};
-  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
-
-  \end{semilogxaxis}
-  \end{tikzpicture}
-  \caption{image-seg}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.33\textwidth}
-    \centering
-    \begin{tikzpicture}
-    \begin{semilogxaxis}[
-    restrict y to domain=-6000:-4500,
-    xlabel = {runtime},
-    xmin = 0,
-    xmax = 4100,
-    %ymin =  75282844.25,
-    %ymax =  81774642.015,
-    %xtick       = { 1 , 60 , 3600 },
-    %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-    %ytick       = {75661636, 78718140, 81774643 },
-    %yticklabels = {$75661636$, $78718140$, $81774643$ },
-    width = 1.0\columnwidth,
-    scaled ticks = false
-    ]
-    %\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
-    %%\addlegendentry{HC-CGC}
-    %
-    \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-150.data};
-    %\addlegendentry{CGC} 
-    %
-    \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-150.data};
-    %\addlegendentry{MCI-CCIFD} 
-    %
-    \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-150.data};
-    %\addlegendentry{MC-Fusion (HC-MC-CGC)}
-    %
-    \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-150.data};
-    %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
-    %
-    \end{semilogxaxis}
-    \end{tikzpicture}
-    \caption{knott-3d-150}
-  \end{subfigure}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{subfigure}[b]{0.33\textwidth}
-  \centering
-  \begin{tikzpicture}
-  \begin{semilogxaxis}[
-  restrict y to domain=-40000:-24000,
-  xlabel = {runtime},
-  xmin = 0,
-  xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
-  width = 1.0\columnwidth,
-  scaled ticks = false,
-  legend to name = named,
-  legend columns=5
-  ]
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
-  \addlegendentry{HC-CGC}
-
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-300.data};
-  \addlegendentry{CGC}
-
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-300.data};
-  \addlegendentry{MCI-CCIFD}
-
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-300.data};
-  \addlegendentry{MC-Fusion (HC-MC-CGC)}
-
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-300.data};
-  \addlegendentry{MC-Fusion (HC-CGC-CGC)}
-
-  \end{semilogxaxis}
-  \end{tikzpicture}
-  \caption{knott-3d-300}
-  \end{subfigure}
-  \newline
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{subfigure}[b]{0.33\textwidth}
-  \centering
-  \begin{tikzpicture}
-  \begin{semilogxaxis}[
-  restrict y to domain=-80000:-60000,
-  xlabel = {runtime},
-  xmin = 0,
-  xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
-  width = 1.0\columnwidth,
-  scaled ticks = false
-  ]
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
-  %\addlegendentry{HC-CGC}
-
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-450.data};
-  %\addlegendentry{CGC}
-
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-450.data};
-  %\addlegendentry{MCI-CCIFD}
-
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-450.data};
-  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
-
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-450.data};
-  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
-
-  \end{semilogxaxis}
-  \end{tikzpicture}
-  \caption{knott-3d-450}
-  \end{subfigure}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{subfigure}[b]{0.33\textwidth}
-  \centering
-  \begin{tikzpicture}
-  \begin{semilogxaxis}[
-  restrict y to domain=-10000000:-100000,
-  xlabel = {runtime},
-  xmin = 0,
-  xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
-  width = 1.0\columnwidth,
-  scaled ticks = false
-  ]
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
-  %\addlegendentry{HC-CGC}
-
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-550.data};
-  %\addlegendentry{CGC}
-
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-550.data};
-  %\addlegendentry{MCI-CCIFD}
-
-  \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-550.data};
-  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
-
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-550.data};
-  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
-
-  \end{semilogxaxis}
-  \end{tikzpicture}
-  \caption{knott-3d-550}
-  \end{subfigure}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{subfigure}[H]
-  \begin{subfigure}[b]{0.33\textwidth}
-  \centering
-  \begin{tikzpicture}
-  \begin{semilogxaxis}[
-  %restrict y to domain=-10000000:-100000,
-  restrict y to domain=-10000000:700000,
-  xlabel = {runtime},
-  xmin = 0,
-  xmax = 4100,
-  %ymin =  75282844.25,
-  %ymax =  81774642.015,
-  %xtick       = { 1 , 60 , 3600 },
-  %xticklabels = { 1 sec. , 1 min.  , 1 hour },
-  %ytick       = {75661636, 78718140, 81774643 },
-  %yticklabels = {$75661636$, $78718140$, $81774643$ },
-  width = 1.0\columnwidth,
-  scaled ticks = false
-  ]
-  \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
-  %\addlegendentry{HC-CGC}
-
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data/seg-3d.data};
-  %\addlegendentry{CGC}
-
-  \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/seg-3d.data};
-  %\addlegendentry{MCI-CCIFD}
-
-  %\addplot[color=yellow,mark=o] table[x=time, y=DYNCC-HC-MC]{data/seg-3d.data};
-  %%\addlegendentry{MC-Fusion (HC-MC)}
-
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
-  %\addlegendentry{MC-Fusion (HC-MC-CGC)}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/seg-3d.data};
-  %DYNCC-HC-CGC-CGC
-  %\addlegendentry{MC-Fusion (HC-CGC-CGC)}
-
-  \end{semilogxaxis}
-  \end{tikzpicture}
-  \caption{seg-3d}
-  \end{subfigure}
-  \begin{center}
-  \hypersetup{linkcolor = black}
-  \ref{named}
-  \hypersetup{linkcolor = red}
-  \end{center}
-  \caption{
-    Among all tested solvers, the proposed method is the only
-    one scaling to large 3D data.
-    Except for the small 3D block, CC-Fusion finds very low
-    energies one to three magnitudes faster 
-    than any other method.
-    With increasing block size, is outperformed even more.
-    For the 2D datasets CGC is very fast, but our proposed
-    solver finds lower energies while still being faster
-    than the global optimal multicut solver.
-  }
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{anytimefigure.tex}
-
 \input{anytimefigure2.tex}

### 2014-11-10 paper/egpaper_for_review.tex
add comments to sec 4- need to be rivised

@@
 due to the agglomeration of edge weights, 
-hierarchical clustering is robust against noise.
+{\color{red} hierarchical clustering is robust against noise}.
+{\color{yellow} [ First most similar nodes are merged...]
 In agglomerative clustering, weights of
-parallel edges are merged into single edges.
+parallel edges are merged into single edges.}
 For image segmentation, the length
-weighted mean is used to do this update.
-
+weighted mean is used to do this update [ref].
+
+[We contrary on those works work directly on energy functions and that why ...]
 We propose to use Energy Based Hierarchical Clustering (EHC) to find
 solutions for correlation clustering.
-In each step, the edge with the highest weight $w$ is
+
+\textit{move this up} [ In each step, the edge with the highest weight $w$ is
 contracted (red edges in fig. ~\ref{fig:hc_alg}).
 Doing so, parallel edges edges can occur.
+]
+
 To make EHC follow the energy, we propose 

### 2014-11-10 paper/egpaper_for_review.tex
my changes

--- 2014-11-09 paper/egpaper_for_review.tex
@@
 \usepackage{filecontents}
+\usepackage{scrextend}
 \usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
@@
 
-\section{Energy Based Hierarchical Clustering (EHC)}
+\section{Energy Based Hierarchical Clustering (EHC)}\label{sec:ehc}
 
@@
 
+Within all experiments we used the following existing solvers 
+with public available implementation.
+\begin{itemize}
+    \item 
+    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
+    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
+    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
+    Therefore we exclude those in our experiments.
+    \item \textbf{KL}\cite{???}  and a public available 
+        implementation \footnote{
+            \label{opengm-master} 
+            \url{https://github.com/opengm/opengm}
+            %\label{opengm-master}
+        }
+    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
+    version of a public available implementation implementation\footref{opengm-master}.
+    We replace a highly used queue with a more suitable and
+    fast \emph{index-min-heap}\cite{???}.
+    MC-R indicates that only the LP is solved, while MC-I solves
+    the ILP.
+    \item non vision solvers here TODO
+\end{itemize}
+And the following proposed solvers:
+\begin{itemize}
+\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
+as described in sec.~\ref{sec:ehc}.
+\item \textbf{EHC-CGC}: As CGC but warm started 
+with the solution from EHC.
+\end{itemize}
+
 \subsection{Parameter Choice}
@@
 A application for large scale correlation clustering are social networks.
-We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{http://snap.stanford.edu/data/index.html}.
+We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
 Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 

### 2014-11-10 paper/inputs/fig_projection.tex
contrat and project

%!TEX root = ../egpaper_for_review.tex

\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=red, font=\small,align=left]
\tikzstyle{eNC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green, font=\small,align=left]
\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]
\tikzstyle{eCC}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left]

\begin{center}
\begin{figure}[h]
\begin{subfigure}[t]{0.4\linewidth}
    \resizebox{\linewidth}{!}{
        \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]
                \draw (0,1) node[nS] (n0) {$\{0,3\}$}; 
                \draw (3,1) node[nS] (n1) {$\{1,4\}$};
                \draw (6,1) node[nS] (n2) {$\{2,5\}$};
                \draw (0,0) node (d) {}; 
                \draw (0,3) node (d) {}; 
                %\draw (4,0) node[nS] (n4) {$4$};
                %\draw (6,0) node[nS] (n5) {$5$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}$} (n1) 
                    (n1) edge[eCC] node[eNS]{$w_{12}+$\\$w_{45}$} (n2) 
                    %(n3) edge[eCC] node[eNS]{$w_{34}$} (n4) 
                    %(n4) edge[eCC] node[eNS]{$w_{45}$} (n5)
                    %(n0) edge[eS] node[eNS]{$w_{03}$} (n3)
                    %(n1) edge[eS] node[eNS]{$w_{14}$} (n4)
                    %(n2) edge[eS] node[eNS]{$w_{25}$} (n5)
                ;
        \end{tikzpicture}
    }
\caption{ cut $y^*$ on contraction graph $G_w$ }
\label{fig:cont_c}
\end{subfigure}
\hfill
\begin{subfigure}[t]{0.4\linewidth}
    \resizebox{\linewidth}{!}{
        \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]
                \draw (2,2) node[nS] (n0) {$0$}; 
                \draw (4,2) node[nS] (n1) {$1$};
                \draw (6,2) node[nS] (n2) {$2$};
                \draw (2,0) node[nS] (n3) {$3$}; 
                \draw (4,0) node[nS] (n4) {$4$};
                \draw (6,0) node[nS] (n5) {$5$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n1) edge[eCC] node[eNS]{$w_{12}$} (n2) 
                    (n3) edge[eS] node[eNS]{$w_{34}$} (n4) 
                    (n4) edge[eCC] node[eNS]{$w_{45}$} (n5)
                    (n0) edge[eS] node[eNS]{$w_{03}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{14}$} (n4)
                    (n2) edge[eS] node[eNS]{$w_{25}$} (n5)
                ;
        \end{tikzpicture}
    }
\caption{ cut $y^*$ projected on $G$}
\label{fig:cont_d}
\end{subfigure}
\hfill
\caption{\emph{(Back projection from Contraction Graph)}
Given a edge labeling $\bar{y}^*$ of a contracted graph $G_y=(V_y,E_y, w_y)$.
We can back project the edge labeling to the original graph by 
assigning each $y_e$ the label of the edge to which it was contracted. 
}\label{fig:projection}
\end{figure}
\end{center}

### 2014-11-10 paper/egpaper_for_review.tex
contrat and project
fix broken package
improved proposal generation

@@
 
-%\begin{algorithm}
-%    \begin{scriptsize}
-%        \caption{Proposal Generators}\label{alg:proposal_gen}   
-%        \begin{algorithmic}[1]
-%            %\Require $J(x) \leq J(x')$
-%            %\Ensure $J(\hat{x}) \leq J(x)$
-%            %\vspace{0.3cm}
-%            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
-%
-%            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
-%            \State \textbf{return} $x'$
-%            \EndProcedure
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $ getRandomSeeds$
-%            \State $ runEdgeWeightedWs$
-%            \EndProcedure   
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
-%            \State $\hat{W} \gets W$
-%            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
-%                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
-%                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
-%            \EndWhile
-%            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
-%            \EndProcedure
-%        \end{algorithmic}
-%    \end{scriptsize}
-%\end{algorithm}
-
-\subsubsection{Randomized HierarchicalClustering (RHC)}
-
-To generate proposals cut we can use bottom up hierarchical clustering.
-In each step we contract the edge with the highest weight.
-Parallel edges are merged into single edges by summing their weights.
-We stop when a certain number of nodes is reached, or the
-largest edge weight among the not yet contracted edges is smaller then a certain threshold.
-To get versatile proposals we either add noise 
-to the edge weighs or permute a certain number of weights.
+\subsubsection{Randomized Energy Based Hierarchical Clustering (REHC)}\label{sec:prop:hc}
+
+To generate fast energy aware proposals we can use energy
+based hierarchical clustering (EHC) as defined in sec.~\ref{sec:ehc}.
+EHC follows the energy function, therefore the \emph{quality}
+of the proposals is high.
+To get \emph{diversity} among the different proposal,
+we add normal distributed noise with a standard deviation of $\sigma_{ehc}$
+to each edge weight.
+To get proposals of the desired \emph{size}, we can use a 
+different stop condition in EHC, and stop when a certain number of connected 
+components is reached.
 
@@
 
-\subsubsection{Randomized Watersheds (RWS)}
+\subsubsection{Randomized Watersheds (RWS)}\label{sec:prop:ws}
 
@@
 with random seeds can be used to get 
-cheap proposals. Instead of $n$ seeds distributed uniformly
-over all nodes we use the following.
+cheap proposals.
+
+To improve \emph{quality} we do not use $n$ seeds distributed uniformly
+over all nodes but use the following.
 Draw $n/k$ random edges only the negative edges, 
-and give the two nodes of each random edge different seeds.
+and give the two nodes of each ``seed-edge'' a different seed.
 Doing so, a random subset of negative edges is forced
 to be cut within each proposal.
-For additional randomness, noise can be added to
+For additional \emph{diversity} randomness, noise can be added to
 the edge weighs.

### 2014-11-10 paper/egpaper_for_review.tex
improved proposal generation

@@
 \usepackage{filecontents}
-\usepackage{scrextend}
+%\usepackage{scrextend}
 \usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
@@
 with public available implementation.
-\begin{itemize}
+\begin{compactitem}
     \item 
@@
     \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
-    version of a public available implementation implementation\footref{opengm-master}.
+    version of a public available implementation implementation %\footref{opengm-master}.
     We replace a highly used queue with a more suitable and
@@
     \item non vision solvers here TODO
-\end{itemize}
+\end{compactitem}
 And the following proposed solvers:
-\begin{itemize}
+\begin{compactitem}
 \item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
@@
 with the solution from EHC.
-\end{itemize}
+
+\item \textbf{Fusion-EHC-MC}
+\item \textbf{Fusion-EHC-GCG}
+\item \textbf{Fusion-WS-MC}
+\item \textbf{Fusion-WS-GCG}
+
+\end{compactitem}
 
@@
 
-\subsection{Synthetic Models}
+%\subsection{Synthetic Models}
 

### 2014-11-10 paper/egpaper_for_review.tex
refactor EHC

--- 2014-11-10 paper/egpaper_for_review.tex
@@
 \usepackage{filecontents}
-\usepackage{scrextend}
+%\usepackage{scrextend}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+\newcommand{\footlabel}[2]{%
+    \addtocounter{footnote}{1}%
+    \footnotetext[\thefootnote]{%
+        \addtocounter{footnote}{-1}%
+        \refstepcounter{footnote}\label{#1}%
+        #2%
+    }%
+    $^{\ref{#1}}$%
+}
+
+\newcommand{\footref}[1]{%
+    $^{\ref{#1}}$%
+}
 \usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 \usepackage{bm}% ändert \boldsymbol
@@
 
-\section{Energy Based Hierarchical Clustering (EHC)}\label{sec:ehc}
+\section{Energy Based Hierarchical Clustering}\label{sec:ehc}
 
@@
 \cite{arbelaez_2006}.
+In each step, the edge with the highest weight $w$ is
+contracted (red edges in Fig.~\ref{fig:hc_alg}).
+Doing so, parallel edges edges can occur.
 
@@
 solutions for correlation clustering.
-
-\textit{move this up} [ In each step, the edge with the highest weight $w$ is
-contracted (red edges in fig. ~\ref{fig:hc_alg}).
-Doing so, parallel edges edges can occur.
-]
 
@@
 \input{inputs/fig_contraction.tex}
+\input{inputs/fig_projection.tex}
 
@@
     \item \textbf{KL}\cite{???}  and a public available 
-        implementation \footnote{
-            \label{opengm-master} 
+        implementation 
+        \footlabel{opengm-master}{%
+        %\footnote{
+        %    \label{opengm-master} 
             \url{https://github.com/opengm/opengm}

### 2014-11-10 paper/egpaper_for_review.tex

--- 2014-11-10 paper/egpaper_for_review.tex
@@
 %\usepackage{scrextend}
+
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+\newcommand{\footlabel}[2]{%
+    \addtocounter{footnote}{1}%
+    \footnotetext[\thefootnote]{%
+        \addtocounter{footnote}{-1}%
+        \refstepcounter{footnote}\label{#1}%
+        #2%
+    }%
+    $^{\ref{#1}}$%
+}
+
+\newcommand{\footref}[1]{%
+    $^{\ref{#1}}$%
+}
+
 \usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}

### 2014-11-10 paper/egpaper_for_review.tex
update HC

--- 2014-11-10 paper/egpaper_for_review.tex
@@
 \section{Energy Based Hierarchical Clustering}\label{sec:ehc}
-
 Agglomerative hierarchical clustering (HC) is widely used
-in graph / image segmentation
-\cite{arbelaez_2006}.
+in graph / image segmentation~\cite{arbelaez_2006}.
 In each step, the edge with the highest weight $w$ is
@@
 Doing so, parallel edges edges can occur.
-
-Hierarchical clustering is fast, and 
-due to the agglomeration of edge weights, 
-{\color{red} hierarchical clustering is robust against noise}.
-{\color{yellow} [ First most similar nodes are merged...]
 In agglomerative clustering, weights of
-parallel edges are merged into single edges.}
+parallel edges are merged into single edges.
 For image segmentation, the length
-weighted mean is used to do this update [ref].
-
-[We contrary on those works work directly on energy functions and that why ...]
-We propose to use Energy Based Hierarchical Clustering (EHC) to find
-solutions for correlation clustering.
-
-To make EHC follow the energy, we propose 
-the following update rule:
+weighted mean is used to do this update~\cite{arbelaez_2006}.
+
+While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
+agglomeration with respect to our energy function.
+For this we propose to use energy based agglomeration
+withe the following update rule:
 Whenever there are multiple edges between 
@@
 minimize the sum of the cut edges.
-The algorithm stops if the highest edge weight is
-smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
+We call HC with this update method Energy base Hierarchical Clustering (EHC).
+
+We stop EHC if the highest edge weight is
+smaller or equal to zero  (green edge in Fig.~\ref{fig:hc_alg}). Any further edge
 contraction leads to worse energies.
+
+% Hierarchical clustering is fast, and 
+% due to the agglomeration of edge weights, 
+% {\color{red} hierarchical clustering is robust against noise}.
+% {\color{yellow} [ First most similar nodes are merged...]
+% In agglomerative clustering, weights of
+% parallel edges are merged into single edges.}
+% For image segmentation, the length
+% weighted mean is used to do this update [ref].
+
+% [We contrary on those works work directly on energy functions and that why ...]
+% We propose to use Energy Based Hierarchical Clustering (EHC) to find
+% solutions for correlation clustering.
+
+% To make EHC follow the energy, we propose 
+% the following update rule:
+% Whenever there are multiple edges between 
+% a pair of nodes, these edges are merged into a single edge
+% by summing up their weights, since we 
+% minimize the sum of the cut edges.
+% The algorithm stops if the highest edge weight is
+% smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
+% contraction leads to worse energies.
 
@@
 But EHC is very fast, and can be used to initialize
-CGC \cite{beier_2014_cvpr}. Excessive time in CGC
+CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
 is spend in the \emph{cut phase} to solve the 
 first 2 coloring on the complete graph.
-As shown in ~\ref{sec:exp},
+As shown in Sec.~\ref{sec:exp},
 allowing CGC to start from the EHC solution
@@
 
-%\input{inputs/fig_hc_alg.tex}
-
-Common cluster distances
-\begin{itemize}
-\item Single-Link: Nearest Neighbor - their closest members.
-\item Complete-Link: Furthest Neighbor - their furthest members.
-\item Centroid: Distance between centroids
-\item Group Average: average of all cross-cluster pairs.
-\end{itemize}
+% Common cluster distances
+% \begin{itemize}
+% \item Single-Link: Nearest Neighbor - their closest members.
+% \item Complete-Link: Furthest Neighbor - their furthest members.
+% \item Centroid: Distance between centroids
+% \item Group Average: average of all cross-cluster pairs.
+% \end{itemize}
 
 %------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion (CCF) Moves}\label{sec:cc_fm}
+\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
 Motivation Using Fusion moves -> problem ambiguity

### 2014-11-10 paper/anytimefigure2.tex
inital version of text under any time plots

@@
   \end{tikzpicture}
-  \caption{image-seg}
+  \caption{image-seg}\label{fig:at:image-seg}
   \end{subfigure}
@@
     \end{tikzpicture}
-    \caption{knott-3d-150}
+    \caption{knott-3d-150}\label{fig:at:knott-150}
   \end{subfigure}
@@
   \end{tikzpicture}
-  \caption{knott-3d-300}
+  \caption{knott-3d-300}\label{fig:at:knott-300}
   \end{subfigure}
@@
   \end{tikzpicture}
-  \caption{knott-3d-450}
+  \caption{knott-3d-450}\label{fig:at:knott-450}
   \end{subfigure}
@@
   \end{tikzpicture}
-  \caption{knott-3d-550}
+  \caption{knott-3d-550}\label{fig:at:knott-550}
   \end{subfigure}
@@
   \end{tikzpicture}
-  \caption{seg-3d}
+  \caption{seg-3d}\label{fig:at:seg3d}
   \end{subfigure}
@@
   \end{tikzpicture}
-  \caption{social nets}
+  \caption{social nets}\label{fig:at:socialnets}
   \end{subfigure}
@@
   \end{tikzpicture}
-  \caption{normalized social nets}
+  \caption{normalized social nets}\label{fig:at:nsocialnets}
   \end{subfigure}
@@
   \end{tikzpicture}
-  \caption{modularity clustering}
+  \caption{modularity clustering}\label{fig:at:modularity}
   \end{subfigure}
@@
   \caption{
-    FOO
-    Among all tested solvers, the proposed method is the only
-    one scaling to large 3D data.
-    Except for the small 3D block, CC-Fusion finds very low
-    energies one to three magnitudes faster 
-    than any other method.
-    With increasing block size, is outperformed even more.
-    For the 2D datasets CGC is very fast, but our proposed
-    solver finds lower energies while still being faster
-    than the global optimal multicut solver.
+    % image seg
+    For the image-seg instances in fig.~\ref{fig:at:image-seg} 
+    Fusion-EHC-MC has performs best and Fusion-WS-MC gives 
+    almost the same results, but a bit slower then with EHC proposals.
+    Using the same proposals but approximate moves (Fusion-EHC-CGC Fusion-WS-CGC )
+    leads to suboptimal results.
+    The warm EHC started version of GCG (EHC-CGC) performs better then GCG itself,
+    but both are outperformed by the proposed algorithms.
+    Global optimal methods (MC-I) and the relaxed version (MC-R) are 
+    still usable fast for these instances.
+    % 3d 
+    For the smallest 3D instances (\ref{fig:at:knott-150}) all solvers
+    except ??? and EHC perform equally, and the proposed fusion algorithms
+    give the best any time performance.
+    With increasing problem size (\ref{fig:at:knott-150}-\ref{fig:at:knott-550} and \ref{fig:at:seg3d})
+    the runtime of MC-I, MC-R and CGC increases drastically, while
+    the proposed solvers still scale well.
+    For these instances, the EHC started version of CGC outperforms 
+    GCG in terms of runtime and energy.
+    % social nets
+    For the social net instances (\ref{fig:at:socialnets},\ref{fig:at:nsocialnets})
+    Fusion-HC-MC and Fusion-HC-CGC perform equally.
+    Only CGC and EHC-CGC leads to better energies after $10^3 sec$, while global optimal methods (MC-I)
+    fail to converge within this time limit.
+    % modularity clustering 
+    For the modularity clustering instances in fig.~\ref{fig:at:modularity} we see
+    an interesting behavior. On these complete graphs, Kernighan Lin (KL) has the 
+    best performance.
+    The proposed methods perform reasonable, but  KL is faster and leads to better energies.
+    %%%
+    %% summary
+    Overall, energy hierarchical clustering based proposals work better
+    then watershed based proposals. They converge to similar energies
+    but the clustering based approach is faster on all tested instances.
+    On all instances except for modularity clustering, it is better
+    to solve the fusion move to optimality (Fusion-HC-MC) then using approximations (FUSION-HC-GCG).
   }

### 2014-11-10 paper/egpaper_for_review.tex
inital version of text under any time plots

--- 2014-11-10 paper/egpaper_for_review.tex
@@
 
-\section{Energy Based Hierarchical Clustering}\label{sec:ehc}
+\section{Energy Based Hierarchical Clustering (EHC)}\label{sec:ehc}
 
@@
 \cite{arbelaez_2006}.
-In each step, the edge with the highest weight $w$ is
-contracted (red edges in Fig.~\ref{fig:hc_alg}).
-Doing so, parallel edges edges can occur.
 
@@
 solutions for correlation clustering.
+
+\textit{move this up} [ In each step, the edge with the highest weight $w$ is
+contracted (red edges in fig. ~\ref{fig:hc_alg}).
+Doing so, parallel edges edges can occur.
+]
 
@@
     \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
-    version of a public available implementation implementation %\footref{opengm-master}.
+    version of a public available implementation implementation \footref{opengm-master}.
     We replace a highly used queue with a more suitable and

### 2014-11-10 paper/egpaper_for_review.tex

--- 2014-11-10 paper/egpaper_for_review.tex
@@
     \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified
-    version of a public available implementation implementation\footref{opengm-master}.
+
+    version of a public available implementation implementation \footref{opengm-master}.
+
     We replace a highly used queue with a more suitable and

### 2014-11-10 paper/egpaper_for_review.tex
seg on fusion

@@
 \section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
+
+\textbf{new}
+
+Fusion moves as defined in \cite{Lempitsky-2010} work
+in the node domain and do not work properly for 
+objective functions as Eq.~\ref{eq:nodeproblem} since
+the node coloring is ambiguous and has no semantic meaning.
+In the following, we propose a more suitable fusion move for correlation
+clustering which works on the edge domain.
+%
+Given two proposal solutions $y'$ and $y''$,
+$\mathcal{C}$ is the set of edges
+which are uncut in $y'$ and $y''$.
+
+\begin{align}
+\breve{y}    & =  y' \cup y'' \\
+\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
+\end{align}
+
+The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
+with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
+
+\begin{align}
+  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
+  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
+\end{align}
+
+By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
+\begin{align}
+  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
+\end{align}
+
+Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
+we can work on a coarser graph, where all nodes which are connected
+via must-link constraints are merged into single nodes.
+This coarser graph is constructed by contracting all must-link edges.
+
+\textbf{old}
+
 Motivation Using Fusion moves -> problem ambiguity

### 2014-11-10 paper/egpaper_for_review.tex
update plots
mystuff

@@
 }}
+
+% Two Colored Circle Split 
+\makeatletter
+\tikzset{circle split part fill/.style  args={#1,#2}{%
+ alias=tmp@name, 
+  postaction={%
+    insert path={
+     \pgfextra{% 
+     \pgfpointdiff{\pgfpointanchor{\pgf@node@name}{center}}%
+                  {\pgfpointanchor{\pgf@node@name}{east}}%            
+     \pgfmathsetmacro\insiderad{\pgf@x}
+      \fill[#1] (\pgf@node@name.base) ([xshift=-\pgflinewidth]\pgf@node@name.east) arc
+                          (0:180:\insiderad-\pgflinewidth)--cycle;
+      \fill[#2] (\pgf@node@name.base) ([xshift=\pgflinewidth]\pgf@node@name.west)  arc
+                           (180:360:\insiderad-\pgflinewidth)--cycle;            
+         }}}}}  
+ \makeatother
 
@@
 
+\input{inputs/fig_fusion.tex}
+
 \textbf{new}
@@
 which are uncut in $y'$ and $y''$.
-
+%
 \begin{align}
@@
 \end{align}
-
+%
 The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
 with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
-
+%
 \begin{align}
@@
 \end{align}
-
+%
 By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
@@
 \end{align}
-
+%
 Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 

### 2014-11-10 paper/inputs/fig_fusion.tex
mystuff

%!TEX root = ../egpaper_for_review.tex

\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{nD}=[shape = circle split,rotate=45,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]

\tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
\tikzstyle{eC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=red, font=\small,align=left]
\tikzstyle{eNC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green!70!black, font=\small,align=left, line width=1mm]
\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]
\tikzstyle{eCC}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left, draw=red!70!black, line width=1mm]

\tikzset{
  head/.style = {fill = orange!90!blue,
                 label = center:\textsf{\Large H}},
  tail/.style = {fill = blue!70!yellow, text = black,
                 label = center:\textsf{\Large T}}
}

\begin{center}
\begin{figure}[ht]
\begin{tiny}

\begin{subfigure}[t]{0.7\linewidth}
    \resizebox{\linewidth}{!}{
        \begin{tikzpicture}[scale=1]%[x=1 cm, y=1 cm]

                \draw (2,2-2) node[nS,fill=red!60] (n0) {$0$}; 
                \draw (4,2-2) node[nS,fill=red!60] (n1) {$1$};
                \draw (2,0-2) node[nS,fill=green!60] (n3) {$2$}; 
                \draw (4,0-2) node[nS,fill=green!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                % 1. FUSION
                \draw (2+4,2) node[nS,fill=red!60] (n0) {$0$}; 
                \draw (4+4,2) node[nS,fill=green!60] (n1) {$1$};
                \draw (2+4,0) node[nS,fill=red!60] (n3) {$2$}; 
                \draw (4+4,0) node[nS,fill=green!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                \draw (2+4,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
                \draw (4+4,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
                \draw (2+4,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
                \draw (4+4,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                % 2. FUSION
                \draw (2+8,2) node[nS,fill=blue!60] (n0) {$0$}; 
                \draw (4+8,2) node[nS,fill=green!60] (n1) {$1$};
                \draw (2+8,0) node[nS,fill=blue!60] (n3) {$2$}; 
                \draw (4+8,0) node[nS,fill=green!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                \draw (2+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
                \draw (4+8,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
                \draw (2+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
                \draw (4+8,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                % 3. FUSION
                \draw (2+12,2) node[nS,fill=red!60] (n0) {$0$}; 
                \draw (4+12,2) node[nS,fill=blue!60] (n1) {$1$};
                \draw (2+12,0) node[nS,fill=red!60] (n3) {$2$}; 
                \draw (4+12,0) node[nS,fill=blue!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                \draw (2+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
                \draw (4+12,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
                \draw (2+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
                \draw (4+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                % 4. FUSION
                \draw (2+16,2) node[nS,fill=magenta!60] (n0) {$0$}; 
                \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
                \draw (2+16,0) node[nS,fill=magenta!60] (n3) {$2$}; 
                \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

                \draw (2+16,2-4) node[nD, circle split part fill={red!60, magenta!60}] (n0) {$ $}; 
                \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
                \draw (2+16,0-4) node[nD, circle split part fill={green!60, magenta!60}] (n3) {$ $}; 
                \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
                \path
                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
                    (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
                    (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
                    (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
                ;

        \end{tikzpicture}
    }
\caption{b}
\label{fig:f_b}
\end{subfigure}

\end{tiny}
\caption{
w
}\label{fig:fusion_abiguty}
\end{figure}
\end{center}

### 2014-11-10 paper/anytimefigure2.tex

@@
   ]
+  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/image-seg.data};    \addlegendentry{PIVOT-BOEM}  
   \anytimeplot{image-seg}
@@
   \end{tikzpicture}
+
   \caption{image-seg}\label{fig:at:image-seg}
@@
     ] 
+    \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/knott-3d-150.data};          \addlegendentry{PIVOT-BOEM}
     \anytimeplot{knott-3d-150}
-    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/knott-3d-150.data};
 
@@
   scaled ticks = false,
-  legend to name = ledgendPosition,
-  legend columns=6
+  %legend to name = ledgendPosition,
+  legend columns=6,
+  every axis legend/.code={\let\addlegendentry\relax} 
   ]  
@@
   ]  
-  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/socialnets.data};              \addlegendentry{HC}
-  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/socialnets.data};          \addlegendentry{HC-CGC}
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/socialnets.data};               \addlegendentry{CGC}
-  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
-  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/socialnets.data};     \addlegendentry{MC-R}
-  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/socialnets.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-CGC}
-  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/socialnets.data};  \addlegendentry{Fusion-WS-CGC}
-  %\anytimeplot{socialnets} 
+  \anytimeplot{socialnets} 
   \end{semilogxaxis}
@@
   ] 
-  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/normalizedsocialnets.data};              \addlegendentry{HC}
-  %\addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/normalizedsocialnets.data};          \addlegendentry{HC-CGC}
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/normalizedsocialnets.data};               \addlegendentry{CGC}
-  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
-  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/normalizedsocialnets.data};     \addlegendentry{MC-R}
-  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/normalizedsocialnets.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-CGC}
-  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-CGC}
- % \anytimeplot{normalizedsocialnets}
+  \anytimeplot{normalizedsocialnets}
   \end{semilogxaxis}
@@
   width = 1.0\columnwidth,
-  scaled ticks = false,
-  every axis legend/.code={\let\addlegendentry\relax} 
+  legend to name = ledgendPosition,
+  legend columns=6,
+  scaled ticks = false%,
+  %every axis legend/.code={\let\addlegendentry\relax} 
   ]
+  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/modularity-clustering.data};    \addlegendentry{PIVOT-BOEM} 
   \anytimeplot{modularity-clustering}
-    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/modularity-clustering.data};
   \end{semilogxaxis}

### 2014-11-10 paper/egpaper_for_review.tex
add figure speedup MC

--- 2014-11-10 paper/egpaper_for_review.tex
@@
   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL} 
+  \addplot[color=yellow!50!black,mark=square] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
   \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
@@
 }
+%  \addplot[color=yellow!50!black,mark=o] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
+  %\addplot[color=green!50,mark=o] table[x=time, y=PIVOT*]{data3/#1.data};          \addlegendentry{PIVOT-BOEM}
 
@@
 
+ \begin{figure}[ht]
+    \centering
+    \begin{tikzpicture}
+    \begin{semilogxaxis}[  mark size=1pt,
+   % restrict y to domain=-6000:-4400,
+   %   restrict x to domain=10:4000,
+    xlabel = {runtime},
+    xmin = 0,
+    xmax = 4100,
+    legend to name = ledgendPositionMC,
+    legend columns=4,
+    width = 1.0\columnwidth,
+    scaled ticks = false
+    ] 
+    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
+    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
+    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
+    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}
+
+    \end{semilogxaxis}
+    \end{tikzpicture}
+  \begin{center}
+  \hypersetup{linkcolor = black}
+  \ref{ledgendPositionMC}
+  \hypersetup{linkcolor = red}
+  \end{center}
+    \caption{knott-3d-450b}\label{fig:at:knott-450b}
+  \end{figure}
+
 \subsection{Parameter Choice}

### 2014-11-10 paper/inputs/fig_fusion.tex
mystuff

@@
 \begin{figure}[ht]
-\begin{tiny}
-
-\begin{subfigure}[t]{0.7\linewidth}
 \resizebox{\linewidth}{!}{
@@
             % 2. FUSION
-                \draw (2+8,2) node[nS,fill=blue!60] (n0) {$0$}; 
-                \draw (4+8,2) node[nS,fill=green!60] (n1) {$1$};
-                \draw (2+8,0) node[nS,fill=blue!60] (n3) {$2$}; 
-                \draw (4+8,0) node[nS,fill=green!60] (n4) {$3$};
+            \draw (2+8,2) node[nS,fill=red!60] (n0) {$0$}; 
+            \draw (4+8,2) node[nS,fill=blue!60] (n1) {$1$};
+            \draw (2+8,0) node[nS,fill=red!60] (n3) {$2$}; 
+            \draw (4+8,0) node[nS,fill=blue!60] (n4) {$3$};
             \path
@@
 
-                \draw (2+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
-                \draw (4+8,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
-                \draw (2+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
+            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
+            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
             \draw (4+8,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
@@
             % 3. FUSION
-                \draw (2+12,2) node[nS,fill=red!60] (n0) {$0$}; 
-                \draw (4+12,2) node[nS,fill=blue!60] (n1) {$1$};
-                \draw (2+12,0) node[nS,fill=red!60] (n3) {$2$}; 
-                \draw (4+12,0) node[nS,fill=blue!60] (n4) {$3$};
+            \draw (2+12,2) node[nS,fill=green!60] (n0) {$0$}; 
+            \draw (4+12,2) node[nS,fill=red!60] (n1) {$1$};
+            \draw (2+12,0) node[nS,fill=green!60] (n3) {$2$}; 
+            \draw (4+12,0) node[nS,fill=red!60] (n4) {$3$};
             \path
@@
 
-                \draw (2+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
-                \draw (4+12,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
-                \draw (2+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
-                \draw (4+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
+            \draw (2+12,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
+            \draw (4+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
+            \draw (2+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
+            \draw (4+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
             \path
@@
             % 4. FUSION
-                \draw (2+16,2) node[nS,fill=magenta!60] (n0) {$0$}; 
+            \draw (2+16,2) node[nS,fill=green!60] (n0) {$0$}; 
             \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
-                \draw (2+16,0) node[nS,fill=magenta!60] (n3) {$2$}; 
+            \draw (2+16,0) node[nS,fill=green!60] (n3) {$2$}; 
             \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
@@
 
-                \draw (2+16,2-4) node[nD, circle split part fill={red!60, magenta!60}] (n0) {$ $}; 
-                \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
-                \draw (2+16,0-4) node[nD, circle split part fill={green!60, magenta!60}] (n3) {$ $}; 
-                \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
+            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
+            \draw (4+16,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
+            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
+            \draw (4+16,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
+            \path
+                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            % 5. FUSION
+            \draw (2+20,2) node[nS,fill=blue!60] (n0) {$0$}; 
+            \draw (4+20,2) node[nS,fill=red!60] (n1) {$1$};
+            \draw (2+20,0) node[nS,fill=blue!60] (n3) {$2$}; 
+            \draw (4+20,0) node[nS,fill=red!60] (n4) {$3$};
+            \path
+                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            \draw (2+20,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
+            \draw (4+20,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
+            \draw (2+20,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (4+20,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
+            \path
+                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            % 6. FUSION
+            \draw (2+24,2) node[nS,fill=blue!60] (n0) {$0$}; 
+            \draw (4+24,2) node[nS,fill=green!60] (n1) {$1$};
+            \draw (2+24,0) node[nS,fill=blue!60] (n3) {$2$}; 
+            \draw (4+24,0) node[nS,fill=green!60] (n4) {$3$};
+            \path
+                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            \draw (2+24,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
+            \draw (4+24,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
+            \draw (2+24,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (4+24,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
+            \path
+                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            % 7. FUSION
+            \draw (2+28,2) node[nS,fill=blue!60] (n0) {$0$}; 
+            \draw (4+28,2) node[nS,fill=yellow!60] (n1) {$1$};
+            \draw (2+28,0) node[nS,fill=blue!60] (n3) {$2$}; 
+            \draw (4+28,0) node[nS,fill=yellow!60] (n4) {$3$};
+            \path
+                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            \draw (2+28,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
+            \draw (4+28,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
+            \draw (2+28,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (4+28,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
             \path
@@
 }
-\caption{b}
-\label{fig:f_b}
-\end{subfigure}
-
-\end{tiny}
 \caption{

### 2014-11-10 paper/egpaper_for_review.tex
start exp sec

@@
 \section{Experiments}\label{sec:exp}
-
-Within all experiments we used the following existing solvers 
-with public available implementation.
-\begin{itemize}
-    \item 
-    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
-    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
-    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
-    Therefore we exclude those in our experiments.
-    \item \textbf{KL}\cite{???}  and a public available 
+In our experiments we compare to the following methods withpublic available implementation.
+
+Cut, Clue \& Cut~\cite{beier_2014_cvpr} (\textbf{CGC}): We used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
+of the original authors.
+\textbf{KL}~\cite{Kerninghan-1970}: We use the the  public available 
         implementation 
@@
 
- \begin{figure}[ht]
+ \begin{figure}[t]
     \centering
@@
     \begin{semilogxaxis}[  mark size=1pt,
-   % restrict y to domain=-6000:-4400,
+     height= 4cm, 
+    restrict y to domain=-80000:1000,
    %   restrict x to domain=10:4000,
     xlabel = {runtime},
-    xmin = 0,
+    xmin = 10,
     xmax = 4100,
+    ymax = 0,
+    ymin = -80000,
     legend to name = ledgendPositionMC,
     legend columns=4,
-    width = 1.0\columnwidth,
+    width = 0.9\columnwidth,
     scaled ticks = false
@@
   \end{center}
-    \caption{knott-3d-450b}\label{fig:at:knott-450b}
+    \caption{Comparison of the Multicut implementation of OpenGM and 
+    our modified implementation, which can deal better with large scale problems. 
+    However, for large scale problems it still does not scale.}
+    \label{fig:at:knott-450b}
   \end{figure}
+
+As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
+    Therefore we exclude those in our experiments.
 

### 2014-11-10 paper/inputs/fig_fusion.tex
cool fig

@@
 \begin{center}
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \resizebox{\linewidth}{!}{
@@
 
-            \draw (2,2-2) node[nS,fill=red!60] (n0) {$0$}; 
-            \draw (4,2-2) node[nS,fill=red!60] (n1) {$1$};
-            \draw (2,0-2) node[nS,fill=green!60] (n3) {$2$}; 
-            \draw (4,0-2) node[nS,fill=green!60] (n4) {$3$};
+            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
+            (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
+            {proposal edge \\ labeling $\bm{x'}$};
+
+            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
+            (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
+            {proposal edge \\ labeling $\bm{x''}$};
+
+            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
+            (5,3.5) -- (5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
+            {proposal node \\ labeling $\bm{l'}$};
+
+            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
+            (5,3-3.5) -- (5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
+            {proposal node \\ labeling $\bm{l''}$};
+
+            \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
+            (5,-4.5) -- (5,-1.5) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
+            {Binary fusion \\ move problem};
+
+            \draw (2-2,2+4) node[nS] (n0) {$0$}; 
+            \draw (4-2,2+4) node[nS] (n1) {$1$};
+            \draw (2-2,0+4) node[nS] (n3) {$2$}; 
+            \draw (4-2,0+4) node[nS] (n4) {$3$};
+            \path
+                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eCC] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eCC] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            \draw (2-2,2) node[nS] (n0) {$0$}; 
+            \draw (4-2,2) node[nS] (n1) {$1$};
+            \draw (2-2,0) node[nS] (n3) {$2$}; 
+            \draw (4-2,0) node[nS] (n4) {$3$};
+            \path
+                (n0) edge[eCC] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eCC] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+            ;
+
+            % first segmentation as coloring
+            \draw (2+4,2+4) node[nS,fill=red!60] (n0) {$0$}; 
+            \draw (4+4,2+4) node[nS,fill=red!60] (n1) {$1$};
+            \draw (2+4,0+4) node[nS,fill=green!60] (n3) {$2$}; 
+            \draw (4+4,0+4) node[nS,fill=green!60] (n4) {$3$};
             \path
@@
             \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
-            \draw (4+16,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
+            \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
             \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
-            \draw (4+16,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
+            \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
             \path
@@
 
+            \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0.8cm]
+            (5,-6) -- (33,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
+            {
+                For all different colorings $l''$, the binary fusion move subproblem is different.
+            };
+
+            \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0.8cm]
+            (5,2) -- (33,2) node [black,midway,xshift=0cm,yshift=1cm] 
+            {
+                All these node labelings encode the same partition
+            };
+
+            \draw[black] (5,-1) -- (33,-1);
+
     \end{tikzpicture}
@@
 }\label{fig:fusion_abiguty}
-\end{figure}
+\end{figure*}
 \end{center}

### 2014-11-10 paper/egpaper_for_review.tex

@@
 
-Cut, Clue \& Cut~\cite{beier_2014_cvpr} (\textbf{CGC}): We used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
-of the original authors.
-\textbf{KL}~\cite{Kerninghan-1970}: We use the the  public available 
-        implementation 
-        \footlabel{opengm-master}{%
-        %\footnote{
-        %    \label{opengm-master} 
-            \url{https://github.com/opengm/opengm}
-            %\label{opengm-master}
-        }
-    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified
-
-    version of a public available implementation implementation \footref{opengm-master}.
-
-    We replace a highly used queue with a more suitable and
-    fast \emph{index-min-heap}\cite{???}.
-    MC-R indicates that only the LP is solved, while MC-I solves
-    the ILP.
-    \item non vision solvers here TODO
-\end{itemize}
-And the following proposed solvers:
-\begin{itemize}
-\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
+For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
+of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
+For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
+of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
+Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
+Secondly, we follow~\cite{kroeger_2012_eccv}. and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+during the separation procedure.
+This procedure is one magnitude faster, but might cause a few extra outer iterations.
+In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
+For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
+From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
+We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
+While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
+We also run classical fusion moves~\cite{Lempinsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
+
+As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
+Therefore we exclude those in our experiments.
+
+We compare this methods to the following methods suggested in the present paper.
+%
+Energy Based Based Hierarchical Clustering (\textbf{EHC})
 as described in sec.~\ref{sec:ehc}.
-\item \textbf{EHC-CGC}: As CGC but warm started 
-with the solution from EHC.
-\end{itemize}
+%
+CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
+%
+The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
+ and MC-I and CGC as subproblem solvers denoted by 
+\textbf{fusionCC-HC-MC},
+\textbf{fusionCC-HC-CGC},
+\textbf{fusionCC-WS-MC}, and 
+\textbf{fusionCC-WS-CGC}, respectively.
+We set the size of the proposals fix to $10\%$ of the original problem size
+and the standard derivation of the random edge noise to $1.5$.
 
@@
 
-As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
-    Therefore we exclude those in our experiments.
-
 \subsection{Parameter Choice}
@@
 Both, the 2D and 3D models are available in a recent graphical model
-benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr}.
+benchmark of Kappes \etal~\cite{kappes_2013_benchmark_cvpr}.
 We use the same names for the datasets as in the benchmark,
@@
 for the models from \cite{kroeger_2012_eccv}.
-The size of instances is given in tab. ~\ref{tab:instance_sizes}.
+The size of instances is given in Tab.~\ref{tab:instance_sizes}.
 
@@
          knott-550        &     27286 - 31249   & ???        & 2            & $\times$ \\
-         3d-seg           &     7958 - 101220   & ???        & 2            & $\times$ \\
+         3d-seg           &     101220   & ???        & 1            & $\times$ \\
          slashdot         &     ???             & ???        & ???          & $\times$ \\     
+      \bottomrule
+   \end{tabular}
+\end{table}
+
+\begin{table}[H]
+   \tiny
+   \centering
+   \caption{Eval}
+   \label{tab:eval}
+   \begin{tabular}{lllllll}
+      \toprule
+         Dataset          &  image-seg &  knott-3d-150 &knott-3d-300 &knott-3d-450 &knott-3d-550 &3d-seg\\
+      \midrule 
+         PIVOT-BOEM       &      \\ 
+         HC               &\\
+         HC-CGC           &    \\
+         CGC              &   \\
+         KL               & \\
+         FUSION           &  \\
+         MC-R             &  \\   
+         MC-I             &  \\  
+         FusionCC-HC-MC   &  \\  
+         FusionCC-HC-CGC  &  \\  
+         FusionCC-WS-MC   &  \\  
+         FusionCC-WS-CGC  &  \\      
       \bottomrule

### 2014-11-10 paper/egpaper_for_review.tex
fixed errors in 2 plots

@@
 \input{inputs/fig_projection.tex}
-
-\subsection{Define Fusion on Segmentations}
-
-Given two proposal solutions $y'$ and $y''$
-the fusion move between those solutions is defined
-as follows:
-
-Let the $\bar{y}$ be the edge wise or of  $y'$ and $y''$.
-\begin{equation}
-\breve{y} =  y' \cup y''.
-\end{equation}
-Contraction of all edges in $G$ where $\bar{y}=0$ defines
-a smaller graph $G_{\bar{y}}$ and the corresponding
-edge weights $W_{\hat{y}}$.
-Any cut $\bar{y}$ on $G_{\hat{y}}$ induces a cut $y$ on $G$.
-The function 
-$\rho_y^{-1}$ maps a cut from $G_{\hat{y}}$  to $G$
-
-\begin{equation}
-   \rho_y^{-1} : P(G_y) \to P(G)
-\end{equation}
-
-Therefore solving eq. \ref{eq:edgeproblem} 
-on $G_{\hat{y}}$
-leads to a cut on $G$ which is guaranteed to 
-to have a better or equal energy
-then any of the two proposal solutions.
 
@@
 
-\begin{center}
-    \begin{eqnarray}
-        y 
-        &=& 
-        \rho_{\hat{y}}^{-1}(
-        \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
-        \sum_{ (i,j) \in E_{\hat{y}} } 
-        w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
-    \end{eqnarray}
-\end{center}
-
-\begin{center}
-    \begin{eqnarray}
-      y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
-    \end{eqnarray}
-\end{center}
+% \begin{center}
+%     \begin{eqnarray}
+%         y 
+%         &=& 
+%         \rho_{\hat{y}}^{-1}(
+%         \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
+%         \sum_{ (i,j) \in E_{\hat{y}} } 
+%         w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
+%     \end{eqnarray}
+% \end{center}
+
+% \begin{center}
+%     \begin{eqnarray}
+%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
+%     \end{eqnarray}
+% \end{center}
 

### 2014-11-10 paper/inputs/fig_hc_alg.tex
update related work, relayout Figure EHC
fixed errors in 2 plots

@@
 
-\tikzstyle{nS}=[circle,minimum size = 0.3cm,inner sep = 0pt,draw, font=\small,align=left]
+\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
 \tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
@@
 \begin{center}
-\begin{figure}
-\resizebox{!}{0.30\linewidth}{%
+\begin{figure*}
+\resizebox{!}{0.15\linewidth}{%
     \begin{tikzpicture}
@@
         (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
-        (n1) edge[eS] node[eNS]{$w_{14}=1$} (n4)
+        (n1) edge[eS] node[eNS]{$w_{14}=2$} (n4)
         (n2) edge[eC] node[eNS]{$w_{25}=3$} (n5)
@@
 }
-
-\resizebox{!}{0.30\linewidth}{%
+%
+\resizebox{!}{0.15\linewidth}{%
     \begin{tikzpicture}
@@
 }\label{fig:hc_alg}
-\end{figure}
+\end{figure*}
 \end{center}

### 2014-11-10 paper/anytimefigure2.tex
fixed errors in 2 plots

@@
   \begin{semilogxaxis}[  mark size=1pt,
-  restrict y to domain=0:4620,
+  %restrict y to domain=0:4620,
   xlabel = {runtime},
@@
     xmin = 0,
-    xmax = 4100,
+    xmax = 100,
     width = 1.0\columnwidth,

### 2014-11-10 paper/inputs/fig_fusion.tex
fixed errors in 2 plots

@@
             (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
-            {proposal edge \\ labeling $\bm{x'}$};
+            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x'}$}};
 
@@
             (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
-            {proposal edge \\ labeling $\bm{x''}$};
+            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x''}$}};
 
@@
             (5,3.5) -- (5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
-            {proposal node \\ labeling $\bm{l'}$};
+            {\Large{proposal node} \\ \Large{labeling \quad $\bm{l'}$}};
 
@@
             (5,3-3.5) -- (5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
-            {proposal node \\ labeling $\bm{l''}$};
+            {\Large{proposal node} \\ \Large{labeling \quad $\bm{l''}$}};
 
@@
             (5,-4.5) -- (5,-1.5) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
-            {Binary fusion \\ move problem};
+            {\Large{Binary fusion} \\ \Large{move problem}};
 
@@
             \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
-            \draw (4+8,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
+            \draw (4+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
             \path
@@
             {
-                For all different colorings $l''$, the binary fusion move subproblem is different.
+                \Large{For all different colorings $\bm{l''}$, the binary fusion move subproblem is different.}
             };
@@
             {
-                All these node labelings encode the same partition
+                \Large{All these node labelings encode the same partition}
             };
@@
 \caption{
-w
+todo: write me (why normal fusion does not work)
 }\label{fig:fusion_abiguty}

### 2014-11-11 paper/egpaper_for_review.tex
experiments

@@
   \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{Fusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{Fusion-HC-CGC}
-  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{Fusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{Fusion-WS-CGC}
+  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CCFusion-HC-MC}
+  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CCFusion-HC-CGC}
+  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CCFusion-WS-MC}
+  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CCFusion-WS-CGC}
 }
@@
 Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv}. and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure.
+Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
 This procedure is one magnitude faster, but might cause a few extra outer iterations.
@@
 While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
-We also run classical fusion moves~\cite{Lempinsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
+We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
 
@@
 \textbf{fusionCC-HC-MC},
-\textbf{fusionCC-HC-CGC},
-\textbf{fusionCC-WS-MC}, and 
-\textbf{fusionCC-WS-CGC}, respectively.
+\textbf{-HC-CGC},
+\textbf{-WS-MC}, and 
+\textbf{-WS-CGC}, respectively.
 We set the size of the proposals fix to $10\%$ of the original problem size
@@
 
-\subsection{Parameter Choice}
-\begin{figure}
+All experiments were run on Intel Core i5-4570 CPUs
+with 3.20 GHz, equipped with 32 GB of RAM.
+In our evaluation we make not use of multiple threads.
+The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
+
+\subsection{Parameter Choice for CCFusion}
+Beside the choice of the proposal generator and fusion method CCFusion has some more parameters, which need to be set.
+The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
+Fig.~\ref{fig:parameterchoice} shows a evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
+The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
+The level of noise has no major impact on the runtime.
+The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
+Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low energy.
+As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
+experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
+%
+%
+\begin{figure}[th]
 \centering
@@
 }
+\label{fig:parameterchoice}
 \end{figure}
-
-\subsection{Synthetic Models}
 
@@
 
-\subsection{Real World Models}
+\subsection{(3D) Image Segmentation}
 To segment images or volumes into a previously
@@
 
-\begin{figure}
-\input{scatterplots/knott-3d-450.tex}
-\caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
-A more aggressive one would lead to much faster runtime with only a bit worse values.
-DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
-}
-\end{figure}
+% \begin{figure}
+% \input{scatterplots/knott-3d-450.tex}
+% \caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
+% A more aggressive one would lead to much faster runtime with only a bit worse values.
+% DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
+% }
+% \end{figure}
 
@@
 
-\newpage
-
-\onecolumn
-\section{Appendix}
-
-\input{tables/anytime/image-seg.tex}
-\input{tables/anytime/knott-3d-150.tex}
-\input{tables/knott-3d-300.tex}
-\input{tables/anytime/knott-3d-450.tex}
-\input{tables/knott-3d-550.tex}
-\input{tables/anytime/seg-3d.tex}
-\input{tables/modularity-clustering.tex}
+% \newpage
+
+% \onecolumn
+% \section{Appendix}
+
+% \input{tables/anytime/image-seg.tex}
+% \input{tables/anytime/knott-3d-150.tex}
+% \input{tables/knott-3d-300.tex}
+% \input{tables/anytime/knott-3d-450.tex}
+% \input{tables/knott-3d-550.tex}
+% \input{tables/anytime/seg-3d.tex}
+% \input{tables/modularity-clustering.tex}
 

### 2014-11-11 paper/egpaper_for_review.tex
shorten related work

@@
 Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
-A common greedy approach is to randomly permute the nodes and than assign 
+A common greedy approach~\cite{Soon-2001,Ng-2002,Elsner-2008} is to randomly permute the nodes and than assign 
 iteratively each node to an existing cluster or create a new cluster if costs cannot be decreased by assigning to a cluster.
-Common assigning strategies are:
-\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
-\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
-\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
+%Common assigning strategies are:
+%\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
+%\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
+%\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
 %
@@
 %
-Typically these algorithms started for many random permutations, 
-and pick the clustering with best objective value.
+%Typically these algorithms started for many random permutations, 
+%and pick the clustering with best objective value.
 

### 2014-11-11 paper/inputs/fig_fusion.tex
changed fig style

@@
             \path
-                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
-                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
-                (n0) edge[eCC] node[eNS]{$w_{02}$} (n3)
-                (n1) edge[eCC] node[eNS]{$w_{13}$} (n4)
+                (n0) edge[eNotCut] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eNotCut] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eCut] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eCut] node[eNS]{$w_{13}$} (n4)
             ;
@@
             \path
-                (n0) edge[eCC] node[eNS]{$w_{01}$} (n1) 
-                (n3) edge[eCC] node[eNS]{$w_{23}$} (n4) 
-                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
-                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+                (n0) edge[eCut] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eCut] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eNotCut] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eNotCut] node[eNS]{$w_{13}$} (n4)
             ;
@@
             \path
-                (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
-                (n3) edge[eS] node[eNS]{$w_{23}$} (n4) 
-                (n0) edge[eS] node[eNS]{$w_{02}$} (n3)
-                (n1) edge[eS] node[eNS]{$w_{13}$} (n4)
+                (n0) edge[eBlack] node[eNS]{$w_{01}$} (n1) 
+                (n3) edge[eBlack] node[eNS]{$w_{23}$} (n4) 
+                (n0) edge[eBlack] node[eNS]{$w_{02}$} (n3)
+                (n1) edge[eBlack] node[eNS]{$w_{13}$} (n4)
             ;

### 2014-11-11 paper/inputs/fig_hc_alg.tex
changed fig style

@@
 \tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
-\tikzstyle{eS}=[thick,minimum size = 0.5cm,inner sep = 0pt,draw, font=\small,align=left]
-\tikzstyle{eC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=red, font=\small,align=left]
-\tikzstyle{eNC}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green, font=\small,align=left]
-\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]
 
@@
     \path
-        (n0) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
-        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
-        (n3) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
-        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
-        (n0) edge[eC] node[eNS]{$w_{03}=4$} (n3)
-        (n1) edge[eS] node[eNS]{$w_{14}=2$} (n4)
-        (n2) edge[eS] node[eNS]{$w_{25}=3$} (n5)
+        (n0) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
+        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
+        (n3) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
+        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
+        (n0) edge[eNotCut] node[eNS]{$w_{03}=4$} (n3)
+        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
+        (n2) edge[eCut] node[eNS]{$w_{25}=3$} (n5)
     ;
@@
     \path
-        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
-        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n2) 
-        (n03) edge[eS] node[eNS]{$w_{34}-2$} (n4) 
-        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n5)
-        (n1) edge[eS] node[eNS]{$w_{14}=2$} (n4)
-        (n2) edge[eC] node[eNS]{$w_{25}=3$} (n5)
+        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
+        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
+        (n03) edge[eCut] node[eNS]{$w_{34}-2$} (n4) 
+        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
+        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
+        (n2) edge[eNotCut] node[eNS]{$w_{25}=3$} (n5)
     ;
@@
     \path
-        (n03) edge[eS] node[eNS]{$w_{01}=-1$} (n1) 
-        (n1) edge[eS] node[eNS]{$w_{12}=-2$} (n25) 
-        (n03) edge[eS] node[eNS]{$w_{34}=-2$} (n4) 
-        (n4) edge[eS] node[eNS]{$w_{45}=1$} (n25)
-        (n1) edge[eC] node[eNS]{$w_{14}=2$} (n4)
+        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
+        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n25) 
+        (n03) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
+        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n25)
+        (n1) edge[eNotCut] node[eNS]{$w_{14}=2$} (n4)
     ;
@@
     \path
-        %(n03) edge[eS] node[eNS]{$w_{01}$} (n1) 
-        (n14) edge[eNC] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
-        (n03) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
+        %(n03) edge[eCut] node[eNS]{$w_{01}$} (n1) 
+        (n14) edge[eBlue] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
+        (n03) edge[eCut] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
     ;
@@
     the multicut objective we contract the edge with the highest weight
-    in each step (to be contracted edge is shown in red). 
+    in each step (to be contracted edge is shown in green).
     Whenever multiple edges are merged into a single edge,
@@
     We stop when the highest edge weight is smaller
-    or equal to zero (edge shown in green).
+    or equal to zero (edge shown in blue).
 }\label{fig:hc_alg}

### 2014-11-11 paper/egpaper_for_review.tex
test

@@
 \usetikzlibrary{calc, matrix, backgrounds}
+
+%%%%%%global tikz styles
+
+\tikzstyle{eBlack}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=black!70!black, font=\small,align=left, line width=1mm]
+\tikzstyle{eNotCut}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green!70!black, font=\small,align=left, line width=1mm]
+\tikzstyle{eBlue}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=blue!70!black, font=\small,align=left, line width=1mm]
+\tikzstyle{eCut}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left, draw=red!70!black, line width=1mm]
 

### 2014-11-11 paper/inputs/fig_fusion.tex
made fusion figure smaller

@@
 \begin{center}
-\begin{figure*}[ht]
+\begin{figure}[ht]
 \resizebox{\linewidth}{!}{
@@
             % first segmentation as coloring
-            \draw (2+4,2+4) node[nS,fill=red!60] (n0) {$0$}; 
-            \draw (4+4,2+4) node[nS,fill=red!60] (n1) {$1$};
-            \draw (2+4,0+4) node[nS,fill=green!60] (n3) {$2$}; 
-            \draw (4+4,0+4) node[nS,fill=green!60] (n4) {$3$};
+            \draw (2+3.5,2+4) node[nS,fill=red!60] (n0) {$0$}; 
+            \draw (4+3.5,2+4) node[nS,fill=red!60] (n1) {$1$};
+            \draw (2+3.5,0+4) node[nS,fill=green!60] (n3) {$2$}; 
+            \draw (4+3.5,0+4) node[nS,fill=green!60] (n4) {$3$};
             \path
@@
             % 1. FUSION
-            \draw (2+4,2) node[nS,fill=red!60] (n0) {$0$}; 
-            \draw (4+4,2) node[nS,fill=green!60] (n1) {$1$};
-            \draw (2+4,0) node[nS,fill=red!60] (n3) {$2$}; 
-            \draw (4+4,0) node[nS,fill=green!60] (n4) {$3$};
+            \draw (2+3.5,2) node[nS,fill=red!60] (n0) {$0$}; 
+            \draw (4+3.5,2) node[nS,fill=green!60] (n1) {$1$};
+            \draw (2+3.5,0) node[nS,fill=red!60] (n3) {$2$}; 
+            \draw (4+3.5,0) node[nS,fill=green!60] (n4) {$3$};
             \path
@@
 
-            \draw (2+4,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
-            \draw (4+4,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
-            \draw (2+4,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
-            \draw (4+4,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
+            \draw (2+3.5,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
+            \draw (4+3.5,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
+            \draw (2+3.5,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
+            \draw (4+3.5,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
             \path
@@
             % 2. FUSION
-            \draw (2+8,2) node[nS,fill=red!60] (n0) {$0$}; 
-            \draw (4+8,2) node[nS,fill=blue!60] (n1) {$1$};
-            \draw (2+8,0) node[nS,fill=red!60] (n3) {$2$}; 
-            \draw (4+8,0) node[nS,fill=blue!60] (n4) {$3$};
+            \draw (2+7,2) node[nS,fill=red!60] (n0) {$0$}; 
+            \draw (4+7,2) node[nS,fill=blue!60] (n1) {$1$};
+            \draw (2+7,0) node[nS,fill=red!60] (n3) {$2$}; 
+            \draw (4+7,0) node[nS,fill=blue!60] (n4) {$3$};
             \path
@@
 
-            \draw (2+8,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
-            \draw (4+8,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
-            \draw (2+8,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
-            \draw (4+8,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
+            \draw (2+7,2-4) node[nD, circle split part fill={red!60, red!60}] (n0) {$ $}; 
+            \draw (4+7,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
+            \draw (2+7,0-4) node[nD, circle split part fill={green!60, red!60}] (n3) {$ $}; 
+            \draw (4+7,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
             \path
@@
             % 3. FUSION
-            \draw (2+12,2) node[nS,fill=green!60] (n0) {$0$}; 
-            \draw (4+12,2) node[nS,fill=red!60] (n1) {$1$};
-            \draw (2+12,0) node[nS,fill=green!60] (n3) {$2$}; 
-            \draw (4+12,0) node[nS,fill=red!60] (n4) {$3$};
+            \draw (2+10.5,2) node[nS,fill=green!60] (n0) {$0$}; 
+            \draw (4+10.5,2) node[nS,fill=red!60] (n1) {$1$};
+            \draw (2+10.5,0) node[nS,fill=green!60] (n3) {$2$}; 
+            \draw (4+10.5,0) node[nS,fill=red!60] (n4) {$3$};
             \path
@@
 
-            \draw (2+12,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
-            \draw (4+12,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
-            \draw (2+12,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
-            \draw (4+12,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
+            \draw (2+10.5,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
+            \draw (4+10.5,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
+            \draw (2+10.5,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
+            \draw (4+10.5,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
             \path
@@
             % 4. FUSION
-            \draw (2+16,2) node[nS,fill=green!60] (n0) {$0$}; 
-            \draw (4+16,2) node[nS,fill=blue!60] (n1) {$1$};
-            \draw (2+16,0) node[nS,fill=green!60] (n3) {$2$}; 
-            \draw (4+16,0) node[nS,fill=blue!60] (n4) {$3$};
+            \draw (2+14,2) node[nS,fill=green!60] (n0) {$0$}; 
+            \draw (4+14,2) node[nS,fill=blue!60] (n1) {$1$};
+            \draw (2+14,0) node[nS,fill=green!60] (n3) {$2$}; 
+            \draw (4+14,0) node[nS,fill=blue!60] (n4) {$3$};
             \path
@@
 
-            \draw (2+16,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
-            \draw (4+16,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
-            \draw (2+16,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
-            \draw (4+16,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
+            \draw (2+14,2-4) node[nD, circle split part fill={red!60, green!60}] (n0) {$ $}; 
+            \draw (4+14,2-4) node[nD, circle split part fill={red!60, blue!60}] (n1) {$ $};
+            \draw (2+14,0-4) node[nD, circle split part fill={green!60, green!60}] (n3) {$ $}; 
+            \draw (4+14,0-4) node[nD, circle split part fill={green!60, blue!60}] (n4) {$ $};
             \path
@@
             % 5. FUSION
-            \draw (2+20,2) node[nS,fill=blue!60] (n0) {$0$}; 
-            \draw (4+20,2) node[nS,fill=red!60] (n1) {$1$};
-            \draw (2+20,0) node[nS,fill=blue!60] (n3) {$2$}; 
-            \draw (4+20,0) node[nS,fill=red!60] (n4) {$3$};
+            \draw (2+17.5,2) node[nS,fill=blue!60] (n0) {$0$}; 
+            \draw (4+17.5,2) node[nS,fill=red!60] (n1) {$1$};
+            \draw (2+17.5,0) node[nS,fill=blue!60] (n3) {$2$}; 
+            \draw (4+17.5,0) node[nS,fill=red!60] (n4) {$3$};
             \path
@@
 
-            \draw (2+20,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
-            \draw (4+20,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
-            \draw (2+20,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
-            \draw (4+20,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
+            \draw (2+17.5,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
+            \draw (4+17.5,2-4) node[nD, circle split part fill={red!60, red!60}] (n1) {$ $};
+            \draw (2+17.5,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (4+17.5,0-4) node[nD, circle split part fill={green!60, red!60}] (n4) {$ $};
             \path
@@
             % 6. FUSION
-            \draw (2+24,2) node[nS,fill=blue!60] (n0) {$0$}; 
-            \draw (4+24,2) node[nS,fill=green!60] (n1) {$1$};
-            \draw (2+24,0) node[nS,fill=blue!60] (n3) {$2$}; 
-            \draw (4+24,0) node[nS,fill=green!60] (n4) {$3$};
+            \draw (2+21,2) node[nS,fill=blue!60] (n0) {$0$}; 
+            \draw (4+21,2) node[nS,fill=green!60] (n1) {$1$};
+            \draw (2+21,0) node[nS,fill=blue!60] (n3) {$2$}; 
+            \draw (4+21,0) node[nS,fill=green!60] (n4) {$3$};
             \path
@@
 
-            \draw (2+24,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
-            \draw (4+24,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
-            \draw (2+24,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
-            \draw (4+24,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
+            \draw (2+21,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
+            \draw (4+21,2-4) node[nD, circle split part fill={red!60, green!60}] (n1) {$ $};
+            \draw (2+21,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (4+21,0-4) node[nD, circle split part fill={green!60, green!60}] (n4) {$ $};
             \path
@@
             % 7. FUSION
-            \draw (2+28,2) node[nS,fill=blue!60] (n0) {$0$}; 
-            \draw (4+28,2) node[nS,fill=yellow!60] (n1) {$1$};
-            \draw (2+28,0) node[nS,fill=blue!60] (n3) {$2$}; 
-            \draw (4+28,0) node[nS,fill=yellow!60] (n4) {$3$};
+            \draw (2+24.5,2) node[nS,fill=blue!60] (n0) {$0$}; 
+            \draw (4+24.5,2) node[nS,fill=yellow!60] (n1) {$1$};
+            \draw (2+24.5,0) node[nS,fill=blue!60] (n3) {$2$}; 
+            \draw (4+24.5,0) node[nS,fill=yellow!60] (n4) {$3$};
             \path
@@
 
-            \draw (2+28,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
-            \draw (4+28,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
-            \draw (2+28,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
-            \draw (4+28,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
+            \draw (2+24.5,2-4) node[nD, circle split part fill={red!60, blue!60}] (n0) {$ $}; 
+            \draw (4+24.5,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
+            \draw (2+24.5,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (4+24.5,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
             \path
@@
             \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0.8cm]
-            (5,-6) -- (33,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
+            (5,-6) -- (29,-6) node [black,midway,xshift=0cm,yshift=-1cm] 
             {
@@
             \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0.8cm]
-            (5,2) -- (33,2) node [black,midway,xshift=0cm,yshift=1cm] 
+            (5,2) -- (29,2) node [black,midway,xshift=0cm,yshift=1cm] 
             {
@@
 
-            \draw[black] (5,-1) -- (33,-1);
+            \draw[black] (5,-1) -- (29,-1);
 
@@
 }\label{fig:fusion_abiguty}
-\end{figure*}
+\end{figure}
 \end{center}

### 2014-11-11 paper/inputs/fig_fusion.tex
made fusion figure smaller

@@
             \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
-            (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
+            (1-1.5,3.5) -- (1-1.5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
             {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x'}$}};
@@
             \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
-            (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
+            (1-1.5,3-3.5) -- (1-1.5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
             {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x''}$}};

### 2014-11-11 paper/egpaper_for_review.tex
made figures a bit more tiny

--- 2014-11-11 paper/egpaper_for_review.tex
@@
   \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CCFusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CCFusion-HC-CGC}
-  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CCFusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CCFusion-WS-CGC}
+  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{Fusion-HC-MC}
+  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{Fusion-HC-CGC}
+  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{Fusion-WS-MC}
+  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{Fusion-WS-CGC}
 }
@@
 Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
+Secondly, we follow~\cite{kroeger_2012_eccv}. and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+during the separation procedure.
 This procedure is one magnitude faster, but might cause a few extra outer iterations.
@@
 While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
-We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
+We also run classical fusion moves~\cite{Lempinsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
 
@@
 \textbf{fusionCC-HC-MC},
-\textbf{-HC-CGC},
-\textbf{-WS-MC}, and 
-\textbf{-WS-CGC}, respectively.
+\textbf{fusionCC-HC-CGC},
+\textbf{fusionCC-WS-MC}, and 
+\textbf{fusionCC-WS-CGC}, respectively.
 We set the size of the proposals fix to $10\%$ of the original problem size
@@
 
-All experiments were run on Intel Core i5-4570 CPUs
-with 3.20 GHz, equipped with 32 GB of RAM.
-In our evaluation we make not use of multiple threads.
-The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
-
-\subsection{Parameter Choice for CCFusion}
-Beside the choice of the proposal generator and fusion method CCFusion has some more parameters, which need to be set.
-The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
-Fig.~\ref{fig:parameterchoice} shows a evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
-The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
-The level of noise has no major impact on the runtime.
-The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
-Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low energy.
-As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
-experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
-%
-%
-\begin{figure}[th]
+\subsection{Parameter Choice}
+\begin{figure}
 \centering
@@
 }
-\label{fig:parameterchoice}
 \end{figure}
+
+\subsection{Synthetic Models}
 
@@
 
-\subsection{(3D) Image Segmentation}
+\subsection{Real World Models}
 To segment images or volumes into a previously
@@
 
-% \begin{figure}
-% \input{scatterplots/knott-3d-450.tex}
-% \caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
-% A more aggressive one would lead to much faster runtime with only a bit worse values.
-% DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
-% }
-% \end{figure}
+\begin{figure}
+\input{scatterplots/knott-3d-450.tex}
+\caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
+A more aggressive one would lead to much faster runtime with only a bit worse values.
+DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
+}
+\end{figure}
 
@@
 
-% \newpage
-
-% \onecolumn
-% \section{Appendix}
-
-% \input{tables/anytime/image-seg.tex}
-% \input{tables/anytime/knott-3d-150.tex}
-% \input{tables/knott-3d-300.tex}
-% \input{tables/anytime/knott-3d-450.tex}
-% \input{tables/knott-3d-550.tex}
-% \input{tables/anytime/seg-3d.tex}
-% \input{tables/modularity-clustering.tex}
+\newpage
+
+\onecolumn
+\section{Appendix}
+
+\input{tables/anytime/image-seg.tex}
+\input{tables/anytime/knott-3d-150.tex}
+\input{tables/knott-3d-300.tex}
+\input{tables/anytime/knott-3d-450.tex}
+\input{tables/knott-3d-550.tex}
+\input{tables/anytime/seg-3d.tex}
+\input{tables/modularity-clustering.tex}
 

### 2014-11-11 paper/egpaper_for_review.tex
drafts for abstract, shorter introduction and shorter related work

--- 2014-11-11 paper/egpaper_for_review.tex
@@
 \usepackage{amsthm}
-\usepackage{dirtytalk}
+% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
 %\usepackage{framed}
@@
   \color{red} \textbf{TODO:}
-   We address the problem of partitioning a  graph
-   into a previously unknown number of clusters.
-   Among all partitions, the one with the minimal 
-   sum of of cut edge weights is chosen. 
-   This problem is known as correlation clustering 
-   or multicut.
-   We propose a general framework to find
-   high quality approximate solutions for 
-   this NP-hard problem based on a move making algorithm:
-   We use candidate solutions from a proposal generator
-   to iteratively improve the best observed solution similar
-   to fusion moves.
-   The proposed solver outperforms any other solver
-   w.r.t. to any time performance.
-   The solutions found by this solver are close
-   to global optimal solutions w.r.t. energy
-   and problem specific measurements as VI for
-   image segmentation problems.
+Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized.
+We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering.
+A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.
+
+%We address the problem of partitioning a  graph
+%   into a previously unknown number of clusters.
+%   Among all partitions, the one with the minimal 
+%   sum of of cut edge weights is chosen. 
+%   This problem is known as correlation clustering 
+%   or multicut.
+%   We propose a general framework to find
+%   high quality approximate solutions for 
+%   this NP-hard problem based on a move making algorithm:
+%   We use candidate solutions from a proposal generator
+%   to iteratively improve the best observed solution similar
+%   to fusion moves.
+%   The proposed solver outperforms any other solver
+%   w.r.t. to any time performance.
+%   The solutions found by this solver are close
+%   to global optimal solutions w.r.t. energy
+%   and problem specific measurements as VI for
+%   image segmentation problems.
 
@@
 \section{Introduction}
+
+Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
+is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
+Its value is, firstly, that it accommodates both positive / attractive \emph{and} negative / repulsive edge weights.
+Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment.
+This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster.
+Secondly, the algorithm does not require a specification of the number of clusters.
+This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.
+
+\paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers.
+The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings.
+Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted.
+Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph.
+We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.
+We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks.
+The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.
+
+\paragraph{Related Work.}
+A natural approach is to solve the integer linear programming problem directly.
+To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found.
+Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation.
+Such an outer relaxation can be iteratively tightened.
+However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
+The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
+
+Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}.
+The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
+Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.
+
+Finally, there are heuristic methods such as ...
+
+---------------END OF SUGGESTION ----------------------------------
 
@@
 
-\textbf{Outline:}
+\textbf{Outline:} {\bf If we are short of space, the following can be ommited:}
 In sec.~\ref{sec:problem_formulation} we will give a 

### 2014-11-11 paper/inputs/fig_projection.tex

@@
                 \path
-                    (n0) edge[eS] node[eNS]{$w_{01}+$\\$w_{34}$} (n1) 
-                    (n1) edge[eCC] node[eNS]{$w_{12}+$\\$w_{45}$} (n2) 
-                    %(n3) edge[eCC] node[eNS]{$w_{34}$} (n4) 
-                    %(n4) edge[eCC] node[eNS]{$w_{45}$} (n5)
-                    %(n0) edge[eS] node[eNS]{$w_{03}$} (n3)
-                    %(n1) edge[eS] node[eNS]{$w_{14}$} (n4)
-                    %(n2) edge[eS] node[eNS]{$w_{25}$} (n5)
+                    (n0) edge[eNotCut] node[eNS]{$w_{01}+$\\$w_{34}$} (n1) 
+                    (n1) edge[eCut] node[eNS]{$w_{12}+$\\$w_{45}$} (n2) 
+                    %(n3) edge[eCut] node[eNS]{$w_{34}$} (n4) 
+                    %(n4) edge[eCut] node[eNS]{$w_{45}$} (n5)
+                    %(n0) edge[eNotCut] node[eNS]{$w_{03}$} (n3)
+                    %(n1) edge[eNotCut] node[eNS]{$w_{14}$} (n4)
+                    %(n2) edge[eNotCut] node[eNS]{$w_{25}$} (n5)
                 ;
@@
                 \path
-                    (n0) edge[eS] node[eNS]{$w_{01}$} (n1) 
-                    (n1) edge[eCC] node[eNS]{$w_{12}$} (n2) 
-                    (n3) edge[eS] node[eNS]{$w_{34}$} (n4) 
-                    (n4) edge[eCC] node[eNS]{$w_{45}$} (n5)
-                    (n0) edge[eS] node[eNS]{$w_{03}$} (n3)
-                    (n1) edge[eS] node[eNS]{$w_{14}$} (n4)
-                    (n2) edge[eS] node[eNS]{$w_{25}$} (n5)
+                    (n0) edge[eNotCut] node[eNS]{$w_{01}$} (n1) 
+                    (n1) edge[eCut] node[eNS]{$w_{12}$} (n2) 
+                    (n3) edge[eNotCut] node[eNS]{$w_{34}$} (n4) 
+                    (n4) edge[eCut] node[eNS]{$w_{45}$} (n5)
+                    (n0) edge[eNotCut] node[eNS]{$w_{03}$} (n3)
+                    (n1) edge[eNotCut] node[eNS]{$w_{14}$} (n4)
+                    (n2) edge[eNotCut] node[eNS]{$w_{25}$} (n5)
                 ;

### 2014-11-11 paper/egpaper_for_review.tex
update

--- 2014-11-11 paper/egpaper_for_review.tex
@@
 \usepackage{amsthm}
-% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
+\usepackage{dirtytalk}
 %\usepackage{framed}
@@
   \color{red} \textbf{TODO:}
-Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized.
-We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering.
-A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.
-
-%We address the problem of partitioning a  graph
-%   into a previously unknown number of clusters.
-%   Among all partitions, the one with the minimal 
-%   sum of of cut edge weights is chosen. 
-%   This problem is known as correlation clustering 
-%   or multicut.
-%   We propose a general framework to find
-%   high quality approximate solutions for 
-%   this NP-hard problem based on a move making algorithm:
-%   We use candidate solutions from a proposal generator
-%   to iteratively improve the best observed solution similar
-%   to fusion moves.
-%   The proposed solver outperforms any other solver
-%   w.r.t. to any time performance.
-%   The solutions found by this solver are close
-%   to global optimal solutions w.r.t. energy
-%   and problem specific measurements as VI for
-%   image segmentation problems.
+   We address the problem of partitioning a  graph
+   into a previously unknown number of clusters.
+   Among all partitions, the one with the minimal 
+   sum of of cut edge weights is chosen. 
+   This problem is known as correlation clustering 
+   or multicut.
+   We propose a general framework to find
+   high quality approximate solutions for 
+   this NP-hard problem based on a move making algorithm:
+   We use candidate solutions from a proposal generator
+   to iteratively improve the best observed solution similar
+   to fusion moves.
+   The proposed solver outperforms any other solver
+   w.r.t. to any time performance.
+   The solutions found by this solver are close
+   to global optimal solutions w.r.t. energy
+   and problem specific measurements as VI for
+   image segmentation problems.
 
@@
 \section{Introduction}
-
-Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
-Its value is, firstly, that it accommodates both positive / attractive \emph{and} negative / repulsive edge weights.
-Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment.
-This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster.
-Secondly, the algorithm does not require a specification of the number of clusters.
-This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.
-
-\paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers.
-The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings.
-Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted.
-Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph.
-We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.
-We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks.
-The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.
-
-\paragraph{Related Work.}
-A natural approach is to solve the integer linear programming problem directly.
-To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found.
-Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation.
-Such an outer relaxation can be iteratively tightened.
-However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
-The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
-
-Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}.
-The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
-Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.
-
-Finally, there are heuristic methods such as ...
-
----------------END OF SUGGESTION ----------------------------------
 
@@
 
-\textbf{Outline:} {\bf If we are short of space, the following can be ommited:}
+\textbf{Outline:}
 In sec.~\ref{sec:problem_formulation} we will give a 
@@
 
-\subsubsection{Randomized HierarchicalClustering (RHC)}
-
+\noindent \textbf{Randomized HierarchicalClustering (RHC):}
+%\subsubsection{Randomized HierarchicalClustering (RHC)}
+%
 To generate proposals cut we can use bottom up hierarchical clustering.
@@
 
-\subsubsection{Randomized Watersheds (RWS)}
-
+\noindent \textbf{Randomized Watersheds (RWS):}
+%\subsubsection{Randomized Watersheds (RWS)}
+%
 The edge weighted watershed algorithm \cite{meyer_2013}
@@
 
-\subsection{Social Networks}
+\subsection{Social Networks and Network Clustering}
 A application for large scale correlation clustering are social networks.
@@
 %
-The first network is called \emph{Slashdot}. 
+The second network is called \emph{Slashdot}. 
 Slashdot is a technology-related news website know for its specific user community. 
@@
 
-We consider the problem to cluster this graphs such that positively weighted edges link inside and negatively weighted between clusters.
+We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
 In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
@@
 
-\subsection{(3D) Image Segmentation}
+{\color{red}\textbf{TODO: Discussion}}
+
+As another example for network clustering we use the modularity-clustering models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
+
+{\color{red}\textbf{TODO: Discussion}}
+
+\subsection{2D and 3D Image Segmentation}
 To segment images or volumes into a previously
 unknown number of clusters, correlation clustering
-can be used.
-Starting from a super-pixel / super-voxel segmentation
-which defines a region adjacency graphs (RAG),
-correlation clustering finds the cut with the lowest energy.
+has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.
+
+Starting from a super-pixel/-voxel segmentation,
+correlation clustering finds the clustering with the lowest energy.
 The energy is based on a likelihood of merging adjacent super-voxels.
@@
 \end{align}
-Where $\beta$ is used as a prior.
-
-For 2D images, we took the models from \cite{andres_2011_iccv}
-which are defined on the images of the Berkeley Segmentation
-Database \cite{martin_2001}.
-For 3D volume segmentation we took the models from
-Andres \etal \cite{kroeger_2012_eccv}.
-We use models with the cube sizes $150^3$, $300^3$, $450^3$, $550^3$ and $900^3$.
-Both, the 2D and 3D models are available in a recent graphical model
-benchmark of Kappes \etal~\cite{kappes_2013_benchmark_cvpr}.
-We use the same names for the datasets as in the benchmark,
-\emph{image-seg} for the models from  \cite{andres_2011_iccv} and \emph{knott-150 - knott-550} and \emph{3d-seg}
-for the models from \cite{kroeger_2012_eccv}.
-The size of instances is given in Tab.~\ref{tab:instance_sizes}.
+Where $\beta$ is used as a prior~\cite{andres_2011_iccv}.
+
+We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
+For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
+For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
+instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
+We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
+More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
+
+{\color{red}\textbf{TODO: Discussion}}
 
@@
          3d-seg           &     101220          & ???              & 1            & $\times$ \\
-         slashdot         &     ???             & ???        & ???          & $\times$ \\     
+         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
       \bottomrule
@@
    \centering
-   \caption{Eval}
+   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
    \label{tab:eval}
@@
       \toprule
-         Dataset          &  image-seg &  knott-3d-150 &knott-3d-300 &knott-3d-450 &knott-3d-550 &3d-seg\\
+         Dataset          &  image-seg   & knott-3d-150&knott-3d-300&knott-3d-450 &knott-3d-550 &3d-seg\\
       \midrule 
-         PIVOT-BOEM       &      \\ 
-         HC               &\\
-         HC-CGC           &    \\
-         CGC              &   \\
-         KL               & \\
-         FUSION           &  \\
-         MC-R             &  \\   
-         MC-I             &  \\  
-         FusionCC-HC-MC   &  \\  
-         FusionCC-HC-CGC  &  \\  
-         FusionCC-WS-MC   &  \\  
-         FusionCC-WS-CGC  &  \\      
+         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &\\ 
+         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ \\
+         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ \\
+         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$\\
+         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$\\
+         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$\\
+         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$\\   
+         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ \\  
+         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$\\  
+         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ \\  
+         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$\\  
+         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ \\      
       \bottomrule

### 2014-11-11 paper/egpaper_for_review.tex
merge

--- 2014-11-11 paper/egpaper_for_review.tex
@@
 
-\subsection{Real World Models}
+{\color{red}\textbf{TODO: Discussion}}
+
+As another example for network clustering we use the modularity-clustering models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
+
+{\color{red}\textbf{TODO: Discussion}}
+
+\subsection{2D and 3D Image Segmentation}
 To segment images or volumes into a previously
 unknown number of clusters, correlation clustering
-can be used.
-Starting from a super-pixel / super-voxel segmentation
-which defines a region adjacency graphs (RAG),
-correlation clustering finds the cut with the lowest energy.
+has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.
+
+Starting from a super-pixel/-voxel segmentation,
+correlation clustering finds the clustering with the lowest energy.
 The energy is based on a likelihood of merging adjacent super-voxels.

### 2014-11-11 paper/egpaper_for_review.tex
started to change sec. 5, and minor figure fixes

@@
 
-\input{inputs/fig_fusion.tex}
-
-\textbf{new}
-
 Fusion moves as defined in \cite{Lempitsky-2010} work
@@
 objective functions as Eq.~\ref{eq:nodeproblem} since
-the node coloring is ambiguous and has no semantic meaning.
+the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
 In the following, we propose a more suitable fusion move for correlation
@@
 
-\textbf{old}
-
-Motivation Using Fusion moves -> problem ambiguity
-
-A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
-in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the node $v\in V$.
-
-We define the contradiction of graph $G_y=(V_y,E_y)$
-with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
+\input{inputs/fig_fusion.tex}
+
+%\textbf{old}
+%
+%Motivation Using Fusion moves -> problem ambiguity
+%
+%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
+%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
+%
+%We define the contradiction of graph $G_y=(V_y,E_y)$
+%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
 
 %\input{inputs/fig_alg_graph.tex}
+
+\subsection{Fast Optimization} \label{sec:fast_optimization}
+TODO:
+Here we need to proof that it is equivalent 
+to optimize the contracted graph !
 
@@
 % \end{center}
+Once we know how to fuse segmentations, the actual algorithm 
+for correlation clustering 
+is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
+We iteratively improve the best solution by
+fusing it with proposal solutions.
+The inherent difference is how we define the fusion.
+We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}
+and optimize the subproblems as described in 
+Sec.\ref{sec:fast_optimization}.
 
@@
 
-\noindent \textbf{Desired Properties:}
 As discussed in \cite{Lempitsky-2010}, proposals
@@
 
-\begin{remark}[Fix-point (pointless to me)]
-Let $Y$ be the set of possible proposals, than
-$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
-\end{remark}
+%\begin{remark}[Fix-point (pointless to me)]
+%Let $Y$ be the set of possible proposals, than
+%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
+%\end{remark}
 

### 2014-11-11 paper/egpaper_for_review.tex
started to change sec. 5, and minor figure fixes

@@
 via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges.
+This coarser graph is constructed by contracting all must-link edges
+(see Fig.~\ref{fig:move_graph}).
 
@@
 and optimize the subproblems as described in 
-Sec.\ref{sec:fast_optimization}.
+Sec.~\ref{sec:fast_optimization} (see Fig. \ref{fig:move_graph}).
 

### 2014-11-11 paper/egpaper_for_review.tex
alternative introductions

--- 2014-11-11 paper/egpaper_for_review.tex
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
 
@@
 \end{abstract}
-\section{Introduction}
-
-Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
-Its value is, firstly, that it accommodates both positive / attractive \emph{and} negative / repulsive edge weights.
-Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment.
-This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster.
-Secondly, the algorithm does not require a specification of the number of clusters.
-This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.
-
-\paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers.
-The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings.
-Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted.
-Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph.
-We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.
-We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks.
-The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.
-
-\paragraph{Related Work.}
-A natural approach is to solve the integer linear programming problem directly.
-To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found.
-Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation.
-Such an outer relaxation can be iteratively tightened.
-However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
-The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
-
-Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}.
-The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
-Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.
-
-Finally, there are heuristic methods such as ...
-
----------------END OF SUGGESTION ----------------------------------
-
-Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010} as a first step
-towards understanding an image or data in general. 
-The correlation clustering problem is the following:
-Given an undirected edge weighted graph, 
-where positive weights (\emph{attractive}) encourage the adjacent nodes to be in the same cluster
-and negative weights (\emph{repulsive}) encourage the nodes to stay in different cluster, 
-find the clustering of nodes such that the sum over weights of edges between clusters is minimized.
-Note that this problem formulation does not included a predefined number of clusters.
-
-Despite the clear mathematical formulation and nice properties of correlation clustering
-to perform a one-shot agglomeration clustering,
-the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}
-which arise from the NP-hardness of the problem~\cite{Bansal-2002}.
-
-In signed social networks, where positive and negative edges encodes friend and foe relationships, respectively,
-correlation clustering is a natural way to detect communities~\cite{Chierichetti-2014,Chen-2012}.
-Correlation clustering can also been used to cluster query refinements in web search~\cite{Sadikov-2010}.
-Because social and web-related networks are often very huge, heuristic methods, \eg the PIVOT-algorithm~\cite{Ailon-2008},
-are very popular~\cite{Chierichetti-2014}.
-
-In computer vision applications, unsupervised image segmentation algorithms usually start with an over-segmentation
-into superpixels (superregions), which are then clustered into ``perceptually meaningful''
-regions by correlation clustering on sparse graphs.
-Such an approach has been shown to yield
-state-of-the-art results on the Berkeley Segmentation Database
-\cite{andres_2011_iccv,yarkony_2012_eccv,alush_2013_simbad}.
-
-Recently, Beier~\etal~\cite{beier_2014_cvpr} presented a promising 
-approximative method called Cut, Clue \& Cut.
-While this scales well for planar graphs, it does not for non planar graphs and has a bad any-time performance.
-A further inherent drawback of this method is that the subproblems are not limited in their size.
-%
-Consequently, partition problems on large scale data, \eg
-huge volume images in computational neuroscience~\cite{kroeger_2012_eccv}
-or social networks~\cite{Leskovec-2010}, 
-are not tractable, because the runtime explodes or the 
-approximations are far away from being useful.
-
-In the present work we will suggest some alternative approaches to deal with large scale correlation clustering problems.
-In the end we ill present a method that can be combined with any other correlation clustering method and 
-allows to reduce the overall problem to a sequence of correlation clustering problems which are by magnitudes smaller.
-
-\textbf{Contribution:}
-In the present work we present some novel approaches that are designed for large scale correlation clustering problems.
-First, we define a novel energy based agglomerative clustering algorithm that monotonically increase the energy.
-With this at hand we show how to improve the anytime performance of Cut, Clue \& Cut.
-Second, we introduce cluster-fusion moves, which extend the original fusion moves~\cite{Lempitsky-2010} 
-used in supervised segmentation to the unsupervised case and give a polyhedral interpretation of this algorithm.
-We propose two versatile proposal generators, and evaluate the proposed methods on existing and new benchmark problems.
-That experiments show that we can improve the computation time by one to two magnitudes without worsening the segmentation 
-quality significantly.
-
-% Given an edge weighted graph, positive weights (\emph{attractive})
-% encourage the adjacent nodes to be in the same 
-% connected component, while negative weights (\emph{repulsive}) encourage
-% the nodes to stay in different connect components.
-% Therefore the sign of the weights encodes if two
-% nodes should be merged or not and the magnitude of the weights encodes
-% the certainty of this desire.
-% The objective of correlation clustering / multicuts
-% is finding the cut with a minimal sum of cut edge weights.
-% The number of connected components / clusters is discovered
-% from the weights ( rewrite?!?).
-% Correlation clustering / the multicut is NP-hard \cite{???}.
-% %
-% Despite the NP-hardness, correlation clustering has been 
-% successfully used for
-% \begin{inparaenum}[(i)]
-%     \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
-%     \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
-%     \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
-%     \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
-%     \item for co-segmentation~\cite{glassner_2011_cvpr}
-%     \item and to cluster sparse and graphs~\cite{???}.
-% \end{inparaenum}
-
-% Despite the nice properties of correlation clustering
-% to perform a \say{one-shot agglomeration of supervoxels} ~\cite{nunez_iglesias_2013},
-% the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}.
-% Existing solvers for correlation clustering do not scale for non planar graphs.
-% Even state of the art approximate move making algorithm fail 
-% to give good approximations non planar graphs.
-% When increasing the problem sizes, either the runtime explodes or the 
-% approximations are far away from being useful.
-
-% \textbf{Contribution:}
-% \begin{inparaenum}[(i)]
-% \item Within this work we propose a fast and scalable move making algorithm for correlation clustering,
-% \item which generalized  fusion moves \cite{???} to correlation clustering problems.
-% \item We reduce the inference to a series of moves where
-% each moves optimizes over a subspace spanned by the current best solution
-% and a proposal solution.
-% \item We propose two versatile proposal generators,
-% \item and show how to optimize these moves.
-% \item We give a polyhedral interpretation of this algorithm,
-% \item and evaluate the proposed method 
-% on existing benchmark problems.
-% \item We show state of the art any time performance on those instances.
-% \end{inparaenum}[(i)]
-
-\textbf{Outline:} {\bf If we are short of space, the following can be ommited:}
-In sec.~\ref{sec:problem_formulation} we will give a 
-detailed problem definition where we introduce 
-the correlation clustering objective.
-In sec.~\ref{sec:related_work} we will 
-discuss existing methods for correlation 
-clustering and briefly explain the concept of fusion moves.
-In sec: ~\ref{sec:cc_fm} we describe our proposed
-method and show the properties of the algorithm.
-In sec.~\ref{sec:exp} we show an evaluation
-of the method on existing parameter  and discuss the effects of parameters.
-Future work will be discussed in sec. \ref{sec:future} and
-we will conclude in ~\ref{sec:conclusion}.
-%-------------------------------------------------------------------------
-
-\section{Notation and Problem Formulation}\label{sec:problem_formulation}
-Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
-%
-The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
-A positive weight expresses the desire that two adjacent nodes should
-be merged, whereas a negative weight indicates
-that these nodes should be separated into two different regions.
-%
-A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
-of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
-%
-A segmentation of the graph $G$ can by either given by an 
-node labeling $l \in \mathbb{N}^{|V|}$
-or an edge labeling $y \in\{0,1\}^{|E|}$.  
-An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.
-We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
-The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.
-
-%$\rho_y : P(G) \to P(G_y)$
-%$\rho_y^{-1} : P(G_y) \to P(G)$
-
-% \begin{itemize}
-%   \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
-%   \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
-%   \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
-% \end{itemize}
-
-% Def: Graph, weighted graph, cut, multicut
-
-Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
-of the edges between distinct segments is minimized. This can be formulated in the node domain
-by assigning each node $v$ a label $l_v \in \mathbb{N}$
-\begin{align}
-  l^* &= \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
-\end{align}  % y_{ij}^* &=& [l_{u} \neq l_{v}] 
-or in the edge domain, by label each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
-\begin{align}
-  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}.%\\ 
-\end{align}
-As shown in~\cite{kappes_2013_arxiv} both problems are equivalent, but formulation \ref{eq:nodeproblem}
-suffers from ambiguities in the formulation~\cite{kappes_2011_emmcvpr}.
-
-% The exist an surjective mapping from a node-label $l$ to edge-labeling $y$ and
-% a bijective mapping from a partitioning of $V$ to vertices of the multicut polytope $MC$.
-% Consequently, 
-% (i) problems \ref{eq:nodeproblem} and \ref{eq:edgeproblem} are equivalent
-% and (ii) the node-labeling is not unique for a given partitioning and introduce some
-% ambiguities.
-
-% \subsubsection{Multicut Objective}
-
-% The multicut / correlation clustering objective 
-% can be formulated in different ways.
-
-% \paragraph{Edge Indicator Variables:}
-% \begin{center}
-%     \begin{eqnarray}
-%         y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
-%         s.t.:& & y \in \textit{Multicut Polytope} \nonumber
-%     \end{eqnarray}
-% \end{center}
-
-% \paragraph{Fully Connected Graph:}
-% \begin{center}
-%     \begin{eqnarray}
-%         y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
-%         s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
-%     \end{eqnarray}
-% \end{center}
-
-% \paragraph{Node Coloring:}
-% \begin{center}
-%     \begin{eqnarray}
-%         l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
-%         y_{ij}^* &=& [l_{u} \neq l_{v}]  
-%     \end{eqnarray}
-% \end{center}
-
-\input{inputs/fig_notation.tex}
-
-\section{Related Work}\label{sec:related_work}%
-%
-Due to the ambiguity of formulation~\ref{eq:nodeproblem},
-a major branch of research has focused on solving 
-relaxations of eq.~\ref{eq:edgeproblem}.
-To keep the objective and system of inequalities small, they 
-work on sparse graphs and
-use cutting plane methods
-in combination with (integer) linear programming and efficient 
-separation procedures~\cite{kappes_2011_emmcvpr,andres_2011_iccv,kappes_2013_arxiv}.
-
-With no time restrictions and integer constraints these methods can solve the problem to global optimality.
-For huge problems both, separation and solving the ILP in each round, becomes very time consuming.
-
-For planar problems, Yarkony \etal~\cite{yarkony_2012_eccv} 
-suggested a column generating strategy for the outer LP-relaxation
-that includes all cycle-inequalities of problem \ref{eq:edgeproblem}.
-The column generation base on solving planar max cut instances.
-While this method is fast, 
-it only solve a relaxation of the problem and so requires additional rounding strategies,
-lacks of a practical stopping condition for the column generation,
-and most important  is restricted to planar problems.
-
-An other branch of research uses move making algorithm 
-to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
-Starting with an initial segmentation, auxiliary problems are solved that 
-strictly improve the segmentation.
-
-Bansal and Bagon propose a modified $\alpha-$expansion~\cite{bansal_2004_ml} 
-algorithm suitable for correlation clustering, that allows all variables to 
-change to cluster $\alpha$ in a single move. While the authors claim that this
-scales to large scale data, in~\cite{beier_2014_cvpr} it has been shown that 
-this is not the case in general. This is not surprising because the auxiliary 
-problems can have as many variables as the original problem.
-
-A more efficient move making method has been presented by Beier \etal~\cite{beier_2014_cvpr}.
-Their Cut, Glue and Cut method iteratively re-optimizes the cuts between adjacent clusters of the current solution.
-While this method scales better then  modified $\alpha-$expansion, it still faces three problems:
-Firstly, the subproblems can be as large as the original problem,
-secondly, the subproblems are max-cut problems on non-planar graphs that are NP-hard 
-and even the used approximation has high polynomial complexity.
-This limits the method, to be applicable to huge problems. The same holds for the 
-method of Kernighan and Lin~\cite{Kernighan-1970}.
-
-   % \begin{itemize}
-   % \item Multicut~\cite{kappes_2011_emmcvpr}
-   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
-   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
-   % \item Break and Conquer \cite{alush_2013_simbad}.
-   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
-   % \end{itemize}
-
-For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
-For many large scale computer vision applications fusion moves lead to good approximations
-with state of the art any time performance~\cite{kappes_2014_ws}.
-
-The fusion move algorithm iteratively fuse the current best solution with a proposal solutions
-by optimizing over the subspace spanned by the two labeling. 
-Due to the ambiguity of a node-labeling, fusion moves can not be applied directly for correlation clustering.
-We will show how to overcome this point later.
+
+\input{introduction-new.tex}
+%\input{introduction-old.tex}
+%\input{introduction-fred.tex}
 
 \input{inputs/fig_hc_alg.tex}
-
-Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
-A common greedy approach~\cite{Soon-2001,Ng-2002,Elsner-2008} is to randomly permute the nodes and than assign 
-iteratively each node to an existing cluster or create a new cluster if costs cannot be decreased by assigning to a cluster.
-%Common assigning strategies are:
-%\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
-%\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
-%\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
-%
-The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
-If the node is not assigned it construct a cluster containing the node and all its 
-unassigned positively linked neighbors.  
-%
-%Typically these algorithms started for many random permutations, 
-%and pick the clustering with best objective value.
-
-A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}.
-Start with an initial clustering one node is removed from a cluster and reassigned to an existing or new cluster such that the costs are minimized.
-BEOM stops if no move can decrease the costs.
-
-% \subsection{Karger-Stein Algorithms}
-% Use randomized procedure to reduce the number of nodes / edges to a reasonable 
-% number.
-% On the smaller graph, more expensive solvers are used.
-
-%\input{inputs/fig_hc_alg.tex}
-
 \section{Energy Based Hierarchical Clustering}\label{sec:ehc}

### 2014-11-11 paper/introduction-fred.tex
alternative introductions

\section{Introduction}

Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}. Its value is, firstly, that it accommodates both positive / attractive \emph{and} negative / repulsive edge weights. Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment. This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster. Secondly, the algorithm does not require a specification of the number of clusters. This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.

\paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers. The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings. Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted. Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph. We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.   We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks. The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.

\paragraph{Related Work.}
A natural approach is to solve the integer linear programming problem directly. To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation. Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning. The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.

Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}. The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs. Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.

Finally, there are heuristic methods such as ...

\section{Notation and Problem Formulation}\label{sec:problem_formulation}
Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
%
The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
A positive weight expresses the desire that two adjacent nodes should
be merged, whereas a negative weight indicates
that these nodes should be separated into two different regions.
%
A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
%
A segmentation of the graph $G$ can by either given by an 
node labeling $l \in \mathbb{N}^{|V|}$
or an edge labeling $y \in\{0,1\}^{|E|}$.  
An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.
We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.

%$\rho_y : P(G) \to P(G_y)$
%$\rho_y^{-1} : P(G_y) \to P(G)$

% \begin{itemize}
%   \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
%   \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
%   \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
% \end{itemize}

% Def: Graph, weighted graph, cut, multicut

Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
of the edges between distinct segments is minimized. This can be formulated in the node domain
by assigning each node $v$ a label $l_v \in \mathbb{N}$
\begin{align}
  l^* &= \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
\end{align}  % y_{ij}^* &=& [l_{u} \neq l_{v}] 
or in the edge domain, by label each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
\begin{align}
  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}.%\\ 
\end{align}
As shown in~\cite{kappes_2013_arxiv} both problems are equivalent, but formulation \ref{eq:nodeproblem}
suffers from ambiguities in the formulation~\cite{kappes_2011_emmcvpr}.

% The exist an surjective mapping from a node-label $l$ to edge-labeling $y$ and
% a bijective mapping from a partitioning of $V$ to vertices of the multicut polytope $MC$.
% Consequently, 
% (i) problems \ref{eq:nodeproblem} and \ref{eq:edgeproblem} are equivalent
% and (ii) the node-labeling is not unique for a given partitioning and introduce some
% ambiguities.

% \subsubsection{Multicut Objective}

% The multicut / correlation clustering objective 
% can be formulated in different ways.

% \paragraph{Edge Indicator Variables:}
% \begin{center}
%     \begin{eqnarray}
%         y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
%         s.t.:& & y \in \textit{Multicut Polytope} \nonumber
%     \end{eqnarray}
% \end{center}

% \paragraph{Fully Connected Graph:}
% \begin{center}
%     \begin{eqnarray}
%         y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
%         s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
%     \end{eqnarray}
% \end{center}

% \paragraph{Node Coloring:}
% \begin{center}
%     \begin{eqnarray}
%         l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
%         y_{ij}^* &=& [l_{u} \neq l_{v}]  
%     \end{eqnarray}
% \end{center}

\input{inputs/fig_notation.tex}

### 2014-11-11 paper/egpaper_for_review.tex

@@
 via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges.
+This coarser graph is constructed by contracting all must-link edges
+(see Fig.~\ref{fig:move_graph}).
 
-\textbf{old}
+\input{inputs/fig_fusion.tex}
 
-Motivation Using Fusion moves -> problem ambiguity
-
-A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
-in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the node $v\in V$.
-
-We define the contradiction of graph $G_y=(V_y,E_y)$
-with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
+%\textbf{old}
+%
+%Motivation Using Fusion moves -> problem ambiguity
+%
+%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
+%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
+%
+%We define the contradiction of graph $G_y=(V_y,E_y)$
+%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
 
 %\input{inputs/fig_alg_graph.tex}
+
+\subsection{Fast Optimization} \label{sec:fast_optimization}
+TODO:
+Here we need to proof that it is equivalent 
+to optimize the contracted graph !
 
@@
 % \end{center}
+Once we know how to fuse segmentations, the actual algorithm 
+for correlation clustering 
+is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
+We iteratively improve the best solution by
+fusing it with proposal solutions.
+The inherent difference is how we define the fusion.
+We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}
+and optimize the subproblems as described in 
+Sec.~\ref{sec:fast_optimization} (see Fig. \ref{fig:move_graph}).
 

### 2014-11-11 paper/inputs/fig_fusion.tex
made figures a bit more tiny

--- 2014-11-11 paper/inputs/fig_fusion.tex
@@
   head/.style = {fill = orange!90!blue,
-                 label = center:\textsf{\Large H}},
+                 label = center:\textsf{\Huge H}},
   tail/.style = {fill = blue!70!yellow, text = black,
-                 label = center:\textsf{\Large T}}
+                 label = center:\textsf{\Huge T}}
 }
@@
 
+            \draw (-3.25,3) node[rotate=90] (dummy){
+                \huge{proposal edge labeling}
+            };
+
             \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt]
             (1-2,3.5) -- (1-2,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
-            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x'}$}};
+            {\huge{$\bm{y'}$}};
 
@@
             (1-2,3-3.5) -- (1-2,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
-            {\Large{proposal edge} \\ \Large{labeling \quad $\bm{x''}$}};
+            {\huge{$\bm{y''}$}};
+
+            \draw (2.75,3) node[rotate=90] (dummy){
+                \huge{proposal node labeling}
+            };
 
@@
             (5,3.5) -- (5,6.5) node [black,midway,xshift=-1.2cm,rotate=90,align=left] 
-            {\Large{proposal node} \\ \Large{labeling \quad $\bm{l'}$}};
+            {\huge{$\bm{l'}$}};
 
@@
             (5,3-3.5) -- (5,6.5-4) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
-            {\Large{proposal node} \\ \Large{labeling \quad $\bm{l''}$}};
+            {\huge{$\bm{l''}$}};
 
@@
             (5,-4.5) -- (5,-1.5) node [black,midway,xshift=-1.2cm, rotate=90,align=left] 
-            {\Large{Binary fusion} \\ \Large{move problem}};
+            {\huge{Fusion Move} \\ \huge{Problem}};
 
-            \draw (2-2,2+4) node[nS] (n0) {$0$}; 
-            \draw (4-2,2+4) node[nS] (n1) {$1$};
-            \draw (2-2,0+4) node[nS] (n3) {$2$}; 
-            \draw (4-2,0+4) node[nS] (n4) {$3$};
+            \draw (2-2.5,2+4) node[nS] (n0) {$0$}; 
+            \draw (4-2.5,2+4) node[nS] (n1) {$1$};
+            \draw (2-2.5,0+4) node[nS] (n3) {$2$}; 
+            \draw (4-2.5,0+4) node[nS] (n4) {$3$};
             \path
@@
 
-            \draw (2-2,2) node[nS] (n0) {$0$}; 
-            \draw (4-2,2) node[nS] (n1) {$1$};
-            \draw (2-2,0) node[nS] (n3) {$2$}; 
-            \draw (4-2,0) node[nS] (n4) {$3$};
+            \draw (2-2.5,2) node[nS] (n0) {$0$}; 
+            \draw (4-2.5,2) node[nS] (n1) {$1$};
+            \draw (2-2.5,0) node[nS] (n3) {$2$}; 
+            \draw (4-2.5,0) node[nS] (n4) {$3$};
             \path
@@
             \draw (4+24.5,2-4) node[nD, circle split part fill={red!60, yellow!60}] (n1) {$ $};
-            \draw (2+24.5,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
+            \draw (2.+24.5,0-4) node[nD, circle split part fill={green!60, blue!60}] (n3) {$ $}; 
             \draw (4+24.5,0-4) node[nD, circle split part fill={green!60, yellow!60}] (n4) {$ $};
@@
             {
-                \Large{For all different colorings $\bm{l''}$, the binary fusion move subproblem is different.}
+                \huge{For all different colorings $\bm{l''}$, the binary fusion move subproblem is different.}
             };
@@
             {
-                \Large{All these node labelings encode the same partition}
+                \huge{All these node labelings encode the same partition}
             };
@@
 \caption{
-todo: write me (why normal fusion does not work)
+To fuse two edge labelings $y'$ and $y''$ with fusion moves
+as defined by Lempitsky \etal~\cite{Lempitsky-2010} 
+$y'$ and $y''$ need to be transfered to the node domain.
+The mapping from edge labels to node labels is ambiguous and
+even for this small graph there are seven node labels
+which result in different binary fusion move problems.
+Enumerating all labelings for a graph of non trival size
+becomes intractable and choosing one labeling is complexity arbitrary.
+%
+%Furthermore it should be noted that 
 }\label{fig:fusion_abiguty}

### 2014-11-11 paper/egpaper_for_review.tex
made figures a bit smaller

--- 2014-11-11 paper/egpaper_for_review.tex
@@
 %
-Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
-we can work on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges
-(see Fig.~\ref{fig:move_graph}).
-
-\input{inputs/fig_fusion.tex}
-
-%\textbf{old}
-%
-%Motivation Using Fusion moves -> problem ambiguity
-%
-%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
-%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
-%
-%We define the contradiction of graph $G_y=(V_y,E_y)$
-%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
-
-%\input{inputs/fig_alg_graph.tex}
-
-\subsection{Fast Optimization} \label{sec:fast_optimization}
-TODO:
-Here we need to proof that it is equivalent 
-to optimize the contracted graph !
-
-\input{inputs/fig_contraction.tex}
-\input{inputs/fig_projection.tex}
-
-\input{inputs/fig_move_graph.tex}
-
-% Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
-% Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
-% but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
-
-% To make multicuts scalable, it is desirable to replace the graph $G$
-% with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
-% If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.
-
-% A trivial way to reduce the size of the graph  is edge contraction.
-% Until a desirable size is reached, one might contract the edge with
-% the highest weight. A cut on the contracted graph  $\hat{G}$ is always
-% a valid cut on $\hat{G}$.
-
-% On the other hand, if an edge $e$ is contracted, it will never be cut.
-% If $e$ is part of the cut in a global optimal solution, we cannot find
-% this cut.
-
-% To overcome this problem  we can randomize the edge contraction,
-% and repeat this multiple times and remember the best solution.
-
-% But this would throw away all the ``not the best'' solutions (rewrite me).
-% Within this work we propose the following nifty trick.
-% Instead of throwing away solutions, we intersect them with the 
-% best solution, and solve the multicut on the resulting
-% graph.
-% Therefore we fuse multiple solutions,
-
-%\begin{algorithm}
-%\begin{scriptsize}
-%\caption{Fusion Based Algorithms}\label{alg:fusion}
-%
-%
-%
-%
-%\begin{algorithmic}[1]
-%\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
-%\State $x^0 \gets \textrm{initial state form } X$
-%\State $n \gets 0 $                                 \Comment{Number of moves}
-%\State $m \gets 0 $                                 \Comment{Number of moves without progress}
-%\While{$m < m_{\max}$ and $n < n_{\max}$ }
-%\State $n \gets n+1$ 
-% \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
-% \If{$J(x^{n-1}) \leq J(x')$}                       
-%   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
-% \Else
-%   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
-% \EndIf
-% \If{$J(x^{n}) \leq J(x^{n-1})$}
-%   \State $m \gets 0$                                 \Comment{Reset counter}
-% \Else
-%   \State $m \gets m+1$                               \Comment{Increment counter}
-% \EndIf
-%\EndWhile
-%\State \textbf{return} $x^n$
-%\EndProcedure
-%\end{algorithmic}
-%\end{scriptsize}
-%\end{algorithm}
-
-%\begin{algorithm}
-%\begin{scriptsize}
-%\caption{Fusion Moves}\label{alg:fusion_moves}
-%\scriptsize
-%\begin{algorithmic}[1]
-%\Require $J(x) \leq J(x')$
-%\Ensure $J(\hat{x}) \leq J(x)$
-%\vspace{0.2cm}
-%\Procedure{Fuse}{$x,x',J$}
-%\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
-%    \Comment{
-%        \begin{minipage}{0.4\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                intersect
-%                uncut edges in $x$ and $x'$,
-%                return  
-%                connected component labeling
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%\vspace{0.1cm}
-%\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
-%    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
-%    \Comment{ 
-%        \begin{minipage}{0.2\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                Contract all edges 
-%                which are uncut in $\bar{x}$ 
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%\vspace{0.1cm}
-%\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
-%    \Comment{ 
-%        \begin{minipage}{0.3\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                Solve the multicut objective
-%                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%
-%\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
-%    \Comment{ 
-%        \begin{minipage}[\textheight]{0.4\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                Translate the connected component
-%                labeling $\tilde{x}^*$ of $\tilde{G}$ 
-%                to a connected component labeling of $G$
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%\State \textbf{return} $\hat{x}$
-%\EndProcedure
-%\vspace{0.3cm}
-%\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
-%\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
-%\EndProcedure
-%\end{algorithmic}
-%\end{scriptsize}
-%\end{algorithm}
-
-%-------------------------------------------------------------------------
-\subsection{Fusion Move Solver}
-
-% \begin{center}
-%     \begin{eqnarray}
-%         y 
-%         &=& 
-%         \rho_{\hat{y}}^{-1}(
-%         \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
-%         \sum_{ (i,j) \in E_{\hat{y}} } 
-%         w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
-%     \end{eqnarray}
-% \end{center}
-
-% \begin{center}
-%     \begin{eqnarray}
-%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
-%     \end{eqnarray}
-% \end{center}
+
 Once we know how to fuse segmentations, the actual algorithm 
@@
 The inherent difference is how we define the fusion.
-We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}
-and optimize the subproblems as described in 
-Sec.~\ref{sec:fast_optimization} (see Fig. \ref{fig:move_graph}).
+We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
+%
+How to optimize  Eq.~\ref{eq:fusion_move_a} in an more efficient way is
+described in the following section.
+
+\input{inputs/fig_fusion.tex}
+
+%\textbf{old}
+%
+%Motivation Using Fusion moves -> problem ambiguity
+%
+%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
+%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
+%
+%We define the contradiction of graph $G_y=(V_y,E_y)$
+%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
+
+%\input{inputs/fig_alg_graph.tex}
+
+\subsection{Fast Optimization} \label{sec:fast_optimization}
+
+Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
+we can work on a coarser graph, where all nodes which are connected
+via must-link constraints are merged into single nodes.
+This coarser graph is constructed by contracting all must-link edges
+(see Fig.~\ref{fig:move_graph}).
+
+TODO:
+Here we need to proof that it is equivalent 
+to optimize the contracted graph !
+
+\input{inputs/fig_contraction.tex}
+\input{inputs/fig_projection.tex}
+
+\input{inputs/fig_move_graph.tex}
+
+%-------------------------------------------------------------------------
+%\subsection{Fusion Move Solver}
 

### 2014-11-11 paper/introduction-new.tex

--- 2014-11-11 paper/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\section{Introduction}
+Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
+is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012},
+see Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph..
 
-\usepackage{eso-pic}
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{xspace}
-\usepackage{booktabs}
-\usepackage{placeins}
-
-% Include other packages here, before hyperref.
-\usepackage{my_macros}
-\usepackage{paralist}
-\usepackage{amsthm}
-% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
-%\usepackage{framed}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{algorithm}
-%\usepackage{algorithmic}
-\usepackage{algpseudocode}
-\usepackage{setspace}
-%for tikz
-\usepackage{tikz,pgfplots}
-\usepackage{pgfplotstable}
-\usepackage{filecontents}
-%\usepackage{scrextend}
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-\newcommand{\footlabel}[2]{%
-    \addtocounter{footnote}{1}%
-    \footnotetext[\thefootnote]{%
-        \addtocounter{footnote}{-1}%
-        \refstepcounter{footnote}\label{#1}%
-        #2%
-    }%
-    $^{\ref{#1}}$%
-}
-
-\newcommand{\footref}[1]{%
-    $^{\ref{#1}}$%
-}
-\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
-\usetikzlibrary{arrows,petri,topaths}
-\usetikzlibrary{positioning,fit,calc}
-\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
-\usetikzlibrary{calc, matrix, backgrounds}
-
-%%%%%%global tikz styles
-
-\tikzstyle{eBlack}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=black!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eNotCut}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eBlue}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=blue!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eCut}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left, draw=red!70!black, line width=1mm]
-
-\pgfplotsset{every axis/.append style={
-  every axis y label/.style = {at={(ticklabel cs:0.5)}, rotate=90, anchor=south},
-  axis x line = {bottom},
-  axis y line = {left},
-  tick align = outside,
-  ymajorgrids = true,
-%  legend style = {draw=none, at={(1.05, 0.5)}, anchor=west, font=\small},
-  legend style = {font=\tiny},
-  legend columns = 1,
-  every axis plot/.append style = {line width=1pt},
-  label style = {font=\small},
-  tick label style={font=\small},
-  scaled ticks = false,
-}}
-
-% Two Colored Circle Split 
-\makeatletter
-\tikzset{circle split part fill/.style  args={#1,#2}{%
- alias=tmp@name, 
-  postaction={%
-    insert path={
-     \pgfextra{% 
-     \pgfpointdiff{\pgfpointanchor{\pgf@node@name}{center}}%
-                  {\pgfpointanchor{\pgf@node@name}{east}}%            
-     \pgfmathsetmacro\insiderad{\pgf@x}
-      \fill[#1] (\pgf@node@name.base) ([xshift=-\pgflinewidth]\pgf@node@name.east) arc
-                          (0:180:\insiderad-\pgflinewidth)--cycle;
-      \fill[#2] (\pgf@node@name.base) ([xshift=\pgflinewidth]\pgf@node@name.west)  arc
-                           (180:360:\insiderad-\pgflinewidth)--cycle;            
-         }}}}}  
- \makeatother
-
-%\usepackage{tkz-berge}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
-\usepackage{xargs} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{remark}{Remark}
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage{bm}% ändert \boldsymbol
-\def\arraystretch{0.8}
-\renewcommand{\tabcolsep}{2pt}
-\newcommand{\thickline}{2pt}
-\newcommand{\scatterplotpath}{./scatterplots/}
-
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
-\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
-\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
-\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
-\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
-\newcommand{\OR}{\textrm{ or }}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\newcommand{\realplot}[1]{
-\begin{tikzpicture}
-    \begin{axis}
-        \addlegendimage{empty legend}\addlegendentry{Matrix #1}
-        \addplot {0};
-        \addplot {1};
-        \addplot {2};
-        \addplot {3};
-    \end{axis}
-\end{tikzpicture}}
-
-% \newcommand{\anytimeplot}[1]{
-%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
-%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
-%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
-%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
-%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
-%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
-%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
-%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
-%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
-%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
-% }
-\newcommand{\anytimeplot}[1]{
-  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
-  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL} 
-  \addplot[color=yellow!50!black,mark=square] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
-  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
-  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CCFusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CCFusion-HC-CGC}
-  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CCFusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CCFusion-WS-CGC}
-}
-%  \addplot[color=yellow!50!black,mark=o] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
-  %\addplot[color=green!50,mark=o] table[x=time, y=PIVOT*]{data3/#1.data};          \addlegendentry{PIVOT-BOEM}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-%%%%%%%%% TITLE
-\include{my_macros.tex}
-%\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
-\title{Fusion Moves for Correlation Clustering}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  \color{red} \textbf{TODO:}
-Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized.
-We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering.
-A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.
-
-%We address the problem of partitioning a  graph
-%   into a previously unknown number of clusters.
-%   Among all partitions, the one with the minimal 
-%   sum of of cut edge weights is chosen. 
-%   This problem is known as correlation clustering 
-%   or multicut.
-%   We propose a general framework to find
-%   high quality approximate solutions for 
-%   this NP-hard problem based on a move making algorithm:
-%   We use candidate solutions from a proposal generator
-%   to iteratively improve the best observed solution similar
-%   to fusion moves.
-%   The proposed solver outperforms any other solver
-%   w.r.t. to any time performance.
-%   The solutions found by this solver are close
-%   to global optimal solutions w.r.t. energy
-%   and problem specific measurements as VI for
-%   image segmentation problems.
-
-\end{abstract}
-\section{Introduction}
-
-Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
-Its value is, firstly, that it accommodates both positive / attractive \emph{and} negative / repulsive edge weights.
-Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment.
-This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster.
-Secondly, the algorithm does not require a specification of the number of clusters.
-This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.
-
-\paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers.
-The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings.
-Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted.
-Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph.
-We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.
-We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks.
-The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.
-
-\paragraph{Related Work.}
-A natural approach is to solve the integer linear programming problem directly.
-To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found.
-Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation.
-Such an outer relaxation can be iteratively tightened.
-However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
-The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
-
-Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}.
-The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
-Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.
-
-Finally, there are heuristic methods such as ...
-
----------------END OF SUGGESTION ----------------------------------
-
-Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010} as a first step
-towards understanding an image or data in general. 
-The correlation clustering problem is the following:
-Given an undirected edge weighted graph, 
-where positive weights (\emph{attractive}) encourage the adjacent nodes to be in the same cluster
-and negative weights (\emph{repulsive}) encourage the nodes to stay in different cluster, 
-find the clustering of nodes such that the sum over weights of edges between clusters is minimized.
-Note that this problem formulation does not included a predefined number of clusters.
-
-Despite the clear mathematical formulation and nice properties of correlation clustering
-to perform a one-shot agglomeration clustering,
-the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}
-which arise from the NP-hardness of the problem~\cite{Bansal-2002}.
+Its value is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights,
+which allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish  or do wish to end up in the same cluster or segment, respectively.
+Secondly, it does not require a specification of the number of clusters beforehand.
 
@@
 
-Recently, Beier~\etal~\cite{beier_2014_cvpr} presented a promising 
-approximative method called Cut, Clue \& Cut.
-While this scales well for planar graphs, it does not for non planar graphs and has a bad any-time performance.
-A further inherent drawback of this method is that the subproblems are not limited in their size.
+Despite the clear mathematical formulation and nice properties,
+correlation clustering is known to be NP-hard. 
 %
@@
 or social networks~\cite{Leskovec-2010}, 
-are not tractable, because the runtime explodes or the 
-approximations are far away from being useful.
+are not tractable, because reasonable solutions cannot be computed in acceptable time.
 
-In the present work we will suggest some alternative approaches to deal with large scale correlation clustering problems.
-In the end we ill present a method that can be combined with any other correlation clustering method and 
-allows to reduce the overall problem to a sequence of correlation clustering problems which are by magnitudes smaller.
+% Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment.
+This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster.
+Secondly, the algorithm does not require a specification of the number of clusters.
+This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.
 
-\textbf{Contribution:}
+% \paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers.
+The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings.
+Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted.
+Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph.
+We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.
+We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks.
+The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.
+\vspace{0.1cm}
+\noindent \textbf{Contribution.}
 In the present work we present some novel approaches that are designed for large scale correlation clustering problems.
@@
 
-% Given an edge weighted graph, positive weights (\emph{attractive})
-% encourage the adjacent nodes to be in the same 
-% connected component, while negative weights (\emph{repulsive}) encourage
-% the nodes to stay in different connect components.
-% Therefore the sign of the weights encodes if two
-% nodes should be merged or not and the magnitude of the weights encodes
-% the certainty of this desire.
-% The objective of correlation clustering / multicuts
-% is finding the cut with a minimal sum of cut edge weights.
-% The number of connected components / clusters is discovered
-% from the weights ( rewrite?!?).
-% Correlation clustering / the multicut is NP-hard \cite{???}.
-% %
-% Despite the NP-hardness, correlation clustering has been 
-% successfully used for
-% \begin{inparaenum}[(i)]
-%     \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
-%     \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
-%     \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
-%     \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
-%     \item for co-segmentation~\cite{glassner_2011_cvpr}
-%     \item and to cluster sparse and graphs~\cite{???}.
-% \end{inparaenum}
+\vspace{0.1cm}
+\noindent \textbf{Related Work.}
+A natural approach is to solve the integer linear programming problem directly.
+To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found.
+Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation.
+Such an outer relaxation can be iteratively tightened.
+However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
+The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
 
-% Despite the nice properties of correlation clustering
-% to perform a \say{one-shot agglomeration of supervoxels} ~\cite{nunez_iglesias_2013},
-% the main draw back of correlation clustering is scalability~\cite{nunez_iglesias_2013}.
-% Existing solvers for correlation clustering do not scale for non planar graphs.
-% Even state of the art approximate move making algorithm fail 
-% to give good approximations non planar graphs.
-% When increasing the problem sizes, either the runtime explodes or the 
-% approximations are far away from being useful.
+Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}.
+The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
+Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.
 
-% \textbf{Contribution:}
-% \begin{inparaenum}[(i)]
-% \item Within this work we propose a fast and scalable move making algorithm for correlation clustering,
-% \item which generalized  fusion moves \cite{???} to correlation clustering problems.
-% \item We reduce the inference to a series of moves where
-% each moves optimizes over a subspace spanned by the current best solution
-% and a proposal solution.
-% \item We propose two versatile proposal generators,
-% \item and show how to optimize these moves.
-% \item We give a polyhedral interpretation of this algorithm,
-% \item and evaluate the proposed method 
-% on existing benchmark problems.
-% \item We show state of the art any time performance on those instances.
-% \end{inparaenum}[(i)]
+Finally, there are heuristic methods such as ...
 
-\textbf{Outline:} {\bf If we are short of space, the following can be ommited:}
+\vspace{0.1cm}
+\noindent \textbf{Outline:} {\bf If we are short of space, the following can be ommited:}
 In sec.~\ref{sec:problem_formulation} we will give a 
@@
 %
-A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
-of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
+%A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
+%of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
 %
@@
 
-%$\rho_y : P(G) \to P(G_y)$
-%$\rho_y^{-1} : P(G_y) \to P(G)$
-
-% \begin{itemize}
-%   \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
-%   \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
-%   \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
-% \end{itemize}
-
-% Def: Graph, weighted graph, cut, multicut
-
 Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
@@
   l^* &= \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
-\end{align}  % y_{ij}^* &=& [l_{u} \neq l_{v}] 
+\end{align} 
 or in the edge domain, by label each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
@@
 suffers from ambiguities in the formulation~\cite{kappes_2011_emmcvpr}.
-
-% The exist an surjective mapping from a node-label $l$ to edge-labeling $y$ and
-% a bijective mapping from a partitioning of $V$ to vertices of the multicut polytope $MC$.
-% Consequently, 
-% (i) problems \ref{eq:nodeproblem} and \ref{eq:edgeproblem} are equivalent
-% and (ii) the node-labeling is not unique for a given partitioning and introduce some
-% ambiguities.
-
-% \subsubsection{Multicut Objective}
-
-% The multicut / correlation clustering objective 
-% can be formulated in different ways.
-
-% \paragraph{Edge Indicator Variables:}
-% \begin{center}
-%     \begin{eqnarray}
-%         y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
-%         s.t.:& & y \in \textit{Multicut Polytope} \nonumber
-%     \end{eqnarray}
-% \end{center}
-
-% \paragraph{Fully Connected Graph:}
-% \begin{center}
-%     \begin{eqnarray}
-%         y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
-%         s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
-%     \end{eqnarray}
-% \end{center}
-
-% \paragraph{Node Coloring:}
-% \begin{center}
-%     \begin{eqnarray}
-%         l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
-%         y_{ij}^* &=& [l_{u} \neq l_{v}]  
-%     \end{eqnarray}
-% \end{center}
 
@@
 %\input{inputs/fig_hc_alg.tex}
-
-\section{Energy Based Hierarchical Clustering}\label{sec:ehc}
-Agglomerative hierarchical clustering (HC) is widely used
-in graph / image segmentation~\cite{arbelaez_2006}.
-In each step, the edge with the highest weight $w$ is
-contracted (red edges in Fig.~\ref{fig:hc_alg}).
-Doing so, parallel edges edges can occur.
-In agglomerative clustering, weights of
-parallel edges are merged into single edges.
-For image segmentation, the length
-weighted mean is used to do this update~\cite{arbelaez_2006}.
-
-While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
-agglomeration with respect to our energy function.
-For this we propose to use energy based agglomeration
-withe the following update rule:
-Whenever there are multiple edges between 
-a pair of nodes, these edges are merged into a single edge
-by summing up their weights, since we 
-minimize the sum of the cut edges.
-We call HC with this update method Energy base Hierarchical Clustering (EHC).
-
-We stop EHC if the highest edge weight is
-smaller or equal to zero  (green edge in Fig.~\ref{fig:hc_alg}). Any further edge
-contraction leads to worse energies.
-
-% Hierarchical clustering is fast, and 
-% due to the agglomeration of edge weights, 
-% {\color{red} hierarchical clustering is robust against noise}.
-% {\color{yellow} [ First most similar nodes are merged...]
-% In agglomerative clustering, weights of
-% parallel edges are merged into single edges.}
-% For image segmentation, the length
-% weighted mean is used to do this update [ref].
-
-% [We contrary on those works work directly on energy functions and that why ...]
-% We propose to use Energy Based Hierarchical Clustering (EHC) to find
-% solutions for correlation clustering.
-
-% To make EHC follow the energy, we propose 
-% the following update rule:
-% Whenever there are multiple edges between 
-% a pair of nodes, these edges are merged into a single edge
-% by summing up their weights, since we 
-% minimize the sum of the cut edges.
-% The algorithm stops if the highest edge weight is
-% smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
-% contraction leads to worse energies.
-
-Given the intrinsic greediness of hierarchical clustering, 
-and the fact that EHC does only local decisions, it is 
-sensitive against salt and paper noise 
-and we do not expect very good solutions.
-
-But EHC is very fast, and can be used to initialize
-CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
-is spend in the \emph{cut phase} to solve the 
-first 2 coloring on the complete graph.
-As shown in Sec.~\ref{sec:exp},
-allowing CGC to start from the EHC solution
-can improve performance drastically.
-
-% Common cluster distances
-% \begin{itemize}
-% \item Single-Link: Nearest Neighbor - their closest members.
-% \item Complete-Link: Furthest Neighbor - their furthest members.
-% \item Centroid: Distance between centroids
-% \item Group Average: average of all cross-cluster pairs.
-% \end{itemize}
-
-%------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
-
-Fusion moves as defined in \cite{Lempitsky-2010} work
-in the node domain and do not work properly for 
-objective functions as Eq.~\ref{eq:nodeproblem} since
-the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
-In the following, we propose a more suitable fusion move for correlation
-clustering which works on the edge domain.
-%
-Given two proposal solutions $y'$ and $y''$,
-$\mathcal{C}$ is the set of edges
-which are uncut in $y'$ and $y''$.
-%
-\begin{align}
-\breve{y}    & =  y' \cup y'' \\
-\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
-\end{align}
-%
-The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
-%
-\begin{align}
-  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
-\end{align}
-%
-By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
-\begin{align}
-  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
-\end{align}
-%
-
-Once we know how to fuse segmentations, the actual algorithm 
-for correlation clustering 
-is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
-We iteratively improve the best solution by
-fusing it with proposal solutions.
-The inherent difference is how we define the fusion.
-We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
-%
-How to optimize  Eq.~\ref{eq:fusion_move_a} in an more efficient way is
-described in the following section.
-
-\input{inputs/fig_fusion.tex}
-
-%\textbf{old}
-%
-%Motivation Using Fusion moves -> problem ambiguity
-%
-%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
-%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
-%
-%We define the contradiction of graph $G_y=(V_y,E_y)$
-%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
-
-%\input{inputs/fig_alg_graph.tex}
-
-\subsection{Fast Optimization} \label{sec:fast_optimization}
-
-Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
-we can work on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges
-(see Fig.~\ref{fig:move_graph}).
-
-TODO:
-Here we need to proof that it is equivalent 
-to optimize the contracted graph !
-
-\input{inputs/fig_contraction.tex}
-\input{inputs/fig_projection.tex}
-
-\input{inputs/fig_move_graph.tex}
-
-%-------------------------------------------------------------------------
-%\subsection{Fusion Move Solver}
-
-%-------------------------------------------------------------------------
-\subsection{Proposal Generators}
-
-As discussed in \cite{Lempitsky-2010}, proposals
-should have two properties: \emph{quality} 
-and \emph{diversity}.
-The quality / energy of the individual proposals
-ensures low energy solutions since the
-result of the fusion cannot be higher then
-the energy of the current best solution.
-Diversity between the individual proposals
-reduces the chances to get stuck in local minima.
-For correlation clustering fusion we add a third
-property: \emph{size}.
-The size of the contraction graph directly
-depends on the number of connected components
-in the proposal solution and the current best solution.
-The extreme  case is a proposal where each 
-node is in a separate connnected component.
-Solving the fusion move with such a proposal
-is equivalent to solving the original problem.
-Solving the fusion move with a proposal with 
-a single connected component will result 
-in the current best solution.
-Therefore the size of the proposals
-should be small enough, such that solving
-eq.~\ref{eq:edgeproblem} can
-be done fast enough, but large enough to make
-meaningful moves (??? this last sentence needs to be rewritten).
-
-%\begin{algorithm}
-%    \begin{scriptsize}
-%        \caption{Proposal Generators}\label{alg:proposal_gen}   
-%        \begin{algorithmic}[1]
-%            %\Require $J(x) \leq J(x')$
-%            %\Ensure $J(\hat{x}) \leq J(x)$
-%            %\vspace{0.3cm}
-%            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
-%
-%            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
-%            \State \textbf{return} $x'$
-%            \EndProcedure
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $ getRandomSeeds$
-%            \State $ runEdgeWeightedWs$
-%            \EndProcedure   
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
-%            \State $\hat{W} \gets W$
-%            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
-%                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
-%                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
-%            \EndWhile
-%            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
-%            \EndProcedure
-%        \end{algorithmic}
-%    \end{scriptsize}
-%\end{algorithm}
-
-\noindent \textbf{Randomized HierarchicalClustering (RHC):}
-%\subsubsection{Randomized HierarchicalClustering (RHC)}
-%
-To generate proposals cut we can use bottom up hierarchical clustering.
-In each step we contract the edge with the highest weight.
-Parallel edges are merged into single edges by summing their weights.
-We stop when a certain number of nodes is reached, or the
-largest edge weight among the not yet contracted edges is smaller then a certain threshold.
-To get versatile proposals we either add noise 
-to the edge weighs or permute a certain number of weights.
-
-%\subsubsection{Randomized MaxCut  (RMC)}
-%
-%To get energy aware proposals we can use max cuts.
-%The max cut objective is the same as
-%the multicut objective, but only two 
-%node colors are allowed.
-%Therefore solutions of the max cut objective
-%might be useful proposals.
-%To create different proposals we set 
-%the weight of edges which are cut 
-%in the best solution to zero.
-%In this way we favor solutions 
-%different form the current best. 
-%In addition we either add noise permute a certain number of weights.
-
-\noindent \textbf{Randomized Watersheds (RWS):}
-%\subsubsection{Randomized Watersheds (RWS)}
-%
-The edge weighted watershed algorithm \cite{meyer_2013}
-with random seeds can be used to get 
-cheap proposals. Instead of $n$ seeds distributed uniformly
-over all nodes we use the following.
-Draw $n/k$ random edges only the negative edges, 
-and give the two nodes of each random edge different seeds.
-Doing so, a random subset of negative edges is forced
-to be cut within each proposal.
-For additional randomness, noise can be added to
-the edge weighs.
-
-%\input{inputs/fig_hc.tex}
-
-\subsection{Properties and Polyhedral Interpretation}
-An alternative interpretation of our method is shown in Fig.~\ref{fig:polyheadral}.
-In each iteration the current and proposed segmentation define an inner polyheadral 
-approximation of the original multicut polytope. 
-Optimizing over this polytope is the same problem as the original one, but much smaller.
-Furthermore, the costs does not change and and improvement in the smaller polytope will 
-be the same in the original graph.
-The choice of the proposal defines the shape of the auxiliary polytope. 
-In the given toy example, the first (red) polytope give a huge improvement, the second proposal
-defines the blue polytope which does not lead to an improvement. 
-The third proposal generates the green polytope that includes the global optimal solution.
-
-This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
-which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
-
-\begin{figure}
-\centering
-\input{polytope-tikz.tex}
-\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
-Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
-and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
-When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
-}
-\label{fig:polyheadral}
-\end{figure}
-
-\begin{theorem}[Equivalence]
-The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
-is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
-with additional must link constraints ($y^* \leq y$).
-%
-\begin{proof}
-Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
-Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
-\end{proof}
-%
-\end{theorem}
-
-\begin{theorem}[Monotone]
-Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
-Than $y^*$  will never decrease the energy:
-$y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
-%
-\begin{proof}
-The feasible set of the fusion move includes per definition  $y'$ and $y''$.
-If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
-and that why not the propose segmentation of a fusion.
-\end{proof}
-%
-\end{theorem}
-
-%\begin{remark}[Fix-point (pointless to me)]
-%Let $Y$ be the set of possible proposals, than
-%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
-%\end{remark}
-
-\begin{remark}[Optimality]
-Let $y'$ be the current and $y''$ the proposed segmentation.
-If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
-\end{remark}
-
-\section{Experiments}\label{sec:exp}
-In our experiments we compare to the following methods withpublic available implementation.
-
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
-of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
-For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
-Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-This procedure is one magnitude faster, but might cause a few extra outer iterations.
-In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
-From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
-We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
-While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
-We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
-
-As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
-Therefore we exclude those in our experiments.
-
-We compare this methods to the following methods suggested in the present paper.
-%
-Energy Based Based Hierarchical Clustering (\textbf{EHC})
-as described in sec.~\ref{sec:ehc}.
-%
-CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
-%
-The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
- and MC-I and CGC as subproblem solvers denoted by 
-\textbf{fusionCC-HC-MC},
-\textbf{-HC-CGC},
-\textbf{-WS-MC}, and 
-\textbf{-WS-CGC}, respectively.
-We set the size of the proposals fix to $10\%$ of the original problem size
-and the standard derivation of the random edge noise to $1.5$.
-
- \begin{figure}[t]
-    \centering
-    \begin{tikzpicture}
-    \begin{semilogxaxis}[  mark size=1pt,
-     height= 4cm, 
-    restrict y to domain=-80000:1000,
-   %   restrict x to domain=10:4000,
-    xlabel = {runtime},
-    xmin = 10,
-    xmax = 4100,
-    ymax = 0,
-    ymin = -80000,
-    legend to name = ledgendPositionMC,
-    legend columns=4,
-    width = 0.9\columnwidth,
-    scaled ticks = false
-    ] 
-    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
-    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
-    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
-    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}
-
-    \end{semilogxaxis}
-    \end{tikzpicture}
-  \begin{center}
-  \hypersetup{linkcolor = black}
-  \ref{ledgendPositionMC}
-  \hypersetup{linkcolor = red}
-  \end{center}
-    \caption{Comparison of the Multicut implementation of OpenGM and 
-    our modified implementation, which can deal better with large scale problems. 
-    However, for large scale problems it still does not scale.}
-    \label{fig:at:knott-450b}
-  \end{figure}
-
-All experiments were run on Intel Core i5-4570 CPUs
-with 3.20 GHz, equipped with 32 GB of RAM.
-In our evaluation we make not use of multiple threads.
-The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
-
-\subsection{Parameter Choice for CCFusion}
-Beside the choice of the proposal generator and fusion method CCFusion has some more parameters, which need to be set.
-The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
-Fig.~\ref{fig:parameterchoice} shows a evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
-The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
-The level of noise has no major impact on the runtime.
-The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
-Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low energy.
-As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
-experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
-%
-%
-\begin{figure}[th]
-\centering
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
-\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
-  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
-}
-\label{fig:parameterchoice}
-\end{figure}
-
-\subsection{Social Networks and Network Clustering}
-A application for large scale correlation clustering are social networks.
-We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
-Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
-%
-The first network is called \emph{Epinions}. 
-This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
-Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ is the edge-weight is positive or negative, respectively.
-The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
-%
-The second network is called \emph{Slashdot}. 
-Slashdot is a technology-related news website know for its specific user community. 
-In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
-The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.
-
-We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
-In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
-% 
-To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
-\begin{align}
-  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
-\end{align}
-We define the following energy function
-\begin{align}
- J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
-      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
-\end{align}
-which is zero if the given partitioning does not violated any relation and larger otherwise.
-
-{\color{red}\textbf{TODO: Discussion}}
-
-As another example for network clustering we use the modularity-clustering models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
-
-{\color{red}\textbf{TODO: Discussion}}
-
-\subsection{2D and 3D Image Segmentation}
-To segment images or volumes into a previously
-unknown number of clusters, correlation clustering
-has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.
-
-Starting from a super-pixel/-voxel segmentation,
-correlation clustering finds the clustering with the lowest energy.
-The energy is based on a likelihood of merging adjacent super-voxels.
-Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
-or to merge them ($p(y_{ij} = 0)$).
-The energy function is defined as following:
-\begin{align}
- J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
-\end{align}
-Where $\beta$ is used as a prior~\cite{andres_2011_iccv}.
-
-We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
-For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
-For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
-instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
-We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
-More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
-
-{\color{red}\textbf{TODO: Discussion}}
-
-\begin{table}[H]
-   \tiny
-   \centering
-   \caption{Datasets used for evaluation}
-   \label{tab:instance_sizes}
-   \begin{tabular}{llllc}
-      \toprule
-         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
-      \midrule 
-         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
-         knott-150        &     572-972         & ???              & 2            & $\times$ \\
-         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
-         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
-         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
-         3d-seg           &     101220          & ???              & 1            & $\times$ \\
-         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
-      \bottomrule
-   \end{tabular}
-\end{table}
-
-\begin{table}[H]
-   \tiny
-   \centering
-   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
-   \label{tab:eval}
-   \begin{tabular}{lllllll}
-      \toprule
-         Dataset          &  image-seg   & knott-3d-150&knott-3d-300&knott-3d-450 &knott-3d-550 &3d-seg\\
-      \midrule 
-         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &\\ 
-         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ \\
-         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ \\
-         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$\\
-         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$\\
-         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$\\
-         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$\\   
-         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ \\  
-         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$\\  
-         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ \\  
-         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$\\  
-         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ \\      
-      \bottomrule
-   \end{tabular}
-\end{table}
-
-%\begin{center}
-%    \begin{figure}
-%        \begin{center}
-%            \begin{subfigure}[b]{0.45\linewidth}
-%                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
-%            \end{subfigure}
-%            \quad
-%            \begin{subfigure}[b]{0.45\linewidth}
-%                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
-%            \end{subfigure}
-%        \end{center}
-%    \caption{
-%        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv%}
-%    }
-%    \end{figure}
-%\end{center}
-%
-%\newpage
-
-\input{anytimefigure2.tex}
-
-% \begin{figure}
-% \input{scatterplots/knott-3d-450.tex}
-% \caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
-% A more aggressive one would lead to much faster runtime with only a bit worse values.
-% DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
-% }
-% \end{figure}
-
-%\subsection{Pixel-wise Multicuts}
-%\input{inputs/fig_pixel_mc.tex}
-
-\section{Further Work}\label{sec:future}
-So far we have generated the proposals randomly and do not take the current segmentation into account.
-
-So far we only enforce must link constraints to obtain smaller problems.
-One can also enforce cannot link constraints to the problem. 
-If those are closed, they automatically lead to a decomposition of the problem, 
-which is a interesting property for very huge data.
-
-Improving proposals.
-
-\section{Conclusion}\label{sec:conclusion}
-
-We have presented a fast and scalable 
-approximate solver for correlation 
-clustering, named Fusion Moves for correlation clustering (FM-CC).
-The best solution is iteratively improved 
-by a fusion with proposal solutions.
-The itself is formulated as correlation
-clustering on a smaller graph fewer edges and nodes
-and can therefore be solved very fast.
-Our evaluation shows that CC-FF
-significantly outperforms 
-other solvers w.r.t. any time performance 
-with increasing problem size.
-
-\newpage
-
-\FloatBarrier
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-% \newpage
-
-% \onecolumn
-% \section{Appendix}
-
-% \input{tables/anytime/image-seg.tex}
-% \input{tables/anytime/knott-3d-150.tex}
-% \input{tables/knott-3d-300.tex}
-% \input{tables/anytime/knott-3d-450.tex}
-% \input{tables/knott-3d-550.tex}
-% \input{tables/anytime/seg-3d.tex}
-% \input{tables/modularity-clustering.tex}
-
-\end{document}

### 2014-11-11 paper/introduction-old.tex

--- 2014-11-11 paper/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{eso-pic}
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{xspace}
-\usepackage{booktabs}
-\usepackage{placeins}
-
-% Include other packages here, before hyperref.
-\usepackage{my_macros}
-\usepackage{paralist}
-\usepackage{amsthm}
-% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
-%\usepackage{framed}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{algorithm}
-%\usepackage{algorithmic}
-\usepackage{algpseudocode}
-\usepackage{setspace}
-%for tikz
-\usepackage{tikz,pgfplots}
-\usepackage{pgfplotstable}
-\usepackage{filecontents}
-%\usepackage{scrextend}
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-\newcommand{\footlabel}[2]{%
-    \addtocounter{footnote}{1}%
-    \footnotetext[\thefootnote]{%
-        \addtocounter{footnote}{-1}%
-        \refstepcounter{footnote}\label{#1}%
-        #2%
-    }%
-    $^{\ref{#1}}$%
-}
-
-\newcommand{\footref}[1]{%
-    $^{\ref{#1}}$%
-}
-\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
-\usetikzlibrary{arrows,petri,topaths}
-\usetikzlibrary{positioning,fit,calc}
-\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
-\usetikzlibrary{calc, matrix, backgrounds}
-
-%%%%%%global tikz styles
-
-\tikzstyle{eBlack}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=black!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eNotCut}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eBlue}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=blue!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eCut}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left, draw=red!70!black, line width=1mm]
-
-\pgfplotsset{every axis/.append style={
-  every axis y label/.style = {at={(ticklabel cs:0.5)}, rotate=90, anchor=south},
-  axis x line = {bottom},
-  axis y line = {left},
-  tick align = outside,
-  ymajorgrids = true,
-%  legend style = {draw=none, at={(1.05, 0.5)}, anchor=west, font=\small},
-  legend style = {font=\tiny},
-  legend columns = 1,
-  every axis plot/.append style = {line width=1pt},
-  label style = {font=\small},
-  tick label style={font=\small},
-  scaled ticks = false,
-}}
-
-% Two Colored Circle Split 
-\makeatletter
-\tikzset{circle split part fill/.style  args={#1,#2}{%
- alias=tmp@name, 
-  postaction={%
-    insert path={
-     \pgfextra{% 
-     \pgfpointdiff{\pgfpointanchor{\pgf@node@name}{center}}%
-                  {\pgfpointanchor{\pgf@node@name}{east}}%            
-     \pgfmathsetmacro\insiderad{\pgf@x}
-      \fill[#1] (\pgf@node@name.base) ([xshift=-\pgflinewidth]\pgf@node@name.east) arc
-                          (0:180:\insiderad-\pgflinewidth)--cycle;
-      \fill[#2] (\pgf@node@name.base) ([xshift=\pgflinewidth]\pgf@node@name.west)  arc
-                           (180:360:\insiderad-\pgflinewidth)--cycle;            
-         }}}}}  
- \makeatother
-
-%\usepackage{tkz-berge}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
-\usepackage{xargs} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{remark}{Remark}
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage{bm}% ändert \boldsymbol
-\def\arraystretch{0.8}
-\renewcommand{\tabcolsep}{2pt}
-\newcommand{\thickline}{2pt}
-\newcommand{\scatterplotpath}{./scatterplots/}
-
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
-\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
-\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
-\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
-\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
-\newcommand{\OR}{\textrm{ or }}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\newcommand{\realplot}[1]{
-\begin{tikzpicture}
-    \begin{axis}
-        \addlegendimage{empty legend}\addlegendentry{Matrix #1}
-        \addplot {0};
-        \addplot {1};
-        \addplot {2};
-        \addplot {3};
-    \end{axis}
-\end{tikzpicture}}
-
-% \newcommand{\anytimeplot}[1]{
-%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
-%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
-%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
-%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
-%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
-%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
-%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
-%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
-%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
-%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
-% }
-\newcommand{\anytimeplot}[1]{
-  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
-  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL} 
-  \addplot[color=yellow!50!black,mark=square] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
-  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
-  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CCFusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CCFusion-HC-CGC}
-  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CCFusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CCFusion-WS-CGC}
-}
-%  \addplot[color=yellow!50!black,mark=o] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
-  %\addplot[color=green!50,mark=o] table[x=time, y=PIVOT*]{data3/#1.data};          \addlegendentry{PIVOT-BOEM}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-%%%%%%%%% TITLE
-\include{my_macros.tex}
-%\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
-\title{Fusion Moves for Correlation Clustering}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  \color{red} \textbf{TODO:}
-Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized.
-We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering.
-A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.
-
-%We address the problem of partitioning a  graph
-%   into a previously unknown number of clusters.
-%   Among all partitions, the one with the minimal 
-%   sum of of cut edge weights is chosen. 
-%   This problem is known as correlation clustering 
-%   or multicut.
-%   We propose a general framework to find
-%   high quality approximate solutions for 
-%   this NP-hard problem based on a move making algorithm:
-%   We use candidate solutions from a proposal generator
-%   to iteratively improve the best observed solution similar
-%   to fusion moves.
-%   The proposed solver outperforms any other solver
-%   w.r.t. to any time performance.
-%   The solutions found by this solver are close
-%   to global optimal solutions w.r.t. energy
-%   and problem specific measurements as VI for
-%   image segmentation problems.
-
-\end{abstract}
 \section{Introduction}
-
-Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
-Its value is, firstly, that it accommodates both positive / attractive \emph{and} negative / repulsive edge weights.
-Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment.
-This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster.
-Secondly, the algorithm does not require a specification of the number of clusters.
-This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.
-
-\paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers.
-The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings.
-Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted.
-Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph.
-We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.
-We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks.
-The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.
-
-\paragraph{Related Work.}
-A natural approach is to solve the integer linear programming problem directly.
-To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found.
-Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation.
-Such an outer relaxation can be iteratively tightened.
-However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
-The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
-
-Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}.
-The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
-Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.
-
-Finally, there are heuristic methods such as ...
-
----------------END OF SUGGESTION ----------------------------------
-
 Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
@@
 BEOM stops if no move can decrease the costs.
-
-% \subsection{Karger-Stein Algorithms}
-% Use randomized procedure to reduce the number of nodes / edges to a reasonable 
-% number.
-% On the smaller graph, more expensive solvers are used.
-
-%\input{inputs/fig_hc_alg.tex}
-
-\section{Energy Based Hierarchical Clustering}\label{sec:ehc}
-Agglomerative hierarchical clustering (HC) is widely used
-in graph / image segmentation~\cite{arbelaez_2006}.
-In each step, the edge with the highest weight $w$ is
-contracted (red edges in Fig.~\ref{fig:hc_alg}).
-Doing so, parallel edges edges can occur.
-In agglomerative clustering, weights of
-parallel edges are merged into single edges.
-For image segmentation, the length
-weighted mean is used to do this update~\cite{arbelaez_2006}.
-
-While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
-agglomeration with respect to our energy function.
-For this we propose to use energy based agglomeration
-withe the following update rule:
-Whenever there are multiple edges between 
-a pair of nodes, these edges are merged into a single edge
-by summing up their weights, since we 
-minimize the sum of the cut edges.
-We call HC with this update method Energy base Hierarchical Clustering (EHC).
-
-We stop EHC if the highest edge weight is
-smaller or equal to zero  (green edge in Fig.~\ref{fig:hc_alg}). Any further edge
-contraction leads to worse energies.
-
-% Hierarchical clustering is fast, and 
-% due to the agglomeration of edge weights, 
-% {\color{red} hierarchical clustering is robust against noise}.
-% {\color{yellow} [ First most similar nodes are merged...]
-% In agglomerative clustering, weights of
-% parallel edges are merged into single edges.}
-% For image segmentation, the length
-% weighted mean is used to do this update [ref].
-
-% [We contrary on those works work directly on energy functions and that why ...]
-% We propose to use Energy Based Hierarchical Clustering (EHC) to find
-% solutions for correlation clustering.
-
-% To make EHC follow the energy, we propose 
-% the following update rule:
-% Whenever there are multiple edges between 
-% a pair of nodes, these edges are merged into a single edge
-% by summing up their weights, since we 
-% minimize the sum of the cut edges.
-% The algorithm stops if the highest edge weight is
-% smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
-% contraction leads to worse energies.
-
-Given the intrinsic greediness of hierarchical clustering, 
-and the fact that EHC does only local decisions, it is 
-sensitive against salt and paper noise 
-and we do not expect very good solutions.
-
-But EHC is very fast, and can be used to initialize
-CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
-is spend in the \emph{cut phase} to solve the 
-first 2 coloring on the complete graph.
-As shown in Sec.~\ref{sec:exp},
-allowing CGC to start from the EHC solution
-can improve performance drastically.
-
-% Common cluster distances
-% \begin{itemize}
-% \item Single-Link: Nearest Neighbor - their closest members.
-% \item Complete-Link: Furthest Neighbor - their furthest members.
-% \item Centroid: Distance between centroids
-% \item Group Average: average of all cross-cluster pairs.
-% \end{itemize}
-
-%------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
-
-Fusion moves as defined in \cite{Lempitsky-2010} work
-in the node domain and do not work properly for 
-objective functions as Eq.~\ref{eq:nodeproblem} since
-the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
-In the following, we propose a more suitable fusion move for correlation
-clustering which works on the edge domain.
-%
-Given two proposal solutions $y'$ and $y''$,
-$\mathcal{C}$ is the set of edges
-which are uncut in $y'$ and $y''$.
-%
-\begin{align}
-\breve{y}    & =  y' \cup y'' \\
-\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
-\end{align}
-%
-The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
-%
-\begin{align}
-  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
-\end{align}
-%
-By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
-\begin{align}
-  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
-\end{align}
-%
-
-Once we know how to fuse segmentations, the actual algorithm 
-for correlation clustering 
-is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
-We iteratively improve the best solution by
-fusing it with proposal solutions.
-The inherent difference is how we define the fusion.
-We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
-%
-How to optimize  Eq.~\ref{eq:fusion_move_a} in an more efficient way is
-described in the following section.
-
-\input{inputs/fig_fusion.tex}
-
-%\textbf{old}
-%
-%Motivation Using Fusion moves -> problem ambiguity
-%
-%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
-%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
-%
-%We define the contradiction of graph $G_y=(V_y,E_y)$
-%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
-
-%\input{inputs/fig_alg_graph.tex}
-
-\subsection{Fast Optimization} \label{sec:fast_optimization}
-
-Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
-we can work on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges
-(see Fig.~\ref{fig:move_graph}).
-
-TODO:
-Here we need to proof that it is equivalent 
-to optimize the contracted graph !
-
-\input{inputs/fig_contraction.tex}
-\input{inputs/fig_projection.tex}
-
-\input{inputs/fig_move_graph.tex}
-
-%-------------------------------------------------------------------------
-%\subsection{Fusion Move Solver}
-
-%-------------------------------------------------------------------------
-\subsection{Proposal Generators}
-
-As discussed in \cite{Lempitsky-2010}, proposals
-should have two properties: \emph{quality} 
-and \emph{diversity}.
-The quality / energy of the individual proposals
-ensures low energy solutions since the
-result of the fusion cannot be higher then
-the energy of the current best solution.
-Diversity between the individual proposals
-reduces the chances to get stuck in local minima.
-For correlation clustering fusion we add a third
-property: \emph{size}.
-The size of the contraction graph directly
-depends on the number of connected components
-in the proposal solution and the current best solution.
-The extreme  case is a proposal where each 
-node is in a separate connnected component.
-Solving the fusion move with such a proposal
-is equivalent to solving the original problem.
-Solving the fusion move with a proposal with 
-a single connected component will result 
-in the current best solution.
-Therefore the size of the proposals
-should be small enough, such that solving
-eq.~\ref{eq:edgeproblem} can
-be done fast enough, but large enough to make
-meaningful moves (??? this last sentence needs to be rewritten).
-
-%\begin{algorithm}
-%    \begin{scriptsize}
-%        \caption{Proposal Generators}\label{alg:proposal_gen}   
-%        \begin{algorithmic}[1]
-%            %\Require $J(x) \leq J(x')$
-%            %\Ensure $J(\hat{x}) \leq J(x)$
-%            %\vspace{0.3cm}
-%            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
-%
-%            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
-%            \State \textbf{return} $x'$
-%            \EndProcedure
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $ getRandomSeeds$
-%            \State $ runEdgeWeightedWs$
-%            \EndProcedure   
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
-%            \State $\hat{W} \gets W$
-%            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
-%                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
-%                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
-%            \EndWhile
-%            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
-%            \EndProcedure
-%        \end{algorithmic}
-%    \end{scriptsize}
-%\end{algorithm}
-
-\noindent \textbf{Randomized HierarchicalClustering (RHC):}
-%\subsubsection{Randomized HierarchicalClustering (RHC)}
-%
-To generate proposals cut we can use bottom up hierarchical clustering.
-In each step we contract the edge with the highest weight.
-Parallel edges are merged into single edges by summing their weights.
-We stop when a certain number of nodes is reached, or the
-largest edge weight among the not yet contracted edges is smaller then a certain threshold.
-To get versatile proposals we either add noise 
-to the edge weighs or permute a certain number of weights.
-
-%\subsubsection{Randomized MaxCut  (RMC)}
-%
-%To get energy aware proposals we can use max cuts.
-%The max cut objective is the same as
-%the multicut objective, but only two 
-%node colors are allowed.
-%Therefore solutions of the max cut objective
-%might be useful proposals.
-%To create different proposals we set 
-%the weight of edges which are cut 
-%in the best solution to zero.
-%In this way we favor solutions 
-%different form the current best. 
-%In addition we either add noise permute a certain number of weights.
-
-\noindent \textbf{Randomized Watersheds (RWS):}
-%\subsubsection{Randomized Watersheds (RWS)}
-%
-The edge weighted watershed algorithm \cite{meyer_2013}
-with random seeds can be used to get 
-cheap proposals. Instead of $n$ seeds distributed uniformly
-over all nodes we use the following.
-Draw $n/k$ random edges only the negative edges, 
-and give the two nodes of each random edge different seeds.
-Doing so, a random subset of negative edges is forced
-to be cut within each proposal.
-For additional randomness, noise can be added to
-the edge weighs.
-
-%\input{inputs/fig_hc.tex}
-
-\subsection{Properties and Polyhedral Interpretation}
-An alternative interpretation of our method is shown in Fig.~\ref{fig:polyheadral}.
-In each iteration the current and proposed segmentation define an inner polyheadral 
-approximation of the original multicut polytope. 
-Optimizing over this polytope is the same problem as the original one, but much smaller.
-Furthermore, the costs does not change and and improvement in the smaller polytope will 
-be the same in the original graph.
-The choice of the proposal defines the shape of the auxiliary polytope. 
-In the given toy example, the first (red) polytope give a huge improvement, the second proposal
-defines the blue polytope which does not lead to an improvement. 
-The third proposal generates the green polytope that includes the global optimal solution.
-
-This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
-which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
-
-\begin{figure}
-\centering
-\input{polytope-tikz.tex}
-\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
-Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
-and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
-When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
-}
-\label{fig:polyheadral}
-\end{figure}
-
-\begin{theorem}[Equivalence]
-The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
-is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
-with additional must link constraints ($y^* \leq y$).
-%
-\begin{proof}
-Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
-Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
-\end{proof}
-%
-\end{theorem}
-
-\begin{theorem}[Monotone]
-Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
-Than $y^*$  will never decrease the energy:
-$y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
-%
-\begin{proof}
-The feasible set of the fusion move includes per definition  $y'$ and $y''$.
-If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
-and that why not the propose segmentation of a fusion.
-\end{proof}
-%
-\end{theorem}
-
-%\begin{remark}[Fix-point (pointless to me)]
-%Let $Y$ be the set of possible proposals, than
-%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
-%\end{remark}
-
-\begin{remark}[Optimality]
-Let $y'$ be the current and $y''$ the proposed segmentation.
-If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
-\end{remark}
-
-\section{Experiments}\label{sec:exp}
-In our experiments we compare to the following methods withpublic available implementation.
-
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
-of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
-For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
-Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-This procedure is one magnitude faster, but might cause a few extra outer iterations.
-In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
-From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
-We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
-While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
-We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
-
-As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
-Therefore we exclude those in our experiments.
-
-We compare this methods to the following methods suggested in the present paper.
-%
-Energy Based Based Hierarchical Clustering (\textbf{EHC})
-as described in sec.~\ref{sec:ehc}.
-%
-CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
-%
-The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
- and MC-I and CGC as subproblem solvers denoted by 
-\textbf{fusionCC-HC-MC},
-\textbf{-HC-CGC},
-\textbf{-WS-MC}, and 
-\textbf{-WS-CGC}, respectively.
-We set the size of the proposals fix to $10\%$ of the original problem size
-and the standard derivation of the random edge noise to $1.5$.
-
- \begin{figure}[t]
-    \centering
-    \begin{tikzpicture}
-    \begin{semilogxaxis}[  mark size=1pt,
-     height= 4cm, 
-    restrict y to domain=-80000:1000,
-   %   restrict x to domain=10:4000,
-    xlabel = {runtime},
-    xmin = 10,
-    xmax = 4100,
-    ymax = 0,
-    ymin = -80000,
-    legend to name = ledgendPositionMC,
-    legend columns=4,
-    width = 0.9\columnwidth,
-    scaled ticks = false
-    ] 
-    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
-    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
-    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
-    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}
-
-    \end{semilogxaxis}
-    \end{tikzpicture}
-  \begin{center}
-  \hypersetup{linkcolor = black}
-  \ref{ledgendPositionMC}
-  \hypersetup{linkcolor = red}
-  \end{center}
-    \caption{Comparison of the Multicut implementation of OpenGM and 
-    our modified implementation, which can deal better with large scale problems. 
-    However, for large scale problems it still does not scale.}
-    \label{fig:at:knott-450b}
-  \end{figure}
-
-All experiments were run on Intel Core i5-4570 CPUs
-with 3.20 GHz, equipped with 32 GB of RAM.
-In our evaluation we make not use of multiple threads.
-The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
-
-\subsection{Parameter Choice for CCFusion}
-Beside the choice of the proposal generator and fusion method CCFusion has some more parameters, which need to be set.
-The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
-Fig.~\ref{fig:parameterchoice} shows a evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
-The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
-The level of noise has no major impact on the runtime.
-The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
-Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low energy.
-As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
-experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
-%
-%
-\begin{figure}[th]
-\centering
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
-\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
-  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
-}
-\label{fig:parameterchoice}
-\end{figure}
-
-\subsection{Social Networks and Network Clustering}
-A application for large scale correlation clustering are social networks.
-We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
-Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
-%
-The first network is called \emph{Epinions}. 
-This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
-Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ is the edge-weight is positive or negative, respectively.
-The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
-%
-The second network is called \emph{Slashdot}. 
-Slashdot is a technology-related news website know for its specific user community. 
-In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
-The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.
-
-We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
-In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
-% 
-To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
-\begin{align}
-  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
-\end{align}
-We define the following energy function
-\begin{align}
- J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
-      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
-\end{align}
-which is zero if the given partitioning does not violated any relation and larger otherwise.
-
-{\color{red}\textbf{TODO: Discussion}}
-
-As another example for network clustering we use the modularity-clustering models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
-
-{\color{red}\textbf{TODO: Discussion}}
-
-\subsection{2D and 3D Image Segmentation}
-To segment images or volumes into a previously
-unknown number of clusters, correlation clustering
-has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.
-
-Starting from a super-pixel/-voxel segmentation,
-correlation clustering finds the clustering with the lowest energy.
-The energy is based on a likelihood of merging adjacent super-voxels.
-Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
-or to merge them ($p(y_{ij} = 0)$).
-The energy function is defined as following:
-\begin{align}
- J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
-\end{align}
-Where $\beta$ is used as a prior~\cite{andres_2011_iccv}.
-
-We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
-For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
-For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
-instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
-We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
-More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
-
-{\color{red}\textbf{TODO: Discussion}}
-
-\begin{table}[H]
-   \tiny
-   \centering
-   \caption{Datasets used for evaluation}
-   \label{tab:instance_sizes}
-   \begin{tabular}{llllc}
-      \toprule
-         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
-      \midrule 
-         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
-         knott-150        &     572-972         & ???              & 2            & $\times$ \\
-         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
-         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
-         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
-         3d-seg           &     101220          & ???              & 1            & $\times$ \\
-         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
-      \bottomrule
-   \end{tabular}
-\end{table}
-
-\begin{table}[H]
-   \tiny
-   \centering
-   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
-   \label{tab:eval}
-   \begin{tabular}{lllllll}
-      \toprule
-         Dataset          &  image-seg   & knott-3d-150&knott-3d-300&knott-3d-450 &knott-3d-550 &3d-seg\\
-      \midrule 
-         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &\\ 
-         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ \\
-         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ \\
-         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$\\
-         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$\\
-         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$\\
-         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$\\   
-         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ \\  
-         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$\\  
-         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ \\  
-         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$\\  
-         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ \\      
-      \bottomrule
-   \end{tabular}
-\end{table}
-
-%\begin{center}
-%    \begin{figure}
-%        \begin{center}
-%            \begin{subfigure}[b]{0.45\linewidth}
-%                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
-%            \end{subfigure}
-%            \quad
-%            \begin{subfigure}[b]{0.45\linewidth}
-%                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
-%            \end{subfigure}
-%        \end{center}
-%    \caption{
-%        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv%}
-%    }
-%    \end{figure}
-%\end{center}
-%
-%\newpage
-
-\input{anytimefigure2.tex}
-
-% \begin{figure}
-% \input{scatterplots/knott-3d-450.tex}
-% \caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
-% A more aggressive one would lead to much faster runtime with only a bit worse values.
-% DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
-% }
-% \end{figure}
-
-%\subsection{Pixel-wise Multicuts}
-%\input{inputs/fig_pixel_mc.tex}
-
-\section{Further Work}\label{sec:future}
-So far we have generated the proposals randomly and do not take the current segmentation into account.
-
-So far we only enforce must link constraints to obtain smaller problems.
-One can also enforce cannot link constraints to the problem. 
-If those are closed, they automatically lead to a decomposition of the problem, 
-which is a interesting property for very huge data.
-
-Improving proposals.
-
-\section{Conclusion}\label{sec:conclusion}
-
-We have presented a fast and scalable 
-approximate solver for correlation 
-clustering, named Fusion Moves for correlation clustering (FM-CC).
-The best solution is iteratively improved 
-by a fusion with proposal solutions.
-The itself is formulated as correlation
-clustering on a smaller graph fewer edges and nodes
-and can therefore be solved very fast.
-Our evaluation shows that CC-FF
-significantly outperforms 
-other solvers w.r.t. any time performance 
-with increasing problem size.
-
-\newpage
-
-\FloatBarrier
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-% \newpage
-
-% \onecolumn
-% \section{Appendix}
-
-% \input{tables/anytime/image-seg.tex}
-% \input{tables/anytime/knott-3d-150.tex}
-% \input{tables/knott-3d-300.tex}
-% \input{tables/anytime/knott-3d-450.tex}
-% \input{tables/knott-3d-550.tex}
-% \input{tables/anytime/seg-3d.tex}
-% \input{tables/modularity-clustering.tex}
-
-\end{document}

### 2014-11-11 paper/introduction-new.tex
introduction in progress

@@
 A natural approach is to solve the integer linear programming problem directly. 
-To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found.
-Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation.
-Such an outer relaxation can be iteratively tightened.
-However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
-The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
+To this end, efficient separation procedures have been found~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
+Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation~\cite{kappes_2013_arxiv}. 
+Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
+For the latter approach column generating methods exits, that works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
 
-Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}.
+Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{beier_2014_cvpr}. 
 The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
-Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.
+% Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}. 
+An other branch of research uses move making algorithm 
+to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
+Starting with an initial segmentation, auxiliary problems are solved that 
+strictly improve the segmentation.
+
+Bansal and Bagon propose a modified $\alpha-$expansion~\cite{bansal_2004_ml} 
+algorithm suitable for correlation clustering, that allows all variables to 
+change to cluster $\alpha$ in a single move. While the authors claim that this
+scales to large scale data, in~\cite{beier_2014_cvpr} it has been shown that 
+this is not the case in general. This is not surprising because the auxiliary 
+problems can have as many variables as the original problem.
+
+A more efficient move making method has been presented by Beier \etal~\cite{beier_2014_cvpr}.
+Their Cut, Glue and Cut method iteratively re-optimizes the cuts between adjacent clusters of the current solution.
+While this method scales better then  modified $\alpha-$expansion, it still faces three problems:
+Firstly, the subproblems can be as large as the original problem,
+secondly, the subproblems are max-cut problems on non-planar graphs that are NP-hard 
+and even the used approximation has high polynomial complexity.
+This limits the method, to be applicable to huge problems. The same holds for the 
+method of Kernighan and Lin~\cite{Kernighan-1970}.
+
+   % \begin{itemize}
+   % \item Multicut~\cite{kappes_2011_emmcvpr}
+   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
+   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
+   % \item Break and Conquer \cite{alush_2013_simbad}.
+   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
+   % \end{itemize}
+
+For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
+For many large scale computer vision applications fusion moves lead to good approximations
+with state of the art any time performance~\cite{kappes_2014_ws}.
 

### 2014-11-11 paper/egpaper_for_review.tex

--- 2014-11-11 paper/egpaper_for_review.tex
@@
 %
-Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
-we can work on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges
-(see Fig.~\ref{fig:move_graph}).
+
+Once we know how to fuse segmentations, the actual algorithm 
+for correlation clustering 
+is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
+We iteratively improve the best solution by
+fusing it with proposal solutions.
+The inherent difference is how we define the fusion.
+We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
+%
+How to optimize  Eq.~\ref{eq:fusion_move_a} in an more efficient way is
+described in the following section.
 
@@
 \subsection{Fast Optimization} \label{sec:fast_optimization}
+
+Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
+we can work on a coarser graph, where all nodes which are connected
+via must-link constraints are merged into single nodes.
+This coarser graph is constructed by contracting all must-link edges
+(see Fig.~\ref{fig:move_graph}).
+
 TODO:
@@
 
-% Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
-% Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
-% but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
-
-% To make multicuts scalable, it is desirable to replace the graph $G$
-% with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
-% If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.
-
-% A trivial way to reduce the size of the graph  is edge contraction.
-% Until a desirable size is reached, one might contract the edge with
-% the highest weight. A cut on the contracted graph  $\hat{G}$ is always
-% a valid cut on $\hat{G}$.
-
-% On the other hand, if an edge $e$ is contracted, it will never be cut.
-% If $e$ is part of the cut in a global optimal solution, we cannot find
-% this cut.
-
-% To overcome this problem  we can randomize the edge contraction,
-% and repeat this multiple times and remember the best solution.
-
-% But this would throw away all the ``not the best'' solutions (rewrite me).
-% Within this work we propose the following nifty trick.
-% Instead of throwing away solutions, we intersect them with the 
-% best solution, and solve the multicut on the resulting
-% graph.
-% Therefore we fuse multiple solutions,
-
-%\begin{algorithm}
-%\begin{scriptsize}
-%\caption{Fusion Based Algorithms}\label{alg:fusion}
-%
-%
-%
-%
-%\begin{algorithmic}[1]
-%\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
-%\State $x^0 \gets \textrm{initial state form } X$
-%\State $n \gets 0 $                                 \Comment{Number of moves}
-%\State $m \gets 0 $                                 \Comment{Number of moves without progress}
-%\While{$m < m_{\max}$ and $n < n_{\max}$ }
-%\State $n \gets n+1$ 
-% \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
-% \If{$J(x^{n-1}) \leq J(x')$}                       
-%   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
-% \Else
-%   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
-% \EndIf
-% \If{$J(x^{n}) \leq J(x^{n-1})$}
-%   \State $m \gets 0$                                 \Comment{Reset counter}
-% \Else
-%   \State $m \gets m+1$                               \Comment{Increment counter}
-% \EndIf
-%\EndWhile
-%\State \textbf{return} $x^n$
-%\EndProcedure
-%\end{algorithmic}
-%\end{scriptsize}
-%\end{algorithm}
-
-%\begin{algorithm}
-%\begin{scriptsize}
-%\caption{Fusion Moves}\label{alg:fusion_moves}
-%\scriptsize
-%\begin{algorithmic}[1]
-%\Require $J(x) \leq J(x')$
-%\Ensure $J(\hat{x}) \leq J(x)$
-%\vspace{0.2cm}
-%\Procedure{Fuse}{$x,x',J$}
-%\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
-%    \Comment{
-%        \begin{minipage}{0.4\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                intersect
-%                uncut edges in $x$ and $x'$,
-%                return  
-%                connected component labeling
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%\vspace{0.1cm}
-%\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
-%    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
-%    \Comment{ 
-%        \begin{minipage}{0.2\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                Contract all edges 
-%                which are uncut in $\bar{x}$ 
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%\vspace{0.1cm}
-%\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
-%    \Comment{ 
-%        \begin{minipage}{0.3\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                Solve the multicut objective
-%                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%
-%\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
-%    \Comment{ 
-%        \begin{minipage}[\textheight]{0.4\linewidth} 
-%            \begin{tiny}
-%            \begin{singlespace}
-%                Translate the connected component
-%                labeling $\tilde{x}^*$ of $\tilde{G}$ 
-%                to a connected component labeling of $G$
-%            \end{singlespace}
-%            \end{tiny}
-%        \end{minipage}
-%    }
-%\State \textbf{return} $\hat{x}$
-%\EndProcedure
-%\vspace{0.3cm}
-%\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
-%\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
-%\EndProcedure
-%\end{algorithmic}
-%\end{scriptsize}
-%\end{algorithm}
-
 %-------------------------------------------------------------------------
-\subsection{Fusion Move Solver}
-
-% \begin{center}
-%     \begin{eqnarray}
-%         y 
-%         &=& 
-%         \rho_{\hat{y}}^{-1}(
-%         \argmin_{y \in MC(G_{\hat{y}})\cap \{0,1\}^{|E_{\hat{y}}|}} 
-%         \sum_{ (i,j) \in E_{\hat{y}} } 
-%         w^{\hat{y}}_{ij} \cdot \bar{y}_{ij} 
-%     \end{eqnarray}
-% \end{center}
-
-% \begin{center}
-%     \begin{eqnarray}
-%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
-%     \end{eqnarray}
-% \end{center}
-Once we know how to fuse segmentations, the actual algorithm 
-for correlation clustering 
-is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
-We iteratively improve the best solution by
-fusing it with proposal solutions.
-The inherent difference is how we define the fusion.
-We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}
-and optimize the subproblems as described in 
-Sec.~\ref{sec:fast_optimization} (see Fig. \ref{fig:move_graph}).
+%\subsection{Fusion Move Solver}
 

### 2014-11-11 paper/inputs/fig_hc_alg.tex

@@
 \begin{center}
-\begin{figure*}
-\resizebox{!}{0.15\linewidth}{%
+\begin{figure}
+\begin{center}
+\resizebox{0.75\linewidth}{!}{
+%\resizebox{!}{0.25\linewidth}{%
     \begin{tikzpicture}
-    \draw (0,-1)node (dummyLow){} ;
-    \draw (0, 3)node (dummyLow){} ;
+    %\draw (0,-1)node (dummyLow){} ;
+    %\draw (0, 3)node (dummyLow){} ;
     \draw (2,2) node[nS] (n0) {$0$}; 
@@
     ;
-    \end{tikzpicture}
-    \begin{tikzpicture}
-    \draw (0,-1)node (dummyLow){} ;
-    \draw (0, 3)node (dummyLow){} ;
-    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
-    \draw (4,2) node[nS] (n1) {$1$};
-    \draw (6,2) node[nS] (n2) {$2$};
-    \draw (4,0) node[nS] (n4) {$4$};
-    \draw (6,0) node[nS] (n5) {$5$};
+
+    %\draw (0+6,-1)node (dummyLow){} ;
+    %\draw (0+6, 3)node (dummyLow){} ;
+    \draw (2+6,1) node[nS] (n03) {$\{0,3\}$}; 
+    \draw (4+6,2) node[nS] (n1) {$1$};
+    \draw (6+6,2) node[nS] (n2) {$2$};
+    \draw (4+6,0) node[nS] (n4) {$4$};
+    \draw (6+6,0) node[nS] (n5) {$5$};
 
@@
     ;
-    \end{tikzpicture}
-}
-%
-\resizebox{!}{0.15\linewidth}{%
-    \begin{tikzpicture}
-    \draw (0,-1)node (dummyLow){} ;
-    \draw (0, 3)node (dummyLow){} ;
-    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
-    \draw (4,2) node[nS] (n1) {$1$};
-    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
-    \draw (4,0) node[nS] (n4) {$4$};
+
+    %\draw (0,-1)node (dummyLow){} ;
+    %\draw (0,3-3)node (dummyLow){} ;
+    \draw (2,1-3) node[nS] (n03) {$\{0,3\}$}; 
+    \draw (4,2-3) node[nS] (n1) {$1$};
+    \draw (6,1-3) node[nS] (n25) {$\{2,5\}$};
+    \draw (4,0-3) node[nS] (n4) {$4$};
     \path
@@
     ;
-    \end{tikzpicture}
-    \begin{tikzpicture}
-    \draw (0,-1)node (dummyLow){} ;
-    \draw (0, 3)node (dummyLow){} ;
-    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
-    \draw (4,1) node[nS] (n14) {$\{1,4\}$};
-    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
+
+    %\draw (0+6,-1 -3)node (dummyLow){} ;
+    %\draw (0+6, 3 -3)node (dummyLow){} ;
+    \draw (2+6,1  -3) node[nS] (n03) {$\{0,3\}$}; 
+    \draw (4+6,1  -3) node[nS] (n14) {$\{1,4\}$};
+    \draw (6+6,1  -3) node[nS] (n25) {$\{2,5\}$};
     \path
@@
     ;
+
     \end{tikzpicture}
+%}
+
 }
 \caption{
-     To use hierarchical clustering as an approximator for
-    the multicut objective we contract the edge with the highest weight
-    in each step (to be contracted edge is shown in green).
-    Whenever multiple edges are merged into a single edge,
-    we use the sum of the weight as a new weight, since
-    we have to pay for all edges which are cut in the uncontracted
-    graph.
-    We stop when the highest edge weight is smaller
+    Hierarchical clustering can be used to optimize
+    Eq.~\ref{eq:edgeproblem}.
+    In each step, the two nodes connected via the edge with 
+    the highest weight are merged by contracting this edge.
+    (to be contracted edge is shown in green).
+    Due to edge contraction parallel edges can occur which 
+    are merged into single ones, and their weights are summed up.
+    The algorithm stops when the highest edge weight is smaller
     or equal to zero (edge shown in blue).
 }\label{fig:hc_alg}
-\end{figure*}
 \end{center}
+\end{figure}
+\end{center}

### 2014-11-11 paper/anytimefigure2.tex
made caption on anytime plot more compact

@@
     % image seg
-    For the image-seg instances in fig.~\ref{fig:at:image-seg} 
-    Fusion-EHC-MC has performs best and Fusion-WS-MC gives 
-    almost the same results, but a bit slower then with EHC proposals.
-    Using the same proposals but approximate moves (Fusion-EHC-CGC Fusion-WS-CGC )
-    leads to suboptimal results.
-    The warm EHC started version of GCG (EHC-CGC) performs better then GCG itself,
-    but both are outperformed by the proposed algorithms.
-    Global optimal methods (MC-I) and the relaxed version (MC-R) are 
-    still usable fast for these instances.
-    % 3d 
-    For the smallest 3D instances (\ref{fig:at:knott-150}) all solvers
-    except ??? and EHC perform equally, and the proposed fusion algorithms
-    give the best any time performance.
+    %For the image-seg instances in fig.~\ref{fig:at:image-seg} 
+    %Fusion-EHC-MC has performs best and Fusion-WS-MC gives 
+    %almost the same results, but a bit slower then with EHC proposals.
+    %Using the same proposals but approximate moves (Fusion-EHC-CGC Fusion-WS-CGC )
+    %leads to suboptimal results.
+  %
+    %Global optimal methods (MC-I) and the relaxed version (MC-R) are 
+    %still usable fast for these instances.
+    %% 3d 
+    %For the smallest 3D instances (\ref{fig:at:knott-150}) all solvers
+    %except ??? and EHC perform equally, and the proposed fusion algorithms
+    %give the best any time performance.
+    %
+    %% social nets
+    %For the social net instances (\ref{fig:at:socialnets},\ref{fig:at:nsocialnets})
+    %Fusion-HC-MC and Fusion-HC-CGC perform equally.
+    %Only CGC and EHC-CGC leads to better energies after $10^3 sec$, while global optimal methods (MC-I)
+    %fail to converge within this time limit.
+    %%%%%
+    Among all proposed solvers, Fusion-HC-MC has the best
+    overall anytime performance.
+    %
     With increasing problem size (\ref{fig:at:knott-150}-\ref{fig:at:knott-550} and \ref{fig:at:seg3d})
@@
     GCG in terms of runtime and energy.
-    % social nets
-    For the social net instances (\ref{fig:at:socialnets},\ref{fig:at:nsocialnets})
-    Fusion-HC-MC and Fusion-HC-CGC perform equally.
-    Only CGC and EHC-CGC leads to better energies after $10^3 sec$, while global optimal methods (MC-I)
-    fail to converge within this time limit.
-    % modularity clustering 
-    For the modularity clustering instances in fig.~\ref{fig:at:modularity} we see
-    an interesting behavior. On these complete graphs, Kernighan Lin (KL) has the 
-    best performance.
-    The proposed methods perform reasonable, but  KL is faster and leads to better energies.
-    %%%
     %% summary
@@
     to solve the fusion move to optimality (Fusion-HC-MC) then using approximations (FUSION-HC-GCG).
+    The warm EHC started version of GCG (EHC-CGC) performs better then GCG itself,
+    but both are outperformed by the proposed algorithms w.r.t. any time performance.
+    % modularity clustering 
+    For the modularity clustering instances in fig.~\ref{fig:at:modularity} we see
+    an interesting behavior. On these complete graphs, Kernighan Lin (KL) has the 
+    best performance.
+    The proposed methods perform reasonable, but  KL is faster and leads to better energies.
   }

### 2014-11-11 paper/introduction-new.tex

@@
 
-Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{beier_2014_cvpr}. 
-The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
-% Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}. 
-An other branch of research uses move making algorithm 
+Another line of work uses move making algorithm 
 to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
-Starting with an initial segmentation, auxiliary problems are solved that 
-strictly improve the segmentation.
+Starting with an initial segmentation, auxiliary max-cut problems are approximately solved,
+such that the segmentation is strictly improved.
+As shown by Beier \etal~\cite{beier_2014_cvpr} only CGC~\cite{beier_2014_cvpr} 
+can deal with large scale problems, but can also suffer on very large auxiliary problems.
 
-Bansal and Bagon propose a modified $\alpha-$expansion~\cite{bansal_2004_ml} 
-algorithm suitable for correlation clustering, that allows all variables to 
-change to cluster $\alpha$ in a single move. While the authors claim that this
-scales to large scale data, in~\cite{beier_2014_cvpr} it has been shown that 
-this is not the case in general. This is not surprising because the auxiliary 
-problems can have as many variables as the original problem.
-
-A more efficient move making method has been presented by Beier \etal~\cite{beier_2014_cvpr}.
-Their Cut, Glue and Cut method iteratively re-optimizes the cuts between adjacent clusters of the current solution.
-While this method scales better then  modified $\alpha-$expansion, it still faces three problems:
-Firstly, the subproblems can be as large as the original problem,
-secondly, the subproblems are max-cut problems on non-planar graphs that are NP-hard 
-and even the used approximation has high polynomial complexity.
-This limits the method, to be applicable to huge problems. The same holds for the 
-method of Kernighan and Lin~\cite{Kernighan-1970}.
-
-   % \begin{itemize}
-   % \item Multicut~\cite{kappes_2011_emmcvpr}
-   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
-   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
-   % \item Break and Conquer \cite{alush_2013_simbad}.
-   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
-   % \end{itemize}
+Outside computer vision greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
+The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
+If the node is not assigned it construct a cluster containing the node and all its 
+unassigned positively linked neighbors.  
+%
+A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigned nodes to clusters.
 
@@
 with state of the art any time performance~\cite{kappes_2014_ws}.
-
-Finally, there are heuristic methods such as ...
+Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} can not be applied directly for correlation clustering.
+We will show how to overcome this point later.
 
 \vspace{0.1cm}
-\noindent \textbf{Outline:} {\bf If we are short of space, the following can be ommited:}
+\noindent \textbf{Outline:} 
 In sec.~\ref{sec:problem_formulation} we will give a 
@@
 \input{inputs/fig_notation.tex}
-
-\section{Related Work}\label{sec:related_work}%
-%
-Due to the ambiguity of formulation~\ref{eq:nodeproblem},
-a major branch of research has focused on solving 
-relaxations of eq.~\ref{eq:edgeproblem}.
-To keep the objective and system of inequalities small, they 
-work on sparse graphs and
-use cutting plane methods
-in combination with (integer) linear programming and efficient 
-separation procedures~\cite{kappes_2011_emmcvpr,andres_2011_iccv,kappes_2013_arxiv}.
-
-With no time restrictions and integer constraints these methods can solve the problem to global optimality.
-For huge problems both, separation and solving the ILP in each round, becomes very time consuming.
-
-For planar problems, Yarkony \etal~\cite{yarkony_2012_eccv} 
-suggested a column generating strategy for the outer LP-relaxation
-that includes all cycle-inequalities of problem \ref{eq:edgeproblem}.
-The column generation base on solving planar max cut instances.
-While this method is fast, 
-it only solve a relaxation of the problem and so requires additional rounding strategies,
-lacks of a practical stopping condition for the column generation,
-and most important  is restricted to planar problems.
-
-An other branch of research uses move making algorithm 
-to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
-Starting with an initial segmentation, auxiliary problems are solved that 
-strictly improve the segmentation.
-
-Bansal and Bagon propose a modified $\alpha-$expansion~\cite{bansal_2004_ml} 
-algorithm suitable for correlation clustering, that allows all variables to 
-change to cluster $\alpha$ in a single move. While the authors claim that this
-scales to large scale data, in~\cite{beier_2014_cvpr} it has been shown that 
-this is not the case in general. This is not surprising because the auxiliary 
-problems can have as many variables as the original problem.
-
-A more efficient move making method has been presented by Beier \etal~\cite{beier_2014_cvpr}.
-Their Cut, Glue and Cut method iteratively re-optimizes the cuts between adjacent clusters of the current solution.
-While this method scales better then  modified $\alpha-$expansion, it still faces three problems:
-Firstly, the subproblems can be as large as the original problem,
-secondly, the subproblems are max-cut problems on non-planar graphs that are NP-hard 
-and even the used approximation has high polynomial complexity.
-This limits the method, to be applicable to huge problems. The same holds for the 
-method of Kernighan and Lin~\cite{Kernighan-1970}.
-
-   % \begin{itemize}
-   % \item Multicut~\cite{kappes_2011_emmcvpr}
-   % \item Expand and Explorer~\cite{bagon_2011_arxiv}
-   % \item Fast Planar CC~\cite{yarkony_2012_eccv}
-   % \item Break and Conquer \cite{alush_2013_simbad}.
-   % \item Cut Glue And Cut~\cite{beier_2014_cvpr}
-   % \end{itemize}
-
-For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
-For many large scale computer vision applications fusion moves lead to good approximations
-with state of the art any time performance~\cite{kappes_2014_ws}.
-
-The fusion move algorithm iteratively fuse the current best solution with a proposal solutions
-by optimizing over the subspace spanned by the two labeling. 
-Due to the ambiguity of a node-labeling, fusion moves can not be applied directly for correlation clustering.
-We will show how to overcome this point later.
-
-\input{inputs/fig_hc_alg.tex}
-
-Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
-A common greedy approach~\cite{Soon-2001,Ng-2002,Elsner-2008} is to randomly permute the nodes and than assign 
-iteratively each node to an existing cluster or create a new cluster if costs cannot be decreased by assigning to a cluster.
-%Common assigning strategies are:
-%\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
-%\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
-%\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
-%
-The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
-If the node is not assigned it construct a cluster containing the node and all its 
-unassigned positively linked neighbors.  
-%
-%Typically these algorithms started for many random permutations, 
-%and pick the clustering with best objective value.
-
-A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}.
-Start with an initial clustering one node is removed from a cluster and reassigned to an existing or new cluster such that the costs are minimized.
-BEOM stops if no move can decrease the costs.
-
-% \subsection{Karger-Stein Algorithms}
-% Use randomized procedure to reduce the number of nodes / edges to a reasonable 
-% number.
-% On the smaller graph, more expensive solvers are used.
-
-%\input{inputs/fig_hc_alg.tex}

### 2014-11-11 paper/anytimefigure2.tex
made caption on anytime plot more compact

@@
     %% summary
+    \newline
     Overall, energy hierarchical clustering based proposals work better
@@
     % modularity clustering 
+    \newline
     For the modularity clustering instances in fig.~\ref{fig:at:modularity} we see

### 2014-11-11 paper/egpaper_for_review.tex
made caption on anytime plot more compact
proofs

@@
 \newtheorem{remark}{Remark}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 
@@
 
+\begin{definition}\emph{(Contradicted Graph)}
+Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
+we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
+We define the contradiction of graph $G_y=(V_y,E_y, \bar{w})$
+by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
+$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
+\end{definition}
+
+\begin{definition}\emph{(Back Projection)}
+Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
+We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
+by 
+\begin{align}
+\rho^G_{uv}(\bar{y})=\left\{ 
+\begin{array}{ll}
+\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
+0                & \textrm{ else}
+\end{array}
+\right.
+\end{align}
+\end{definition}
+
+\begin{theorem}[Equivalence]
+The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
+is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
+with additional must link constraints ($y^* \leq y$).
+%
+\begin{proof}
+Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
+Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
+\end{proof}
+%
+\end{theorem}
+
 TODO:
@@
 
-\begin{theorem}[Equivalence]
-The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
-is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
-with additional must link constraints ($y^* \leq y$).
-%
-\begin{proof}
-Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
-Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
-\end{proof}
-%
-\end{theorem}
-
-\begin{theorem}[Monotone]
-Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
-Than $y^*$  will never decrease the energy:
-$y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
-%
-\begin{proof}
-The feasible set of the fusion move includes per definition  $y'$ and $y''$.
-If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
-and that why not the propose segmentation of a fusion.
-\end{proof}
-%
-\end{theorem}
+% \begin{theorem}[Monotone]
+% Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
+% Than $y^*$  will never decrease the energy:
+% $y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
+% %
+% \begin{proof}
+% The feasible set of the fusion move includes per definition  $y'$ and $y''$.
+% If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
+% and that why not the propose segmentation of a fusion.
+% \end{proof}
+% %
+% \end{theorem}
 

### 2014-11-12 paper/egpaper_for_review.tex
update sec 1-4

@@
 \pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
+\usepackage{everypage}
+\AddEverypageHook{%
+  \makeatletter%
+  \special{pdf: put @thispage <</Group << /S /Transparency /I true /CS /DeviceRGB>> >>}%
+  \makeatother%
+}%
 
@@
 In each step, the edge with the highest weight $w$ is
-contracted (red edges in Fig.~\ref{fig:hc_alg}).
+contracted (green edges in Fig.~\ref{fig:hc_alg}).
 Doing so, parallel edges edges can occur.
@@
 While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
-agglomeration with respect to our energy function.
+agglomeration with respect to our energy function~\ref{eq:edgeproblem}.
 For this we propose to use energy based agglomeration
-withe the following update rule:
+with the following update rule:
 Whenever there are multiple edges between 
@@
 We stop EHC if the highest edge weight is
-smaller or equal to zero  (green edge in Fig.~\ref{fig:hc_alg}). Any further edge
+smaller or equal to zero  (blue edge in Fig.~\ref{fig:hc_alg}). Any further edge
 contraction leads to worse energies.
@@
 and the fact that EHC does only local decisions, it is 
-sensitive against salt and paper noise 
-and we do not expect very good solutions.
+sensitive against noise and we cannot expect optimal solutions.
 
@@
 objective functions as Eq.~\ref{eq:nodeproblem} since
-the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
+the node coloring is ambiguous and has no semantic meaning, \cf Fig.~\ref{fig:fusion_abiguty}.
 In the following, we propose a more suitable fusion move for correlation
@@
 \begin{align}
-\breve{y}    & =  y' \cup y'' \\
-\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
+\breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
+\mathcal{E}_0  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
 \end{align}
@@
 The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
+with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0$.
 %
 \begin{align}
-  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
+  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
+      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0 \nonumber
 \end{align}
 %
-By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
-\begin{align}
-  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
-\end{align}
+By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
+because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
+%\begin{align}
+%  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
+%\end{align}
 %
@@
 We iteratively improve the best solution by
-fusing it with proposal solutions.
+fusing it with proposal solution.
 The inherent difference is how we define the fusion.
@@
       \toprule
-         Dataset          &  image-seg   & knott-3d-150&knott-3d-300&knott-3d-450 &knott-3d-550 &3d-seg\\
+         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
       \midrule 
-         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &\\ 
-         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ \\
-         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ \\
-         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$\\
-         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$\\
-         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$\\
-         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$\\   
-         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ \\  
-         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$\\  
-         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ \\  
-         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$\\  
-         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ \\      
+         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &              &              &  --\\ 
+         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &              & $       2.8395$\\
+         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &              & $       1.7603$ \\
+         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &              & $       6.8908$ \\
+         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &              & $       7.1057$\\
+         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &              & $       6.5366$ \\
+         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &              & $       6.5058$\\   
+         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &              & $       4.3319$\\  
+         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &              & $\bf    1.3347$ \\  
+         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &              & $       2.1347$ \\  
+         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &              & $\bf    1.3334$ \\  
+         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &              & $       3.3514$ \\      
       \bottomrule
@@
 by a fusion with proposal solutions.
-The itself is formulated as correlation
+The fusion move itself is formulated as correlation
 clustering on a smaller graph fewer edges and nodes

### 2014-11-12 paper/introduction-new.tex
update sec 1-4

@@
 \noindent \textbf{Outline:} 
-In sec.~\ref{sec:problem_formulation} we will give a 
+In Sec.~\ref{sec:problem_formulation} we will give a 
 detailed problem definition where we introduce 
 the correlation clustering objective.
-In sec.~\ref{sec:related_work} we will 
-discuss existing methods for correlation 
-clustering and briefly explain the concept of fusion moves.
-In sec: ~\ref{sec:cc_fm} we describe our proposed
+In Sec.~\ref{sec:cc_fm} we describe our proposed
 method and show the properties of the algorithm.
-In sec.~\ref{sec:exp} we show an evaluation
-of the method on existing parameter  and discuss the effects of parameters.
-Future work will be discussed in sec. \ref{sec:future} and
-we will conclude in ~\ref{sec:conclusion}.
+In Sec.~\ref{sec:exp} we show an evaluation
+of the proposed methods methods and state of the art
+and conclude in Sec.~\ref{sec:future} and\ref{sec:conclusion}.
 %-------------------------------------------------------------------------
@@
 The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
+We will use $w_e$ as a shorthand for $w(e)$.
 A positive weight expresses the desire that two adjacent nodes should
@@
 node labeling $l \in \mathbb{N}^{|V|}$
-or an edge labeling $y \in\{0,1\}^{|E|}$.  
+or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation} .
 An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.
@@
 As shown in~\cite{kappes_2013_arxiv}  both problems are equivalent, but formulation \ref{eq:nodeproblem}
-suffers from ambiguities in the formulation~\cite{kappes_2011_emmcvpr}.
+suffers from ambiguities in the formulation, \cf Fig.~\ref{fig:notation}.
 

### 2014-11-12 paper/egpaper_for_review.tex
readded my old proposal tex  which has been removed somehow =)

@@
 %
-To generate proposals cut we can use bottom up hierarchical clustering.
-In each step we contract the edge with the highest weight.
-Parallel edges are merged into single edges by summing their weights.
-We stop when a certain number of nodes is reached, or the
-largest edge weight among the not yet contracted edges is smaller then a certain threshold.
-To get versatile proposals we either add noise 
-to the edge weighs or permute a certain number of weights.
+To generate fast energy aware proposals we can use energy
+based hierarchical clustering (EHC) as defined in sec.~\ref{sec:ehc}.
+EHC follows the energy function, therefore the \emph{quality}
+of the proposals is high.
+To get \emph{diversity} among the different proposal,
+we add normal distributed noise with a standard deviation of $\sigma_{ehc}$
+to each edge weight.
+To get proposals of the desired \emph{size}, we can use a
+different stop condition in EHC, and stop when a certain number of connected
+components is reached.
 
@@
 with random seeds can be used to get
-cheap proposals. Instead of $n$ seeds distributed uniformly
-over all nodes we use the following.
+cheap proposals.
+To improve \emph{quality} we do not use $n$ seeds distributed uniformly
+over all nodes but use the following.
 Draw $n/k$ random edges only the negative edges,
-and give the two nodes of each random edge different seeds.
+and give the two nodes of each ``seed-edge'' a different seed.
 Doing so, a random subset of negative edges is forced
 to be cut within each proposal.
-For additional randomness, noise can be added to
+For additional \emph{diversity} randomness, noise can be added to
 the edge weighs.

### 2014-11-12 paper/egpaper_for_review.tex
sec 4

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 %------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
+\section{Correlation-Clustering-Fusion}\label{sec:cc_fm}
 
-Fusion moves as defined in \cite{Lempitsky-2010} work
-in the node domain and do not work properly for 
-objective functions as Eq.~\ref{eq:nodeproblem} since
-the node coloring is ambiguous and has no semantic meaning, \cf Fig.~\ref{fig:fusion_abiguty}.
+Fusion move algorithms~\cite{Lempitsky-2010} are a popular technique 
+for large scale discrete energy minimization problems.
+They iteratively fuse two node labelings by optimizing over the label space spanned by those.
+Different fusion algorithms vary in the proposals and method used for the auxiliary fusion problem~\cite{kappes_2014_ws}.
+
+As fusion algorithms work with node labelings, % \cf Eq.~\ref{eq:nodeproblem},
+we face the problem that the node coloring is ambiguous and has no semantic meaning.
+This causes that a fusion move is not well defined, because different choices of colors 
+lead to different auxiliary problems, as shown in Fig.~\ref{fig:fusion_abiguty}.
+
 In the following, we propose a more suitable fusion move for correlation
@@
 Given two proposal solutions $y'$ and $y''$,
-$\mathcal{C}$ is the set of edges
+$\mathcal{E}^0_{\breve{y}}$ is the set of edges
 which are uncut in $y'$ and $y''$.
@@
 \breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
-\mathcal{E}_0  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
+\mathcal{E}^0_{\breve{y}}  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
 \end{align}
@@
 The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0$.
+with additional \emph{must-link constraints} for all edges in $\mathcal{E}^0_{\breve{y}}$.
 %
@@
   y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0 \nonumber
+      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}^0_{\breve{y}} \nonumber
 \end{align}

### 2014-11-12 paper/egpaper_for_review.tex
work on sec 4

@@
 clustering which works on the edge domain.
+It allows to change all edge labelings, which are active in at least one of the two labelings.
 %
@@
 By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
-because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
+because $y'$ and $y''$ are feasible solutions.
 %\begin{align}
@@
 
-Once we know how to fuse segmentations, the actual algorithm 
-for correlation clustering 
-is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
-We iteratively improve the best solution by
+The  correlation clustering fusion algorithm (CCFusion) iteratively improve the best solution by
 fusing it with proposal solution.
-The inherent difference is how we define the fusion.
+The inherent difference to classical fusion~\cite{Lempitsky-2010} is how we define the fusion.
 We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
-%
-How to optimize  Eq.~\ref{eq:fusion_move_a} in an more efficient way is
-described in the following section.
+
+A further difference is how we efferently calculate the correlation clustering fusion move and how we generate proposals.
+Both will be discussed next.
 
@@
 
-\subsection{Fast Optimization} \label{sec:fast_optimization}
+\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
 

### 2014-11-12 paper/egpaper_for_review.tex
removed some links and improved proposal generation

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 %------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion}\label{sec:cc_fm}
+\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
 
-Fusion move algorithms~\cite{Lempitsky-2010} are a popular technique 
-for large scale discrete energy minimization problems.
-They iteratively fuse two node labelings by optimizing over the label space spanned by those.
-Different fusion algorithms vary in the proposals and method used for the auxiliary fusion problem~\cite{kappes_2014_ws}.
-
-As fusion algorithms work with node labelings, % \cf Eq.~\ref{eq:nodeproblem},
-we face the problem that the node coloring is ambiguous and has no semantic meaning.
-This causes that a fusion move is not well defined, because different choices of colors 
-lead to different auxiliary problems, as shown in Fig.~\ref{fig:fusion_abiguty}.
-
+Fusion moves as defined in \cite{Lempitsky-2010} work
+in the node domain and do not work properly for 
+objective functions as Eq.~\ref{eq:nodeproblem} since
+the node coloring is ambiguous and has no semantic meaning, \cf Fig.~\ref{fig:fusion_abiguty}.
 In the following, we propose a more suitable fusion move for correlation
@@
 Given two proposal solutions $y'$ and $y''$,
-$\mathcal{E}^0_{\breve{y}}$ is the set of edges
+$\mathcal{C}$ is the set of edges
 which are uncut in $y'$ and $y''$.
@@
 \breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
-\mathcal{E}^0_{\breve{y}}  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
+\mathcal{E}_0  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
 \end{align}
@@
 The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{E}^0_{\breve{y}}$.
+with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0$.
 %
@@
   y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}^0_{\breve{y}} \nonumber
+      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0 \nonumber
 \end{align}
@@
 To get \emph{diversity} among the different proposal,
-we add normal distributed noise with a standard deviation of $\sigma_{ehc}$
+we add normal distributed noise  $\mathcal{N}(0, \sigma_{ehc})$
 to each edge weight.
-To get proposals of the desired \emph{size}, we can use a
-different stop condition in EHC, and stop when a certain number of connected
+To get proposals of the desired \emph{size}, we use a
+different stop condition in EHC, and stop iff a certain number of connected
 components is reached.
@@
 %\subsubsection{Randomized Watersheds (RWS)}
+Watersheds have become quite popular for
+graph segmentation and have a strong connection
+to energy minimization~\cite{couprie_2011}.
 %
-The edge weighted watershed algorithm \cite{meyer_2013}
+The edge weighted watershed algorithm~\cite{meyer_2013}
 with random seeds can be used to get
@@
 over all nodes but use the following.
-Draw $n/k$ random edges only the negative edges,
-and give the two nodes of each ``seed-edge'' a different seed.
+%
+Draw $n/k$ negative edges,  and give the endpoints a different seed.
 Doing so, a random subset of negative edges is forced
 to be cut within each proposal.
-For additional \emph{diversity} randomness, noise can be added to
-the edge weighs.
+For additional \emph{diversity}, noise $\mathcal{N} (0, sigma_{ws})$
+can be added to the edge weighs.
 
@@
 
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
+For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}
+\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
+}
 of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.

### 2014-11-12 paper/egpaper_for_review.tex
removed some links and improved proposal generation
woring oon proof

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 A further difference is how we efferently calculate the correlation clustering fusion move and how we generate proposals.
-Both will be discussed next.
+Both will be discussed next. The overall framework is sketched in Fig.~\ref{fig:move_graph}.
 
@@
 \subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
-
-Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
-we can work on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges
-(see Fig.~\ref{fig:move_graph}).
-
-\begin{definition}\emph{(Contradicted Graph)}
+In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is still NP-hard.
+However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
+into a correlation clustering problem on a coarser graph, where all nodes which are connected
+via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
+%
+\begin{definition}\emph{(Contracted Graph)}
 Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
 we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
-We define the contradiction of graph $G_y=(V_y,E_y, \bar{w})$
+We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
 by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
@@
 \end{definition}
-
-\begin{definition}\emph{(Back Projection)}
-Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
-We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
-by 
+%
+Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $y$ the original graph $G=(V,E)$ by
+%
 \begin{align}
-\rho^G_{uv}(\bar{y})=\left\{ 
+y_{uv}&=\left\{ 
 \begin{array}{ll}
@@
 \end{array}
-\right.
+\right.& \forall uv \in E
 \end{align}
-\end{definition}
+Furthermore, the back projection of the optimal segmentation $\bar{y}$ of the contracted graph is a solution of problem~\ref{eq:fusion_move_a}.
+
+% Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
+% we can work on a coarser graph, where all nodes which are connected
+% via must-link constraints are merged into single nodes.
+% This coarser graph is constructed by contracting all must-link edges
+% (see Fig.~\ref{fig:move_graph}).
+
+% \begin{definition}\emph{(Back Projection)}
+% Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
+% We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
+% by 
+% \begin{align}
+% \rho^G_{uv}(\bar{y})=\left\{ 
+% \begin{array}{ll}
+% \bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
+% 0                & \textrm{ else}
+% \end{array}
+% \right.
+% \end{align}
+% \end{definition}
 
 \begin{theorem}[Equivalence]
-The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
-is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
-with additional must link constraints ($y^* \leq y$).
-%
+The back projection of the optimal segmentation $\bar{y}^*$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
+is an optimal solution of problem~\ref{eq:fusion_move_a}.
 \begin{proof}
-Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
+Let $y'$ be the back propagation of $\bar{y}^*$, which is by definition a feasible solution of~\ref{eq:fusion_move_a}.
+If
+
+Since $\bar{y}^*$ fulfills all-must link constraints of~\ref{eq:fusion_move_a} it is a feasible solution.
+Let
+
+, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
 Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.

### 2014-11-12 paper/egpaper_for_review.tex

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 \breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
-\mathcal{E}_0  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
+\mathcal{E}_0^{\breve{y}}  & =  \{ ij \in E \; | \; \breve{y}_{ij} = 0 \}
 \end{align}
@@
 The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0$.
+with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0^{\breve{y}}$.
 %
@@
   y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0 \nonumber
+      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0^{\breve{y}} \nonumber
 \end{align}
@@
 We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
-%
-How to optimize  Eq.~\ref{eq:fusion_move_a} in an more efficient way is
-described in the following section.
+
+A further difference is how we efferently calculate the correlation clustering fusion move and how we generate proposals.
+Both will be discussed next. The overall framework is sketched in Fig.~\ref{fig:move_graph}.
 
@@
 
-\subsection{Fast Optimization} \label{sec:fast_optimization}
-
-Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
-we can work on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes.
-This coarser graph is constructed by contracting all must-link edges
-(see Fig.~\ref{fig:move_graph}).
-
-\begin{definition}\emph{(Contradicted Graph)}
+\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
+In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is still NP-hard.
+However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
+into a correlation clustering problem on a coarser graph, where all nodes which are connected
+via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
+%
+\begin{definition}\emph{(Contracted Graph)}
 Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
 we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
-We define the contradiction of graph $G_y=(V_y,E_y, \bar{w})$
+We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
 by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
@@
 \end{array}
-\right.
+\right.& \forall uv \in E
 \end{align}
-\end{definition}
+Furthermore, the back projection of the optimal segmentation $\bar{y}$ of the contracted graph is a solution of problem~\ref{eq:fusion_move_a}.
+
+% Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
+% we can work on a coarser graph, where all nodes which are connected
+% via must-link constraints are merged into single nodes.
+% This coarser graph is constructed by contracting all must-link edges
+% (see Fig.~\ref{fig:move_graph}).
+
+% \begin{definition}\emph{(Back Projection)}
+% Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
+% We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
+% by 
+% \begin{align}
+% \rho^G_{uv}(\bar{y})=\left\{ 
+% \begin{array}{ll}
+% \bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
+% 0                & \textrm{ else}
+% \end{array}
+% \right.
+% \end{align}
+% \end{definition}
 
 \begin{theorem}[Equivalence]
-The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
-is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
-with additional must link constraints ($y^* \leq y$).
-%
+The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
+is an optimal solution of problem~\ref{eq:fusion_move_a}.
 \begin{proof}
-Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
-Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
+Let $y'$ be the back propagation of $\bar{y}'$, which is by definition a feasible for~\ref{eq:fusion_move_a}.
+If $y'$ would not be an optimal solution than there must exists $y''$ with 
+$\sum_{e\in E} w_ey_e'' > \sum_{e\in E} w_ey_e''$.
+Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
+\begin{align*}
+  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
+ &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
+  = \sum_{e\in E} w_ey_e'' \\
+ &> \sum_{e\in E} w_ey_e''
+  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
+  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
+\end{align*}
+where $\bar{y}''$ is the projection from $y''$ on $G_y$.
+This contradicts that $y'$ is a optimal segmentation of $G_y$.
 \end{proof}
@@
 
-TODO:
-Here we need to proof that it is equivalent 
-to optimize the contracted graph !
+Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
+This is, depending on the intersection of the current and proposed solution, magnitudes smaller than $G$.
+The correlation clustering problem on $G_{\breve{y}}$ can be solved by any correlation clustering solver.
+Since $G_{\breve{y}}$ is smaller exact methods or good approximative methods like 
+multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
+become tractable.
 
-\input{inputs/fig_contraction.tex}
-\input{inputs/fig_projection.tex}
+%\input{inputs/fig_contraction.tex}
+%\input{inputs/fig_projection.tex}
 
@@
 For additional \emph{diversity}, noise $\mathcal{N} (0, sigma_{ws})$
-can be added to the edge weighs.
+can be added to
+the edge weighs.
 

### 2014-11-12 paper/egpaper_for_review.tex
reloacte section polyhedral representation

@@
 
-Fusion moves as defined in \cite{Lempitsky-2010} work
+Fusion moves as defined in~\cite{Lempitsky-2010} work
 in the node domain and do not work properly for 
@@
 for correlation clustering 
-is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
+is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{Lempitsky-2010}.
 We iteratively improve the best solution by
@@
 
-\begin{theorem}[Equivalence]
+\begin{theorem}[Equivalence]\label{thm:Equivalence}
 The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
@@
 %-------------------------------------------------------------------------
-%\subsection{Fusion Move Solver}
+\subsection{Polyhedral Interpretation}
+A polyheadral interpretation of fusion moves is shown in Fig.~\ref{fig:polyheadral}.
+In each iteration the current and proposed segmentation define an inner polyheadral 
+approximation of the original polytope. This interpretation holds for original 
+fusion moves~\cite{Lempitsky-2010} as well as for the proposed CCFusion.
+
+In our case, optimizing over the inner polytope is the same kind of problem as the original multicut polytope, but much smaller.
+Furthermore, the costs does not change and and improvement in the smaller polytope will 
+be the same in the original graph, as shown in Theorem~\ref{thm:Equivalence}.
+
+The choice of the proposal defines the shape of the auxiliary polytope. 
+In the given toy example, the first (red) polytope give a huge improvement, the second proposal
+defines the blue polytope which does not lead to an improvement. 
+The third proposal generates the green polytope that includes the global optimal solution.
+
+This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
+which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
+
+\begin{figure}
+\centering
+\input{polytope-tikz.tex}
+\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
+Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
+and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
+When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
+}
+\label{fig:polyheadral}
+\end{figure}
+
+% \begin{theorem}[Monotone]
+% Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
+% Than $y^*$  will never decrease the energy:
+% $y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
+% %
+% \begin{proof}
+% The feasible set of the fusion move includes per definition  $y'$ and $y''$.
+% If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
+% and that why not the propose segmentation of a fusion.
+% \end{proof}
+% %
+% \end{theorem}
+
+%\begin{remark}[Fix-point (pointless to me)]
+%Let $Y$ be the set of possible proposals, than
+%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
+%\end{remark}
+
+% \begin{remark}[Optimality]
+% Let $y'$ be the current and $y''$ the proposed segmentation.
+% If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
+% \end{remark}
 
@@
 and \emph{diversity}.
-The quality / energy of the individual proposals
+%
+The quality of the individual proposals
 ensures low energy solutions since the
@@
 the energy of the current best solution.
+%
 Diversity between the individual proposals
-reduces the chances to get stuck in local minima.
+increase the chances to escape from local minima.
+%
 For correlation clustering fusion we add a third
@@
 
-\subsection{Properties and Polyhedral Interpretation}
-An alternative interpretation of our method is shown in Fig.~\ref{fig:polyheadral}.
-In each iteration the current and proposed segmentation define an inner polyheadral 
-approximation of the original multicut polytope. 
-Optimizing over this polytope is the same problem as the original one, but much smaller.
-Furthermore, the costs does not change and and improvement in the smaller polytope will 
-be the same in the original graph.
-The choice of the proposal defines the shape of the auxiliary polytope. 
-In the given toy example, the first (red) polytope give a huge improvement, the second proposal
-defines the blue polytope which does not lead to an improvement. 
-The third proposal generates the green polytope that includes the global optimal solution.
+%-----------------------------------------------------------------------
+\subsection{Limitations}
 
-This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
-which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
-
-\begin{figure}
-\centering
-\input{polytope-tikz.tex}
-\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
-Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
-and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
-When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
-}
-\label{fig:polyheadral}
-\end{figure}
-
-% \begin{theorem}[Monotone]
-% Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
-% Than $y^*$  will never decrease the energy:
-% $y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
-% %
-% \begin{proof}
-% The feasible set of the fusion move includes per definition  $y'$ and $y''$.
-% If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
-% and that why not the propose segmentation of a fusion.
-% \end{proof}
-% %
-% \end{theorem}
-
-%\begin{remark}[Fix-point (pointless to me)]
-%Let $Y$ be the set of possible proposals, than
-%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
-%\end{remark}
-
-\begin{remark}[Optimality]
-Let $y'$ be the current and $y''$ the proposed segmentation.
-If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
-\end{remark}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2014-11-12 paper/egpaper_for_review.tex
fixed some typos

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 
-While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
+While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interested in an 
 agglomeration with respect to our energy function~\ref{eq:edgeproblem}.

### 2014-11-12 paper/egpaper_for_review.tex
fixed some typos

@@
 a pair of nodes, these edges are merged into a single edge
-by summing up their weights, since we 
+and the weights are summed up, since we 
 minimize the sum of the cut edges.

### 2014-11-12 paper/egpaper_for_review.tex
work on orposal gen

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 
-While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interested in an 
+While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
 agglomeration with respect to our energy function~\ref{eq:edgeproblem}.
@@
 
-As discussed in \cite{Lempitsky-2010}, proposals
+As discussed in~\cite{Lempitsky-2010}, proposals
 should have two properties: \emph{quality} 
@@
 %
+A proposal have a high quality if it at least loacly
 The quality of the individual proposals

### 2014-11-12 paper/egpaper_for_review.tex
fixed some typos

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 Given two proposal solutions $y'$ and $y''$,
-$\mathcal{C}$ is the set of edges
+$\mathcal{E}_0^{\breve{y}}$ is the set of edges
 which are uncut in $y'$ and $y''$.
@@
 
-A further difference is how we efferently calculate the correlation clustering fusion move and how we generate proposals.
+A further difference is how we efficiently calculate the correlation clustering fusion move and how we generate proposals.
 Both will be discussed next. The overall framework is sketched in Fig.~\ref{fig:move_graph}.

### 2014-11-12 paper/introduction-new.tex

@@
 is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012},
-see Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph..
+see Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.
 
@@
 \noindent \textbf{Contribution.}
-In the present work we present some novel approaches that are designed for large scale correlation clustering problems.
+In this work we present some novel approaches that are designed for large scale correlation clustering problems.
 First, we define a novel energy based agglomerative clustering algorithm that monotonically increase the energy.
@@
 We propose two versatile proposal generators, and evaluate the proposed methods on existing and new benchmark problems.
-That experiments show that we can improve the computation time by one to two magnitudes without worsening the segmentation 
+Experiments show that we can improve the computation time by one to two magnitudes without worsening the segmentation 
 quality significantly.
@@
 Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation~\cite{kappes_2013_arxiv}. 
-Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
-For the latter approach column generating methods exits, that works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.
+Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
+For the latter approach column generating methods exits, that works best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
 
@@
 Outside computer vision greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
-The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
-If the node is not assigned it construct a cluster containing the node and all its 
+The PIVOT Algorithm~\cite{Ailon-2008} iterates over all nodes in random order.
+If the node is not assigned it constructs a cluster containing the node and all its 
 unassigned positively linked neighbors.  
 %
-A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigned nodes to clusters.
+A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigns nodes to clusters.
 

### 2014-11-12 paper/egpaper_for_review.tex
fixed missing bracket in fast opt.

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 \begin{definition}\emph{(Contracted Graph)}
-Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
+Given a weighted graph $G=(V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
 we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.

### 2014-11-12 paper/egpaper_for_review.tex
exp

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 
+As classical fusion, CCFusion does not provide and lower bound on the objective and 
+has no sound stopping condition.
+For later we set a maximal number of iterations and maximal number of iteration without improvement.
+
 \input{inputs/fig_fusion.tex}
@@
 \subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
-In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is still NP-hard.
+In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, still NP-hard.
 However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
@@
 and \emph{diversity}.
-%
-A proposal have a high quality if it at least loacly
-The quality of the individual proposals
-ensures low energy solutions since the
-result of the fusion cannot be higher then
-the energy of the current best solution.
-%
-Diversity between the individual proposals
-increase the chances to escape from local minima.
-%
+
+A proposal have a high quality if it at least in some regions have a low energy.
+For high quality proposals the chance that the inner polytope includes 
+better solution (vertex) is larger than for those with low quality.
+
+Diversity between the individual proposals increase the chances
+to span diverse internal polytopes, cover with the intersection of
+inner polytopes a large part of the original polytope and so  
+more likely find the global optimal solution or escape from local minima.
+
 For correlation clustering fusion we add a third
 property: \emph{size}.
-The size of the contraction graph directly
+The size of the contracted graph directly
 depends on the number of connected components
-in the proposal solution and the current best solution.
-The extreme  case is a proposal where each 
-node is in a separate connnected component.
-Solving the fusion move with such a proposal
-is equivalent to solving the original problem.
-Solving the fusion move with a proposal with 
-a single connected component will result 
-in the current best solution.
+of the intersection of the proposal solution and the current best solution.
+%
+In the extreme case, where each 
+node is in a separate connnected component,
+the fusion move is equivalent to solving the original problem.
+In the other extreme, where the proposal has 
+a single connected component, the current best solution will not change.
+% 
 Therefore the size of the proposals
 should be small enough, such that solving
-eq.~\ref{eq:edgeproblem} can
-be done fast enough, but large enough to make
-meaningful moves (??? this last sentence needs to be rewritten).
+eq.~\ref{eq:fusion_move_a} can
+be done fast enough, but  on the other side 
+large enough to define a large internal polytope and so a powerful move.
+%
+To this end we suggest two proposal generators.
 
@@
 To generate fast energy aware proposals we can use energy
-based hierarchical clustering (EHC) as defined in sec.~\ref{sec:ehc}.
+based hierarchical clustering (EHC) as defined in Sec.~\ref{sec:ehc}.
 EHC follows the energy function, therefore the \emph{quality}
@@
 To get proposals of the desired \emph{size}, we use a
-different stop condition in EHC, and stop iff a certain number of connected
+different stop condition as in EHC, and stop iff a certain number of connected
 components is reached.
@@
 %
-Draw $n/k$ negative edges,  and give the endpoints a different seed.
+We draw $n/2$ negative edges, and assign to the endpoints a different seed.
 Doing so, a random subset of negative edges is forced
@@
 For additional \emph{diversity}, noise $\mathcal{N} (0, sigma_{ws})$
-can be added to
-the edge weighs.
+can be added to the edge weighs.
 
 %\input{inputs/fig_hc.tex}
-
-%-----------------------------------------------------------------------
-\subsection{Limitations}
 
@@
 
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}
-\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
-}
+For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}}
 of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
-For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
-Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-This procedure is one magnitude faster, but might cause a few extra outer iterations.
-In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
+For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
+ the public available implementation in OpenGM\footref{opengm-master} of Kappes~\etal, as described in Sec.~\ref{sec:tunedMC}.
+%
+%We realize that their implementation has some limitations on large problems and make the following modifications.
+%Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
+%Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+%during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
+%This procedure is one magnitude faster, but might cause a few extra outer iterations.
+%In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
+%For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
+%
 From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
@@
  and MC-I and CGC as subproblem solvers denoted by 
-\textbf{fusionCC-HC-MC},
+\textbf{CCFusion-HC-MC},
 \textbf{-HC-CGC},
@@
 
+All experiments were run on Intel Core i5-4570 CPUs
+with 3.20 GHz, equipped with 32 GB of RAM.
+In our evaluation we make not use of multiple threads.
+The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
+
+\subsection{Tuned Multicut Algorithm}\label{sec:tunedMC} 
  \begin{figure}[t]
@@
   \end{figure}
-
-All experiments were run on Intel Core i5-4570 CPUs
-with 3.20 GHz, equipped with 32 GB of RAM.
-In our evaluation we make not use of multiple threads.
-The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
+When using the  public available implementation in OpenGM\footref{opengm-master}
+of Kappes~\etal~\cite{kappes_2013_arxiv}, we realize that their implementation has some limitations on large problems.
+This results in a very slow separation and make the following modifications.
+Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
+Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
+This procedure is one magnitude faster, but might cause a few extra outer iterations.
+In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
+For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
 

### 2014-11-12 paper/egpaper_for_review.tex
later
fix typos

@@
 Given the intrinsic greediness of hierarchical clustering, 
-and the fact that EHC does only local decisions, it is 
-sensitive against noise and we cannot expect optimal solutions.
+EHC is sensitive against noise and we cannot expect optimal solutions.
 
@@
 has no sound stopping condition.
-For later we set a maximal number of iterations and maximal number of iteration without improvement.
+For latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.
 
@@
 If $y'$ would not be an optimal solution than there must exists $y''$ with 
-$\sum_{e\in E} w_ey_e'' > \sum_{e\in E} w_ey_e''$.
+$\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
 Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
@@
  &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
-  = \sum_{e\in E} w_ey_e'' \\
+  = \sum_{e\in E} w_ey_e' \\
  &> \sum_{e\in E} w_ey_e''
@@
 
-Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
+Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~\ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
 This is, depending on the intersection of the current and proposed solution, magnitudes smaller than $G$.

### 2014-11-12 paper/egpaper_for_review.tex
section title change
remove https

@@
 to be cut within each proposal.
-For additional \emph{diversity}, noise $\mathcal{N} (0, sigma_{ws})$
+For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
 can be added to the edge weighs.
@@
 
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}}
-of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
+For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
+of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
 For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
@@
 
-\subsection{Tuned Multicut Algorithm}\label{sec:tunedMC} 
+\subsection{Improvements for the Multicut Algorithm}\label{sec:tunedMC} 
  \begin{figure}[t]

### 2014-11-12 paper/egpaper_for_review.tex
fixed missing bracket in fast opt.

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 
-As classical fusion, CCFusion does not provide and lower bound on the objective and 
-has no sound stopping condition.
-For later we set a maximal number of iterations and maximal number of iteration without improvement.
-
 \input{inputs/fig_fusion.tex}
@@
 \subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
-In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, still NP-hard.
+In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is still NP-hard.
 However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
@@
 If $y'$ would not be an optimal solution than there must exists $y''$ with 
-$\sum_{e\in E} w_ey_e'' > \sum_{e\in E} w_ey_e''$.
+$\sum_{e\in E} w_ey_e'' < \sum_{e\in E} w_ey_e'$.
 Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
@@
 
-As discussed in~\cite{Lempitsky-2010}, proposals
+As discussed in \cite{Lempitsky-2010}, proposals
 should have two properties: \emph{quality} 
 and \emph{diversity}.
-
-A proposal have a high quality if it at least in some regions have a low energy.
-For high quality proposals the chance that the inner polytope includes 
-better solution (vertex) is larger than for those with low quality.
-
-Diversity between the individual proposals increase the chances
-to span diverse internal polytopes, cover with the intersection of
-inner polytopes a large part of the original polytope and so  
-more likely find the global optimal solution or escape from local minima.
-
+%
+The quality of the individual proposals
+ensures low energy solutions since the
+result of the fusion cannot be higher then
+the energy of the current best solution.
+%
+Diversity between the individual proposals
+increase the chances to escape from local minima.
+%
 For correlation clustering fusion we add a third
 property: \emph{size}.
-The size of the contracted graph directly
+The size of the contraction graph directly
 depends on the number of connected components
-of the intersection of the proposal solution and the current best solution.
-%
-In the extreme case, where each 
-node is in a separate connnected component,
-the fusion move is equivalent to solving the original problem.
-In the other extreme, where the proposal has 
-a single connected component, the current best solution will not change.
-% 
+in the proposal solution and the current best solution.
+The extreme  case is a proposal where each 
+node is in a separate connnected component.
+Solving the fusion move with such a proposal
+is equivalent to solving the original problem.
+Solving the fusion move with a proposal with 
+a single connected component will result 
+in the current best solution.
 Therefore the size of the proposals
 should be small enough, such that solving
-eq.~\ref{eq:fusion_move_a} can
-be done fast enough, but  on the other side 
-large enough to define a large internal polytope and so a powerful move.
-%
-To this end we suggest two proposal generators.
+eq.~\ref{eq:edgeproblem} can
+be done fast enough, but large enough to make
+meaningful moves (??? this last sentence needs to be rewritten).
 
@@
 To generate fast energy aware proposals we can use energy
-based hierarchical clustering (EHC) as defined in Sec.~\ref{sec:ehc}.
+based hierarchical clustering (EHC) as defined in sec.~\ref{sec:ehc}.
 EHC follows the energy function, therefore the \emph{quality}
@@
 To get proposals of the desired \emph{size}, we use a
-different stop condition as in EHC, and stop iff a certain number of connected
+different stop condition in EHC, and stop iff a certain number of connected
 components is reached.
@@
 %
-We draw $n/2$ negative edges, and assign to the endpoints a different seed.
+Draw $n/k$ negative edges,  and give the endpoints a different seed.
 Doing so, a random subset of negative edges is forced
@@
 For additional \emph{diversity}, noise $\mathcal{N} (0, sigma_{ws})$
-can be added to the edge weighs.
+can be added to
+the edge weighs.
 
 %\input{inputs/fig_hc.tex}
+
+%-----------------------------------------------------------------------
+\subsection{Limitations}
 
@@
 
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}}
+For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}
+\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
+}
 of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
-For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
- the public available implementation in OpenGM\footref{opengm-master} of Kappes~\etal, as described in Sec.~\ref{sec:tunedMC}.
-%
-%We realize that their implementation has some limitations on large problems and make the following modifications.
-%Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-%Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-%during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-%This procedure is one magnitude faster, but might cause a few extra outer iterations.
-%In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-%For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
-%
+For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
+of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
+Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
+Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
+This procedure is one magnitude faster, but might cause a few extra outer iterations.
+In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
+For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
 From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
@@
  and MC-I and CGC as subproblem solvers denoted by 
-\textbf{CCFusion-HC-MC},
+\textbf{fusionCC-HC-MC},
 \textbf{-HC-CGC},
@@
 
-All experiments were run on Intel Core i5-4570 CPUs
-with 3.20 GHz, equipped with 32 GB of RAM.
-In our evaluation we make not use of multiple threads.
-The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
-
-\subsection{Tuned Multicut Algorithm}\label{sec:tunedMC} 
  \begin{figure}[t]
@@
   \end{figure}
-When using the  public available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal~\cite{kappes_2013_arxiv}, we realize that their implementation has some limitations on large problems.
-This results in a very slow separation and make the following modifications.
-Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-This procedure is one magnitude faster, but might cause a few extra outer iterations.
-In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
+
+All experiments were run on Intel Core i5-4570 CPUs
+with 3.20 GHz, equipped with 32 GB of RAM.
+In our evaluation we make not use of multiple threads.
+The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
 

### 2014-11-12 paper/introduction-new.tex

@@
 
-Another line of work uses move making algorithm 
+Another line of work uses move making algorithms 
 to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
@@
 of the proposed methods methods and state of the art
-and conclude in Sec.~\ref{sec:future} and\ref{sec:conclusion}.
+and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
 %-------------------------------------------------------------------------
@@
 node labeling $l \in \mathbb{N}^{|V|}$
-or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation} .
+or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation}.
 An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.

### 2014-11-12 paper/egpaper_for_review.tex
fixed missing bracket in fast opt.

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 be done fast enough, but  on the other side 
-large enough to define a large internal polytope and so a powerful move.
+large enough to define a large internal polytope and therefore a powerful move.
 %
@@
 %
-We draw $n/2$ negative edges, and assign to the endpoints a different seed.
+We draw $n/2$ negative edges, and assign different seed to the endpoints
+of each edge.
 Doing so, a random subset of negative edges is forced
@@
 For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
-can be added to the edge weighs.
+is added to the edge weighs.
 
@@
 For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
-of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
+of Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
 For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of

### 2014-11-12 paper/egpaper_for_review.tex
fixed typo in param choise

@@
 The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
-Fig.~\ref{fig:parameterchoice} shows a evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
+Fig.~\ref{fig:parameterchoice} shows an evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
 The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.

### 2014-11-12 paper/egpaper_for_review.tex
work on exp sec

--- 2014-11-12 paper/egpaper_for_review.tex
@@
 be done fast enough, but  on the other side 
-large enough to define a large internal polytope and therefore a powerful move.
+large enough to define a large internal polytope and so a powerful move.
 %
@@
 %
-We draw $n/2$ negative edges, and assign different seed to the endpoints
-of each edge.
+We draw $n/2$ negative edges, and assign to the endpoints a different seed.
 Doing so, a random subset of negative edges is forced
@@
 For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
-is added to the edge weighs.
+can be added to the edge weighs.
 
@@
 For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
-of Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
+of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
 For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
@@
 We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
-While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
+While this implementation uses full adjacency matrixes it does not scale as well and can not be applied on all datasets.
 We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
-
+%
 As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
@@
 %
-Energy Based Based Hierarchical Clustering (\textbf{EHC})
-as described in sec.~\ref{sec:ehc}.
+Energy Based Based Hierarchical Clustering (\textbf{EHC}),
+as described in Sec.~\ref{sec:ehc}.
 %
@@
 We set the size of the proposals fix to $10\%$ of the original problem size
-and the standard derivation of the random edge noise to $1.5$.
+and the standard derivation of the random edge noise is set to $1.5$.
 
@@
 \subsection{Improvements for the Multicut Algorithm}\label{sec:tunedMC} 
+When using the  public available implementation in OpenGM\footref{opengm-master}
+of Kappes~\etal~\cite{kappes_2013_arxiv}, we realize that their implementation has some limitations on large problems.
+This results in a very slow separation and make the following modifications.
+Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
+Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
+This procedure is one magnitude faster, but might cause a few extra outer iterations.
+In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
+For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
+
  \begin{figure}[t]
@@
   \end{figure}
-When using the  public available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal~\cite{kappes_2013_arxiv}, we realize that their implementation has some limitations on large problems.
-This results in a very slow separation and make the following modifications.
-Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-This procedure is one magnitude faster, but might cause a few extra outer iterations.
-In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
 
@@
 The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
-Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low energy.
+Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low quality.
 As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
@@
 \subsection{Social Networks and Network Clustering}
-A application for large scale correlation clustering are social networks.
+An application for large scale correlation clustering are social networks.
 We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
@@
 This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
-Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ is the edge-weight is positive or negative, respectively.
+Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
 The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
@@
 
-{\color{red}\textbf{TODO: Discussion}}
+As shown in Fig.~\ref{fig:anytime} (g,h) CCFusion provides for the first minutes the best results.
+Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
+MC-I and MC-R can even not be applied on such large problems.
+We belief that with better proposal generators, which are more suited for such network problems,
+we can improve CCFusion. One candidate for such a generated would be a scalable method for the 
+PIVOT algorithm.
 
 As another example for network clustering we use the modularity-clustering models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
-
-{\color{red}\textbf{TODO: Discussion}}
+Although, CCFusion and the used parameters was not designed and chosen for this type of problem, it performs on par to competitive methods. 
+Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime} (i)
 

### 2014-11-12 paper/egpaper_for_review.tex
fixed typo in param choise
exp

@@
 
+An overview of the used datasets is given in Tab.~\ref{tab:instance_sizes} and described in detail in Sec.\ref{sec:nets} and \ref{sec:imseg}.
+
+\begin{table}[th]
+   \tiny
+   \centering
+   \caption{Datasets used for evaluation}
+   \label{tab:instance_sizes}
+   \begin{tabular}{llllc}
+      \toprule
+         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
+      \midrule 
+         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
+         knott-150        &     572-972         & ???              & 2            & $\times$ \\
+         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
+         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
+         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
+         3d-seg           &     101220          & ???              & 1            & $\times$ \\
+         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
+      \bottomrule
+   \end{tabular}
+\end{table}
+
 \subsection{Improvements for the Multicut Algorithm}\label{sec:tunedMC} 
@@
 
-\subsection{Social Networks and Network Clustering}
+\subsection{Social Networks and Network Clustering}\label{sec:nets}
 An application for large scale correlation clustering are social networks.
@@
 which is zero if the given partitioning does not violated any relation and larger otherwise.
+We name this two datasets \emph{social nets} and \emph{normalized social nets}.
 
-As shown in Fig.~\ref{fig:anytime} (g,h) CCFusion provides for the first minutes the best results.
+As shown in Fig.~\ref{fig:anytime}(g,h) CCFusion provides for the first minutes the best results.
 Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
@@
 
-As another example for network clustering we use the modularity-clustering models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
+As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
 Although, CCFusion and the used parameters was not designed and chosen for this type of problem, it performs on par to competitive methods. 
-Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime} (i)
+Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime}(i)
 
-\subsection{2D and 3D Image Segmentation}
+\subsection{2D and 3D Image Segmentation}\label{sec:imseg}
 To segment images or volumes into a previously
@@
 
-{\color{red}\textbf{TODO: Discussion}}
+For image-seg CCFusion is faster than competitive methods, \cf Fig.~\ref{fig:anytime}(a).
+The variation of information~\cite{} (VI) of the CCFusion methods is also best, \cf Tab.~\ref{tab:eval}.
+Proposals by EHC seemed to be a bit better than WS-based ones.
 
-\begin{table}[H]
-   \tiny
-   \centering
-   \caption{Datasets used for evaluation}
-   \label{tab:instance_sizes}
-   \begin{tabular}{llllc}
-      \toprule
-         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
-      \midrule 
-         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
-         knott-150        &     572-972         & ???              & 2            & $\times$ \\
-         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
-         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
-         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
-         3d-seg           &     101220          & ???              & 1            & $\times$ \\
-         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
-      \bottomrule
-   \end{tabular}
-\end{table}
+For the knott-datasets similar holds. With increasing problem size CCFusion-HC-MC and CCFusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
+Also in terms of VI they are only slightly worse than the global optimal solution found by MC-I.
+The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
+For the largest 3D volume seg-3d, HC-CGC gives the first good solution, \cf  Fig.~\ref{fig:anytime}(f).
+However, after a view minutes  CCFusion-HC-MC and CCFusion-WS-MC give much better results and also overall best in terms of energy and VI, \cf Tab.~\ref{tab:eval}.
 
-\begin{table}[H]
+Pure HC, Fusion and PIVOT-BOEM do not give useful results on any dataset.
+
+\begin{table}[th]
    \tiny

### 2014-11-12 paper/egpaper_for_review.tex
future work

@@
 
-%\input{inputs/fig_contraction.tex}
+\input{inputs/fig_contraction.tex}
 %\input{inputs/fig_projection.tex}
@@
 
-An overview of the used datasets is given in Tab.~\ref{tab:instance_sizes} and described in detail in Sec.\ref{sec:nets} and \ref{sec:imseg}.
+% An overview of the used datasets is given in Tab.~\ref{tab:instance_sizes} and described in detail in Sec.\ref{sec:nets} and \ref{sec:imseg}.
 
-\begin{table}[th]
-   \tiny
-   \centering
-   \caption{Datasets used for evaluation}
-   \label{tab:instance_sizes}
-   \begin{tabular}{llllc}
-      \toprule
-         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
-      \midrule 
-         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
-         knott-150        &     572-972         & ???              & 2            & $\times$ \\
-         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
-         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
-         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
-         3d-seg           &     101220          & ???              & 1            & $\times$ \\
-         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
-      \bottomrule
-   \end{tabular}
-\end{table}
+% \begin{table}[th]
+%    \tiny
+%    \centering
+%    \caption{Datasets used for evaluation}
+%    \label{tab:instance_sizes}
+%    \begin{tabular}{llllc}
+%       \toprule
+%          Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
+%       \midrule 
+%          image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
+%          knott-150        &     572-972         & ???              & 2            & $\times$ \\
+%          knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
+%          knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
+%          knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
+%          3d-seg           &     101220          & ???              & 1            & $\times$ \\
+%          socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
+%       \bottomrule
+%    \end{tabular}
+% \end{table}
 
@@
 We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
-More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
+%More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
 
@@
 
-\begin{table}[th]
+\begin{table}[t]
    \tiny
@@
 
-\section{Further Work}\label{sec:future}
-So far we have generated the proposals randomly and do not take the current segmentation into account.
-
-So far we only enforce must link constraints to obtain smaller problems.
-One can also enforce cannot link constraints to the problem. 
-If those are closed, they automatically lead to a decomposition of the problem, 
-which is a interesting property for very huge data.
-
-Improving proposals.
+\section{Future Work}\label{sec:future}
+In future work we would like to investigate in much larger problem instances.
+Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
+If those build a closed surface, the problem decompose into two independent problems.
+This is also useful for interactive correlation clustering, by enforcing
+updates only in local regions by appropriate proposals.
+Overall, a more specific selection of proposals, maybe conditioned on the current solution,
+should lead better proposals and to faster progress of CCFusion.
 

### 2014-11-12 paper/egpaper_for_review.tex
update

@@
       \midrule 
-         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &              &              &  --\\ 
-         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &              & $       2.8395$\\
-         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &              & $       1.7603$ \\
-         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &              & $       6.8908$ \\
-         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &              & $       7.1057$\\
-         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &              & $       6.5366$ \\
-         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &              & $       6.5058$\\   
-         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &              & $       4.3319$\\  
-         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &              & $\bf    1.3347$ \\  
-         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &              & $       2.1347$ \\  
-         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &              & $\bf    1.3334$ \\  
-         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &              & $       3.3514$ \\      
+         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &    $ 4.4986$   &      --      &    --        &  --\\ 
+         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &    --        & $       2.8395$\\
+         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &    --        & $       1.7603$ \\
+         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &    --        & $       6.8908$ \\
+         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &    --        & $       7.1057$\\
+         FUSION           &$\bf 2.1406$  &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &    --        & $       6.5366$ \\
+         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &    --        & $       6.5058$\\   
+         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &    --        & $       4.3319$\\  
+         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &    --        & $\bf    1.3347$ \\  
+         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &    --        & $       2.1347$ \\  
+         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &    --        & $\bf    1.3334$ \\  
+         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &    --        & $       3.3514$ \\      
+      \bottomrule
+   \end{tabular}
+\end{table}
+
+\begin{table}[t]
+   \tiny
+   \centering
+   \caption{Evaluation of Rand Index (RI) for datasets with available ground-truth.}
+   \label{tab:eval2}
+   \begin{tabular}{lllllll}
+      \toprule
+         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
+      \midrule 
+         PIVOT-BOEM       &   $ 0.7438$  &    $ 0.7851$ &    $  0.8792$  &      --      &    --        &  --\\ 
+         HC               &   $ 0.7560$  &    $ 0.8139$ &    $  0.8084$  &    $ 0.7610$ &    --        & $ 0.9651$\\
+         HC-CGC           &   $ 0.7724$  &    $ 0.9226$ &    $  0.8713$  &    $ 0.8433$ &    --        & $ 0.9861$ \\
+         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$ &    --        & $ 0.6024$ \\
+         KL               &   $ 0.6400$  &    $ 0.8085$ &    $  0.6858$  &    $ 0.6409$ &    --        & $ 0.5849$\\
+         FUSION           &   $ 0.5480$  &    $ 0.2849$ &    $  0.1420$  &    $ 0.0998$ &    --        & $ 0.0345$ \\
+         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &    $ 0.6713$ &    --        & $ 0.0432$ \\   
+         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$ &    --        & $ 0.5461$\\  
+         FusionCC-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        & $\bf 0.9906$ \\  
+         FusionCC-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &    --        & $ 0.9775$ \\  
+         FusionCC-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &    --        & $ 0.8895$ \\  
+         FusionCC-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &    --        & $\bf 0.9906$ \\      
       \bottomrule
@@
 should lead better proposals and to faster progress of CCFusion.
+%
+Furthermore, we can extend our approach to higher-order correlation clustering~\cite{Kim-2011,kappes_2013_arxiv}
+by using higher order subproblems.
 
@@
 approximate solver for correlation 
-clustering, named Fusion Moves for correlation clustering (FM-CC).
+clustering, named Correlation Clustering Fusion (CCFusion).
 The best solution is iteratively improved 
@@
 clustering on a smaller graph fewer edges and nodes
-and can therefore be solved very fast.
-Our evaluation shows that CC-FF
-significantly outperforms 
-other solvers w.r.t. any time performance 
+and can therefore be solved much faster than the original problem.
+
+Our evaluation shows that several CCFusion
+outperforms state-of-the-art solvers w.r.t. any time performance 
 with increasing problem size.

### 2014-11-13 paper/introduction-new.tex
update introduction/notation

@@
 state-of-the-art results on the Berkeley Segmentation Database
-\cite{andres_2011_iccv,yarkony_2012_eccv,alush_2013_simbad}.
+\cite{andres_2011_iccv,Kim-2011,yarkony_2012_eccv,alush_2013_simbad}.
 
@@
 First, we define a novel energy based agglomerative clustering algorithm that monotonically increase the energy.
-With this at hand we show how to improve the anytime performance of Cut, Clue \& Cut.
-Second, we introduce cluster-fusion moves, which extend the original fusion moves~\cite{Lempitsky-2010} 
+With this at hand we show how to improve the anytime performance of Cut, Clue \& Cut~\cite{beier_2014_cvpr}.
+%
+Second, we improve the anytime performance of polyhedral multicut methods~\cite{kappes_2013_arxiv} by more efficient separation procedures.
+%
+Third, we introduce cluster-fusion moves, which extend the original fusion moves~\cite{Lempitsky-2010} 
 used in supervised segmentation to the unsupervised case and give a polyhedral interpretation of this algorithm.
@@
 \noindent \textbf{Related Work.}
-A natural approach is to solve the integer linear programming problem directly. 
+A natural approach is to solve the integer linear program (ILP) directly. 
 To this end, efficient separation procedures have been found~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
-Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation~\cite{kappes_2013_arxiv}. 
+Alternatively, it is possible to relax the integrality constraints of the ILP formulation~\cite{kappes_2013_arxiv}. 
 Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
@@
 to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
-Starting with an initial segmentation, auxiliary max-cut problems are approximately solved,
+Starting with an initial segmentation, auxiliary max-cut problems are (approximately) solved,
 such that the segmentation is strictly improved.
-As shown by Beier \etal~\cite{beier_2014_cvpr} only CGC~\cite{beier_2014_cvpr} 
+As shown by Beier \etal~\cite{beier_2014_cvpr} only Cut, Clue \& Cut (CGC)~\cite{beier_2014_cvpr} 
 can deal with large scale problems, but can also suffer on very large auxiliary problems.
@@
 Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} can not be applied directly for correlation clustering.
-We will show how to overcome this point later.
+We will show how to overcome this point in Sec.~\ref{sec:cc_fm}.
 
@@
 the correlation clustering objective.
-In Sec.~\ref{sec:cc_fm} we describe our proposed
-method and show the properties of the algorithm.
-In Sec.~\ref{sec:exp} we show an evaluation
-of the proposed methods methods and state of the art
-and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
+Followed by a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
+our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
+We evaluate the proposed methods methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
+
 %-------------------------------------------------------------------------
 
+\input{inputs/fig_notation.tex}
 \section{Notation and Problem Formulation}\label{sec:problem_formulation}
@@
 %
+%\input{inputs/fig_notation.tex}
 A segmentation of the graph $G$ can by either given by an 
@@
 The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.
+%
+By $l(y)$ we denote a node labeling for a segmentation given by $y$.
 
@@
 
-\input{inputs/fig_notation.tex}
+%\input{inputs/fig_notation.tex}

### 2014-11-13 paper/egpaper_for_review.tex
update introduction/notation
update EHC
update 4.0

@@
 %%%%%%global tikz styles
+\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
+\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]
 
@@
 smaller or equal to zero  (blue edge in Fig.~\ref{fig:hc_alg}). Any further edge
-contraction leads to worse energies.
+contraction does not improve the energies.
 
@@
 
-Once we know how to fuse segmentations, the actual algorithm 
-for correlation clustering 
-is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{Lempitsky-2010}.
-We iteratively improve the best solution by
+%Once we know how to fuse segmentations, the actual algorithm 
+%for correlation clustering 
+%is simple and similar to the fusion move algorithm of 
+As Lempitsky \etal~\cite{Lempitsky-2010}, 
+we iteratively improve the best solution by
 fusing it with proposal solution.
 The inherent difference is how we define the fusion.
-We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
-
-A further difference is how we efficiently calculate the correlation clustering fusion move and how we generate proposals.
-Both will be discussed next. The overall framework is sketched in Fig.~\ref{fig:move_graph}.
+%We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
 
@@
 For latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.
+
+A further difference is how we efficiently calculate the correlation clustering fusion move and how we generate proposals.
+Both will be discussed next. The overall framework is sketched in Fig.~\ref{fig:move_graph}.
 

### 2014-11-13 paper/egpaper_for_review.tex
update 4.1

@@
 \subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
-In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, still NP-hard.
+In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
 However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
@@
 \begin{definition}\emph{(Contracted Graph)}
-Given a weighted graph $G=(V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
-we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
+Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
 We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
-by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
-$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
+by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
+$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, l_u(y)=\bar{u},l_v(y)=\bar{v}}w_{uv}$ 
 \end{definition}
 %
-Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $y$ the original graph $G=(V,E)$ by
+Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ the original graph $G=(V,E)$ by
 %
 \begin{align}
-y_{uv}&=\left\{ 
+\tilde{y}_{uv}&=\left\{ 
 \begin{array}{ll}
-\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
+\bar{y}_{l_u(y)l_v(y)}& \textrm{ if }l_u(y) \neq l_v(y)\\
 0                & \textrm{ else}
@@
 \end{align}
-Furthermore, the back projection of the optimal segmentation $\bar{y}$ of the contracted graph is a solution of problem~\ref{eq:fusion_move_a}.
 
@@
 \begin{proof}
-Let $y'$ be the back propagation of $\bar{y}'$, which is by definition a feasible for~\ref{eq:fusion_move_a}.
+Let $y'$ be the back propagation of $\bar{y}'$, which is by definition feasible for~\ref{eq:fusion_move_a}.
 If $y'$ would not be an optimal solution than there must exists $y''$ with 

### 2014-11-13 paper/egpaper_for_review.tex
update 4.1 including figures

@@
 multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
-become tractable.
+are very fast.
 

### 2014-11-13 paper/egpaper_for_review.tex
update 4.2
update 4.3

@@
 
-The choice of the proposal defines the shape of the auxiliary polytope. 
+The choice of the proposal defines the shape of the inner polytope. 
 In the given toy example, the first (red) polytope give a huge improvement, the second proposal
@@
 to span diverse internal polytopes, cover with the intersection of
-inner polytopes a large part of the original polytope and so  
-more likely find the global optimal solution or escape from local minima.
+inner polytopes a large part of the original polytope and find 
+more likely the global optimal solution or escape from local minima.
 

### 2014-11-13 paper/egpaper_for_review.tex
update 5.0

@@
 \section{Experiments}\label{sec:exp}
-In our experiments we compare to the following methods withpublic available implementation.
+In our experiments we compare to the following methods with public available implementation.
 
@@
 and the standard derivation of the random edge noise is set to $1.5$.
+%
+As stopping condition we choose 10000 iterations and 100 iterations with no improvement.
 

### 2014-11-13 paper/egpaper_for_review.tex
update 5.1
update 6/7

@@
 \newcommand{\scatterplotpath}{./scatterplots/}
+\newcommand{\rd}{\color{red}}
 
@@
 of Kappes~\etal~\cite{kappes_2013_arxiv}, we realize that their implementation has some limitations on large problems.
-This results in a very slow separation and make the following modifications.
+This results in a very slow separation and we make the following modifications.
 Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
 Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-This procedure is one magnitude faster, but might cause a few extra outer iterations.
+during the separation procedure. 
 In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
 For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
+%
+Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
+This procedure is one magnitude faster, but might cause a few extra outer iterations.
 
@@
    \centering
-   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
+   \caption{Evaluation by Variation of Information (VOI) Rand Index (RI) for datasets with available ground-truth.}
    \label{tab:eval}
@@
       \toprule
-         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
+         VOI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
       \midrule 
-         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &    $ 4.4986$   &      --      &    --        &  --\\ 
+         PIVOT-BOEM       &\rd$ 4.9633$  &\rd $ 2.9936$ &\rd $ 4.4986$   &      --      &    --        &  --\\ 
          HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &    --        & $       2.8395$\\
          HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &    --        & $       1.7603$ \\
-         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &    --        & $       6.8908$ \\
-         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &    --        & $       7.1057$\\
-         FUSION           &$\bf 2.1406$  &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &    --        & $       6.5366$ \\
-         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &    --        & $       6.5058$\\   
-         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &    --        & $       4.3319$\\  
+         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &    --        & $\rd    6.8908$ \\
+         KL               &   $ 2.6432$  &\rd $ 2.0648$ &\rd $ 4.1318$   &\rd $ 4.9270$ &    --        & $\rd    7.1057$\\
+         FUSION           &$\bf 2.1406$  &\rd $ 2.8787$ &\rd $ 4.0744$   &\rd $ 4.6616$ &    --        & $\rd    6.5366$ \\
+         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &    --        & $\rd    6.5058$\\   
+         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &    --        & $\rd    4.3319$\\  
          FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &    --        & $\bf    1.3347$ \\  
@@
    \end{tabular}
-\end{table}
 
-\begin{table}[t]
-   \tiny
-   \centering
-   \caption{Evaluation of Rand Index (RI) for datasets with available ground-truth.}
-   \label{tab:eval2}
    \begin{tabular}{lllllll}
       \toprule
-         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
+          RI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
       \midrule 
-         PIVOT-BOEM       &   $ 0.7438$  &    $ 0.7851$ &    $  0.8792$  &      --      &    --        &  --\\ 
-         HC               &   $ 0.7560$  &    $ 0.8139$ &    $  0.8084$  &    $ 0.7610$ &    --        & $ 0.9651$\\
+         PIVOT-BOEM       &   $ 0.7438$  &\rd $ 0.7851$ &    $  0.8792$  &      --      &    --        &  --\\ 
+         HC               &   $ 0.7560$  &\rd $ 0.8139$ &\rd $  0.8084$  &\rd $ 0.7610$ &    --        &   $ 0.9651$\\
          HC-CGC           &   $ 0.7724$  &    $ 0.9226$ &    $  0.8713$  &    $ 0.8433$ &    --        &   $ 0.9861$ \\
-         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$ &    --        & $ 0.6024$ \\
-         KL               &   $ 0.6400$  &    $ 0.8085$ &    $  0.6858$  &    $ 0.6409$ &    --        & $ 0.5849$\\
-         FUSION           &   $ 0.5480$  &    $ 0.2849$ &    $  0.1420$  &    $ 0.0998$ &    --        & $ 0.0345$ \\
-         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &    $ 0.6713$ &    --        & $ 0.0432$ \\   
-         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$ &    --        & $ 0.5461$\\  
-         FusionCC-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        & $\bf 0.9906$ \\  
+         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$ &    --        &\rd$ 0.6024$ \\
+         KL               &\rd$ 0.6400$  &\rd $ 0.8085$ &\rd $  0.6858$  &\rd $ 0.6409$ &    --        &\rd$ 0.5849$\\
+         FUSION           &\rd$ 0.5480$  &\rd $ 0.2849$ &\rd $  0.1420$  &\rd $ 0.0998$ &    --        &\rd$ 0.0345$ \\
+         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &\rd $ 0.6713$ &    --        &\rd$ 0.0432$ \\   
+         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$ &    --        &\rd$ 0.5461$\\  
+         FusionCC-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        &$\bf 0.9906$ \\  
          FusionCC-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &    --        &   $ 0.9775$ \\  
@@
 \section{Future Work}\label{sec:future}
-In future work we would like to investigate in much larger problem instances.
+In future work we would like to investigate in much larger problem instances
+and interactive correlation clustering, by enforcing
+updates only in local regions by appropriate proposals.
+%
 Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
 If those build a closed surface, the problem decompose into two independent problems.
-This is also useful for interactive correlation clustering, by enforcing
-updates only in local regions by appropriate proposals.
+%
 Overall, a more specific selection of proposals, maybe conditioned on the current solution,
@@
 clustering, named Correlation Clustering Fusion (CCFusion).
+It is orthogonal to previous research, \ie it can be combined with and
+correlation clustering solver.
+%
 The best solution is iteratively improved 

### 2014-11-13 paper/datasets.tex
refactor experimental section

--- 2014-11-13 paper/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{eso-pic}
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{xspace}
-\usepackage{booktabs}
-\usepackage{placeins}
-
-% Include other packages here, before hyperref.
-\usepackage{my_macros}
-\usepackage{paralist}
-\usepackage{amsthm}
-% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
-%\usepackage{framed}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{algorithm}
-%\usepackage{algorithmic}
-\usepackage{algpseudocode}
-\usepackage{setspace}
-%for tikz
-\usepackage{tikz,pgfplots}
-\usepackage{pgfplotstable}
-\usepackage{filecontents}
-%\usepackage{scrextend}
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-\pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
-\usepackage{everypage}
-\AddEverypageHook{%
-  \makeatletter%
-  \special{pdf: put @thispage <</Group << /S /Transparency /I true /CS /DeviceRGB>> >>}%
-  \makeatother%
-}%
-
-\newcommand{\footlabel}[2]{%
-    \addtocounter{footnote}{1}%
-    \footnotetext[\thefootnote]{%
-        \addtocounter{footnote}{-1}%
-        \refstepcounter{footnote}\label{#1}%
-        #2%
-    }%
-    $^{\ref{#1}}$%
-}
-
-\newcommand{\footref}[1]{%
-    $^{\ref{#1}}$%
-}
-\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
-\usetikzlibrary{arrows,petri,topaths}
-\usetikzlibrary{positioning,fit,calc}
-\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
-\usetikzlibrary{calc, matrix, backgrounds}
-
-%%%%%%global tikz styles
-\tikzstyle{nS}=[circle,minimum size = 0.6cm,inner sep = 0pt,draw, font=\small,align=left]
-\tikzstyle{eNS}=[fill=white,minimum size = 0.5cm,inner sep = 0pt, font=\tiny,align=left]
-
-\tikzstyle{eBlack}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=black!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eNotCut}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eBlue}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=blue!70!black, font=\small,align=left, line width=1mm]
-\tikzstyle{eCut}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left, draw=red!70!black, line width=1mm]
-
-\pgfplotsset{every axis/.append style={
-  every axis y label/.style = {at={(ticklabel cs:0.5)}, rotate=90, anchor=south},
-  axis x line = {bottom},
-  axis y line = {left},
-  tick align = outside,
-  ymajorgrids = true,
-%  legend style = {draw=none, at={(1.05, 0.5)}, anchor=west, font=\small},
-  legend style = {font=\tiny},
-  legend columns = 1,
-  every axis plot/.append style = {line width=1pt},
-  label style = {font=\small},
-  tick label style={font=\small},
-  scaled ticks = false,
-}}
-
-% Two Colored Circle Split 
-\makeatletter
-\tikzset{circle split part fill/.style  args={#1,#2}{%
- alias=tmp@name, 
-  postaction={%
-    insert path={
-     \pgfextra{% 
-     \pgfpointdiff{\pgfpointanchor{\pgf@node@name}{center}}%
-                  {\pgfpointanchor{\pgf@node@name}{east}}%            
-     \pgfmathsetmacro\insiderad{\pgf@x}
-      \fill[#1] (\pgf@node@name.base) ([xshift=-\pgflinewidth]\pgf@node@name.east) arc
-                          (0:180:\insiderad-\pgflinewidth)--cycle;
-      \fill[#2] (\pgf@node@name.base) ([xshift=\pgflinewidth]\pgf@node@name.west)  arc
-                           (180:360:\insiderad-\pgflinewidth)--cycle;            
-         }}}}}  
- \makeatother
-
-%\usepackage{tkz-berge}
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
-\usepackage{xargs} 
-\newtheorem{theorem}{Theorem}
-\newtheorem{remark}{Remark}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage{bm}% ändert \boldsymbol
-\def\arraystretch{0.8}
-\renewcommand{\tabcolsep}{2pt}
-\newcommand{\thickline}{2pt}
-\newcommand{\scatterplotpath}{./scatterplots/}
-
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
-\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
-\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
-\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
-\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
-\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
-\newcommand{\OR}{\textrm{ or }}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-\newcommand{\realplot}[1]{
-\begin{tikzpicture}
-    \begin{axis}
-        \addlegendimage{empty legend}\addlegendentry{Matrix #1}
-        \addplot {0};
-        \addplot {1};
-        \addplot {2};
-        \addplot {3};
-    \end{axis}
-\end{tikzpicture}}
-
-% \newcommand{\anytimeplot}[1]{
-%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
-%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
-%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
-%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
-%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
-%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
-%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
-%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
-%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
-%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
-% }
-\newcommand{\anytimeplot}[1]{
-  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
-  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
-  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
-  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL} 
-  \addplot[color=yellow!50!black,mark=square] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
-  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
-  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CCFusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CCFusion-HC-CGC}
-  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CCFusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CCFusion-WS-CGC}
-}
-%  \addplot[color=yellow!50!black,mark=o] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
-  %\addplot[color=green!50,mark=o] table[x=time, y=PIVOT*]{data3/#1.data};          \addlegendentry{PIVOT-BOEM}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-\begin{document}
-%%%%%%%%% TITLE
-\include{my_macros.tex}
-%\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
-\title{Fusion Moves for Correlation Clustering}
-
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
-
-\maketitle
-%\thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  \color{red} \textbf{TODO:}
-Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized.
-We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering.
-A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.
-
-%We address the problem of partitioning a  graph
-%   into a previously unknown number of clusters.
-%   Among all partitions, the one with the minimal 
-%   sum of of cut edge weights is chosen. 
-%   This problem is known as correlation clustering 
-%   or multicut.
-%   We propose a general framework to find
-%   high quality approximate solutions for 
-%   this NP-hard problem based on a move making algorithm:
-%   We use candidate solutions from a proposal generator
-%   to iteratively improve the best observed solution similar
-%   to fusion moves.
-%   The proposed solver outperforms any other solver
-%   w.r.t. to any time performance.
-%   The solutions found by this solver are close
-%   to global optimal solutions w.r.t. energy
-%   and problem specific measurements as VI for
-%   image segmentation problems.
-
-\end{abstract}
-
-\input{introduction-new.tex}
-%\input{introduction-old.tex}
-%\input{introduction-fred.tex}
-
-\input{inputs/fig_hc_alg.tex}
-\section{Energy Based Hierarchical Clustering}\label{sec:ehc}
-Agglomerative hierarchical clustering (HC) is widely used
-in graph / image segmentation~\cite{arbelaez_2006}.
-In each step, the edge with the highest weight $w$ is
-contracted (green edges in Fig.~\ref{fig:hc_alg}).
-Doing so, parallel edges edges can occur.
-In agglomerative clustering, weights of
-parallel edges are merged into single edges.
-For image segmentation, the length
-weighted mean is used to do this update~\cite{arbelaez_2006}.
-
-While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interested in an 
-agglomeration with respect to our energy function~\ref{eq:edgeproblem}.
-For this we propose to use energy based agglomeration
-with the following update rule:
-Whenever there are multiple edges between 
-a pair of nodes, these edges are merged into a single edge
-and the weights are summed up, since we 
-minimize the sum of the cut edges.
-We call HC with this update method Energy base Hierarchical Clustering (EHC).
-
-We stop EHC if the highest edge weight is
-smaller or equal to zero  (blue edge in Fig.~\ref{fig:hc_alg}). Any further edge
-contraction does not improve the energies.
-
-% Hierarchical clustering is fast, and 
-% due to the agglomeration of edge weights, 
-% {\color{red} hierarchical clustering is robust against noise}.
-% {\color{yellow} [ First most similar nodes are merged...]
-% In agglomerative clustering, weights of
-% parallel edges are merged into single edges.}
-% For image segmentation, the length
-% weighted mean is used to do this update [ref].
-
-% [We contrary on those works work directly on energy functions and that why ...]
-% We propose to use Energy Based Hierarchical Clustering (EHC) to find
-% solutions for correlation clustering.
-
-% To make EHC follow the energy, we propose 
-% the following update rule:
-% Whenever there are multiple edges between 
-% a pair of nodes, these edges are merged into a single edge
-% by summing up their weights, since we 
-% minimize the sum of the cut edges.
-% The algorithm stops if the highest edge weight is
-% smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
-% contraction leads to worse energies.
-
-Given the intrinsic greediness of hierarchical clustering, 
-EHC is sensitive against noise and we cannot expect optimal solutions.
-
-But EHC is very fast, and can be used to initialize
-CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
-is spend in the \emph{cut phase} to solve the 
-first 2 coloring on the complete graph.
-As shown in Sec.~\ref{sec:exp},
-allowing CGC to start from the EHC solution
-can improve performance drastically.
-
-% Common cluster distances
-% \begin{itemize}
-% \item Single-Link: Nearest Neighbor - their closest members.
-% \item Complete-Link: Furthest Neighbor - their furthest members.
-% \item Centroid: Distance between centroids
-% \item Group Average: average of all cross-cluster pairs.
-% \end{itemize}
-
-%------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
-
-Fusion moves as defined in~\cite{Lempitsky-2010} work
-in the node domain and do not work properly for 
-objective functions as Eq.~\ref{eq:nodeproblem} since
-the node coloring is ambiguous and has no semantic meaning, \cf Fig.~\ref{fig:fusion_abiguty}.
-In the following, we propose a more suitable fusion move for correlation
-clustering which works on the edge domain.
-%
-Given two proposal solutions $y'$ and $y''$,
-$\mathcal{E}_0^{\breve{y}}$ is the set of edges
-which are uncut in $y'$ and $y''$.
-%
-\begin{align}
-\breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
-\mathcal{E}_0^{\breve{y}}  & =  \{ ij \in E \; | \; \breve{y}_{ij} = 0 \}
-\end{align}
-%
-The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0^{\breve{y}}$.
-%
-\begin{align}
-  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0^{\breve{y}} \nonumber
-\end{align}
-%
-By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
-because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
-%\begin{align}
-%  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
-%\end{align}
-%
-
-%Once we know how to fuse segmentations, the actual algorithm 
-%for correlation clustering 
-%is simple and similar to the fusion move algorithm of 
-As Lempitsky \etal~\cite{Lempitsky-2010}, 
-we iteratively improve the best solution by
-fusing it with proposal solution.
-The inherent difference is how we define the fusion.
-%We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
-
-As classical fusion, CCFusion does not provide and lower bound on the objective and 
-has no sound stopping condition.
-For latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.
-
-A further difference is how we efficiently calculate the correlation clustering fusion move and how we generate proposals.
-Both will be discussed next. The overall framework is sketched in Fig.~\ref{fig:move_graph}.
-
-\input{inputs/fig_fusion.tex}
-
-%\textbf{old}
-%
-%Motivation Using Fusion moves -> problem ambiguity
-%
-%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
-%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
-%
-%We define the contradiction of graph $G_y=(V_y,E_y)$
-%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.
-
-%\input{inputs/fig_alg_graph.tex}
-
-\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
-In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
-However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
-into a correlation clustering problem on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
-%
-\begin{definition}\emph{(Contracted Graph)}
-Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
-We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
-by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
-$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, l_u(y)=\bar{u},l_v(y)=\bar{v}}w_{uv}$ 
-\end{definition}
-%
-Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ the original graph $G=(V,E)$ by
-%
-\begin{align}
-\tilde{y}_{uv}&=\left\{ 
-\begin{array}{ll}
-\bar{y}_{l_u(y)l_v(y)}& \textrm{ if }l_u(y) \neq l_v(y)\\
-0                & \textrm{ else}
-\end{array}
-\right.& \forall uv \in E
-\end{align}
-
-% Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
-% we can work on a coarser graph, where all nodes which are connected
-% via must-link constraints are merged into single nodes.
-% This coarser graph is constructed by contracting all must-link edges
-% (see Fig.~\ref{fig:move_graph}).
-
-% \begin{definition}\emph{(Back Projection)}
-% Given a segmentation $\bar{y}$ of a contradicted graph $G_y=(V_y,E_y)$.
-% We define the back projection $\rho^G$ from $\bar{y}$ to a segmentation of original graph  $G=(V,E)$
-% by 
-% \begin{align}
-% \rho^G_{uv}(\bar{y})=\left\{ 
-% \begin{array}{ll}
-% \bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
-% 0                & \textrm{ else}
-% \end{array}
-% \right.
-% \end{align}
-% \end{definition}
-
-\begin{theorem}[Equivalence]\label{thm:Equivalence}
-The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
-is an optimal solution of problem~\ref{eq:fusion_move_a}.
-\begin{proof}
-Let $y'$ be the back propagation of $\bar{y}'$, which is by definition feasible for~\ref{eq:fusion_move_a}.
-If $y'$ would not be an optimal solution than there must exists $y''$ with 
-$\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
-Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
-\begin{align*}
-  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
- &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
-  = \sum_{e\in E} w_ey_e' \\
- &> \sum_{e\in E} w_ey_e''
-  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
-  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
-\end{align*}
-where $\bar{y}''$ is the projection from $y''$ on $G_y$.
-This contradicts that $y'$ is a optimal segmentation of $G_y$.
-\end{proof}
-%
-\end{theorem}
-
-Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~\ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
-This is, depending on the intersection of the current and proposed solution, magnitudes smaller than $G$.
-The correlation clustering problem on $G_{\breve{y}}$ can be solved by any correlation clustering solver.
-Since $G_{\breve{y}}$ is smaller exact methods or good approximative methods like 
-multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
-are very fast.
-
-\input{inputs/fig_contraction.tex}
-%\input{inputs/fig_projection.tex}
-
-\input{inputs/fig_move_graph.tex}
-
-%-------------------------------------------------------------------------
-\subsection{Polyhedral Interpretation}
-A polyheadral interpretation of fusion moves is shown in Fig.~\ref{fig:polyheadral}.
-In each iteration the current and proposed segmentation define an inner polyheadral 
-approximation of the original polytope. This interpretation holds for original 
-fusion moves~\cite{Lempitsky-2010} as well as for the proposed CCFusion.
-
-In our case, optimizing over the inner polytope is the same kind of problem as the original multicut polytope, but much smaller.
-Furthermore, the costs does not change and and improvement in the smaller polytope will 
-be the same in the original graph, as shown in Theorem~\ref{thm:Equivalence}.
-
-The choice of the proposal defines the shape of the inner polytope. 
-In the given toy example, the first (red) polytope give a huge improvement, the second proposal
-defines the blue polytope which does not lead to an improvement. 
-The third proposal generates the green polytope that includes the global optimal solution.
-
-This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
-which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
-
-\begin{figure}
-\centering
-\input{polytope-tikz.tex}
-\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
-Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
-and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
-When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
-}
-\label{fig:polyheadral}
-\end{figure}
-
-% \begin{theorem}[Monotone]
-% Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
-% Than $y^*$  will never decrease the energy:
-% $y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
-% %
-% \begin{proof}
-% The feasible set of the fusion move includes per definition  $y'$ and $y''$.
-% If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
-% and that why not the propose segmentation of a fusion.
-% \end{proof}
-% %
-% \end{theorem}
-
-%\begin{remark}[Fix-point (pointless to me)]
-%Let $Y$ be the set of possible proposals, than
-%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
-%\end{remark}
-
-% \begin{remark}[Optimality]
-% Let $y'$ be the current and $y''$ the proposed segmentation.
-% If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
-% \end{remark}
-
-%-------------------------------------------------------------------------
-\subsection{Proposal Generators}
-
-As discussed in~\cite{Lempitsky-2010}, proposals
-should have two properties: \emph{quality} 
-and \emph{diversity}.
-
-A proposal have a high quality if it at least in some regions have a low energy.
-For high quality proposals the chance that the inner polytope includes 
-better solution (vertex) is larger than for those with low quality.
-
-Diversity between the individual proposals increase the chances
-to span diverse internal polytopes, cover with the intersection of
-inner polytopes a large part of the original polytope and find 
-more likely the global optimal solution or escape from local minima.
-
-For correlation clustering fusion we add a third
-property: \emph{size}.
-The size of the contracted graph directly
-depends on the number of connected components
-of the intersection of the proposal solution and the current best solution.
-%
-In the extreme case, where each 
-node is in a separate connnected component,
-the fusion move is equivalent to solving the original problem.
-In the other extreme, where the proposal has 
-a single connected component, the current best solution will not change.
-% 
-Therefore the size of the proposals
-should be small enough, such that solving
-eq.~\ref{eq:fusion_move_a} can
-be done fast enough, but  on the other side 
-large enough to define a large internal polytope and therefore a powerful move.
-%
-To this end we suggest two proposal generators.
-
-%\begin{algorithm}
-%    \begin{scriptsize}
-%        \caption{Proposal Generators}\label{alg:proposal_gen}   
-%        \begin{algorithmic}[1]
-%            %\Require $J(x) \leq J(x')$
-%            %\Ensure $J(\hat{x}) \leq J(x)$
-%            %\vspace{0.3cm}
-%            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
-%
-%            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
-%            \State \textbf{return} $x'$
-%            \EndProcedure
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $ getRandomSeeds$
-%            \State $ runEdgeWeightedWs$
-%            \EndProcedure   
-%            %
-%            %
-%            \vspace{0.3cm}
-%            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
-%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
-%            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
-%            \State $\hat{W} \gets W$
-%            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
-%                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
-%                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
-%            \EndWhile
-%            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
-%            \EndProcedure
-%        \end{algorithmic}
-%    \end{scriptsize}
-%\end{algorithm}
-
-\noindent \textbf{Randomized HierarchicalClustering (RHC):}
-%\subsubsection{Randomized HierarchicalClustering (RHC)}
-%
-To generate fast energy aware proposals we can use energy
-based hierarchical clustering (EHC) as defined in Sec.~\ref{sec:ehc}.
-EHC follows the energy function, therefore the \emph{quality}
-of the proposals is high.
-To get \emph{diversity} among the different proposal,
-we add normal distributed noise  $\mathcal{N}(0, \sigma_{ehc})$
-to each edge weight.
-To get proposals of the desired \emph{size}, we use a
-different stop condition as in EHC, and stop iff a certain number of connected
-components is reached.
-
-%\subsubsection{Randomized MaxCut  (RMC)}
-%
-%To get energy aware proposals we can use max cuts.
-%The max cut objective is the same as
-%the multicut objective, but only two 
-%node colors are allowed.
-%Therefore solutions of the max cut objective
-%might be useful proposals.
-%To create different proposals we set 
-%the weight of edges which are cut 
-%in the best solution to zero.
-%In this way we favor solutions 
-%different form the current best. 
-%In addition we either add noise permute a certain number of weights.
-
-\noindent \textbf{Randomized Watersheds (RWS):}
-%\subsubsection{Randomized Watersheds (RWS)}
-Watersheds have become quite popular for
-graph segmentation and have a strong connection
-to energy minimization~\cite{couprie_2011}.
-%
-The edge weighted watershed algorithm~\cite{meyer_2013}
-with random seeds can be used to get
-cheap proposals.
-To improve \emph{quality} we do not use $n$ seeds distributed uniformly
-over all nodes but use the following.
-%
-We draw $n/2$ negative edges, and assign different seed to the endpoints
-of each edge.
-Doing so, a random subset of negative edges is forced
-to be cut within each proposal.
-For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
-is added to the edge weighs.
-
-%\input{inputs/fig_hc.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Experiments}\label{sec:exp}
-In our experiments we compare to the following methods withpublic available implementation.
-
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
-of Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
-For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
- the public available implementation in OpenGM\footref{opengm-master} of Kappes~\etal, as described in Sec.~\ref{sec:tunedMC}.
-%
-%We realize that their implementation has some limitations on large problems and make the following modifications.
-%Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-%Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-%during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-%This procedure is one magnitude faster, but might cause a few extra outer iterations.
-%In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-%For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
-%
-From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
-We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
-While this implementation uses full adjacency matrixes it does not scale as well and can not be applied on all datasets.
-We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
-%
-As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
-Therefore we exclude those in our experiments.
-
-We compare this methods to the following methods suggested in the present paper.
-%
-Energy Based Based Hierarchical Clustering (\textbf{EHC}),
-as described in Sec.~\ref{sec:ehc}.
-%
-CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
-%
-The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
- and MC-I and CGC as subproblem solvers denoted by 
-\textbf{CCFusion-HC-MC},
-\textbf{-HC-CGC},
-\textbf{-WS-MC}, and 
-\textbf{-WS-CGC}, respectively.
-We set the size of the proposals fix to $10\%$ of the original problem size
-and the standard derivation of the random edge noise is set to $1.5$.
-
-All experiments were run on Intel Core i5-4570 CPUs
-with 3.20 GHz, equipped with 32 GB of RAM.
-In our evaluation we make not use of multiple threads.
-The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
-
-% An overview of the used datasets is given in Tab.~\ref{tab:instance_sizes} and described in detail in Sec.\ref{sec:nets} and \ref{sec:imseg}.
-
-% \begin{table}[th]
-%    \tiny
-%    \centering
-%    \caption{Datasets used for evaluation}
-%    \label{tab:instance_sizes}
-%    \begin{tabular}{llllc}
-%       \toprule
-%          Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
-%       \midrule 
-%          image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
-%          knott-150        &     572-972         & ???              & 2            & $\times$ \\
-%          knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
-%          knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
-%          knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
-%          3d-seg           &     101220          & ???              & 1            & $\times$ \\
-%          socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
-%       \bottomrule
-%    \end{tabular}
-% \end{table}
-
-\subsection{Improvements for the Multicut Algorithm}\label{sec:tunedMC} 
-When using the  public available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal~\cite{kappes_2013_arxiv}, we realize that their implementation has some limitations on large problems.
-This results in a very slow separation and make the following modifications.
-Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
-during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
-This procedure is one magnitude faster, but might cause a few extra outer iterations.
-In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
-
- \begin{figure}[t]
-    \centering
-    \begin{tikzpicture}
-    \begin{semilogxaxis}[  mark size=1pt,
-     height= 4cm, 
-    restrict y to domain=-80000:1000,
-   %   restrict x to domain=10:4000,
-    xlabel = {runtime},
-    xmin = 10,
-    xmax = 4100,
-    ymax = 0,
-    ymin = -80000,
-    legend to name = ledgendPositionMC,
-    legend columns=4,
-    width = 0.9\columnwidth,
-    scaled ticks = false
-    ] 
-    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
-    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
-    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
-    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}
-
-    \end{semilogxaxis}
-    \end{tikzpicture}
-  \begin{center}
-  \hypersetup{linkcolor = black}
-  \ref{ledgendPositionMC}
-  \hypersetup{linkcolor = red}
-  \end{center}
-    \caption{Comparison of the Multicut implementation of OpenGM and 
-    our modified implementation, which can deal better with large scale problems. 
-    However, for large scale problems it still does not scale.}
-    \label{fig:at:knott-450b}
-  \end{figure}
-
-\subsection{Parameter Choice for CCFusion}
-Beside the choice of the proposal generator and fusion method CCFusion has some more parameters, which need to be set.
-The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
-Fig.~\ref{fig:parameterchoice} shows an evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
-The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
-The level of noise has no major impact on the runtime.
-The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
-Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low quality.
-As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
-experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
-%
-%
-\begin{figure}[th]
-\centering
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
-\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
-\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
-  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
-}
-\label{fig:parameterchoice}
-\end{figure}
-
-\subsection{Social Networks and Network Clustering}\label{sec:nets}
+\subsection{Datasets}\label{sec:datasets}
+\textbf{Social Networks.}\label{sec:nets}
 An application for large scale correlation clustering are social networks.
@@
 
-As shown in Fig.~\ref{fig:anytime}(g,h) CCFusion provides for the first minutes the best results.
-Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
-MC-I and MC-R can even not be applied on such large problems.
-We belief that with better proposal generators, which are more suited for such network problems,
-we can improve CCFusion. One candidate for such a generated would be a scalable method for the 
-PIVOT algorithm.
+\textbf{Network Modularity Clustering.}
+As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
 
-As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
-Although, CCFusion and the used parameters was not designed and chosen for this type of problem, it performs on par to competitive methods. 
-Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime}(i)
-
-\subsection{2D and 3D Image Segmentation}\label{sec:imseg}
+\textbf{2D and 3D Image Segmentation}\label{sec:imseg}
 To segment images or volumes into a previously
@@
 %More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
-
-For image-seg CCFusion is faster than competitive methods, \cf Fig.~\ref{fig:anytime}(a).
-The variation of information~\cite{} (VI) of the CCFusion methods is also best, \cf Tab.~\ref{tab:eval}.
-Proposals by EHC seemed to be a bit better than WS-based ones.
-
-For the knott-datasets similar holds. With increasing problem size CCFusion-HC-MC and CCFusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
-Also in terms of VI they are only slightly worse than the global optimal solution found by MC-I.
-The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
-For the largest 3D volume seg-3d, HC-CGC gives the first good solution, \cf  Fig.~\ref{fig:anytime}(f).
-However, after a view minutes  CCFusion-HC-MC and CCFusion-WS-MC give much better results and also overall best in terms of energy and VI, \cf Tab.~\ref{tab:eval}.
-
-Pure HC, Fusion and PIVOT-BOEM do not give useful results on any dataset.
-
-\begin{table}[t]
-   \tiny
-   \centering
-   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
-   \label{tab:eval}
-   \begin{tabular}{lllllll}
-      \toprule
-         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
-      \midrule 
-         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &    $ 4.4986$   &      --      &    --        &  --\\ 
-         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &    --        & $       2.8395$\\
-         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &    --        & $       1.7603$ \\
-         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &    --        & $       6.8908$ \\
-         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &    --        & $       7.1057$\\
-         FUSION           &$\bf 2.1406$  &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &    --        & $       6.5366$ \\
-         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &    --        & $       6.5058$\\   
-         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &    --        & $       4.3319$\\  
-         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &    --        & $\bf    1.3347$ \\  
-         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &    --        & $       2.1347$ \\  
-         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &    --        & $\bf    1.3334$ \\  
-         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &    --        & $       3.3514$ \\      
-      \bottomrule
-   \end{tabular}
-\end{table}
-
-\begin{table}[t]
-   \tiny
-   \centering
-   \caption{Evaluation of Rand Index (RI) for datasets with available ground-truth.}
-   \label{tab:eval2}
-   \begin{tabular}{lllllll}
-      \toprule
-         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
-      \midrule 
-         PIVOT-BOEM       &   $ 0.7438$  &    $ 0.7851$ &    $  0.8792$  &      --      &    --        &  --\\ 
-         HC               &   $ 0.7560$  &    $ 0.8139$ &    $  0.8084$  &    $ 0.7610$ &    --        & $ 0.9651$\\
-         HC-CGC           &   $ 0.7724$  &    $ 0.9226$ &    $  0.8713$  &    $ 0.8433$ &    --        & $ 0.9861$ \\
-         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$ &    --        & $ 0.6024$ \\
-         KL               &   $ 0.6400$  &    $ 0.8085$ &    $  0.6858$  &    $ 0.6409$ &    --        & $ 0.5849$\\
-         FUSION           &   $ 0.5480$  &    $ 0.2849$ &    $  0.1420$  &    $ 0.0998$ &    --        & $ 0.0345$ \\
-         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &    $ 0.6713$ &    --        & $ 0.0432$ \\   
-         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$ &    --        & $ 0.5461$\\  
-         FusionCC-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        & $\bf 0.9906$ \\  
-         FusionCC-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &    --        & $ 0.9775$ \\  
-         FusionCC-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &    --        & $ 0.8895$ \\  
-         FusionCC-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &    --        & $\bf 0.9906$ \\      
-      \bottomrule
-   \end{tabular}
-\end{table}
-
-%\begin{center}
-%    \begin{figure}
-%        \begin{center}
-%            \begin{subfigure}[b]{0.45\linewidth}
-%                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
-%            \end{subfigure}
-%            \quad
-%            \begin{subfigure}[b]{0.45\linewidth}
-%                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
-%            \end{subfigure}
-%        \end{center}
-%    \caption{
-%        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv%}
-%    }
-%    \end{figure}
-%\end{center}
-%
-%\newpage
-
-\input{anytimefigure2.tex}
-
-% \begin{figure}
-% \input{scatterplots/knott-3d-450.tex}
-% \caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
-% A more aggressive one would lead to much faster runtime with only a bit worse values.
-% DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
-% }
-% \end{figure}
-
-%\subsection{Pixel-wise Multicuts}
-%\input{inputs/fig_pixel_mc.tex}
-
-\section{Future Work}\label{sec:future}
-In future work we would like to investigate in much larger problem instances.
-Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
-If those build a closed surface, the problem decompose into two independent problems.
-This is also useful for interactive correlation clustering, by enforcing
-updates only in local regions by appropriate proposals.
-Overall, a more specific selection of proposals, maybe conditioned on the current solution,
-should lead better proposals and to faster progress of CCFusion.
-%
-Furthermore, we can extend our approach to higher-order correlation clustering~\cite{Kim-2011,kappes_2013_arxiv}
-by using higher order subproblems.
-
-\section{Conclusion}\label{sec:conclusion}
-
-We have presented a fast and scalable 
-approximate solver for correlation 
-clustering, named Correlation Clustering Fusion (CCFusion).
-The best solution is iteratively improved 
-by a fusion with proposal solutions.
-The fusion move itself is formulated as correlation
-clustering on a smaller graph fewer edges and nodes
-and can therefore be solved much faster than the original problem.
-
-Our evaluation shows that several CCFusion
-outperforms state-of-the-art solvers w.r.t. any time performance 
-with increasing problem size.
-
-\newpage
-
-\FloatBarrier
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
-% \newpage
-
-% \onecolumn
-% \section{Appendix}
-
-% \input{tables/anytime/image-seg.tex}
-% \input{tables/anytime/knott-3d-150.tex}
-% \input{tables/knott-3d-300.tex}
-% \input{tables/anytime/knott-3d-450.tex}
-% \input{tables/knott-3d-550.tex}
-% \input{tables/anytime/seg-3d.tex}
-% \input{tables/modularity-clustering.tex}
-
-\end{document}

### 2014-11-13 paper/egpaper_for_review.tex
fix formulation
refactor experimental section

@@
   \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
-  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CCFusion-HC-MC}
-  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CCFusion-HC-CGC}
-  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CCFusion-WS-MC}
-  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CCFusion-WS-CGC}
+  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CC-Fusion-HC-MC}
+  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CC-Fusion-HC-CGC}
+  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CC-Fusion-WS-MC}
+  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CC-Fusion-WS-CGC}
 }
@@
 
-As classical fusion, CCFusion does not provide and lower bound on the objective and 
+As classical fusion, CC-Fusion does not provide and lower bound on the objective and 
 has no sound stopping condition.
@@
 
-\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
+\subsection{Fast Optimization of CC-Fusion Moves} \label{sec:fast_optimization}
 In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
@@
 approximation of the original polytope. This interpretation holds for original 
-fusion moves~\cite{Lempitsky-2010} as well as for the proposed CCFusion.
+fusion moves~\cite{Lempitsky-2010} as well as for the proposed CC-Fusion.
 
@@
 \input{polytope-tikz.tex}
-\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
-Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
+\caption{Each move can be interpreted as an optimization of an inner polytope.
+Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
 and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
-When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
+When optimizing over the green polytope we find $y_2$ which we will never leave again or any polytope containing~$y_2$. 
 }
@@
 In our experiments we compare to the following methods with public available implementation.
-
+%
 For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
@@
  and MC-I and CGC as subproblem solvers denoted by 
-\textbf{CCFusion-HC-MC},
+\textbf{CC-Fusion-HC-MC},
 \textbf{-HC-CGC},
@@
 We set the size of the proposals fix to $10\%$ of the original problem size
-and the standard derivation of the random edge noise is set to $1.5$.
+and use random edge noise with $\sigma=1.5$.
 %
-As stopping condition we choose 10000 iterations and 100 iterations with no improvement.
+As stopping condition we choose $10^4$ iterations and $100$ iterations with no improvement.
 
@@
 % \end{table}
+
+\input{datasets.tex}
 
@@
 
-\subsection{Parameter Choice for CCFusion}
-Beside the choice of the proposal generator and fusion method CCFusion has some more parameters, which need to be set.
+\subsection{Parameter Choice for CC-Fusion}
+Beside the choice of the proposal generator and fusion method CC-Fusion has some more parameters, which need to be set.
 The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
@@
 
-\subsection{Social Networks and Network Clustering}\label{sec:nets}
-An application for large scale correlation clustering are social networks.
-We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
-Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
-%
-The first network is called \emph{Epinions}. 
-This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
-Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
-The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
-%
-The second network is called \emph{Slashdot}. 
-Slashdot is a technology-related news website know for its specific user community. 
-In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
-The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.
+\input{evaluation.tex}
+% \subsection{Social Networks and Network Clustering}\label{sec:nets}
+% An application for large scale correlation clustering are social networks.
+% We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
+% Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
+% %
+% The first network is called \emph{Epinions}. 
+% This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
+% Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
+% The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
+% %
+% The second network is called \emph{Slashdot}. 
+% Slashdot is a technology-related news website know for its specific user community. 
+% In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
+% The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.
 
-We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
-In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
-% 
-To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
-\begin{align}
-  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
-\end{align}
-We define the following energy function
-\begin{align}
- J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
-      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
-\end{align}
-which is zero if the given partitioning does not violated any relation and larger otherwise.
-We name this two datasets \emph{social nets} and \emph{normalized social nets}.
+% We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
+% In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
+% % 
+% To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
+% \begin{align}
+%   \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
+% \end{align}
+% We define the following energy function
+% \begin{align}
+%  J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
+%       &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
+% \end{align}
+% which is zero if the given partitioning does not violated any relation and larger otherwise.
+% We name this two datasets \emph{social nets} and \emph{normalized social nets}.
 
-As shown in Fig.~\ref{fig:anytime}(g,h) CCFusion provides for the first minutes the best results.
-Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
-MC-I and MC-R can even not be applied on such large problems.
-We belief that with better proposal generators, which are more suited for such network problems,
-we can improve CCFusion. One candidate for such a generated would be a scalable method for the 
-PIVOT algorithm.
+% As shown in Fig.~\ref{fig:anytime}(g,h) CC-Fusion provides for the first minutes the best results.
+% Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
+% MC-I and MC-R can even not be applied on such large problems.
+% We belief that with better proposal generators, which are more suited for such network problems,
+% we can improve CC-Fusion. One candidate for such a generated would be a scalable implementations of the 
+% PIVOT algorithm.
 
-As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
-Although, CCFusion and the used parameters was not designed and chosen for this type of problem, it performs on par to competitive methods. 
-Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime}(i)
+% As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
+% Although, CC-Fusion and the used parameters was not designed and chosen for this type of problem, it performs on par to competitive methods. 
+% Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime}(i)
 
-\subsection{2D and 3D Image Segmentation}\label{sec:imseg}
-To segment images or volumes into a previously
-unknown number of clusters, correlation clustering
-has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.
+% \subsection{2D and 3D Image Segmentation}\label{sec:imseg}
+% To segment images or volumes into a previously
+% unknown number of clusters, correlation clustering
+% has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.
 
-Starting from a super-pixel/-voxel segmentation,
-correlation clustering finds the clustering with the lowest energy.
-The energy is based on a likelihood of merging adjacent super-voxels.
-Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
-or to merge them ($p(y_{ij} = 0)$).
-The energy function is defined as following:
-\begin{align}
- J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
-\end{align}
-Where $\beta$ is used as a prior~\cite{andres_2011_iccv}.
+% Starting from a super-pixel/-voxel segmentation,
+% correlation clustering finds the clustering with the lowest energy.
+% The energy is based on a likelihood of merging adjacent super-voxels.
+% Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
+% or to merge them ($p(y_{ij} = 0)$).
+% The energy function is defined as following:
+% \begin{align}
+%  J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
+% \end{align}
+% Where $\beta$ is used as a prior~\cite{andres_2011_iccv}.
 
-We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
-For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
-For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
-instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
-We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
-%More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
+% We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
+% For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
+% For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
+% instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
+% We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
+% %More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
 
-For image-seg CCFusion is faster than competitive methods, \cf Fig.~\ref{fig:anytime}(a).
-The variation of information~\cite{} (VI) of the CCFusion methods is also best, \cf Tab.~\ref{tab:eval}.
-Proposals by EHC seemed to be a bit better than WS-based ones.
+% For image-seg CC-Fusion is faster than competitive methods, \cf Fig.~\ref{fig:anytime}(a).
+% The variation of information~\cite{} (VI) of the CC-Fusion methods is also best, \cf Tab.~\ref{tab:eval}.
+% Proposals by EHC seemed to be a bit better than WS-based ones.
 
-For the knott-datasets similar holds. With increasing problem size CCFusion-HC-MC and CCFusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
-Also in terms of VI they are only slightly worse than the global optimal solution found by MC-I.
-The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
-For the largest 3D volume seg-3d, HC-CGC gives the first good solution, \cf  Fig.~\ref{fig:anytime}(f).
-However, after a view minutes  CCFusion-HC-MC and CCFusion-WS-MC give much better results and also overall best in terms of energy and VI, \cf Tab.~\ref{tab:eval}.
+% For the knott-datasets similar holds. With increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
+% Also in terms of VI they are only slightly worse than the global optimal solution found by MC-I.
+% The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
+% For the largest 3D volume seg-3d, HC-CGC gives the first good solution, \cf  Fig.~\ref{fig:anytime}(f).
+% However, after a view minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy and VI, \cf Tab.~\ref{tab:eval}.
 
-Pure HC, Fusion and PIVOT-BOEM do not give useful results on any dataset.
+% Pure HC, Fusion and PIVOT-BOEM do not give useful results on any dataset.
 
@@
          MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &    --        & $\rd    4.3319$\\  
-         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &    --        & $\bf    1.3347$ \\  
-         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &    --        & $       2.1347$ \\  
-         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &    --        & $\bf    1.3334$ \\  
-         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &    --        & $       3.3514$ \\      
+         CC-Fusion-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &    --        & $\bf    1.3347$ \\  
+         CC-Fusion-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &    --        & $       2.1347$ \\  
+         CC-Fusion-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &    --        & $\bf    1.3334$ \\  
+         CC-Fusion-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &    --        & $       3.3514$ \\      
       \bottomrule
@@
          MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$ &    --        &\rd$ 0.5461$\\  
-         FusionCC-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        &$\bf 0.9906$ \\  
-         FusionCC-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &    --        &   $ 0.9775$ \\  
-         FusionCC-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &    --        &   $ 0.8895$ \\  
-         FusionCC-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &    --        &   $\bf 0.9906$ \\      
+         CC-Fusion-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        &$\bf 0.9906$ \\  
+         CC-Fusion-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &    --        &   $ 0.9775$ \\  
+         CC-Fusion-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &    --        &   $ 0.8895$ \\  
+         CC-Fusion-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &    --        &   $\bf 0.9906$ \\      
       \bottomrule
@@
 Overall, a more specific selection of proposals, maybe conditioned on the current solution,
-should lead better proposals and to faster progress of CCFusion.
+should lead better proposals and to faster progress of CC-Fusion.
 %
@@
 approximate solver for correlation 
-clustering, named Correlation Clustering Fusion (CCFusion).
+clustering, named Correlation Clustering Fusion (CC-Fusion).
 It is orthogonal to previous research, \ie it can be combined with and
@@
 
-Our evaluation shows that several CCFusion
+Our evaluation shows that several CC-Fusion
 outperforms state-of-the-art solvers w.r.t. any time performance 

### 2014-11-13 paper/evaluation.tex
refactor experimental section

\subsection{Evaluation}
For the evaluation of the diffrent methods on the datasets introduced in Sec.~\ref{sec:datasets},
we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
Anytime plots with no zooming and a detailed evalution are given in supplementray material.

For \emph{social-nets} CC-Fusion methods provides for the first minutes the best results.
Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
MC-I and MC-R can even not be applied on such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generated would be a scalable implementations of the 
PIVOT algorithm.

For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even it 
and the used parameters was not designed and chosen for this type of problem.
Especially is does a better job than MC-I.

For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
Because, the models are designed to have a high boundary recall (oversegmentation), 
classical fusion, which return undersegmentations, with best VOI but worse RI and energy.
Proposals generated by EHC seemed to be a bit better than WS-based ones.

For the \emph{knott-datasets} similar holds as for image-seg. 
With increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VOI and RI they are only slightly worse than the global optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first usefull solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a view minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
%
Pure EHC, Fusion and PIVOT-BOEM do not give useful results on any dataset.

### 2014-11-13 paper/abstract-new.tex
add new abstract

Correlation clustering, or multicut partitioning,
is a widely used in image segmentation for
partitioning an undirected graph or image with positive and negative edge weights 
such that the sum of cut edge weights is minimized.
%
Due to its NP-hardness, exact solvers do not scale and approximative solvers often give nonsatisfying results.

We investigate scalable methods for correlation clustering.
To this end we define fusion moves for the correlation clustering problem.
Our algorithm iteratively fuse the current and a proposed partitioning which  monotonously improve
the partitioning and maintain a valid partitioning at all times.
Furthermore, it scales to larger datasets, gives near optimal solutions, and at the same time shows
a very good anytime performance.

### 2014-11-13 paper/egpaper_for_review.tex
replaced figure with png because there where rendering issues
add new abstract

@@
 \usepackage{filecontents}
+
 %\usepackage{scrextend}
@@
 \begin{abstract}
-  \color{red} \textbf{TODO:}
-Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized.
+\input{abstract-new.tex}
+%   \color{red} \textbf{TODO:}
+% Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized.
 We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering.
 A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.
-
+%    
 %We address the problem of partitioning a  graph
@@
 %   image segmentation problems.
-
+%
 \end{abstract}
+\vspace{-0.5cm}
 

### 2014-11-14 paper/abstract-new.tex
fixed typo

@@
 Correlation clustering, or multicut partitioning,
-is a widely used in image segmentation for
+is widely used in image segmentation for
 partitioning an undirected graph or image with positive and negative edge weights 

### 2014-11-14 paper/abstract-new.tex
fixed typos in abstract

@@
 %
-Due to its NP-hardness, exact solvers do not scale and approximative solvers often give nonsatisfying results.
+Due to its NP-hardness, exact solvers do not scale and approximative solvers often give non satisfying results.
 
@@
 To this end we define fusion moves for the correlation clustering problem.
-Our algorithm iteratively fuse the current and a proposed partitioning which  monotonously improve
+Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
 the partitioning and maintain a valid partitioning at all times.

### 2014-11-14 paper/introduction-new.tex
fixed all first order changes on the first page

@@
 Correlation clustering can also been used to cluster query refinements in web search~\cite{Sadikov-2010}.
-Because social and web-related networks are often very huge, heuristic methods, \eg the PIVOT-algorithm~\cite{Ailon-2008},
-are very popular~\cite{Chierichetti-2014}.
+Because social and web-related networks are often huge, heuristic methods, \eg the PIVOT-algorithm~\cite{Ailon-2008},
+are popular~\cite{Chierichetti-2014}.
 
-In computer vision applications, unsupervised image segmentation algorithms usually start with an over-segmentation
+In computer vision applications, unsupervised image segmentation algorithms often start with an over-segmentation
 into superpixels (superregions), which are then clustered into ``perceptually meaningful''
@@
 or social networks~\cite{Leskovec-2010}, 
-are not tractable, because reasonable solutions cannot be computed in acceptable time.
+are not tractable because reasonable solutions cannot be computed in acceptable time.
 
@@
 In this work we present some novel approaches that are designed for large scale correlation clustering problems.
-First, we define a novel energy based agglomerative clustering algorithm that monotonically increase the energy.
+First, we define a novel energy based agglomerative clustering algorithm that monotonically increases the energy.
 With this at hand we show how to improve the anytime performance of Cut, Clue \& Cut~\cite{beier_2014_cvpr}.
@@
 Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
-For the latter approach column generating methods exits, that works best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
+For the latter approach column generating methods exits, that work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
 
@@
 such that the segmentation is strictly improved.
-As shown by Beier \etal~\cite{beier_2014_cvpr} only Cut, Clue \& Cut (CGC)~\cite{beier_2014_cvpr} 
+As shown in ~\cite{beier_2014_cvpr} only Cut, Glue \& Cut (CGC)~\cite{beier_2014_cvpr} 
 can deal with large scale problems, but can also suffer on very large auxiliary problems.

### 2014-11-14 paper/egpaper_for_review.tex
maybe fixed the error
fixed all changes until page 4 for which i knew the fix

@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-\pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
-\usepackage{everypage}
-\AddEverypageHook{%
-  \makeatletter%
-  \special{pdf: put @thispage <</Group << /S /Transparency /I true /CS /DeviceRGB>> >>}%
-  \makeatother%
-}%
+% \pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
+% \usepackage{everypage}
+% \AddEverypageHook{%
+%   \makeatletter%
+%   \special{pdf: put @thispage <</Group << /S /Transparency /I true /CS /DeviceRGB>> >>}%
+%   \makeatother%
+% }%
 
@@
 
-While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interested in an 
+Because we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interested in an 
 agglomeration with respect to our energy function~\ref{eq:edgeproblem}.
@@
 minimize the sum of the cut edges.
-We call HC with this update method Energy base Hierarchical Clustering (EHC).
+We call HC with this update method Energy based Hierarchical Clustering (EHC).
 
@@
 is spend in the \emph{cut phase} to solve the 
-first 2 coloring on the complete graph.
+first two coloring on the complete graph.
 As shown in Sec.~\ref{sec:exp},
@@
 %------------------------------------------------------------------------
-\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
+\section{Correlation Clustering Fusion Moves}\label{sec:cc_fm}
 
@@
 %
-By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
+By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy w.r.t. the proposal
+$y'$ and $y''$,
 because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
@@
 we iteratively improve the best solution by
-fusing it with proposal solution.
+fusing it with proposal solutions.
 The inherent difference is how we define the fusion.
@@
 
-As classical fusion, CC-Fusion does not provide and lower bound on the objective and 
+As classical fusion, CC-Fusion does not provide a lower bound on the objective and 
 has no sound stopping condition.
@@
 Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
-We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
+we define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
 by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
@@
 Let $y'$ be the back propagation of $\bar{y}'$, which is by definition feasible for~\ref{eq:fusion_move_a}.
-If $y'$ would not be an optimal solution than there must exists $y''$ with 
+If $y'$ would not be an optimal solution there must be a $y''$ with 
 $\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.

### 2014-11-14 paper/introduction-new.tex
fixed all changes until page 4 for which i knew the fix

@@
+%!TEX root = ./egpaper_for_review.tex
+%
 \section{Introduction}
@@
 
-Outside computer vision greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
+Outside computer vision greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} have been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
 The PIVOT Algorithm~\cite{Ailon-2008} iterates over all nodes in random order.
@@
 %
-A widely use post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigns nodes to clusters.
+A widely used post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigns nodes to clusters.
 
@@
 with state of the art any time performance~\cite{kappes_2014_ws}.
-Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} can not be applied directly for correlation clustering.
+Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} cannot be applied directly for correlation clustering.
 We will show how to overcome this point in Sec.~\ref{sec:cc_fm}.
@@
 the correlation clustering objective.
-Followed by a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
+Next we give a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
 our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
@@
 %\input{inputs/fig_notation.tex}
-A segmentation of the graph $G$ can by either given by an 
+A segmentation of the graph $G$ can be either given by a
 node labeling $l \in \mathbb{N}^{|V|}$
@@
 \end{align} 
-or in the edge domain, by label each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
+or in the edge domain, by labeling each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
 \begin{align}

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes until page 4 for which i knew the fix

@@
 \subsection{Polyhedral Interpretation}
-A polyheadral interpretation of fusion moves is shown in Fig.~\ref{fig:polyheadral}.
-In each iteration the current and proposed segmentation define an inner polyheadral 
+A polyhedral interpretation of fusion moves is shown in Fig.~\ref{fig:polyheadral}.
+In each iteration the current and proposed segmentation define an inner polyhedral 
 approximation of the original polytope. This interpretation holds for original 
@@
 In our case, optimizing over the inner polytope is the same kind of problem as the original multicut polytope, but much smaller.
-Furthermore, the costs does not change and and improvement in the smaller polytope will 
+Furthermore, the cost do not change and an improvement in the smaller polytope will 
 be the same in the original graph, as shown in Theorem~\ref{thm:Equivalence}.

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes including page 4 for which i knew the fix

@@
 defines the blue polytope which does not lead to an improvement. 
-The third proposal generates the green polytope that includes the global optimal solution.
+The third proposal generates the green polytope that includes the globally optimal solution.
 
-This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
-which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
+This procedure is fundamentally different from common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
+which tighten an outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.
 
@@
 
-A proposal have a high quality if it at least in some regions have a low energy.
-For high quality proposals the chance that the inner polytope includes 
+A proposal has a high quality if it at least in some regions has a low energy.
+For high quality proposals the chance that the inner polytope includes a
 better solution (vertex) is larger than for those with low quality.
 
-Diversity between the individual proposals increase the chances
+Diversity between the individual proposals increases the chances
 to span diverse internal polytopes, cover with the intersection of
@@
 To get \emph{diversity} among the different proposal,
-we add normal distributed noise  $\mathcal{N}(0, \sigma_{ehc})$
+we add normally distributed noise  $\mathcal{N}(0, \sigma_{ehc})$
 to each edge weight.

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes including page 5

@@
 For additional \emph{diversity}, noise $\mathcal{N} (0, \sigma_{ws})$
-is added to the edge weighs.
+is added to the edge weighs \cite{straehle_2012}.
 
@@
 \section{Experiments}\label{sec:exp}
-In our experiments we compare to the following methods with public available implementation.
+In our experiments we compare to the following methods with publicly available implementation.
 %
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}}
-of Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
-For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use an modified version of
- the public available implementation in OpenGM\footref{opengm-master} of Kappes~\etal, as described in Sec.~\ref{sec:tunedMC}.
+For \textbf{CGC}~\cite{beier_2014_cvpr} we used the publicly available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}} and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
+For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use a modified version of
+ the publicly available implementation in OpenGM\footref{opengm-master}, as described in Sec.~\ref{sec:tunedMC}.
 %
@@
 From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
-We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
-While this implementation uses full adjacency matrixes it does not scale as well and can not be applied on all datasets.
+We use the publicly available code\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
+While this implementation uses full adjacency matrices it does not scale as well and can not be applied on all datasets.
 We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
 %
-As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
+As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies than PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
 Therefore we exclude those in our experiments.
 
-We compare this methods to the following methods suggested in the present paper.
+We compare these methods to the following methods suggested in the present paper.
 %
@@
 \textbf{-WS-CGC}, respectively.
-We set the size of the proposals fix to $10\%$ of the original problem size
+We set the size of the proposals to $10\%$ of the original problem size
 and use random edge noise with $\sigma=1.5$.
@@
 with 3.20 GHz, equipped with 32 GB of RAM.
-In our evaluation we make not use of multiple threads.
+In our evaluation we make no use of multiple threads.
 The methods were stopped if they exceed 30 minutes at the next possible interrupt point.

### 2014-11-14 paper/datasets.tex
fixed all changes including page 5

@@
+%!TEX root = ./egpaper_for_review.tex
 \subsection{Datasets}\label{sec:datasets}
 \textbf{Social Networks.}\label{sec:nets}
-An application for large scale correlation clustering are social networks.
+One important application for large scale correlation clustering are social networks.
 We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
@@
 The first network is called \emph{Epinions}. 
-This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
-Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
+This is who-trust-whom online social network of a a general consumer review site. 
+Each directed edge $a\to b$ indicates that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
 The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
@@
 The second network is called \emph{Slashdot}. 
-Slashdot is a technology-related news website know for its specific user community. 
-In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
-The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.
+Slashdot is a technology-related news website known for its specific user community. 
+In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friend or foe. 
+The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges of which $76.73\%$ are positively weighted.
 
@@
 % 
-To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
+To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact on the overall network, by enforcing.
 \begin{align}

### 2014-11-14 paper/datasets.tex
fixed all changes where i knew the fix up tp parameter choise

@@
 which is zero if the given partitioning does not violated any relation and larger otherwise.
-We name this two datasets \emph{social nets} and \emph{normalized social nets}.
+We name these two datasets \emph{social nets} and \emph{normalized social nets}.
 
@@
 or to merge them ($p(y_{ij} = 0)$).
-The energy function is defined as following:
+The energy function is
 \begin{align}
@@
 \end{align}
-Where $\beta$ is used as a prior~\cite{andres_2011_iccv}.
+where $\beta$ is used as a prior~\cite{andres_2011_iccv}.
 
-We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
-For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
+We use the publicly available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
+For 2D images from the Berkeley Segmentation Database~\cite{martin_2001}, we took the segmentation problems called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
 For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
-instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
-We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
+instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underlying cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
+We also request larger instances from the authors of~\cite{kroeger_2012_eccv} who kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
 %More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes where i knew the fix up tp parameter choise

@@
 \subsection{Improvements for the Multicut Algorithm}\label{sec:tunedMC} 
-When using the  public available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal~\cite{kappes_2013_arxiv}, we realize that their implementation has some limitations on large problems.
+When using the  publicly available implementation in OpenGM\footref{opengm-master}
+of Kappes~\etal~\cite{kappes_2013_arxiv}, we have realize that their implementation has some limitations on large problems.
 This results in a very slow separation and we make the following modifications.
@@
 during the separation procedure. 
-In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
-For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
+In~\cite{kroeger_2012_eccv} this has been used for MC-I only. 
+For MC-R this search procedure is not sufficient and needs to be followed by a search for shortest non-chordal paths.
 %
-Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
+Fig.~\ref{fig:at:knott-450b} shows the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
 This procedure is one magnitude faster, but might cause a few extra outer iterations.

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes where i knew the fix up tp parameter choise

@@
 Beside the choice of the proposal generator and fusion method CC-Fusion has some more parameters, which need to be set.
-The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
+The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is used to generate diversity.
 Fig.~\ref{fig:parameterchoice} shows an evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
-The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
+The runtime depends on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
 The level of noise has no major impact on the runtime.

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes where i knew the fix up tp parameter choise

@@
 The level of noise has no major impact on the runtime.
-The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
-Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low quality.
+The energy of the final solution improves with finer proposals since this increases the search space of the moves.
+The level of noise has to be large enough to generate diverse proposals but not to large to generate proposals with low quality.
 As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
-experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
+experiments. However we would like to note, that in practice we can improve the performance by adjusting these parameters for the specific problem setting.
 %
@@
 \caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
-  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
+  Proposals with many segments cause longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
 }

### 2014-11-14 paper/anytimefigure2.tex
work on exp sec
update
pimp fig 9
fixed all changes where i knew the fix up tp parameter choise

@@
   \begin{semilogxaxis}[  mark size=1pt,
-  restrict y to domain=-40000:-24000,
+  %restrict y to domain=-40000:-24000,
   xlabel = {runtime},
@@
   ]
+  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/knott-3d-300.data};          \addlegendentry{PIVOT-BOEM}  
   \anytimeplot{knott-3d-300}
@@
   \end{subfigure}
+  {\color{gray}\hspace{1cm}\rule{0.939\textwidth}{1pt}}\vspace{0.2cm}
   \newline
@@
   \end{subfigure}
+  {\color{gray}\hspace{1cm}\rule{0.93\textwidth}{1pt}}\vspace{0.2cm}
+  \newline
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     Overall, energy hierarchical clustering based proposals work better
-    then watershed based proposals. They converge to similar energies
+    than watershed based proposals. They converge to similar energies
     but the clustering based approach is faster on all tested instances.
     On all instances except for modularity clustering, it is better
-    to solve the fusion move to optimality (Fusion-HC-MC) then using approximations (FUSION-HC-GCG).
-    The warm EHC started version of GCG (EHC-CGC) performs better then GCG itself,
+    to solve the fusion move to optimality (Fusion-HC-MC) than using approximations (FUSION-HC-GCG).
+    The warm EHC started version of GCG (EHC-CGC) performs better than GCG itself,
     but both are outperformed by the proposed algorithms w.r.t. any time performance.
@@
     best performance.
-    The proposed methods perform reasonable, but  KL is faster and leads to better energies.
+    The proposed methods performs reasonable, but  KL is faster and leads to better energies.
   }
+  \label{fig:anytime}
 \end{figure*}

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes where i knew the fix up tp parameter choise

@@
 Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
-If those build a closed surface, the problem decompose into two independent problems.
+If those build a closed surface, the problem decomposes into two independent problems.
 %
@@
 clustering, named Correlation Clustering Fusion (CC-Fusion).
-It is orthogonal to previous research, \ie it can be combined with and
+It is orthogonal to previous research, \ie it can be combined with
 correlation clustering solver.
@@
 The fusion move itself is formulated as correlation
-clustering on a smaller graph fewer edges and nodes
+clustering on a smaller graph with fewer edges and nodes
 and can therefore be solved much faster than the original problem.
 
-Our evaluation shows that several CC-Fusion
+Our evaluation shows that several CC-Fusion algorithms
 outperforms state-of-the-art solvers w.r.t. any time performance 

### 2014-11-14 paper/evaluation.tex
fixed all changes including page 5
fixed all changes where i knew the fix up tp parameter choise

@@
+%!TEX root = ./egpaper_for_review.tex
 \subsection{Evaluation}
-For the evaluation of the diffrent methods on the datasets introduced in Sec.~\ref{sec:datasets},
+For the evaluation of the different methods on the datasets introduced in Sec.~\ref{sec:datasets},
 we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
 and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
-Anytime plots with no zooming and a detailed evalution are given in supplementray material.
+Anytime plots with no zooming and a detailed evaluation are given in supplementary material.
 
-For \emph{social-nets} CC-Fusion methods provides for the first minutes the best results.
-Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
-MC-I and MC-R can even not be applied on such large problems.
+For \emph{social-nets} CC-Fusion methods provide the best results for the first minutes .
+Only CGC and HC-CGC are able to find better solutions after more than 1000 seconds.
+MC-I and MC-R can not be applied to such large problems.
 We belief that with better proposal generators, which are more suited for such network problems,
-we can improve CCFusion. One candidate for such a generated would be a scalable implementations of the 
+we can improve CCFusion. One candidate for such a generator would be a scalable implementation of the 
 PIVOT algorithm.
 
-For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even it 
-and the used parameters was not designed and chosen for this type of problem.
-Especially is does a better job than MC-I.
+For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even CC-Fusion 
+and the used parameters have not been designed and chosen for this type of problem.
+Especially it does a better job than MC-I.
 
 For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
-Because, the models are designed to have a high boundary recall (oversegmentation), 
-classical fusion, which return undersegmentations, with best VOI but worse RI and energy.
+Because  the models are designed to have a high boundary recall (oversegmentation), 
+classical fusion, which return undersegmentations, is best best VOI but worse RI and energy.
 Proposals generated by EHC seemed to be a bit better than WS-based ones.
@@
 With increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
-Also in terms of VOI and RI they are only slightly worse than the global optimal solution found by MC-I.
+Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
 The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
-For the largest 3D volume seg-3d, HC-CGC gives the first usefull solution, \cf  Fig.~\ref{fig:anytime}(f).
-However, after a view minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
+For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).
+However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
 %

### 2014-11-14 paper/introduction-new.tex
fixed all changes where i knew the fix to

@@
 Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012},
-see Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.
+is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
+See Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.
 

### 2014-11-14 paper/datasets.tex
fixed some still missing stuff from fred
changes thorsten und joerg

@@
 The first network is called \emph{Epinions}. 
-This is who-trust-whom online social network of a a general consumer review site. 
+This is a who-trust-whom online social network of a a general consumer review site. 
 Each directed edge $a\to b$ indicates that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
@@
 \end{align}
-which is zero if the given partitioning does not violated any relation and larger otherwise.
+which is zero if the given partitioning does not violates any relation and larger otherwise.
 We name these two datasets \emph{social nets} and \emph{normalized social nets}.

### 2014-11-14 paper/egpaper_for_review.tex
fixed some still missing stuff from fred
changes thorsten und joerg

@@
 CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
-is spend in the \emph{cut phase} to solve the 
+is spent in the \emph{cut phase} to solve the 
 first two coloring on the complete graph.
@@
 has no sound stopping condition.
-For latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.
+For the latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.
 
@@
 %
-Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ the original graph $G=(V,E)$ by
+Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ of the original graph $G=(V,E)$ by
 %
@@
 Let $y'$ be the back propagation of $\bar{y}'$, which is by definition feasible for~\ref{eq:fusion_move_a}.
-If $y'$ would not be an optimal solution there must be a $y''$ with 
+If $y'$ would not be an optimal solution, there must be a $y''$ with 
 $\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
@@
 \input{polytope-tikz.tex}
-\caption{Each move can be interpreted as an optimization of an inner polytope.
+\caption{Each fusion move can be interpreted as an optimization of an inner polytope.
 Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
@@
     \caption{Comparison of the Multicut implementation of OpenGM and 
-    our modified implementation, which can deal better with large scale problems. 
+    our modified implementation, which improves the runtime.
     However, for large scale problems it still does not scale.}
@@
 The energy of the final solution improves with finer proposals since this increases the search space of the moves.
-The level of noise has to be large enough to generate diverse proposals but not to large to generate proposals with low quality.
+The level of noise has to be large enough to generate diverse proposals, but not too large which would lead to proposals with low quality.
 As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
-experiments. However we would like to note, that in practice we can improve the performance by adjusting these parameters for the specific problem setting.
+experiments. However we would like to note that in practice we can improve the performance by adjusting these parameters for the specific problem setting.
 %
@@
    \centering
-   \caption{Evaluation by Variation of Information (VOI) Rand Index (RI) for datasets with available ground-truth.}
+   \caption{Evaluation by Variation of Information (VOI) and Rand Index (RI) for datasets with available ground truth.}
    \label{tab:eval}
-   \begin{tabular}{lllllll}
+   \begin{tabular}{llllll}
       \toprule
-         VOI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
+         VOI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 &3d-seg\\
       \midrule 
-         PIVOT-BOEM       &\rd$ 4.9633$  &\rd $ 2.9936$ &\rd $ 4.4986$   &      --      &    --        &  --\\ 
-         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &    --        & $       2.8395$\\
-         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &    --        & $       1.7603$ \\
-         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &    --        & $\rd    6.8908$ \\
-         KL               &   $ 2.6432$  &\rd $ 2.0648$ &\rd $ 4.1318$   &\rd $ 4.9270$ &    --        & $\rd    7.1057$\\
-         FUSION           &$\bf 2.1406$  &\rd $ 2.8787$ &\rd $ 4.0744$   &\rd $ 4.6616$ &    --        & $\rd    6.5366$ \\
-         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &    --        & $\rd    6.5058$\\   
-         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &    --        & $\rd    4.3319$\\  
-         CC-Fusion-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &    --        & $\bf    1.3347$ \\  
-         CC-Fusion-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &    --        & $       2.1347$ \\  
-         CC-Fusion-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &    --        & $\bf    1.3334$ \\  
-         CC-Fusion-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &    --        & $       3.3514$ \\      
+         PIVOT-BOEM       &\rd$ 4.9633$  &\rd $ 2.9936$ &\rd $ 4.4986$   &      --       &  --\\ 
+         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$  & $       2.8395$\\
+         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$  & $       1.7603$ \\
+         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$  & $\rd    6.8908$ \\
+         KL               &   $ 2.6432$  &\rd $ 2.0648$ &\rd $ 4.1318$   &\rd $ 4.9270$  & $\rd    7.1057$\\
+         FUSION           &$\bf 2.1406$  &\rd $ 2.8787$ &\rd $ 4.0744$   &\rd $ 4.6616$  & $\rd    6.5366$ \\
+         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$  & $\rd    6.5058$\\   
+         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$  & $\rd    4.3319$\\  
+         CC-Fusion-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ & $\bf    1.3347$ \\  
+         CC-Fusion-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ & $       2.1347$ \\  
+         CC-Fusion-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ & $\bf    1.3334$ \\  
+         CC-Fusion-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ & $       3.3514$ \\      
       \bottomrule
@@
 
-   \begin{tabular}{lllllll}
+   \begin{tabular}{llllll}
       \toprule
-          RI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
+          RI              &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450  &3d-seg\\
       \midrule 
-         PIVOT-BOEM       &   $ 0.7438$  &\rd $ 0.7851$ &    $  0.8792$  &      --      &    --        &  --\\ 
-         HC               &   $ 0.7560$  &\rd $ 0.8139$ &\rd $  0.8084$  &\rd $ 0.7610$ &    --        &   $ 0.9651$\\
-         HC-CGC           &   $ 0.7724$  &    $ 0.9226$ &    $  0.8713$  &    $ 0.8433$ &    --        &   $ 0.9861$ \\
-         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$ &    --        &\rd$ 0.6024$ \\
-         KL               &\rd$ 0.6400$  &\rd $ 0.8085$ &\rd $  0.6858$  &\rd $ 0.6409$ &    --        &\rd$ 0.5849$\\
-         FUSION           &\rd$ 0.5480$  &\rd $ 0.2849$ &\rd $  0.1420$  &\rd $ 0.0998$ &    --        &\rd$ 0.0345$ \\
-         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &\rd $ 0.6713$ &    --        &\rd$ 0.0432$ \\   
-         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$ &    --        &\rd$ 0.5461$\\  
-         CC-Fusion-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &    --        &$\bf 0.9906$ \\  
-         CC-Fusion-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &    --        &   $ 0.9775$ \\  
-         CC-Fusion-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &    --        &   $ 0.8895$ \\  
-         CC-Fusion-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &    --        &   $\bf 0.9906$ \\      
+         PIVOT-BOEM       &   $ 0.7438$  &\rd $ 0.7851$ &    $  0.8792$  &      --       &  --\\ 
+         HC               &   $ 0.7560$  &\rd $ 0.8139$ &\rd $  0.8084$  &\rd $ 0.7610$  &   $ 0.9651$\\
+         HC-CGC           &   $ 0.7724$  &    $ 0.9226$ &    $  0.8713$  &    $ 0.8433$  &   $ 0.9861$ \\
+         CGC              &   $ 0.7590$  &    $ 0.9206$ &    $  0.8666$  &    $ 0.8341$  &\rd$ 0.6024$ \\
+         KL               &\rd$ 0.6400$  &\rd $ 0.8085$ &\rd $  0.6858$  &\rd $ 0.6409$  &\rd$ 0.5849$\\
+         FUSION           &\rd$ 0.5480$  &\rd $ 0.2849$ &\rd $  0.1420$  &\rd $ 0.0998$  &\rd$ 0.0345$ \\
+         MC-R             &   $ 0.7822$  &    $ 0.9232$ & $\bf  0.8849$  &\rd $ 0.6713$  &\rd$ 0.0432$ \\   
+         MC-I             &   $ 0.7821$  & $\bf 0.9236$ & $\bf  0.8849$  & $\bf 0.8670$  &\rd$ 0.5461$\\  
+         CC-Fusion-HC-MC   &   $ 0.7801$  &    $ 0.9042$ &    $  0.8824$  &    $ 0.8573$ &$\bf 0.9906$ \\  
+         CC-Fusion-HC-CGC  &   $ 0.7780$  &    $ 0.9031$ &    $  0.8763$  &    $ 0.8470$ &   $ 0.9775$ \\  
+         CC-Fusion-WS-MC   &$\bf 0.7825$  &    $ 0.9042$ &    $  0.8802$  &    $ 0.8582$ &   $ 0.8895$ \\  
+         CC-Fusion-WS-CGC  &   $ 0.7750$  &    $ 0.8951$ &    $  0.8596$  &    $ 0.8394$ &   $\bf 0.9906$ \\      
       \bottomrule
@@
 and can therefore be solved much faster than the original problem.
+%
+Our evaluation shows that several CC-Fusion algorithms
+outperform state-of-the-art solvers w.r.t. any time performance 
+with increasing problem size.
 
-Our evaluation shows that several CC-Fusion algorithms
-outperforms state-of-the-art solvers w.r.t. any time performance 
-with increasing problem size.
+\enlargethispage{0.4cm}
 

### 2014-11-14 paper/evaluation.tex
fixed all changes where i knew the fix to
changes thorsten und joerg

@@
 Anytime plots with no zooming and a detailed evaluation are given in supplementary material. 
-
+%
 For \emph{social-nets} CC-Fusion methods provide the best results for the first minutes .
@@
 PIVOT algorithm.
-
+%
 For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even CC-Fusion 
@@
 Especially it does a better job than MC-I.
-
+%
 For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
@@
 Proposals generated by EHC seemed to be a bit better than WS-based ones.
-
-For the \emph{knott-datasets} similar holds as for image-seg. 
-With increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
+%
+For the \emph{knott-datasets}
+with increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
 Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.

### 2014-11-14 paper/introduction-new.tex
fixed issuses in references, removed double citation and citeted bagon
changes thorsten und joerg

@@
 Its value is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights,
-which allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish  or do wish to end up in the same cluster or segment, respectively.
+which allows doing justice to evidence in the data that two nodes or pixels do not wish or do wish to end up in the same cluster or segment, respectively.
 Secondly, it does not require a specification of the number of clusters beforehand.
@@
 into superpixels (superregions), which are then clustered into ``perceptually meaningful''
-regions by correlation clustering on sparse graphs.
+regions by correlation clustering.
 Such an approach has been shown to yield
@@
 
-Despite the clear mathematical formulation and nice properties,
-correlation clustering is known to be NP-hard. 
+While it has a clear mathematical formulation and nice properties,
+correlation clustering suffers on its NP-hardness. 
 %
@@
 Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
-For the latter approach column generating methods exits, that work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
+For the latter approach column generating methods exits, which work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
 
 Another line of work uses move making algorithms 
-to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
+to optimize correlation clustering~\cite{bagon_2011_arxiv,beier_2014_cvpr,Kernighan-1970}.
 Starting with an initial segmentation, auxiliary max-cut problems are (approximately) solved,
 such that the segmentation is strictly improved.
-As shown in ~\cite{beier_2014_cvpr} only Cut, Glue \& Cut (CGC)~\cite{beier_2014_cvpr} 
+As shown in~\cite{beier_2014_cvpr} only Cut, Glue \& Cut (CGC)
 can deal with large scale problems, but can also suffer on very large auxiliary problems.
@@
 In Sec.~\ref{sec:problem_formulation} we will give a 
-detailed problem definition where we introduce 
+detailed problem definition and introduce 
 the correlation clustering objective.
@@
 or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation}.
-An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.
+An edge labeling is only consistent if it contains no violated cycle constraints~\cite{kappes_2013_arxiv}.
 We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.

### 2014-11-14 paper/egpaper_for_review.tex
uv to ij

@@
 we define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
-by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
-$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, l_u(y)=\bar{u},l_v(y)=\bar{v}}w_{uv}$ 
+by $V_y=\{l_i(y)|i\in V\}$, $E_y=\{l_i(y)l_j(y)|ij\in E\}$, and 
+$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{ij\in E, l_i(y)=\bar{u},l_j(y)=\bar{v}}w_{ij}$ 
 \end{definition}
@@
 \begin{align}
-\tilde{y}_{uv}&=\left\{ 
+\tilde{y}_{ij}&=\left\{ 
 \begin{array}{ll}
-\bar{y}_{l_u(y)l_v(y)}& \textrm{ if }l_u(y) \neq l_v(y)\\
+\bar{y}_{l_i(y)l_j(y)}& \textrm{ if }l_i(y) \neq l_j(y)\\
 0                & \textrm{ else}

### 2014-11-14 paper/introduction-new.tex
uv to ij
fic consistent edge label sentece

@@
 or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation}.
-An edge labeling is only consistent if it contains no violated cycle constraints~\cite{kappes_2013_arxiv}.
+An edge labeling is only consistent if it does not violate any cycle constraint~\cite{kappes_2013_arxiv}.
 We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
@@
 of the edges between distinct segments is minimized. This can be formulated in the node domain
-by assigning each node $v$ a label $l_v \in \mathbb{N}$
+by assigning each node $i$ a label $l_i \in \mathbb{N}$
 \begin{align}

### 2014-11-14 paper/abstract-new.tex
typos found by paul

@@
 Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
-the partitioning and maintain a valid partitioning at all times.
+the partitioning and maintains a valid partitioning at all times.
 Furthermore, it scales to larger datasets, gives near optimal solutions, and at the same time shows
-a very good anytime performance.
+a good anytime performance.

### 2014-11-14 paper/anytimefigure2.tex
typos found by paul

@@
     With increasing problem size (\ref{fig:at:knott-150}-\ref{fig:at:knott-550} and \ref{fig:at:seg3d})
-    the runtime of MC-I, MC-R and CGC increases drastically, while
+    the runtimes of MC-I, MC-R and CGC increase drastically, while
     the proposed solvers still scale well.

### 2014-11-14 paper/datasets.tex
typos found by paul

--- 2014-11-14 paper/datasets.tex
@@
 The first network is called \emph{Epinions}. 
-This is who-trust-whom online social network of a a general consumer review site. 
+This is a who-trust-whom online social network of a general consumer review site. 
 Each directed edge $a\to b$ indicates that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
@@
 
-We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
+We consider the problem to cluster these graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
 In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
@@
 \end{align}
-which is zero if the given partitioning does not violated any relation and larger otherwise.
+which is zero if the given partitioning does not violate any relation and larger otherwise.
 We name these two datasets \emph{social nets} and \emph{normalized social nets}.
@@
 instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underlying cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
-We also request larger instances from the authors of~\cite{kroeger_2012_eccv} who kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
+We also requested larger instances from the authors of~\cite{kroeger_2012_eccv} who kindly provided us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
 %More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.

### 2014-11-14 paper/egpaper_for_review.tex
typos found by paul

@@
 \end{abstract}
-\vspace{-0.5cm}
+\vspace{-0.6cm}
 
@@
 
-But EHC is very fast, and can be used to initialize
+However, EHC is very fast and can be used to initialize
 CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
@@
 The correlation clustering problem on $G_{\breve{y}}$ can be solved by any correlation clustering solver.
-Since $G_{\breve{y}}$ is smaller exact methods or good approximative methods like 
+Since $G_{\breve{y}}$ is smaller, exact methods or good approximative methods like 
 multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
@@
 The choice of the proposal defines the shape of the inner polytope. 
-In the given toy example, the first (red) polytope give a huge improvement, the second proposal
+In the given toy example, the first (red) polytope gives a huge improvement, the second proposal
 defines the blue polytope which does not lead to an improvement. 
@@
 We use the publicly available code\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
-While this implementation uses full adjacency matrices it does not scale as well and can not be applied on all datasets.
+As this implementation uses full adjacency matrices it does not scale as well and can not be applied on all datasets.
 We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
@@
 When using the  publicly available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal~\cite{kappes_2013_arxiv}, we have realize that their implementation has some limitations on large problems.
+of Kappes~\etal~\cite{kappes_2013_arxiv}, we have noticed that their implementation has some limitations on large problems.
 This results in a very slow separation and we make the following modifications.
@@
 The energy of the final solution improves with finer proposals since this increases the search space of the moves.
-The level of noise has to be large enough to generate diverse proposals, but not too large which would lead to proposals with low quality.
+The level of noise has to be large enough to generate diverse proposals, but not too large as this would lead to proposals with low quality.
 As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
@@
    \label{tab:eval}
+   \vspace{-0.1cm}
    \begin{tabular}{llllll}
@@
 \section{Future Work}\label{sec:future}
-In future work we would like to investigate in much larger problem instances
+In future work we would like to investigate much larger problem instances
 and interactive correlation clustering, by enforcing
@@
 Overall, a more specific selection of proposals, maybe conditioned on the current solution,
-should lead better proposals and to faster progress of CC-Fusion.
+should lead to better proposals and to faster progress of CC-Fusion.
 %
@@
 It is orthogonal to previous research, \ie it can be combined with
-correlation clustering solver.
+any correlation clustering solver.
 %
@@
 Our evaluation shows that several CC-Fusion algorithms
-outperform state-of-the-art solvers w.r.t. any time performance 
+outperform state-of-the-art solvers w.r.t. anytime performance 
 with increasing problem size.

### 2014-11-14 paper/evaluation.tex
typos found by paul

@@
 and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
-Anytime plots with no zooming and a detailed evaluation are given in supplementary material. 
+Anytime plots with no zooming and a detailed evaluation are given in the supplementary material. 
 %
@@
 MC-I and MC-R can not be applied to such large problems.
-We belief that with better proposal generators, which are more suited for such network problems,
+We believe that with better proposal generators, which are more suited for such network problems,
 we can improve CCFusion. One candidate for such a generator would be a scalable implementation of the 
@@
 %
-For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even CC-Fusion 
+For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even though CC-Fusion 
 and the used parameters have not been designed and chosen for this type of problem.
@@
 Because  the models are designed to have a high boundary recall (oversegmentation), 
-classical fusion, which return undersegmentations, is best best VOI but worse RI and energy.
+classical fusion, which return undersegmentations, has best VOI but worse RI and energy.
 Proposals generated by EHC seemed to be a bit better than WS-based ones.
@@
 For the \emph{knott-datasets}
-with increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
+CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance with increasing problem size compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
 Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
@@
 For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).
-However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
+However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and are also overall best in terms of energy, VOI, and RI.
 %

### 2014-11-14 paper/inputs/fig_fusion.tex
update 4.1 including figures
typos found by paul

@@
 as defined by Lempitsky \etal~\cite{Lempitsky-2010} 
-$y'$ and $y''$ need to be transfered to the node domain.
+$y'$ and $y''$ need to be transferred to the node domain.
 The mapping from edge labels to node labels is ambiguous and
@@
 Enumerating all labelings for a graph of non trival size
-becomes intractable and choosing one labeling is complexity arbitrary.
+becomes intractable.% and choosing one labeling is completely arbitrary.
 %

### 2014-11-14 paper/introduction-new.tex
typos found by paul

@@
 
-Its value is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights,
+Its merit is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights,
 which allows doing justice to evidence in the data that two nodes or pixels do not wish or do wish to end up in the same cluster or segment, respectively.
@@
 
-In signed social networks, where positive and negative edges encodes friend and foe relationships, respectively,
+In signed social networks, where positive and negative edges encode friend and foe relationships, respectively,
 correlation clustering is a natural way to detect communities~\cite{Chierichetti-2014,Chen-2012}.
-Correlation clustering can also been used to cluster query refinements in web search~\cite{Sadikov-2010}.
+Correlation clustering can also be used to cluster query refinements in web search~\cite{Sadikov-2010}.
 Because social and web-related networks are often huge, heuristic methods, \eg the PIVOT-algorithm~\cite{Ailon-2008},
@@
 While it has a clear mathematical formulation and nice properties,
-correlation clustering suffers on its NP-hardness. 
+correlation clustering suffers from NP-hardness. 
 %
@@
 Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
-For the latter approach column generating methods exits, which work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
+For the latter approach column generating methods exist, which work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
 
@@
 As shown in~\cite{beier_2014_cvpr} only Cut, Glue \& Cut (CGC)
-can deal with large scale problems, but can also suffer on very large auxiliary problems.
+can deal with large scale problems, but can also suffer from very large auxiliary problems.
 
-Outside computer vision greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} have been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
+Outside computer vision, greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} have been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
 The PIVOT Algorithm~\cite{Ailon-2008} iterates over all nodes in random order.
@@
 For many large scale computer vision applications fusion moves lead to good approximations
-with state of the art any time performance~\cite{kappes_2014_ws}.
+with state of the art anytime performance~\cite{kappes_2014_ws}.
 Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} cannot be applied directly for correlation clustering.
-We will show how to overcome this point in Sec.~\ref{sec:cc_fm}.
+We will show how to overcome this problem in Sec.~\ref{sec:cc_fm}.
 
@@
 our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
-We evaluate the proposed methods methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
+We evaluate the proposed methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
 

### 2014-11-14 paper/egpaper_for_review.tex
fixed typos in abtract

@@
 contracted (green edges in Fig.~\ref{fig:hc_alg}).
-Doing so, parallel edges edges can occur.
+Doing so, parallel edges can occur.
 In agglomerative clustering, weights of
@@
 
-Because we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interested in an 
-agglomeration with respect to our energy function~\ref{eq:edgeproblem}.
-For this we propose to use energy based agglomeration
+Because we, contrary to~\cite{arbelaez_2006}, directly work on energies, we use energy based agglomeration
 with the following update rule:
@@
 
-Given the intrinsic greediness of hierarchical clustering, 
-EHC is sensitive against noise and we cannot expect optimal solutions.
+Given the intrinsic greediness of hierarchical clustering, we cannot expect
+EHC to yield optimal solutions in general.
 
@@
 As shown in Sec.~\ref{sec:exp},
-allowing CGC to start from the EHC solution
+allowing CGC to start from the EHC solution instead
 can improve performance drastically.
@@
 However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
-into a correlation clustering problem on a coarser graph, where all nodes which are connected
-via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
+into a correlation clustering problem on a coarsened graph, where all nodes which are connected
+via must-link constraints are merged into single nodes. We call this graph a \emph{contracted graph}.
 %
@@
 
-A proposal has a high quality if it at least in some regions has a low energy.
+A proposal has a high quality if  it has a low energy at least in some regions.
 For high quality proposals the chance that the inner polytope includes a
@@
 inner polytopes a large part of the original polytope and find 
-more likely the global optimal solution or escape from local minima.
+more likely the globally optimal solution or escape from local minima.
 
@@
 %
-In the extreme case, where each 
+In one extreme case, where each 
 node is in a separate connnected component,
@@
 
-\noindent \textbf{Randomized HierarchicalClustering (RHC):}
+\noindent \textbf{Randomized Hierarchical Clustering (RHC):}
 %\subsubsection{Randomized HierarchicalClustering (RHC)}
@@
 To get proposals of the desired \emph{size}, we use a
-different stop condition as in EHC, and stop iff a certain number of connected
+different stop condition as in EHC, and stop only if a certain number of connected
 components is reached.

### 2014-11-14 paper/introduction-new.tex
fixed typos in abtract

@@
 \section{Introduction}
-Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
+Correlation clustering~\cite{Bansal-2002}, also known as the multicut problem~\cite{chopra_1993_mp} 
 is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
@@
 
-Its merit is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights,
-which allows doing justice to evidence in the data that two nodes or pixels do not wish or do wish to end up in the same cluster or segment, respectively.
+Its merit is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights.
+This allows doing justice to evidence in the data that two nodes or pixels do not wish or do wish to end up in the same cluster or segment, respectively.
 Secondly, it does not require a specification of the number of clusters beforehand.
@@
 \noindent \textbf{Contribution.}
-In this work we present some novel approaches that are designed for large scale correlation clustering problems.
+In this work we present novel approaches that are designed for large scale correlation clustering problems.
 First, we define a novel energy based agglomerative clustering algorithm that monotonically increases the energy.
@@
 used in supervised segmentation to the unsupervised case and give a polyhedral interpretation of this algorithm.
-We propose two versatile proposal generators, and evaluate the proposed methods on existing and new benchmark problems.
+Finally, we propose two versatile proposal generators, and evaluate the proposed methods on existing and new benchmark problems.
 Experiments show that we can improve the computation time by one to two magnitudes without worsening the segmentation 
@@
 \noindent \textbf{Related Work.}
-A natural approach is to solve the integer linear program (ILP) directly. 
+A natural approach is to solve the integer linear program (ILP) directly~\ref{eq:edgeproblem}. 
 To this end, efficient separation procedures have been found~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
@@
 Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
-For the latter approach column generating methods exist, which work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.
+For the latter approach column generating methods exist, which work best on planar graphs~\cite{yarkony_2012_eccv}. %or almost planar \cite{yarkony-andres-2013} graphs.
 

### 2014-11-14 paper/egpaper_for_review.tex
fixed stuff

@@
 %
-By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy w.r.t. the proposal
+By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy w.r.t. the proposals
 $y'$ and $y''$,
@@
 has no sound stopping condition.
-For the latter we use a maximal number of iterations and maximal number of iteration without improvement as stopping condition.
+For the latter we use a maximal number of iterations and maximal number of iterations without improvement.
 
@@
 Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
-and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
-When optimizing over the green polytope we find $y_2$ which we will never leave again or any polytope containing~$y_2$. 
+and find $y_1$ as optimum. When optimizing over the blue polytope we stay in $y_1$ as optimum,
+when optimizing over the green polytope we find $y_2$ which we will never leave again. 
 }
@@
 As discussed in~\cite{Lempitsky-2010}, proposals
-should have two properties: \emph{quality} 
-and \emph{diversity}.
+should have two properties: \emph{high quality} 
+and \emph{large diversity}.
 
@@
 To get proposals of the desired \emph{size}, we use a
-different stop condition as in EHC, and stop only if a certain number of connected
+different stop condition for EHC, and stop only if a certain number of connected
 components is reached.
@@
 The edge weighted watershed algorithm~\cite{meyer_2013}
-with random seeds can be used to get
+with random seeds can be used to find
 cheap proposals.
@@
 %
-We draw $n/2$ negative edges, and assign different seed to the endpoints
+We draw $n/2$ negative edges, and assign different seeds to the endpoints
 of each edge.

### 2014-11-14 paper/egpaper_for_review.tex
fixed stuff

@@
 Each inner polytope includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
-and find $y_1$ as optimum. When optimizing over the blue polytope we stay in $y_1$ as optimum,
+and find $y_1$ as optimum. Finally, when optimizing over the blue polytope we stay in $y_1$ as optimum,
 when optimizing over the green polytope we find $y_2$ which we will never leave again. 

### 2014-11-14 paper/inputs/fig_hc_alg.tex
proofs
fixed stuff

@@
 \begin{center}
-\begin{figure}
+\begin{figure}[t]
 \begin{center}
@@
 \caption{
-    Hierarchical clustering can be used to optimize
+    Energy-based Hierarchical clustering can be used to greedily optimize
     Eq.~\ref{eq:edgeproblem}.
@@
     the highest weight are merged by contracting this edge.
-    (to be contracted edge is shown in green).
-    Due to edge contraction parallel edges can occur which 
+    (edge to be contracted is shown in green).
+    Due to edge contraction parallel edges can occur, which 
     are merged into single ones, and their weights are summed up.
-    The algorithm stops when the highest edge weight is smaller
+    The algorithm terminates when the highest edge weight is smaller
     or equal to zero (edge shown in blue).

### 2014-11-14 paper/introduction-new.tex
fixed stuff

@@
 \noindent \textbf{Outline:} 
-In Sec.~\ref{sec:problem_formulation} we will give a 
+In Sec.~\ref{sec:problem_formulation} we give a 
 detailed problem definition and introduce 
@@
 be merged, whereas a negative weight indicates
-that these nodes should be separated into two different regions.
+that these nodes should be separated into two distinct regions.
 %
@@
 %
-By $l(y)$ we denote a node labeling for a segmentation given by $y$.
+By $l(y)$ we denote some node labeling for a segmentation given by $y$.
 
@@
 \begin{align}
-  l^* &= \argmin_{L \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
+  l^* &= \argmin_{l \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
 \end{align} 
@@
 As shown in~\cite{kappes_2013_arxiv}  both problems are equivalent, but formulation \ref{eq:nodeproblem}
-suffers from ambiguities in the formulation, \cf Fig.~\ref{fig:notation}.
+suffers from ambiguities in the representation, \cf Fig.~\ref{fig:notation}.
 

### 2014-11-14 paper/datasets.tex
fixed stuff

@@
 We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
-Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
+Both networks are given by weighted directed graphs with edge weights $-1$ and $+1$. 
 %
@@
 % 
-To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact on the overall network, by enforcing.
+To compensate the large impact of nodes with high degree we can normalize the edge weights such that each person has the same impact on the overall network, by enforcing.
 \begin{align}
@@
 For 2D images from the Berkeley Segmentation Database~\cite{martin_2001}, we took the segmentation problems called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
-For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
+For 3D volume segmentation we use the models \emph{knott-3d-150}, \emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
 instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underlying cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.

### 2014-11-14 paper/egpaper_for_review.tex
fixed stuff

@@
 %
-For \textbf{CGC}~\cite{beier_2014_cvpr} we used the publicly available implementation\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}} and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
-For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we use a modified version of
- the publicly available implementation in OpenGM\footref{opengm-master}, as described in Sec.~\ref{sec:tunedMC}.
+For \textbf{CGC}~\cite{beier_2014_cvpr} we used a branch of OpenGM\footnote{\label{opengm-cvpr2014}{\url{github.com/opengm/opengm/tree/cgc-cvpr2014}}} and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{github.com/opengm/opengm}}.
+For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we modified OpenGM\footref{opengm-master}, as described in Sec.~\ref{sec:tunedMC}.
 %
@@
 %
-From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
-We use the publicly available code\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
-As this implementation uses full adjacency matrices it does not scale as well and can not be applied on all datasets.
+From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
+This implementation uses full adjacency matrices it does not scale and cannot be applied to all datasets.
 We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
 %
-As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies than PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
+According to~\cite{beier_2014_cvpr}, CGC is faster and gives better energies than PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
 Therefore we exclude those in our experiments.
 
-We compare these methods to the following methods suggested in the present paper.
+We compare all of the above to the following methods suggested in the present paper:
 %
-Energy Based Based Hierarchical Clustering (\textbf{EHC}),
+Energy Based Hierarchical Clustering (\textbf{EHC}),
 as described in Sec.~\ref{sec:ehc}.
 %
-CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
+CGC warm started with the solution from EHC (\textbf{EHC-CGC}).
 %
 The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
- and MC-I and CGC as subproblem solvers denoted by 
+ and MC-I and CGC as subproblem solvers ( 
 \textbf{CC-Fusion-HC-MC},
@@
 \textbf{-WS-MC}, and 
-\textbf{-WS-CGC}, respectively.
-We set the size of the proposals to $10\%$ of the original problem size
+\textbf{-WS-CGC}) respectively.
+We set the number of connected components in the proposals to  $10\%$ of the 
+number of nodes of
 and use random edge noise with $\sigma=1.5$.
@@
 In our evaluation we make no use of multiple threads.
-The methods were stopped if they exceed 30 minutes at the next possible interrupt point.
+The methods were stopped once they exceed 30 minutes at the next possible interrupt point.
 
@@
 \subsection{Improvements for the Multicut Algorithm}\label{sec:tunedMC} 
-When using the  publicly available implementation in OpenGM\footref{opengm-master}
-of Kappes~\etal~\cite{kappes_2013_arxiv}, we have noticed that their implementation has some limitations on large problems.
+When using the  publicly available implementation in OpenGM\footref{opengm-master}, we have noticed that their implementation has some limitations on large problems.
 This results in a very slow separation and we make the following modifications.
-Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
-Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
+Firstly, we used \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm,
+which speeds up MC-R.
+Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal,instead of searching for the shortest non-chordal path
 during the separation procedure. 
-In~\cite{kroeger_2012_eccv} this has been used for MC-I only. 
+In~\cite{kroeger_2012_eccv} this was used for MC-I only. 
 For MC-R this search procedure is not sufficient and needs to be followed by a search for shortest non-chordal paths.
@@
 \subsection{Parameter Choice for CC-Fusion}
-Beside the choice of the proposal generator and fusion method CC-Fusion has some more parameters, which need to be set.
+Beside the choice of the proposal generator and fusion method, CC-Fusion has some more parameters, which need to be set.
 The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is used to generate diversity.
@@
 \fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
-\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
+\caption{Empirical evaluation of the impact of noise used for proposal generation and the size of the proposals.
   Proposals with many segments cause longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
@@
 %
-Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
-If those build a closed surface, the problem decomposes into two independent problems.
+%Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
+%If those build a closed surface, the problem decomposes into two independent problems.
 %

### 2014-11-14 paper/evaluation.tex
fixed stuff

@@
 Only CGC and HC-CGC are able to find better solutions after more than 1000 seconds.
-MC-I and MC-R can not be applied to such large problems.
+MC-I and MC-R cannot be applied to such large problems.
 We believe that with better proposal generators, which are more suited for such network problems,
@@
 %
-For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even though CC-Fusion 
+For \emph{modularity-clustering} CC-Fusion performs on par with competitive methods, even though CC-Fusion 
 and the used parameters have not been designed and chosen for this type of problem.
-Especially it does a better job than MC-I.
+In particular, it does a better job than MC-I.
 %
@@
 Because  the models are designed to have a high boundary recall (oversegmentation), 
-classical fusion, which return undersegmentations, has best VOI but worse RI and energy.
-Proposals generated by EHC seemed to be a bit better than WS-based ones.
+classical fusion, which returns undersegmentations, has best VOI but worse RI and energy.
+Proposals generated by EHC are a bit better than WS-based ones.
 %
@@
 Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
-The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
+The initialization of CGC by HC, denoted by HC-CGC, also improves the performance compared to native CGC.
 For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).

### 2015-01-19 rebuttal.txt
add rebuttal

We thank all reviews for their constructive comments.

All reviewers mention the
 * clear presentation
 * Detailed experiments
 * improves state-of-the-art

---
**R1: Analogues of the proposed EHC in the literature?**
???

**R1: Misses important prior work outside computer vision (multi-level graph partitioning algorithm)**
As stated by Buluc et al it is assumed that edge weights are positive and a volume constrained are used. 
The METIS software can not applied on our graphs with include positive and _negative_ weighted edges.

From the algorithmic view our proposed method is different to multi-level graph partitioning. 
We refine the graph with respect to the current labeling and solve the problem on the finer graph and not on a coarser (In Fig 5 (c) is finer than (a)).

**Remarks:**
We will improve the readability of the figures  
---

**R2: The proposed method is rather straightforward**
We belief that this is a clear pro of our method and not a con. Important is its novelty.

**R2: The proposed fusion move's convergence is sometimes worse than the CGC**
For the social nets we belief that our proposal generator is not a good choice and parameters can be tuned. But even whit this default it works fine.

**R2: Proposal generation algorithms themselves are not validated**
Due to lack of space we skipped this. However, (E)HC is compared in Fig. 9. One can see that proposals are not globally meaningful.

**R2: The effect of the proposed third criterion "size" **
See Fig. 8. If the size is to large the subproblems become intractable.

**R2: Generated proposals not divergent**
Empirically we observe that the proposals are divergent. 
Of cause that requires that the signal to noise ratio is not to small.

**R2: parameter selection for the proposal generation is verified with only a single instance**
We never claim that we have found the optimal parameter. We expect that we can improve the results by tuning the parameters what we have _not_ done.

**R2: Theorem 1 and eq. 5**
R2 is right it is "for any y" and "\breve{y}=y". We will make this more clear.
While this looks obvious on first glance it isn't on the second. 
We feel that its important to proof this.

**R2: no theoretical guarantee**
Theorem 1 and Sec 4.2 give some theoretical interpretation, e.g. that the method is not energy increasing.
Since there is no free lunch we have to give up the lower bound for faster speed.
---

**R3: Will the implementation become available if paper is accepted?**
We will our implementation public available if paper is accepted. 
Beyond the theoretical contribution in includes several implementation issues which we could not discuss to lack of space.

### 2015-03-12 paper/introduction-new.tex
added technical_report

@@
 Correlation clustering~\cite{Bansal-2002}, also known as the multicut problem~\cite{chopra_1993_mp} 
-is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}.
+is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Arasu-2009,Sadikov-2010,Chen-2012,Chierichetti-2014}.
 See Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.
@@
 In signed social networks, where positive and negative edges encode friend and foe relationships, respectively,
-correlation clustering is a natural way to detect communities~\cite{Chierichetti-2014,Chen-2012}.
+correlation clustering is a natural way to detect communities~\cite{Chen-2012,Chierichetti-2014}.
 Correlation clustering can also be used to cluster query refinements in web search~\cite{Sadikov-2010}.
@@
 Another line of work uses move making algorithms 
-to optimize correlation clustering~\cite{bagon_2011_arxiv,beier_2014_cvpr,Kernighan-1970}.
+to optimize correlation clustering~\cite{Kernighan-1970,bagon_2011_arxiv,beier_2014_cvpr}.
 Starting with an initial segmentation, auxiliary max-cut problems are (approximately) solved,

### 2015-03-12 paper/technical_report.tex
added technical_report

--- 2014-11-14 paper/egpaper_for_review.tex
@@
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{1881} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Thorsten Beier\\
+%Institution1\\
+%Institution1 address\\
+{\tt\small thorsten.beier@iwr.uni-heidelberg.de}
 % For a paper whose authors are all at the same institution,
@@
 \and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+Fred A. Hamprecht\\
+%Institution2\\
+%First line of institution2 address\\
+{\tt\small fred.hamprecht@iwr.uni-heidelberg.de}
+\and
+J\"org H. Kappes \\
+%Institution2\\
+%First line of institution2 address\\
+{\tt\small kappes@math.uni-heidelberg.de}
 }
@@
 \section{Energy Based Hierarchical Clustering}\label{sec:ehc}
+We now describe a fast heuristic for solving Eq.~\ref{eq:edgeproblem}
+which will be used later as a subroutine.
 Agglomerative hierarchical clustering (HC) is widely used
@@
 parallel edges are merged into single edges.
-For image segmentation, the length
-weighted mean is used to do this update~\cite{arbelaez_2006}.
+For image segmentation, the weighted mean of the edge weights is used~\cite{arbelaez_2006}.
 
@@
 Given two proposal solutions $y'$ and $y''$,
-$\mathcal{E}_0^{\breve{y}}$ is the set of edges
+$E_0^{\breve{y}}$ is the set of edges
 which are uncut in $y'$ and $y''$.
@@
 \breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
-\mathcal{E}_0^{\breve{y}}  & =  \{ ij \in E \; | \; \breve{y}_{ij} = 0 \}
+E_0^{\breve{y}}  & =  \{ ij \in E \; | \; \breve{y}_{ij} = 0 \}
 \end{align}
@@
 The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
-with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0^{\breve{y}}$.
+with additional \emph{must-link constraints} for all edges in $E_0^{\breve{y}}$.
 %
@@
   y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
-      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0^{\breve{y}} \nonumber
+      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in E_0^{\breve{y}} \nonumber
 \end{align}
@@
 
-As classical fusion, CC-Fusion does not provide a lower bound on the objective and 
+As classical fusion, the proposed algorithm does not provide a lower bound on the objective and 
 has no sound stopping condition.
@@
 $\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
-Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
+Since $y_e'$ and $y_e''$ are $0$ for all $e \in E_0^{\breve{y}}$ we would have
 \begin{align*}
   \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
- &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
+ &= \sum_{e\in E \setminus E_0^{\breve{y}}} w_ey_e'          
   = \sum_{e\in E} w_ey_e' \\
  &> \sum_{e\in E} w_ey_e''
-  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
+  = \sum_{e\in E \setminus E_0^{\breve{y}}} w_ey_e''
   =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}

### 2015-03-17 paper/datasets.tex
added joergs newest bibtex ref

@@
 \textbf{Network Modularity Clustering.}
-As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
+As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes-2015-ijcv} which are small but fully connected.
 
@@
 
-We use the publicly available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
+We use the publicly available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes-2015-ijcv}.
 For 2D images from the Berkeley Segmentation Database~\cite{martin_2001}, we took the segmentation problems called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
-For 3D volume segmentation we use the models \emph{knott-3d-150}, \emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
+For 3D volume segmentation we use the models \emph{knott-3d-150}, \emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes-2015-ijcv} as well as the large
 instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underlying cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.

### 2015-04-06 paper/cvpr15_abstract_mine.tex
added extended abstract

--- 2015-03-12 paper/introduction-new.tex
@@
-%!TEX root = ./egpaper_for_review.tex
+% Use class option [extendedabs] to prepare the 1-page extended abstract.
+\documentclass[extendedabs]{bmvc2k}
+\usepackage[colorlinks = true,
+            linkcolor = blue,
+            urlcolor  = blue,
+            citecolor = blue,
+            anchorcolor = blue]{hyperref}
+
+% Document starts here
+\begin{document}
+
+\title{Fusion Moves for Correlation Clustering}
+\addauthor{
+Thorsten Beier$^1$, 
+Fred A. Hamprecht$^2$
+J\"org H. Kappes$^3$
+}{}{1}
+\addinstitution{
+$^1$thorsten.beier@iwr.uni-heidelberg.de 
+$^2$fred.hamprecht@iwr.uni-heidelberg.de
+$^3$kappes@math.uni-heidelberg.de
+}
+
+\maketitle
+\let\thefootnote\relax\footnote{This is an extended abstract. The full paper is available at the \href{http://www.cv-foundation.org/openaccess/CVPR2015.py}{Computer Vision Foundation webpage}. }
+\vspace{-0.2in}
+
+% Extended abstract begins here.  In a one-page document, there is
+% little need for section headers, but you may use \section etc if you
+% wish.
+
+\noindent
+Correlation clustering, or multicut partitioning,
+is widely used in image segmentation for
+partitioning an undirected graph or image with positive and negative edge weights 
+such that the sum of cut edge weights is minimized.
 %
-\section{Introduction}
+Due to its NP-hardness, exact solvers do not scale and approximative solvers often give unsatisfactory results.
+We investigate scalable methods for correlation clustering.
+To this end we define fusion moves for the correlation clustering problem.
+
+Our algorithm iteratively fuses the current and a proposed partitioning which 
+monotonously improves
+the partitioning and maintains a valid partitioning at all times.
+Furthermore, it scales to larger datasets, gives near optimal solutions, and at the same time shows
+a good anytime performance.
+
 Correlation clustering~\cite{Bansal-2002}, also known as the multicut problem~\cite{chopra_1993_mp} 
 is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Arasu-2009,Sadikov-2010,Chen-2012,Chierichetti-2014}.
-See Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.
+%See Sec.~\ref{sec:problem_formulation} for its formal definition of clustering the nodes of a graph.
 
@@
 
-% Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment.
-This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster.
-Secondly, the algorithm does not require a specification of the number of clusters.
-This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.
-
-% \paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers.
-The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings.
-Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted.
-Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph.
-We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.
-We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks.
-The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.
 \vspace{0.1cm}
@@
 
-\vspace{0.1cm}
-\noindent \textbf{Related Work.}
-A natural approach is to solve the integer linear program (ILP) directly~\ref{eq:edgeproblem}. 
-To this end, efficient separation procedures have been found~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
-Alternatively, it is possible to relax the integrality constraints of the ILP formulation~\cite{kappes_2013_arxiv}. 
-Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
-For the latter approach column generating methods exist, which work best on planar graphs~\cite{yarkony_2012_eccv}. %or almost planar \cite{yarkony-andres-2013} graphs.
+\bibliography{egbib}
 
-Another line of work uses move making algorithms 
-to optimize correlation clustering~\cite{Kernighan-1970,bagon_2011_arxiv,beier_2014_cvpr}.
-Starting with an initial segmentation, auxiliary max-cut problems are (approximately) solved,
-such that the segmentation is strictly improved.
-As shown in~\cite{beier_2014_cvpr} only Cut, Glue \& Cut (CGC)
-can deal with large scale problems, but can also suffer from very large auxiliary problems.
-
-Outside computer vision, greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} have been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
-The PIVOT Algorithm~\cite{Ailon-2008} iterates over all nodes in random order.
-If the node is not assigned it constructs a cluster containing the node and all its 
-unassigned positively linked neighbors.  
-%
-A widely used post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigns nodes to clusters.
-
-For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
-For many large scale computer vision applications fusion moves lead to good approximations
-with state of the art anytime performance~\cite{kappes_2014_ws}.
-Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} cannot be applied directly for correlation clustering.
-We will show how to overcome this problem in Sec.~\ref{sec:cc_fm}.
-
-\vspace{0.1cm}
-\noindent \textbf{Outline:} 
-In Sec.~\ref{sec:problem_formulation} we give a 
-detailed problem definition and introduce 
-the correlation clustering objective.
-Next we give a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
-our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
-We evaluate the proposed methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
-
-%-------------------------------------------------------------------------
-
-\input{inputs/fig_notation.tex}
-\section{Notation and Problem Formulation}\label{sec:problem_formulation}
-Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
-%
-The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
-We will use $w_e$ as a shorthand for $w(e)$.
-A positive weight expresses the desire that two adjacent nodes should
-be merged, whereas a negative weight indicates
-that these nodes should be separated into two distinct regions.
-%
-%A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
-%of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
-%
-%\input{inputs/fig_notation.tex}
-A segmentation of the graph $G$ can be either given by a
-node labeling $l \in \mathbb{N}^{|V|}$
-or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation}.
-An edge labeling is only consistent if it does not violate any cycle constraint~\cite{kappes_2013_arxiv}.
-We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
-The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.
-%
-By $l(y)$ we denote some node labeling for a segmentation given by $y$.
-
-Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
-of the edges between distinct segments is minimized. This can be formulated in the node domain
-by assigning each node $i$ a label $l_i \in \mathbb{N}$
-\begin{align}
-  l^* &= \argmin_{l \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
-\end{align} 
-or in the edge domain, by labeling each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
-\begin{align}
-  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}.%\\ 
-\end{align}
-As shown in~\cite{kappes_2013_arxiv}  both problems are equivalent, but formulation \ref{eq:nodeproblem}
-suffers from ambiguities in the representation, \cf Fig.~\ref{fig:notation}.
-
-%\input{inputs/fig_notation.tex}
+\end{document}

### 2015-05-26 paper/poster.tex
added inital poster

\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
\usepackage{grffile}
\mode<presentation>{\usetheme{I6pd2}}{
% \usetheme{Berlin}
\usetheme{Dreuw}
}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{amsmath,amsthm, amssymb, latexsym}
%\usepackage{times}\usefonttheme{professionalfonts}  % obsolete
%\usefonttheme[onlymath]{serif}
\boldmath
\usepackage[orientation=portrait,size=a0,scale=1.4,debug]{beamerposter}

\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}

% change list indention level
% \setdefaultleftmargin{3em}{}{}{}{}{}

%\usepackage{snapshot} % will write a .dep file with all dependencies, allows for easy bundling

\usepackage{array,booktabs,tabularx}
\newcolumntype{Z}{>{\centering\arraybackslash}X} % centered tabularx columns
\newcommand{\pphantom}{\textcolor{ta3aluminium}} % phantom introduces a vertical space in p formatted table columns??!!

\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{figures/}}

\title{\huge Fusion Moves for Correlation Clustering}
\author{Thorsten Beier, Fred A. Hamprecht and J\"org H. Kappes }
\institute[RWTH Aachen University]{Heidelberg Collaboratory for Image Processing, University of Heidelberg, Germany}
\date[\today]{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength{\columnheight}
\setlength{\columnheight}{105cm}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}
  \begin{columns}
    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.49\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth}  % tweaks the width, makes a new \textwidth
          \parbox[t][\columnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content            
            \begin{block}{Introduction}

            Correlation clustering~\cite{Bansal-2002}, or multicut partitioning~\cite{chopra_1993_mp} ,
            is widely used partitioning an undirected graph with positive and negative edge weights
            ~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad}.
            Since it is NP-hard, exact solvers do not scale and approximative solvers often give bad results.
            Inspired by \cite{Lempitsky-2010} Here we define fusion moves for the correlation clustering problem.
            Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
            the partitioning and maintains a valid partitioning at all times.
            Furthermore, it scales to larger datasets, gives near optimal solutions, and at the same time shows
            a good anytime performance.

            \end{block}
            \vfill
            \begin{block}{Correlation Clustering / Multicut Objective:}

            Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
            of the edges between distinct segments is minimized. This can be formulated in the node domain
            by assigning each node $i$ a label $l_i \in \mathbb{N}$
            \begin{align}
              l^* &= \argmin_{l \in \mathbb{N}^{|V|}} \sum_{ (i,j) \in E } w_{ij} \cdot [l_{i} \neq l_{j}], \label{eq:nodeproblem}
            \end{align} 
            or in the edge domain, by labeling each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
            \begin{align}
              y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:edgeproblem}.%\\ 
            \end{align}
            \centering
            \includegraphics[width=0.9\linewidth]{ne-crop.pdf}

            \end{block}

            \vfill
            \begin{block}{Correlation Clustering Fusion Moves}

              Given two proposal solutions $y'$ and $y''$,
              $E_0^{\breve{y}}$ is the set of edges
              which are uncut in $y'$ and $y''$.
              %
              \begin{align}
              \breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
              E_0^{\breve{y}}  & =  \{ ij \in E \; | \; \breve{y}_{ij} = 0 \}
              \end{align}
              %
              The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
              with additional \emph{must-link constraints} for all edges in $E_0^{\breve{y}}$.
              %
              \begin{align}
                y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
                    &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in E_0^{\breve{y}} \nonumber
              \end{align}
              %

              We can reformulate~\ref{eq:fusion_move_a}
              into a correlation clustering problem on a coarsened graph, where all nodes which are connected
              via must-link constraints are merged into single nodes. We call this graph a \emph{contracted graph}.

              Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ of the original graph $G=(V,E)$

              \vfill
              \vspace{2cm}
              \centering
              \includegraphics[width=1.0\linewidth]{si-crop.pdf}

            \end{block}
            \vfill

          }
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column

    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.49\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
          \parbox[t][\columnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content

            \begin{block}{Results}
            Among all proposed solvers, Fusion-HC-MC has the best overall anytime performance. With increasing problems
            size (9b-9e and 9f) the runtimes of MC-I, MC-R and CGC increase drastically, while the proposed solvers still scale well.

            \includegraphics[width=0.9\linewidth]{res_images.pdf}

            \end{block}
            \vfill
            \begin{block}{Evaluation by Variation of Information (VI) and Rand Index (RI)}
              \centering
              \includegraphics[width=0.8\linewidth]{virib.pdf}            
            \end{block}
            \vfill
            % \begin{block}{Conclusions}
            %     We have presented a fast and scalable 
            %     approximate solver for correlation 
            %     clustering, named Correlation Clustering Fusion (CC-Fusion).
            %     It is orthogonal to previous research, \ie it can be combined with
            %     any correlation clustering solver.
            %     %
            %     The best solution is iteratively improved 
            %     by a fusion with proposal solutions.
            %     The fusion move itself is formulated as correlation
            %     clustering on a smaller graph with fewer edges and nodes
            %     and can therefore be solved much faster than the original problem.
            %     %
            %     Our evaluation shows that several CC-Fusion algorithms
            %     outperform state-of-the-art solvers w.r.t. anytime performance 
            %     with increasing problem size.
            % \end{block}
            \vfill
            \begin{block}{References}
                \small
                \bibliographystyle{ieee}
                \bibliography{egbib}
            \end{block}
            \vfill
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vskip1ex
  %\tiny\hfill\textcolor{ta2gray}{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php}}
  %\tiny\hfill{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php} \hskip1em}
\end{frame}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Local Variables: 
%%% mode: latex
%%% TeX-PDF-mode: t
%%% End:

### 2015-05-26 paper/poster.tex
added inital poster

@@
             Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
-            the partitioning and maintains a valid partitioning at all times.
-            Furthermore, it scales to larger datasets, gives near optimal solutions, and at the same time shows
+            the partitioning. It scales well gives near optimal solutions, and has
             a good anytime performance.
@@
             \vfill
+            \begin{block}{Proposal Generators}
+
+            As discussed in~\cite{Lempitsky-2010}, proposals
+            should have two properties: \emph{high quality} 
+            and \emph{large diversity}.
+            For correlation clustering fusion we add a third
+            property: \emph{size}.
+            We use the following two proposal generators (see paper for details):
+            \begin{itemize}
+                \item \textbf{Randomized Hierarchical Clustering (RHC):}
+                we add normally distributed noise  $\mathcal{N}(0, \sigma_{ehc})$ to each edge weight.
+                In each step the edge with the highest weight is contracted.
+
+                \item \textbf{Randomized Watersheds (RWS):}
+                The edge weighted watershed algorithm~\cite{meyer_2013}
+                with random seeds can be used to find
+                cheap proposals.
+            \end{itemize}
+
+            \end{block}
 
@@
             \begin{block}{Results}
-            Among all proposed solvers, Fusion-HC-MC has the best overall anytime performance. With increasing problems
-            size (9b-9e and 9f) the runtimes of MC-I, MC-R and CGC increase drastically, while the proposed solvers still scale well.
-
+            Among all proposed solvers, Fusion-HC-MC has the best overall anytime performance.
             \includegraphics[width=0.9\linewidth]{res_images.pdf}
@@
               \centering
-              \includegraphics[width=0.8\linewidth]{virib.pdf}            
+              \includegraphics[width=0.7\linewidth]{virib.pdf}            
             \end{block}
@@
             \begin{block}{References}
-                \small
+                \footnotesize
                 \bibliographystyle{ieee}

### 2015-05-26 paper/poster.tex
added inital poster

@@
 
+\usepackage{multicol}
 \usepackage{tikz,pgfplots}
@@
 \begin{document}
+\setbeamertemplate{bibliography item}{[\theenumiv]}
 \begin{frame}
@@
 
-            Correlation clustering~\cite{Bansal-2002}, or multicut partitioning~\cite{chopra_1993_mp} ,
+            \small  
+            \begin{itemize}
+                \item  Correlation clustering~\cite{Bansal-2002}, or multicut partitioning~\cite{chopra_1993_mp} ,
                 is widely used partitioning an undirected graph with positive and negative edge weights
                 ~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad}. 
-            Since it is NP-hard, exact solvers do not scale and approximative solvers often give bad results.
-            Inspired by \cite{Lempitsky-2010} Here we define fusion moves for the correlation clustering problem.
-            Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
-            the partitioning. It scales well gives near optimal solutions, and has
-            a good anytime performance.
+                \item NP-hard,  exact solvers do not scale and approximative solvers often give bad results.
+                \item Inspired by \cite{Lempitsky-2010} we define fusion moves for the correlation clustering
+                where we iteratively fuses the current and a proposed partitioning and monotonously improve the partitioning
+                \item Scales well, gives near optimal solutions, has good anytime performance
+            \end{itemize}
+
+            % Correlation clustering~\cite{Bansal-2002}, or multicut partitioning~\cite{chopra_1993_mp} ,
+            % is widely used partitioning an undirected graph with positive and negative edge weights
+            % ~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad}.
+            % Since it is NP-hard, exact solvers do not scale and approximative solvers often give bad results.
+            % Inspired by \cite{Lempitsky-2010} Here we define fusion moves for the correlation clustering problem.
+            % Our algorithm iteratively fuses the current and a proposed partitioning which  monotonously improves
+            % the partitioning. It scales well gives near optimal solutions, and has
+            % a good anytime performance.
 
@@
             \begin{block}{Correlation Clustering / Multicut Objective:}
-
-            Given a weighted graph $G=(V,E,w)$ we consider the problem of segmenting $G$ such that the costs
-            of the edges between distinct segments is minimized. This can be formulated in the node domain
+            \begin{small}
+            \begin{itemize}
+            \item Given a weighted graph $G=(V,E,w)$ 
+            \item We consider the problem of segmenting $G$ such that the costs
+            of the edges between distinct segments is minimized. 
+            \item Can be formulated in the node domain
             by assigning each node $i$ a label $l_i \in \mathbb{N}$
@@
             \end{align} 
-            or in the edge domain, by labeling each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
+            \item Can be formulated in in the edge domain, by labeling each edge $e$ as cut $y_e=1$ or uncut $y_e=0$ 
             \begin{align}
@@
             \end{align}
+            \end{itemize}
             \centering
             \includegraphics[width=0.9\linewidth]{ne-crop.pdf}
+            \end{small}
 
@@
             \begin{block}{Correlation Clustering Fusion Moves}
+              \begin{small}
 
-              Given two proposal solutions $y'$ and $y''$,
-              $E_0^{\breve{y}}$ is the set of edges
+              \begin{itemize}
+
+              \item Given two proposal solutions $y'$ and $y''$, $E_0^{\breve{y}}$ is the set of edges
               which are uncut in $y'$ and $y''$.
@@
               %
-              The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
+              \item The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
               with additional \emph{must-link constraints} for all edges in $E_0^{\breve{y}}$.
@@
 
-              We can reformulate~\ref{eq:fusion_move_a}
+              \item We can reformulate~\ref{eq:fusion_move_a}
               into a correlation clustering problem on a coarsened graph, where all nodes which are connected
@@
 
-              Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ of the original graph $G=(V,E)$
-
+              \item Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ of the original graph $G=(V,E)$
+              \end{itemize}
+              \end{small}
               \vfill
@@
             \begin{block}{Proposal Generators}
-
+            \begin{small}
             As discussed in~\cite{Lempitsky-2010}, proposals
@@
             \end{itemize}
-
+            \end{small}
             \end{block}
@@
             \begin{block}{Results}
+            \small{
             Among all proposed solvers, Fusion-HC-MC has the best overall anytime performance.
+            }
             \includegraphics[width=0.9\linewidth]{res_images.pdf}
@@
             \vfill
-            \begin{block}{Evaluation by Variation of Information (VI) and Rand Index (RI)}
+            \begin{block}{Evaluation by Segmentation Metrics}
+                \small{
+                Evaluation by Variation of Information (VOI) and
+                Rand Index (RI) for datasets with available ground truth:
+                }
+                \vspace{1cm}
+
               \centering
@@
             \vfill
-            % \begin{block}{Conclusions}
+            % \begin{block}{Cofonclusions}
             %     We have presented a fast and scalable 
@@
             \begin{block}{References}
+                \begin{multicols}{2}
                 \footnotesize
@@
                 \bibliography{egbib}
+                \end{multicols}
             \end{block}
